### 2022-03-02 abstract.tex
Initial Overleaf Import

The online world presents new avenues for the spread of information in addition to the traditional word of mouth effects of social networks. It also provides new big data sources for social science research because they are bigger, cheaper, and already available. In my dissertation, I combine these two areas of inquiry by examining the differences between the social network contagion of ideas (push) and information seeking (pull) and their relation to the creation of social norms. My first article tests the construct validity of the Google Search Trends source of big data as an indicator of three different cases, namely cultural attitudes, disease prevalence and voting behavior, using pairwise correlations . My second article establishes how individuals perform information search, whether through interpersonal networks or online, using my original survey data of 900 Adults in the United States. My final article builds on these by investigating how new health-behavior social norms form in the face of assortative signals through associative cognitive diffusion. This research will be a contribution to methodology of computational social science as it tests the reliability of a big data source, questions what behavioral processes lead to macro-level outcomes recorded in big data sources, and uses novel combinations of data sources and methodology to investigate questions of sociological interest. This research will also contribute to the sociology study of information technologies in the digital age, medical sociology, and social networks.

### 2022-03-02 ch1.tex
Initial Overleaf Import

\hypertarget{intro}{%
\chapter{Introduction}\label{intro}}

This dissertation focuses on how people search for information and how
people rely on this information and other cues to inform their
health-behaviors and develop norms. I will investigate the following
questions:

- How can we operationalize Google Search Trends as a valid indicator for uses in social science research?    
- How do computer-mediated or interpersonal information-seeking strategies vary
across populations?
- What factors lead people to perform health information search on the Covid-19 vaccine online versus among social network ties? 
- How are new health behavior norms regarding public health recommendations formed during the Covid-19 pandemic?  
- How are patterns of information-search related to social norm stabilization during the Covid-19 pandemic?

Information is all around us and permeates every facet of human society,
from the hordes of data gathered during the internet age or passing
gossip between friends. Human communication and human society are based
on the circulation of information and knowledge. Information can be
shared by others through information campaigns and consumed by an
individual, called information push, or intentionally sought out by
individuals, called information pull \citep{cybenkoFoundationsInformationPush1999}.

\emph{need to cite \citep{bayer_etal20, bossetta18}}

A critical turning point in the study of the flow information was put forth by renowned Sociologist Paul Lazarsfeld \citeyearpar{lazarsfeldPeopleChoice1944}. Lazarsfeld and others theorized that the media did not directly influence the masses, but that a "Two-Step Flow" was occurring where "opinion leaders" interpreted messages from mass media and then, in turn, promoted their opinions to the masses \citep{katzPersonalInfluencePart1955}. The opinion leaders interpret, explain, and diffuse contents to "opinion followers". From a networks
perspective, "people rarely act on mass-media information unless it is also transmitted thro\citep[p. 1374]{granovetterStrengthWeakTies1973}. Lazarsfeld's first study focused on politics \citeyearpar{lazarsfeldPeopleChoice1944} but follow up studies from \citep{katzPersonalInfluencePart1955} showed that this model matched information flows beyond the political realm. In contrast to the one-step flow, where media directly influences the masses, Lazarsfeld's theory remains in prominence today. While many scholars assumed that
modern micro-targeted marketing strategies would provide evidence for a one-step flow perspective \citep{bennettOneStepFlowCommunication2006}, many scholars find that "opinion leaders" (often influencers and celebrities) still create a two-step flow of information transmission \citep{choi15, hilbertOneStepTwo2017}.

The spread of information has also been studied thoroughly from the
prospective of social networks. Individuals engage with each other and
their distributive ties to create community contexts where norms,
beliefs, and values circulate. Information diffuses through communities
and social networks \citep{fowler2010cooperative, bond_etal12, klarEffectNetworkStructure2017}.
However, "different things spread in different ways and to
different extents" \citep[p. 563]{christakisSocialContagionTheory2013} and information can
spread differently than a virus or behavior. Important studies in the
spread of information through networks include the study of adoption of
innovations by physicians \citep{colemanDiffusionInnovationPhysicians1957}, how new
inventions are adopted from early adopters to laggards \citep{rogersDiffusionInnovations1962},
how weak ties help cohere networks and diffuse information
\citep{granovetterStrengthWeakTies1973}, how social ties spread information about job
opportunities \citep{granovetterGettingJobStudy1995, montgomeryJobSearchNetwork1992}, how information
spreads best when weak and strong ties are balanced (embeddedness) \citep{uzziSocialStructureCompetition1997}, and more recent innovations in the stickiness of complex contagion \citep{centolaComplexContagionsWeakness2007}.

So far, I have only been discussing the way that information is
passively consumed through push efforts by opinion leaders and social
networks. However, sociological literature is really sparse on the
opposite behavior: active directed searching by individuals to obtain
information. \citep{pejtersenDesignComputeraidedUsersystem1984}, a scholar of library and information
science, theorized that there are 5 strategies for searching for
information. The most common strategy is browsing, where people follow
leads based on associations without planning ahead. Another strategy is
analytical, which includes an explicit consideration of all facets of
the question to guide a search. The empirical method guides the search
based on tactics that were successful in past research. The known site
strategy is to go to the direct source of the information if known. And
finally, the similarity method is to find information based on another
similar question that already has an answer. These 5 strategies vary in
their demands for prior knowledge, cognitive processing, memory, and
time spent. While this theory is aimed at finding information in a
library setting, scholars have extended the theory to other fields and
validated the framework \citep{fidelHumanInformationInteraction2012}; the frame is a useful beginning
point for my theories of information search through network activation
or through computer-mediated communication.

Some communication theorists ask why an answer to a question is sought
in the first place. The Theory of Uncertainty Management \citep{brashersCommunicationUncertaintyManagement2001}
professes that people search for information when their uncertainty
around the subject leads to anxiety or other cognitive harms. The Theory
of Motivated Information Management \citep{afifiSeekingInformationSexual2006, afifiTheoryMotivatedInformation2004}
extends the prior by adding that uncertainty itself is not the catalyst
for information-search; rather, it is driven by a discrepancy between
the current level of uncertainty on a subject and desired level of
uncertainty.

One way to find information is to activate network ties to find out
information through a form of social support. Social support, while
previously used interchangeably with the term social networks and social
integration \citep{houseStructuresProcessesSocial1988}, are the emotional,
informational, and instrumental assistance functions performed between
social ties and have strong and measurable association with health
outcomes \citep{houseMeasuresConceptsSocial1985, thoitsMechanismsLinkingSocial2011}. Informational support is
the process of seeking "help in defining, understanding, and coping with
problematic events and include education, advice, or referral to another
source of support" \citep[p. 640]{winemiller_etal93}. Brashers, a health
communications researcher, defines informational support slightly
differently, focusing on the exchange of information that "facilitates
coping with life stresses... that may be exchanged among members of a
support network" \citeyearpar[p. 260]{brashersInformationSeekingAvoiding2002}.
Both of these definitions provide important
lenses for my question of how computer-mediated or interpersonal
information-seeking strategies vary. If information is needed but there
is no search for coping or deeper understanding of important matters,
people are likely to choose to search online.

\subsubsection{Uses and Gratification Theory}

From studies of mass communication, uses and gratifications theory (UGT)
\citep{blumlerUsesMassCommunications1974, tanMassCommunicationTheories1985}
may also lend itself to theorizing why
computer-mediated or interpersonal information-seeking strategies vary.
UGT posits that users are not passive consumers of media and that people
have an active role in choosing different sources of media based on
their satisfaction of specific needs on an individual basis. UGT is
based on Maslow's \citeyearpar{maslowTheoryHumanMotivation1943}
hierarchy of needs and is compatible with
Lazarsfeld and Katz's theory of two-step flow because people can choose
their media and the opinion leaders they follow. Modern-day theorists
have extended UGT theory and classified the uses and gratifications of
the internet and of social media. \citet{staffordDeterminingUsesGratifications2004}
theorize that the internet provides gratification through useful content
that meets expectations, gratification from purposeful navigating or
random browsing as a process, and social gratification from forming and
deepening social ties. \citet{leungGenerationalDifferencesContent2013} theorizes that 
social media is
gratifying for users because it allows for venting of negative feelings,
provides recognition, provides entertainment, promotes social affection,
and fulfills cognitive needs. Adapting UGT to my own purposes, I
theorize that informational support will be activated from network ties
when the informational need is related to forming and deepening social
ties but search will be conducted online when information is needed but
an individual does not have an additional cognitive need to fill through
social interaction. Alternative goals such as identity management or
relational maintenance \citep{brashersInformationSeekingAvoiding2002}
need to be balanced and will determine where search is conducted.

\subsubsection{Social Norms}

One area previously mentioned that motivates information search is to
minimize uncertainty based on the Theory of Motivated Information
Management; this dissertation will also focus on developing new social
norms in situations of uncertainty about how to behave. Minimal research
exists in quickly emerging norms in times of emergency, but shows that
people likely to rely on the behavior of others' to set their own norms
for behavior \citep{alvarez2018, horneNormsIntegratedFramework2020}. This project will investigate how search contributes to the
development of said spontaneous norms.

Social norms form the building blocks of social organization and have
been a focus of sociology since the beginning. In a recent Annual Review
of Sociology piece focused on social norms, Horne and Mollborn define
norms as "group-level evaluations of behavior ... [or] when people
have expectations about how others evaluate behaviors" \citeyearpar[p. 468-69]{horneNormsIntegratedFramework2020}. Durkheim saw that society exerted powerful
forces on individuals and classified people's norms, beliefs, and values
as parts of collective consciousness that provide for societal
integration \citep{durkheimDivisionLaborSociety1933, durkheimSuicide1897}.
Weber, on the other hand,
distinguished social behavior from social action, which was an action a
person takes through subjective understanding and interpretation of
actions of others. % TODO CITE ME

The causes and logics of social norms are debated. The consequentialist
argument for norms focuses merely on the consequence a behavior has on
group members and that norms will be promoted if the behavior benefits
others and denounced if it negatively affects others \citep{ullmannmargalitEmergenceNorms1977}.
 While this theory has been tested and performs well in the lab,
researchers have raised questions regarding its ecological validity
\citep{horneNormsIntegratedFramework2020}. One of the main critiques of the
consequentialist argument is that it relies on the same interpretation
by all parties of what is harmful and beneficial -- a critical question
for the research question in Part 4: Paper 3. The Relational argument % TODO ADD LINK
for norms is based on the value people place on their relationships and
the assumption that people will behave in ways that will garner them
positive social reactions. This argument relies on individuals assuming
what their peers will approve and disapprove of. In turn, norms are
developed when individuals make inferences from their social worlds
\citep{fryeCulturalMeaningsAggregation2017}.

Importantly, people look to others performing an action and often
interpret that performance as an indication that an action is approved,
paying particular attention to high-status individuals and institutions
\citep{robalinoPeerEffectsAdolescent2018, tankardEffectSupremeCourt2017}.

Norms are formed in social networks; "Networks operate in a larger
cultural context that can facilitate or inhibit acceptance of general
cultural norms and beliefs \citep{pescosolidoDurkheimSuicideReligion1989, whiteSocialStructureMultiple1976}. Because of this, people tend to resemble
their network as a form of network autocorrelation and homophily
\citep{dellapostaWhyLiberalsDrink2015}. While "birds of a feather flock
together" in homophily \citep{mcphersonBirdsFeatherHomophily2001},
attitudes and behaviors are shaped by peers, creating filter bubbles of
social influence \citep{dellapostaWhyLiberalsDrink2015}.

\citet{goldbergSocialContagionAssociative2018} argue that the state of the literature on
diffusion and social contagion, discussed above, is erroneous. They
propose an important linkage that had been missed in previous research
of the diffusion of behavior (or, as I interpret it, the creation of new
norms). They argue that what actually diffuses during social contagion
are the perceptions about which beliefs or behaviors are compatible with
one another, what they call "associative diffusion". In times of
behavioral uncertainty, I theorize that individuals strategically look
towards other high-status individuals, institutions, and perform
regimented searches to establish for themselves the behavior that is
compatible with other cognitive biases they hold.

\subsection{Broader Impact}

% from Marshall Foundation

The vaccines against the COVID-19 coronavirus prevent severe illness,
hospitalization, and death. However, as I'm writing this, less than 55%
of Arizonans over 12 years old are fully vaccinated against the virus.
We know that people exposed to misinformation are much less likely to
receive vaccinations against the virus \citep{loombaMeasuringImpactCOVID192021}. It is not
an exaggeration to claim that misinformation has been deadly for Arizona
\citep{pathakInfodemicsCOVID19Role2020}.

misinformation \citep{greene_murphy21}

My research on information search and norm development provides clear
and timely social implications for Arizona and the United States. This
dissertation uncovers how norms are created during periods of norm
uncertainty and builds the foundation to theorize and test interventions
that promote positive norms in times of disasters and uncertainty.
Specifically, I investigate how local diffusion leads to social norms
through information search which will have strong implications for the
prevention of global polarization and the spread of misinformation.

In academia and policy, the main focus is on the information that is
sent to consumers, seeing people as passive receivers of information. My dissertation instead
focuses on individuals as active agents in their search for information
which helps me uncover the information individuals are exposed to. By
looking at how individuals search, I aim to identify pain points and focus areas for
future interventions in the misinformation process.

The information that spread to communities in Arizona led to the health
behaviors exhibited today by Arizonans. While the information spread in
various ways, like through diffusion and polarization, it contributed to
our newly established norms. By uncovering how norms were created during
this time of norm uncertainty, my research will contribute to the recommended interventions to promote effective health-related behavioral norms before politicization and
misinformation occurs. This will create a healthier, happier Arizona

This dissertation researches information search and norm development,
both of which have implications for academic research and communities.

% Original

This research will first and foremost impact sociology. While the spread
of information is investigated in the discipline (diffusion, mass
communication, social influence), it is almost always from a structural
perspective which disregards individual agency and choice in the
acquisition of new information. This perspective aligns with Uses and
Gratifications Theory, discussed in Section B: Background, and sees
people as active agents in their search for information instead of just
passive receivers of information signals.

Taking this agentic perspective is critical in the study of information
diffusion when combined with cognitive perspectives like that of
Goldberg and Stein (2018). How people search for information determines
the information that they find; the information they uncover is filtered
through cognitive biases and predispositions to how they interpret and
act upon the newfound information. Searching for informational support
through social network ties theoretically will uncover potentially
different information than that would be uncovered through online web
search and will change how people are organized and how people behave.

Additionally, this dissertation will investigate how social norms are
formed in situations of uncertainty, an area that is less developed in
sociology. While sociologists have studied social norms since the
formation of the discipline, focus on the quick formation of social
norms has implications for social behavioral outcomes, cultural change,
organizational reactions to unrest and disasters, and many more areas
that influence humanity.

This dissertation will also have implications for the study of social
networks and social support. Not only is this work situated in the
sociological study of social support and social influence, but I utilize
rarely-used-in-sociology sources of big data to better understand these
mechanisms and test existing theories.

This dissertation also contributes to computational social science &
critical big data studies. I base much of my dissertation around Google
Search Trends, which are relatively underutilized in the social sciences
compared to health sciences and business. Not only does this project
introduce Google Search Trends in new ways, but I perform explicit tests
of how this data should be used in the social sciences, providing the
groundwork for this exciting source of big data for future computational
social scientists. Because my research takes a critical big data studies
approach, I take into account the potential pitfalls with any source of
big data (McFarland and McFarland 2015) and attempt to explicitly answer
questions posed by this field, such as "what are the behavioral
processes that lead to macro-level outcomes" proposed by \citet{breigerScaling2015}.

I also make important contributions to social epidemiology through this
research. Each of the three papers in this dissertation use health case
studies for questions of sociological interest. Because of this, I will
contribute to social epidemiological questions on vaccine hesitancy,
health communication, and diffusion of high-risk health behaviors. While
all of these areas are important to social epidemiology, there are
potential important health implications for these contributions on
outside of the academy.

Outside of the academic research impacts that this dissertation makes,
there are clear and timely social implications that will stem from this
work. First, by uncovering how norms are created during norm
uncertainty, I may be able to establish recommendations for
interventions to be applied during disasters and other times of unrest
to promote effective positive norms. Second, my research may have
implications for how to optimize gratifications in search processes to
promote healthy social relationships and improved online algorithm
deployment.

This work also relates to polarization and misinformation, two major
social issues of our time. \citet{axelrodDisseminationCultureModel1997} shows that network structure,
autocorrelation, and diffusion create local convergence of attitudes and
culture which then leads to global polarization \citep{dellapostaWhyLiberalsDrink2015}. In investigating how local diffusion leads to social norms
through information search, some of my findings may have strong
implications and interventions for the prevention of global
polarization. Relatedly, understanding where and how people search for
information has implications for the information they are exposed to and
the norms they develop. This project will attempt to relate to where
misinformation is uncovered and how to intervene in its absorption.

\subsection{Three Empirical Articles}

To make my intended contributions to the literatures on computational
social science, sociological methodology, social norms, social networks,
and diffusion, my dissertation will take the following format:

\subsubsection{Article 1: Construct Validity and Correspondence of Google Trends}
% TODO Double check name
% TODO link to article  
I will first investigate how Google Search Trends can be operationalized
as cultural attitudes, disease prevalence and voting behaviors through
comparing trends data to observed valid indicators of these cases.
Specifically, I will test cultural indicators from the NORC General
Social Survey, United States county-level suicide rates from National
Center for Health Statistics, US case rates of Covid-19 from The New
York Times, historical US Presidential Election results, and the
American National Election Survey against selected Google Trends terms
and analyze the data using correlation methods. The aim of this article
is to assess the construct validity and will contribute to critical big
data studies and sociological methodology.
% TODO ADD IN ARTICLE 1 ABSTRACT

\subsubsection{Article 2: Information-Seeking Behaviors for Information on Covid-19 Vaccinations}
% TODO Double check name
% TODO link to article  
The second article in my dissertation investigates the question "what
are the behavioral processes that lead to macro-level outcomes" (in this
case, Google Trends results) proposed by \citet{breigerScaling2015}. Knowing that
Google trends data only encompasses a small portion of the
information-seeking done by modern humans, it is important to
investigate what leads individuals to search for a question online using
a search engine (contributing to macro-level trends data) versus more
traditional means of information gathering, such as network activation
(asking someone in their social network for informational support). To
investigate this, I use the case of receiving, requesting, and sharing
information about the Covid-19 vaccine in a survey I received funding to
conduct of 900 Adults in the United States.

Previous research has greatly failed to distinguish between the activation of
information seeking behaviors online and offline. Using theories of social
support and uses and gratifications theory I investigate the factors associated
with each vehicle type when on information seeking vehicle: personal connection,
doctor, social networking site, online forum, and online search engine. Using
novel survey data of % TODO  nrow(rain) Americans and their experience seeking out
information about the Covid-19 vaccines, I find little evidence that online
search is more utilized than seeking social support from personal network
connections or health professionals. I find evidence that the vehicles queried
in this survey are conceptually different and that the utilization of different
vehicles varies by demography and information sources. Finally, I find that
different fountains of information and information search vehicles hold real
world consequences through their associations with Covid-19 vaccination rates
and intentions, as information from a doctor increased the Covid-19 vaccination
uptake while receiving information from a Social Networking Site like Facebook
or Twitter was associated with lower odds of vaccination.

\subsubsection{Article 3: Social Norms under Uncertain Times: A dynamic study of Stay-At-Home and Vaccination Rates During the Covid-19 Pandemic}
% TODO Double check name
% TODO link to article  
My final article takes a deeper dive into the formation of social norms
governing health behaviors in cases of extreme uncertainty using the
cases of both a) population mobility during early 2020 and b)
vaccination rates during early 2021, both as responses to public health
recommendations to mitigate the Covid-19 pandemic. Using theories of
associative diffusion and the integrated theoretical framework of norms,
I test how these health behaviors are outcomes of assortative signaling
from networks and other sources, such as social isolation and connection
between communities, religious and political conservativism, and
attention to media sources, and online norms as measured by
information-search behaviors. To investigate this, I conduct statistical
modelling on a dataset I compiled from multiple sources, including
Google, Facebook, and the Center for Disease Control and Prevention.

This paper examines how social norms are formed under conditions of uncertainty
using the case studies of stay-at-home and vaccination rates during the Covid-19
pandemic.  I test fear-based models of behavioral adaption to public health
recommendations as well as patterns of complex social contagion using linear
mixed effects models. These models show that complex contagion is a valid
framework for the social contagion of new norms during Covid-19. However, I find
important moderating effect of signal discordance, the contextual diversity of
signals received by an ego.

### 2022-03-02 paper1.tex
Initial Overleaf Import

\hypertarget{paper-1}{%
\chapter{Digital Trace Data as Indicators of Social Data Validating Google Trends for  use in Scientific Research}\label{paper-1}}

Possible titles Digital Trace Data as Social Indicators: Indicators of
Attention Rather Than Support

Digital Trace Data as Indicators of Social Data: Validating Google Trends for
 use in Scientific Research

\section{Abstract}

\section{Introduction}
New big data sources have led to vast possibilities for social science
research because they are bigger, cheaper, and already available
\citep{kingEnsuringDataRichFuture2011, lazerComputationalSocialScience2009,
salganikBitBitSocial2017}. Before overenthusiastically embracing these
sources into our workflows, social scientists must clearly establish
parameters under which these data sources could be operationalized
\citep{bailCulturalEnvironmentMeasuring2014, lazerParableGoogleFlu2014}. As
prior research outlined, the "quantity of data does not mean that one
can ignore foundational issues of measurement and construct validity and
reliability and dependencies among data" \citep[p. 1203]{lazerParableGoogleFlu2014}. Building on this prior research outlining these various
issues with big data \citep{boydCriticalQuestionsBig2012,
lazerIssuesConstructValidity2015}, this paper tests the construct
validity of Google Search Trends as an indicator of three different
cases, namely cultural attitudes, disease prevalence and voting
behavior. These three cases will be tested using cultural indicators
from the NORC General Social Survey, United States county-level suicide
rates from National Center for Health Statistics, US cases rates of
Covid-19 from The New York Times, historical US Presidential Election
results, and the American National Election Survey. Data will be
analyzed against corresponding operationalized Google Trends
longitudinal data using Pearson's r for pairwise correlations, testing
for the strength of relationships between the Google Trend indicator and
the respective comparison indicator. This paper will contribute to the
creation of methodological norms and standards of how to use Google
Trends as a big data source for societal research and serve as a
critical inquiry into the adoption of big data without a critical eye
for the ecological validity of the sources.

With the expansion of big data, some research has shown extremely
innovative methods that lead to groundbreaking results that are shown to
be reliable. As an example, \citet{blumenstockPredictingPovertyWealth2015} use
county-level cell-phone records to construct the distribution of poverty
and wealth in Rwanda, a country where national surveys and censes are
rare and costly. However, \citet{blumenstockPredictingPovertyWealth2015} go to
great lengths to demonstrate that their operationalization of the cell
phone data creates a reliable and valid construct; few social science
papers utilizing big data dig into the construct validity of their
metrics to this extent and even fewer publications focus on
methodological guidelines of how to use sources of big data
\citep{asseoTrackingCOVID19Using2020, stilesAssessingCriterionValidity2018}.
However, research has shown the small adjustments to an algorithm or
metric may void any research insight we are able to pull from such data
\citep{lazerParableGoogleFlu2014}. Because of this, I propose a
methodological validation study of the Google Search Trends source of
big data to investigate how it is advisable to utilize this data in
social scientific research.

I will use three categorizations of ways I propose Google Trends could
be operationalized for social scientific usage. First, I'll test Google
Trends as an operationalization of cultural attitudes with the General
Social Survey. After \citet{bailCulturalEnvironmentMeasuring2014}'s call for
cultural sociologists to utilize the ever-expanding world of big data,
Google trends as a data source began appearing in sociological and
social science research. From research on mass shootings and firearms
\citep{brownsteinInternetSearchPatterns2020,
semenzaInformationseekingWakeTragedy2020}, protest and anti-Muslim
sentiment \citep{bailUsingInternetSearch2018,
barrieSearchingRacismGeorge2020, grossThereFergusonEffect2017}, to
analyzing country-level changes in social perception \citep{reyes_etal18},
Google search trends are a new and innovative indicator of cultural
interest. Extending into social networks and culture,
\citet{bailPrestigeProximityPrejudice2019} even used Google trends to measure
how culture spreads around the globe.

Google Search Trends have also been used continuously in estimations of
disease prevalence and population health in journals like the Journal of
Medical Internet Research. While much of this research has focused on
the Covid-19 pandemic \citep{jimenez_etal20,
jimenezCOVID19SymptomGoogle2020,
limEstimatingInformationSeekingBehaviour2020,
mavraganiCOVID19PredictabilityUnited2020,
nguyenGoogleTrendsAnalysis2020, todorovaInternetBasedData2021} , other
research has investigated Google Trends as an indicator of wellbeing
\citep{brodeurCOVID19LockdownsWellbeing2021,
carpiTwitterSubjectiveWellBeing2020, duCOVID19IncreasesOnline2020},
suicidality \citep{burnettTimeTrendsPublic2020}, vaccination uptake
\citep{dalumhansenEnsembleLearnedVaccination2016}, obesity
\citep{sarigulNowcastingObesityUsing2014}, and even insomnia
\citep{zittingGoogleTrendsReveal2020}, to cover a few examples. For a partial
review of other utilizations, see \citet{nutiUseGoogleTrends2014}. According to
\citet{jaidkaInformationseekingVsSharing2021}, the majority of studies profess
a correlation of \> .70, "demonstrating the vast potential of Google
Search as a proxy for monitoring population health" (p. 3) based on
assumptions that individuals search because of self-diagnosis and to
identify possible courses of treatment
\citep{dechoudhurySeekingSharingHealth2014}.

% <!-- Following reports say that Google searches can predict covid  -->

% <!-- 14. Brunori, P. & Resce, G. Searching for the peak Google Trends and the Covid-19 outbreak in Italy. SERIES working papers N. 04/2020 -->

% <!-- Lampos, V. et al. Tracking COVID-19 using online search. Preprint at https://arxiv.org/abs/2003.08086 (2020). -->

% <!-- 16. Walker, A., Hopkins, C. & Surda, P. The use of google trends to investigate the loss of smell related searches during COVID‐19 outbreak. Int. Forum Allergy Rh. 10, 839–847 (2020). -->

% <!-- 17. Stephens-Davidowitz, S. Google Searches Can Help Us Find Emerging Covid-19 Outbreaks. The New York Times https://www.nytimes.com/2020/04/05/opinion/coronavirus-google-searches.html (2020). -->

% <!-- 18. Frank, T. Goldman says fewer ‘loss of smell’ Google queries suggest better COVID outlook. Consumer News and Business Channel. CNBC https://www.cnbc.com/2020/04/15/goldman-says-fewer-loss-of-smell-google-searches-is-a-positive-sign-for-pandemic.html (2020) -->

Various sources have also used Google Trends as a way to forecast
political elections and political attitudes
\citep{wolfTrendingRightDirection2018}. For instance,
\citet{swearingenGoogleInsightsSenate2014} investigate how U.S. Senate
Elections relate to attention measured by search traffic.
\citet{prado-romanGoogleTrendsPredictor2020} compare how Google Search trends
are able to predict presidential election results in both the United
States and Canada. Finally, the OECD Development Centre is investigating
how Google data can help elucidate governments' approval in Latin
America \citep{montoyaUsingGoogleData2020}.

Research Question - How can we operationalize Google Search Trends as a
valid indicator for uses in social science research?

<https://journals.sagepub.com/doi/10.1177/0894439316631043> What
constructs might google trends capture and not capture well? Capture
attention but not attitudes

Also Asseo - "we assumed that media coverage may potentially decouple
the search popularity from the number of cases, since searches would
result not only from self-symptoms, but also from interest elicited by
media coverage."

\section{Methods}
To investigate the construct and criterion validity of the use of Google Trends
in these three areas, I gathered geo-located social science data across multiple
sources to address the three areas of inquiry for this paper.  Table
\@ref(tab:data-sources-table) outlines which data sources are used for this
project and which trends are matched to each source.

TABLE HERE

\subsection{Measures}

\subsubsection{Google Trends}
This paper focuses on a validation of Google search trends \citep{googletrends}.
Google trends portray the search frequency for specific search terms across
designated media markets areas (DMAs), a nonoverlapping aggregation of U.S.
counties to 210 media markets based on similar population clusters \citep{dma_key}.
Raw data is on a scale from 0 to 100, with 100 being the maximum search
popularity out of all DMAs. When available, I use Google search topics to
measure trends as opposed to search terms. Search topics are a more robust
measurement than a single search term: topics are aggregations of the rates of
multiple, highly correlated search terms together into a cohesive topic. For
example, while 'Beyoncé', 'Beyonce' and 'beyonce knowles' are all separate
search terms, 'Beyoncé Knowles' encompasses all of these into a single search
topic. Google Search Trend are only available cross-sectionally (a single time
period across a geography) or as time-series (a single geo-location across
time). To remedy this and build a longitudinal dataset of each search topic for
the longitudinal datasets, I follow the method proposed in \citet[p. 5]{park_etal}.
This method involves building a dataset of unscaled cross-sectional values,
selecting a DMA to use to establish the rescaling ratio (I use 'Los Angeles
CA'), and then finding the time-series values for the one DMA. To find the
rescaling ratio for each week in the time-series, you divide the time-series
value for each week by the cross-sectional value for each week, resulting in a
rescaling vector to be used for all weeks in the dataset across geographies. To
rescale each longitudinal value, multiply the respective week's rescaling ratio
by the cross-sectional value. Rescaled longitudinal data was compared against
time-series data for multiple test counties and was equivalent. For a more
in-depth explanation of this procedure, see \citet[p. 5]{park_etal}. Missing
datapoints in longitudinal datasets were filled in with interpolated values
using `zoo::na.approx()` \citep{zoo}.

\subsubsection{Attitudinal}
<!-- \citep{gss_data} (let's see if I get access first) -->

One measure of attitudinal indicators is the Vaccine Hesitancy for COVID-19
\citep{vaches_data}. The CDC uses the U.S. Census Bureau’s Household Pulse Survey
(HPS) and the 2019 American Community Survey (ACS) 1-year Public Use Microdata
Sample (PUMS) to measure U.S. residents’ intentions to receive the COVID-19
vaccine if available during May 26, 2021 – June 7, 2021. This dataset consists
of x observations, one for each U.S. County. The variable
measures the precent of adults in the county who describe themselves as
“unsure”, “probably not”, or “definitely not” going to get a COVID-19 vaccine
once one is available to them. The variable ranges from x to y.

Another attitudinal indicator I use is the Mask-Wearing Survey Data conducted by
Dynata for the New York Times from July 2 through 14, 2020 \citep{mask_data}. 250,000
survey respondents were asked, "How often do you wear a mask in public when you
expect to be within six feet of another person?". The NYT weighted each response
to create a county level measure of what percent of the county never, rarely,
sometimes, frequently, and always wore a mask when in public. This dataset
consists of x observations, one for each U.S. County. This measure
represents the percent of adults in the county who never or rarely wear a mask
(range = x to x)

\subsubsection{Health}

I also use U.S. Covid-19 rates to validate health and disease related topics. I
retrieve U.S. county-level Covid-19 rates from by \citet{covid_data}, who compile this
data based on reports from state and local health agencies. It is widely
acknowledged that there are biases in this data due to inconsistencies and
availability in testing as well as different community propensity to test
\citep{gu22, cdc20a} However, it is the best measure we have of actual case rates.
Case Rate is measured as number of cases per 100,000 population. Observations
vary from a minimum of 0 to a maximum of x for each 
Monday from x through x. There are x cases across x counties and x dates. Missing data were interpolated using `zoo::na.approx()` \citep{zoo}.

I also use county-level suicide rates from the US Centers for Disease Control
and Prevention \citeyearpar{suic_data}. Data is grouped by year from 2010-2020. Raw death
rates are scaled by population size for each year and can be interpreted as the
death rate by suicide for every 1000 people. There are x total
cases, resulting from x observations of x counties. Missing data were interpolated using
`zoo::na.approx()` \citep{zoo}. Measures range from x to x.

\subsubsection{Political}

Finally, I test Google Trends as an operationalization of political
attitudes by first looking at actual voting outcomes in historical US
Presidential Election results. This data comes from  \citet{pres_data}, who scraped the
results from Townhall.com, Fox News, Politico, and the New York Times. Data on 
presidential outcomes were available for x counties in 2016 and
x counties in 2020. Each variable measures the percent of votes
for the candidate, with the lowest percent at x and the highest at x.

In addition, I use data on political opinions from the the American National
Election Survey 2020 Time-Series Study \citep{anes_data}. This data is paired with
restricted data provided by ICPSR, the Inter-university Consortium for Political
and Social Research, that contains the geo-ids of the 5,441
survey respondents. The study interviewed respondents in a pre-election survey
that was conducted between August 18, 2020 and the day of the US Presidential
election day, November 3, 2020.

% TODO: WHICH VARIABLES
% TODO: VARIABLE SCALE

\subsubsection{Other}

In addition to specific outcomes of interest, I also gathered various county
controls to investigate possible variable confounding. The first Seven of these
variables come from the 2010-2019 5-year American Community Surveys
\citep{acs2019, acs2018, acs2017, acs2016, acs2015, acs2014, acs2013, acs2012, acs2011, acs2010}. 
These data include total population, population density,
unemployment rate for those 16 and over, median county income, average commute
time, percent of households living under the poverty line, and percent above 65
years old. In addition, some models employ the U.S. Current Population Survey &
American Community Survey Geographic Estimates of Internet Use, 1997-2018
\citep{internet_use} to estimate households with broadband internet subscriptions.
This final variable is an attempt to capture the latent propensity to use the
internet for information search.

% ACS 5 year estimates
% a00001 total population
% a00002 population density
% a17005 unemployment rate 16+
% a14006 median income
% a09003 average commute time
% poverty percent
% 01001B 65 plus

\subsection{Analysis}
Google Search Trends data and additional demographic data are merged with each
individual indicator based on County FIPS Codes and date. After creating these
different datasets, I use the Pearson correlation formula (formula
%\@ref(eq:pearsoncorr)
) for cross-sectional numeric data to calculate the
strength of the relationship between each Google Trend and the respective
data source.

\begin{equation}
 r =
  \frac{ \sum_{i=1}^{n}(x_i-\bar{x})(y_i-\bar{y}) }{
        \sqrt{\sum_{i=1}^{n}(x_i-\bar{x})^2}\sqrt{\sum_{i=1}^{n}(y_i-\bar{y})^2}} %(\#eq:pearsoncorr)
\end{equation}

To address longitudinal correlations, I employ Repeated Measures Correlation
using the `rmcorr` package in R \citep{bland1995, bakdash2017}. Repeated Measures
Correlation is useful for determining the within-county association for paired
measures across time and counties. Results of these correlations can be seen in 
table %\@ref(tab:corr-results).

As an additional test of the relationships, I employ multiple linear regression
(for cross-sectional datasets) and random intercept hierarchical linear models
\citep{pinheiro_etal21} (for longitudinal datasets) to identify the strength of
relationships across locales: I include city-data like county population size,
broadband rates, and median income to attempt to disentangle possible
confounders of the relationship between Google search Trends and verified
indicators. Identifying these possible confounded relationships will help to
explain why some articles find relationships between the trends and outcomes
while others did not. For linear regression models, I normalize independent
variables, i.e.variables have been centered and scaled to have a mean of 0 and
standard deviation 1.

\section{Results}

\subsection{Validating Google Trends as metrics of attitudinal indicators}

% \citep{gss_data} (let's see if I get access first)

The first attitudinal indicators is Vaccine Hesitancy for COVID-19 vaccines
\citep{vaches_data}. When comparing the measure of vaccine hesitancy to four
different Google Search Trends, the correlation does not exceed -0.4657
('Coronavirus (Disease)' and vaccine hesitancy). Correlation's under |0.40| are
considered to be weak according to the common rules of thumb. When running these
correlations in multiple linear regression (see the results in table
% \@ref(tab:vacc_hes_analysis)
), I see an $r^2$ of 0.233 (Model 1) and 0.411
(Model 2), indicating that the Google Trends are able to explain about 23% of
the variation in Vaccine Hesitancy alone. Demographic characteristics like the
percentage of households with broadband internet and the population density are
able to explain about 35% of the variation (model 2), outperforming the first
models. The Trend coefficients themselves, however, are significant and remain
significant when controlling for demographics. This reinforces the finding from
the Pearson Correlation that there is a significant but weak relationship
between the Google Trends and Vaccine Hesitancy.

The second attitudinal measure I test is how Google Trends relates to rare mask
usage. As with vaccine hesitancy, the Pearson correlations are negligible.
Correlation's under |0.20| are considered to be negigible according to the
common rules of thumb. I introduce these trends in multiple linear regression in
table 
% \@ref(tab:mask_analysis)
. Model 1 demonstrates that these five Google
Search Trends can explain about 7\% of the variance in mask usage across U.S.
counties, reinforcing the conclusion that the relationship is quite weak. The
coefficients themselves are somewhat significant in Model 1. However, after
including the demographic variables in Models 2 and 3, we see that the
relationship between the Google Search Trends and mask usage is strengthened in
magnitude and in significance, likely indicating a suppression effect due to
underlying relationships between the trends and demographic variables. While the
trends are significant and match the demographic variables in magnitude, the
low $r^2$ of 0.203 for the trends still provides evidence that Google Search
Trends data cannot replace survey analysis when trying to measure rare mask
usage.

\subsection{Validating Google Trends as metrics of health outcomes}

In addition to attitudinal measures, I attempt to validate Google Trends for
uses in the measurements of health indicators. The first indicator I test is
Covid-19 case rates from 2020 through 2021. The Pearson correlation results
indicate negligible to weak relationships between the search terms and the
actual case rates across time and place. The repeated measures correlation
coefficient, a more reliable and less biased measure for longitudinal
correlations, reveals similarly weak results with a maximum correlation of 0.32
between 'smell loss' and rates of Covid-19. To further test the relationship, I
include the three trends in random intercept hierarchical linear models. Model 1
of table 
% \@ref(tab:covid_analysis)
indicates that the trends themselves are able
to explain about 20\% of the variation in Covid-19 rates ($r^2$ = 0.201). Few
of the demographic variables have an effect on Covid-19 rates in models 2 or 3,
though it seems there is some suppression for median income, unemployment rates,
and population density. Model 3 has an $r^2$ of 0.200. I conclude that the
Google Trends are slightly related to Covid-19 rates, but that this relationship
is weak and we should not attempt to use Google Trends as an indicator of actual
health outcomes.

Another indicator of health outcomes I test to validate Google Trends as
possible health indicators are county suicide rates. As with previous cases,
there is only negligible correlation between actual suicide rates and Google
Search Trends, not exceeding 0.0845. In the more accurate repeated measures
correlation coefficient we see a maximum of 0.142 correlation, remaining
negligible. I introduce these trends into a random intercept model to control
for inter-group variation over time in table 
% \@ref(tab:suicide_analysis)
. While
table 
% \@ref(tab:suicide_analysis)
model 1 reveals a significant relationship
between suicide hotline trends and suicide rates, the effect is small and the
entire model only has an $r^2$ of 0.058. Adding in demographic features in model
2 improves the $r^2$ quite a lot. In model 3, the inclusion of Google Trends
actually decreases the overall amount of suicide rate variance explained
compared to model 2. These analyses lead me to conclude that Google Search
Trends should not be used as indicators of suicide rates or intentions.

\subsection{Validating Google Trends as metrics of political support}

Previous research has showed some relationship between Google Search Trends and
political election results. I test here the relationships between search trends
and U.S. Presidential Election results in 2016 and 2020. In 2016, Pearson
correlations for Both Hilary Clinton and Donald Trump do not exceed a |0.17|
correlation with the actual percentage of votes for either candidate. In 2020,
results are even less related, with searches for neither Joe Biden nor Donald
Trump holding any real correlation with the 2020 results.

In table 
% \@ref(tab:pres_2016_analysis)
, I outline the results for the model
predicting the county percentage of votes for Hillary Clinton. Model 1
demonstrates how well Google Trends are able to predict the votes; while the
trend for 'Hillary Clinton' is significantly associated with votes, the model's
$r^2$ ($r^2$ = 0.027) shows that it does little to help explain the model
variance. On the other hand, adding in demographic features improves the model
fit quite well, bringing the $r^2$ up to 0.313 in model 2 and $r^2$ 0.327 in
model 3. In table 
% \@ref(tab:pres_2020_analysis)
shows this same analysis for the
2020 election and predicts the percentage of votes for Joe Biden. While this
model is largely similar to those in table 
% \@ref(tab:pres_2016_analysis)
, this
model 1 demonstrates how unrelated Google Trends can be from actual outcomes. In
conclusion, I find that Google Trends are an unreliable and invalid indicator of
political support.

\section{Discussion}

The external validity of these voting

While I expect these tests to show high correlation between observed
indicators and Google search trends, there will be three important
questions that surface. First, just because something is correlated,
does that mean it can replace the collection of other types of data?
Second, how correlated does a trend need to be for social scientists to
justifiably rely on it to indicate some outcome? And finally, how can we
construct analyses like this to be robust to changes in the terms used
across time and location?

The purpose of this paper is more methodological than theoretical, and I
see this paper having an impact on the social sciences and computational
social science as researchers pursue more projects using this source of
big data. Google Trends are relatively underutilized in the field
compared to in the health sciences and business. Once I assess how this
data can be used, I would like to be able to join
\citet{bailCulturalEnvironmentMeasuring2014} in encouraging social scientists
to pursue more research with big data while taking into account the
potential pitfalls with any source of big data
\citep{mcfarlandBigDataDanger2015}.

\section{Conclusion}

### 2022-03-02 paper2.tex
Initial Overleaf Import

\hypertarget{paper-2}{%
\chapter{Information-Seeking Behaviors for Information on Covid-19 Vaccinations}\label{paper-2}}

\hypertarget{abstract}{%
\section{Abstract}\label{abstract}}

Previous research has greatly failed to distinguish between the activation of
information seeking behaviors online and offline. Using theories of social
support and uses and gratifications theory I investigate the factors associated
with each vehicle type when on information seeking vehicle: personal connection,
doctor, social networking site, online forum, and online search engine. Using
novel survey data of 948 Americans and their experience seeking out
information about the Covid-19 vaccines, I find little evidence that online
search is more utilized than seeking social support from personal network
connections or health professionals. I find evidence that the vehicles queried
in this survey are conceptually different and that the utilization of different
vehicles varies by demography and information sources. Finally, I find that
different fountains of information and information search vehicles hold real
world consequences through their associations with Covid-19 vaccination rates
and intentions, as information from a doctor increased the Covid-19 vaccination
uptake while receiving information from a Social Networking Site like Facebook
or Twitter was associated with lower odds of vaccination.

\textbf{Keywords}: Information-Seeking Behavior, Covid-19, Vaccine Hesitancy, Social Networks, Social Support, Information \& Communication Technologies

\hypertarget{intro-1}{%
\section{Intro}\label{intro-1}}

Information is all around us and permeates every facet of human society, from
the hordes of data gathered during the internet age or passing gossip between
friends. Human communication and human society are based on the circulation of
information and knowledge. Information can be shared by others through
information campaigns and consumed by an individual, called information push, or
intentionally sought out by individuals, called information pull
\citep{cybenkoFoundationsInformationPush1999}.

Information is especially important given the prominent trends of
misinformation, disinformation, and mistrust in traditional institutions
\citep{starbird19, kata10}. While no belief in false information can be thought of as
harmless \citep{douglas21} some discredited theories such as 'vaccines cause autism'
have major ramifications for both the individual and the social world that
surrounds them. For example, a newfound public resistance to vaccination
against Measles by so-called 'anti-vaxxers' caused a 17\% increase in rates
worldwide in 2019. This increase killed  142,000 people, most of whom were
children under the age of five \citep{givetash19}. However, even in the ever-evolving
research agenda of misinformation and infodemiology \citep{eysenbach02}, much of the
research focuses on the 'push' or 'supply' side of information, like spaces where
individuals first encounter with conspiracy theories or other information
\citep{johnsonOnlineCompetitionPro2020, broniatowski_etal20}.
% cite something else here

The lack of research in which vehicles are likely to be chosen when an
individual faces a need for information makes it difficult for policy makers to
propose effective information campaigns that promote the health and wellbeing of
individuals in our society. Even outside of the misinformation literature, much
of the research conducted in social networks and communication focus on senders,
influencers, and persuasion strategies 
\citep{mertonManifestLatentFunctions1968, katzPersonalInfluencePart1955, lazarsfeldPeopleChoice1944},
rather than on
“the receiver as an active information seeker and processor." \citep{johnsonComprehensiveModelCancerRelated1993},
though there are always exceptions \cite{ysenbach09}

I use the case of information around Covid-19 vaccinations to explore the
variation of usage of information search vehicles. In doing so, I seek to answer
how computer-mediated or interpersonal information-seeking strategies vary
across populations in their search for information about Covid-19 vaccinations
and investigate how these strategies affect vaccination uptake.

Before addressing my central research questions, I offer an overview of the
current state of social science literature in regards to information-seeking
strategies before providing a description of the research methodology and
analytic sample. I discuss the implications of these findings for the
sociological understanding of information search and vaccination uptake.

\hypertarget{information-search}{%
\subsection{Information Search}\label{information-search}}

Active, directed searching by individuals to obtain information is sparsely
discussed in the sociological literature. Pejtersen \citet{pejtersen1984}, a scholar
of library and information science, theorized that there are 5 strategies for
searching for information. The most common strategy is browsing, where people
follow leads based on associations without premeditation. Another strategy is
analytical, which includes an explicit consideration of all facets of the
question to guide a search. The empirical method guides the search based on
tactics that were successful in past research. The known site strategy is to go
to the direct source of the information if known. And finally, the similarity
method is to find information based on another similar question that already has
an answer. These 5 strategies vary in their demands for prior knowledge,
cognitive processing, memory, and time spent. While this theory is aimed at
finding information in a library setting, scholars have extended the theory to
other fields and validated the framework
\citep{fidelHumanInformationInteraction2012}; the frame is a useful beginning point
for my theories of information search through network activation or through
computer-mediated communication.

Some communication theorists ask why an answer to a question is sought in the
first place. The Theory of Uncertainty Management
\citep{brashersCommunicationUncertaintyManagement2001} professes that people search
for information when their uncertainty around the subject leads to anxiety or
other cognitive harms. The Theory of Motivated Information Management
\citep{afifiTheoryMotivatedInformation2004, afifiSeekingInformationSexual2006}
extends the prior by adding that uncertainty itself is not the catalyst for
information-search; rather, it is driven by a discrepancy between the current
level of uncertainty on a subject and desired level of uncertainty. In other
words, individuals only perform information search when they are distressed by
their lack of knowledge or understanding on a subject.

One way to find information is to activate network ties to find out information
through a form of social support. Social support, while previously used
interchangeably with the term social networks and social integration
\citep{houseStructuresProcessesSocial1988}, are the emotional, informational, and
instrumental assistance functions performed between social ties and have strong
and measurable association with health outcomes
\citep{houseMeasuresConceptsSocial1985, thoitsMechanismsLinkingSocial2011}.
Informational support is the process of seeking “help in defining,
understanding, and coping with problematic events and include education, advice,
or referral to another source of support” \citep{winemiller_etal93}[p. 640].
Brashers, a health communications researcher, defines informational support
slightly differently, focusing on the exchange of information that “facilitates
coping with life stresses… that may be exchanged among members of a support
network” \citet{brashersInformationSeekingAvoiding2002}[p. 260].These definitions
help to differentiate between seeking information through social ties or through
something anonymous like online search; a need for coping or deeper
understanding of important matters is thought to sway that decision.

Social support has long been theorized to stem from core discussion networks and
much of the historical social support surveys only looked at these core
networks. The underlying assumption is that individuals reach out to a handful
of strong ties when in need of support, which could be elicited in surveys using
name generators \citep{marsdenCoreDiscussionNetworks1987}. This approach has yielded
important insights, but largely overlooks crucial
processes of resource activation \citep{hurlbertCoreNetworksTie2000,
perrySocialNetworkActivation2015, smithDonPutMy2005}. For instance, Small
\citet{smallSomeoneTalk2017} shows that the core discussion network does not capture
how people activate social support in practice and indicates that people draw on
much broader social connections for support, reminiscent of the weak ties
research by Granovetter \citet{granovetterStrengthWeakTies1973}. There is ongoing
research investigating how weak-tie support holds for different support types
based on the architecture put forward by 
\citet{houseStructuresProcessesSocial1988} of instrumental, emotional, and
informational support.

However, informational support can also be sought outside of the social network
context, namely via computer-mediated information search tools such as the
process of “Googling”. As the online environment began penetrating all facets of
modern human life, it makes sense that performing online search has become one
of the most convenient vehicles for information search. While Small
\citet{smallSomeoneTalk2017} focuses on how support can depend on a network tie
simply "happened to be there", online search is theoretically the most
frictionless and costless mode of support. No social capital or relationship is
necessary when choosing to utilize a search engine.

%%% STOPED PASTING CITATIONS HERE

There are three computer-mediated vehicles I consider for this analysis: online
search engines like Google or Bing, posting questions on online forums like
subreddits or Facebook groups, and posting a status update online via Facebook
or Twitter. While the first two are largely anonymous and don't require a
personal network, the third is a unique hybrid between personal network
connections and online search.

There are important factors that can influence information-seeking strategies
besides the strength of social capital or ease of search. For instance, we can
borrow uses and gratifications theory (UGT) from studies of mass communication
\citep{blumlerUsesMassCommunications1974, tanMassCommunicationTheories1985}
. UGT
posits that users are not passive consumers of media and that people have an
active role in choosing different sources of media based on their satisfaction
of specific needs on an individual basis. UGT is based on Maslow’s  \citeyear{maslowTheoryHumanMotivation1943} hierarchy of needs and is compatible with
Lazarsfeld and Katz’s theory of two-step flow \cite{katzPersonalInfluencePart1955}
because people can choose their media and the opinion leaders they follow.
Modern-day theorists have extended UGT theory and classified the uses and
gratifications of the internet and of social media. \cite{staffordDeterminingUsesGratifications2004} theorize that the internet
provides gratification through useful content that meets expectations,
gratification from purposeful navigating or random browsing as a process, and
social gratification from forming and deepening social ties. \cite{leungGenerationalDifferencesContent201} theorizes that social media is
gratifying for users because it allows for venting of negative feelings,
provides recognition, provides entertainment, promotes social affection, and
fulfills cognitive needs.

Adapting these facets of UGT and social support to my own case, I theorize that
online search allows for increased anonymity, a lowered social cost, and the
potential avoidance of embarrassment and other negative social interactions,
especially in the case on search engines. Stephen Rains
(2018) finds that patients tend to search for
technical information about an illness online but they then turn to their social
network for experiential information from others facing similar circumstances in
the case of cancer. The type of information sought is therefore important.
If specific expertise on a specific topic is desired by a searcher, they may
reach out to personal connections that they see as expert such as a doctor, or
if an individual distrusts the medical establishment, they may be more likely to
activate informational support among their social network or turn to online
groups that validate their worldview (Bogers and Wernersen 2014). Finally, UGT and
Brasher's definition of social support
(2002) help us to theorize that the
psychosocial needs like identity management or relational maintenance
(Brashers et al. 2002) of an individual may influence their
chosen information search vehicle: when the informational need is related to
forming and deepening social ties search is likely to be done from network ties.

\hypertarget{research-methodology}{%
\section{Research Methodology}\label{research-methodology}}

The data used for this research project are based on original survey data
sampled between December 03, 2021 through
December 12, 2021. This survey was hosted on Qualtrics and
participants were paid and recruited using Amazon Turk (MTurk). The total valid
survey responses (\emph{n} = 948) were selected from a total of 1,066
respondents; some responses were disqualified due to a few factors such as
detected usage of a VPN, random answer clicking (determined by illogical
responses), poor quality typed responses (e.g., social network alters
consistently named random nouns), or taking the survey more than once. The same
is slighted gender unbalanced, slightly skewing towards a male sample. For the
respondents who provided their zip code (p =
0.98), the
sample is quite balanced with a slight skew towards MTurkers in the South (p =
0.41).
The survey took an average of 24.48 minutes with a
standard deviation of 13.23 minutes. The shortest
valid survey took 3.75 minutes and the longest took
111.08 minutes. Participants were paid \$6.00 for their
time after Amazon administrative fees, funded by a Grant awarded to Kelsey E.
Gonzalez and Nicolas Legewie by the Summer Institute in Computational Social
Science and the Russell Sage Foundation. The main portion of this survey
replicates the book, Someone to Talk To (Small 2017) by expanding on
Small's finding that people draw on much broader sources than ``important people''
for support by segregating weak-tie social support into instrumental, emotional,
and informational support (see House et al. 1988). The latter
part of the survey focuses on resource activation for the specific case-study of
information during the Covid-19 pandemic analyzed in this paper.

\begin{table}[!h]

\caption{\label{tab:table-1-desc}Descriptive Statistics for Dichotomous and Numeric Variables}
\centering
\begin{tabular}[t]{lrr}
\toprule
  & Mean & SD\\
\midrule
\cellcolor{gray!6}{Received info} & \cellcolor{gray!6}{\num{0.66}} & \cellcolor{gray!6}{\num{0.47}}\\
Received info, Doctor & \num{0.47} & \num{0.50}\\
\cellcolor{gray!6}{Received info, Person} & \cellcolor{gray!6}{\num{0.67}} & \cellcolor{gray!6}{\num{0.47}}\\
Received info, News & \num{0.65} & \num{0.48}\\
\cellcolor{gray!6}{Received info, Social Networking Site} & \cellcolor{gray!6}{\num{0.40}} & \cellcolor{gray!6}{\num{0.49}}\\
Received info, Online Forum & \num{0.35} & \num{0.48}\\
\cellcolor{gray!6}{Sought Info} & \cellcolor{gray!6}{\num{0.78}} & \cellcolor{gray!6}{\num{0.41}}\\
Sought Info, Doctor & \num{0.44} & \num{0.50}\\
\cellcolor{gray!6}{Sought Info, Person} & \cellcolor{gray!6}{\num{0.42}} & \cellcolor{gray!6}{\num{0.49}}\\
Sought Info, Social Networking Site & \num{0.18} & \num{0.39}\\
\cellcolor{gray!6}{Sought Info, Online Forum} & \cellcolor{gray!6}{\num{0.27}} & \cellcolor{gray!6}{\num{0.44}}\\
Sought Info, Online Search & \num{0.41} & \num{0.49}\\
\cellcolor{gray!6}{Vaccination Status} & \cellcolor{gray!6}{\num{0.84}} & \cellcolor{gray!6}{\num{0.36}}\\
Vaccination Outlook & \num{0.87} & \num{0.34}\\
\cellcolor{gray!6}{Age} & \cellcolor{gray!6}{\num{37.76}} & \cellcolor{gray!6}{\num{10.75}}\\
Hispanic or Latino/x & \num{0.15} & \num{0.36}\\
\cellcolor{gray!6}{Race, White} & \cellcolor{gray!6}{\num{0.88}} & \cellcolor{gray!6}{\num{0.33}}\\
Race, Black & \num{0.08} & \num{0.27}\\
\cellcolor{gray!6}{Race, Native American} & \cellcolor{gray!6}{\num{0.03}} & \cellcolor{gray!6}{\num{0.16}}\\
Race, Asian or Pacific Islander & \num{0.04} & \num{0.20}\\
\cellcolor{gray!6}{Associate's Deg or above} & \cellcolor{gray!6}{\num{0.74}} & \cellcolor{gray!6}{\num{0.44}}\\
\bottomrule
\multicolumn{3}{l}{\rule{0pt}{1em}Notes: 948 Surveyed, Conducted December 03 through December 12, 2021.}\\
\end{tabular}
\end{table}

\hypertarget{measures}{%
\subsection{Measures}\label{measures}}

\hypertarget{sought-information}{%
\subsubsection{Sought Information}\label{sought-information}}

There are multiple dependent variables of interest for this paper. The first
variable is a dichotomous indicator of whether someone intentionally sought out
information about Covid-19 vaccinations. The survey asked, ``And how about you
yourself intentionally looking for information about a Covid-19 vaccine? Such
information can include things such as advice, clarification, facts, and
experiences.'' About 78\% (\(\widehat{p}\))
of respondents had intentionally sought out information about Covid-19
vaccinations (95\% Confidence Interval = \{76\%, 81\%\}).

Further dependent variables segment the above question into multiple options;
``How did you look for information about the Covid-19 vaccine?'' Respondents were
posed with 5 responses and `other,' of which they could select multiple. The
largest proportion, 44\%, asked their
`doctor or another health professional' (95\% Confidence Interval =
\{41\%, 47\%\}).
About 42\% said they asked, `a person
like friend, neighbor, or family member that {[}they{]} know' (95\% Confidence
Interval = \{39\%, 45\%\}). An additional
41\% searched `for {[}their{]} question
using an online search engine such as Google or Bing' (95\% Confidence Interval
= \{38\%, 45\%\}). About a quarter of the
sample, 27\%, `posted queries in an
online discussion group, listserve, or other online forum like a Facebook Group
or Subreddit' (95\% Confidence Interval = \{24\%, 30\%\}).
And finally, 18\% of the sample `posted queries
on a social networking site such as Facebook timeline, Twitter status update, or
LinkedIn' (95\% Confidence Interval = \{16\%, 21\%\}).
Much of the question wording and the specific categories of search were inspired
by ICPSR project 37220 (Scanlon 2019).

\begin{table}[!h]

\caption{\label{tab:table-2-desc}Descriptive Statistics for Categorical Variables}
\centering
\begin{tabular}[t]{llrr}
\toprule
  &    & N & Percent\\
\midrule
\cellcolor{gray!6}{Gender} & \cellcolor{gray!6}{Female} & \cellcolor{gray!6}{418} & \cellcolor{gray!6}{\num{44.09}}\\
 & Male & 524 & \num{55.27}\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Other} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{\num{0.63}}\\
Highest Education Level & Graduate or professional degree & 145 & \num{15.30}\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Bachelor's degree} & \cellcolor{gray!6}{560} & \cellcolor{gray!6}{\num{59.07}}\\
 & Associate's or Technical degree & 72 & \num{7.59}\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Some college} & \cellcolor{gray!6}{100} & \cellcolor{gray!6}{\num{10.55}}\\
 & High school graduate & 68 & \num{7.17}\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Less than high school} & \cellcolor{gray!6}{3} & \cellcolor{gray!6}{\num{0.32}}\\
Plan to be Vaccinated if not & Probably not & 38 & \num{4.01}\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Definitely yes} & \cellcolor{gray!6}{13} & \cellcolor{gray!6}{\num{1.37}}\\
 & Definitely not & 61 & \num{6.43}\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Might or might not} & \cellcolor{gray!6}{22} & \cellcolor{gray!6}{\num{2.32}}\\
 & Probably yes & 13 & \num{1.37}\\
\cellcolor{gray!6}{Found Info Sought Useful} & \cellcolor{gray!6}{Very useful} & \cellcolor{gray!6}{345} & \cellcolor{gray!6}{\num{36.39}}\\
 & Moderately useful & 112 & \num{11.81}\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Extremely useful} & \cellcolor{gray!6}{264} & \cellcolor{gray!6}{\num{27.85}}\\
 & Slightly useful & 18 & \num{1.90}\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Not at all useful} & \cellcolor{gray!6}{2} & \cellcolor{gray!6}{\num{0.21}}\\
Census Region & Midwest & 171 & \num{18.04}\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Northeast} & \cellcolor{gray!6}{170} & \cellcolor{gray!6}{\num{17.93}}\\
 & South & 365 & \num{38.50}\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{West} & \cellcolor{gray!6}{223} & \cellcolor{gray!6}{\num{23.52}}\\
\bottomrule
\multicolumn{4}{l}{\rule{0pt}{1em}Notes: 948 Surveyed, Conducted December 03 through December 12, 2021.}\\
\end{tabular}
\end{table}

\hypertarget{vaccination-outlook}{%
\subsubsection{Vaccination Outlook}\label{vaccination-outlook}}

Another Dependent variable for this analysis is a dichotomous variable
indicating whether the respondent has received or plans to receive a vaccination against Covid-19. For this survey, the number of doses or timeline of receipt were less
relevant to the research question. This variable instead focuses on intent or
opinion about the vaccine. About 87\% have a
positive view about the vaccine. This construct is made through the combination
of two survey items. The first item is actual vaccination status, obtained through
the question `Did you receive a Covid-19 vaccine?'
84\% of the sample said that
they had indeed received a vaccination (95\% Confidence Interval = \{82\%, 87\%\}). As the national vaccination rate is
closer to 75\% (CDC 2020a), this indicates some bias in our sample that must be
acknowledged: either MTurkers are more likely to be vaccinated that the normal
population (sampling bias) or there is some conformity bias in the responses
causing survey takers to provide false answers. The second survey item that
contributes to `Vaccination Outlook' was only given to those who had not
responded `yes' to the to their vaccination status. These respondents were asked `Do you
plan to receive a vaccine for the prevention of the Covid-19 virus?' Of those
who were asked this question (n = 147),
9\%
said they were `definitely yes' getting the vaccine;
9\%
said they were `probably yes' going to receive vaccine. The rest of the sample was more unsure:
15\%
said they `Might or might not,'
26\%
said `Probably not,' and finally
41\%
said they would `definitely not' receive the vaccine. The variable `Vaccination
Outlook' indicates that either the respondent received a Covid-19 vaccine or
either probably or definitely will in the future.

\hypertarget{independent-variables}{%
\subsubsection{Independent Variables}\label{independent-variables}}

The first independent variables used in this analysis are based on the question,
`In the past 12 months, without searching for it, did you receive information
about the Covid-19 vaccine from \ldots{} (check all sources you received information
from).' This differs from the `How did you look for information' question above
because this is based on passive reception of information. The largest proportion
of respondents had received information from a person like friend, neighbor, or
family member that {[}they{]} know (\(\widehat{p}\) = 67\%
). Respondents also commonly received information from a television news channel
or a newspaper, about 65\% of the sample.
47\% of the sample had received information from
their doctor or other health professional while 40\%
received information from a social networking site such as Facebook timeline,
Twitter status update, or LinkedIn. Finally, the lowest proportion of the sample
had received information from an online discussion group, listserve, or other
online forum like a Facebook group or subreddit
(\(\widehat{p}\) = 35\%).

We also asked various demographic questions to understand our sample. The
average age of our sample was 37.76.
Our sample was 44\%
female, and 55\%
male. The sample is diverse racially though some ethnic groups are underrepresented compared to national averages. Race was evaluated using the
question, `What is your race? If you are ``mixed race,'' select all that apply.'
Because of the multi-selection question, each variable is dichotomous and
proportions are shown. 88\% of the sample claimed
they were `White,' 8\% claimed to be `Black or
African American,' 3\% chose `American Indian or
Alaskan Native,' 4\% selected `Asian,' and finally
when asked, `Are you Hispanic, Latino/a/x, or Latin American Origin?'
15\% selected `Yes.' Respondents were also asked to
select the highest level of education that you have completed. Based on the
breakdown between `Less than high school,' `High school graduate,' `Some college,'
`Associate's or Technical degree,' `Bachelor's degree,' and `Graduate or
professional degree,' 74\% of the sample were classified
to have a college-level education (Associate's degree or above).

\hypertarget{analysis}{%
\section{Analysis}\label{analysis}}

My analytic strategy proceeds in four steps. In Tables \ref{tab:table-1-desc}
\& \ref{tab:table-2-desc}, I present descriptive statistics for all study
variables, including variable ranges, means, and standard deviations. For this
paper, I rely heavily on logistic regression, modeled in \texttt{r}; specifically, I
fit a series of Binomial Generalized Linear Models (Venables and Ripley 2002). In Table \ref{tab:table-model-1}\footnote{All tables in this paper were created with the modelsummary package in \texttt{r} (Arel-Bundock 2022)}
, I fit a logistic regression model predicting
whether someone sought information about Covid-19 using their sources of
information (`Received info') as well as various demographic variables such as
age, education level and race. Figure \ref{fig:plot-model-1} then illustrates
the relationship between the coefficients and information seeking.\footnote{Figures in
  this paper were all created using the \texttt{r} packages jtools (Long 2020) and ggplot2 (Wickham 2011; Wickham, Chang, and Henry n.d.)}.
In Table \ref{tab:model-2-phi} I disaggregate information seeking behaviors by
investigating the difference in proportions of each of the 5 different avenues
of seeking information about Covid-19: from another person, from a doctor, on an
online forum, on a social networking site, or using an online search tool. I
investigate these differences through a phi coefficient (Warrens 2008), otherwise
known as a mean square contingency coefficient which is used to investigate the
degree of association between two binary variables.\footnote{To calculate the Phi
  Coefficient, I utilize the Psych \texttt{r} package (Revelle 2015)} I then investigate the
associations between my predictors and the 5 information search vehicles by
modelling a series of logistic regressions in Table \ref{tab:table-model-2}.
Finally, in Table \ref{tab:table-model-3}, I investigate whether there is a
relationship between information receiving and information seeking behaviors and
the choice to get vaccinated against Covid-19 through a logistic regression
model predicting Vaccination Outlook. Figure \ref{fig:plot-model-3} then
illustrates the relationship between the coefficients and vaccination outlook.

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{information-seeking}{%
\subsection{Information Seeking}\label{information-seeking}}

\begin{table}[!h]

\caption{\label{tab:table-model-1}What predicts someone intentionally searched for information}
\centering
\begin{tabular}[t]{lc}
\toprule
  & Model 1\\
\midrule
\cellcolor{gray!6}{Received Info, Doctor} & \cellcolor{gray!6}{\num{1.037}*** (\num{0.181})}\\
Received Info, Person & \num{0.624}*** (\num{0.171})\\
\cellcolor{gray!6}{Received Info, News} & \cellcolor{gray!6}{\num{0.316}+ (\num{0.175})}\\
Received Info, Social Networking Site & \num{0.320}+ (\num{0.187})\\
\cellcolor{gray!6}{Received Info, Online Forum} & \cellcolor{gray!6}{\num{0.873}*** (\num{0.203})}\\
Age & \num{0.025}** (\num{0.009})\\
\cellcolor{gray!6}{Associate's Deg or above} & \cellcolor{gray!6}{\num{0.456}* (\num{0.192})}\\
White & \num{0.857} (\num{0.575})\\
\cellcolor{gray!6}{Black} & \cellcolor{gray!6}{\num{1.274}* (\num{0.625})}\\
Native American & \num{0.405} (\num{0.710})\\
\cellcolor{gray!6}{Asian} & \cellcolor{gray!6}{\num{0.105} (\num{0.588})}\\
Hispanic or Latino/x & \num{0.425} (\num{0.271})\\
\cellcolor{gray!6}{Num.Obs.} & \cellcolor{gray!6}{\num{948}}\\
\midrule
$R_{McFadden}^2$ & \num{0.110}\\
\cellcolor{gray!6}{BIC} & \cellcolor{gray!6}{\num{988.1}}\\
Log.Lik. & \num{-442.618}\\
\bottomrule
\multicolumn{2}{l}{\rule{0pt}{1em}Raw, Unexponentiated Coefficients}\\
\multicolumn{2}{l}{\rule{0pt}{1em}* p $<$ .05. ** p $<$ .01. *** p $<$ .001 (two-tailed test).}\\
\end{tabular}
\end{table}

\begin{figure}

{\centering \includegraphics[width=0.8\linewidth]{dissertation_files/figure-latex/plot-model-1-1}

}

\caption{Plot of Coefficients, Model 1}\label{fig:plot-model-1}
\end{figure}

Table \ref{tab:table-model-1} provides the results of my logistic regression
analysis predicting whether someone sought information about Covid-19. These
initial results suggest similar results for each vehicle of information
delivery: each mode of receiving information whether from a doctor, a person,
the news, a social networking site, or an online forum, all increase the odds of
seeking out information. For example, respondents who had received information
from a doctor or other medical professional were 2.82
(relative odds ratio = \(exp(\beta k)\), \emph{p} \textless{} 0.001) times more likely to seek
out information over someone who hadn't. Similarly, respondents who had received
information from `a person like friend, neighbor, or family member that {[}they{]} know'
were 1.87
( \emph{p} \textless{} 0.001) times more likely to seek out information over someone who hadn't
received information from a person like that. Interesting, those who had
received information from an online discussion group, listserve, or other online
forum including a Facebook group or subreddit were
2.39 ( \emph{p} \textless{} 0.001)
times more likely to search out more information than someone who hadn't. While
most demographic variables don't seem to have a strong effect on whether someone
sought out information about the Covid-19 vaccine, a few key variables had strong
associations. Age, for instance, is associated with seeking information; every
additional year of age a person holds they are
3\%
more likely to search for information, possibly indicating a generational effect
of information seeking patterns ( \emph{p} \textless{} 0.01). Additionally, those who were more
educated, that is those with an associate's degree or higher, were
1.58
more likely to seek additional information than those without the degree
( \emph{p} \textless{} 0.05). And finally, there is evidence to suggest that the Black or
African American sample was more likely to seek out information, specifically:
Blacks were 3.58 times more likely
to seek out information over non-Blacks ( \emph{p} \textless{} 0.05). Figure \ref{fig:plot-model-1} illustrates
the relationship between the coefficients and information seeking.

\hypertarget{information-search-vehicles}{%
\subsection{Information Search Vehicles}\label{information-search-vehicles}}

\begin{table}[!h]

\caption{\label{tab:model-2-phi}Phi Coefficient ($\phi$) of binary association between each Information Search Vehicle}
\centering
\begin{tabular}[t]{l|l|r|r|r|r}
\hline
 & Person & Dr & Online Forum & Social Networking Site & Online Search\\
\hline
\cellcolor{gray!6}{Person} & \cellcolor{gray!6}{NA} & \cellcolor{gray!6}{0.28} & \cellcolor{gray!6}{0.172} & \cellcolor{gray!6}{0.275} & \cellcolor{gray!6}{0.216}\\
\hline
Dr & NA & NA & 0.192 & 0.152 & 0.098\\
\hline
\cellcolor{gray!6}{Online Forum} & \cellcolor{gray!6}{NA} & \cellcolor{gray!6}{NA} & \cellcolor{gray!6}{NA} & \cellcolor{gray!6}{0.371} & \cellcolor{gray!6}{-0.073}\\
\hline
Social Networking Site & NA & NA & NA & NA & 0.057\\
\hline
\cellcolor{gray!6}{Online Search} & \cellcolor{gray!6}{NA} & \cellcolor{gray!6}{NA} & \cellcolor{gray!6}{NA} & \cellcolor{gray!6}{NA} & \cellcolor{gray!6}{NA}\\
\hline
\end{tabular}
\end{table}

To further investigate how people search for information, I asked those who had
sought information out intentionally, ``How did you look for information about
the Covid-19 vaccine?'' Because respondents could select as many responses as
applicable, each response is recorded as a dichotomous variable. Table
\ref{tab:table-1-desc} reveals differences in the prevalence of usage of the
various information seeking vehicles: Around 40\% of the sample has inquired for
information from a doctor, a person, or using online search tool (
44\%,
42\%,
41\%) while my
respondents used vehicles like online forums (
27\%) and social
networking sites (18\%)
to seek out information at significantly lower rates. To investigate how each
Information Search Vehicle are related to each other using the Phi Coefficient
(\(\\phi\)) of binary association between each Information Search Vehicle pair.
The Phi coefficient can be interpreted like a correlation coefficient, with
numbers closer to -1 or positive one indicating a very strong relationship
(Warrens 2008). Table \ref{tab:model-2-phi} shows the results of these
coefficients. Out of the five information search vehicles investigated, there is
evidence that the vehicles are distinctly different concepts because most
coefficients fall under 0.3, the general rule of thumb for correlation
coefficients to indicate a relationship. There does seem to be a relationship
between Online Forums and Social Networking Sites, possibly due to an
individual's propensity to use online networks over in-person networks. These
coefficients indicate a weak relationship between any two vehicles of
information search and that respondents in my sample utilize each of these a
little bit differently.

\begin{table}[!h]

\caption{\label{tab:table-model-2}What predicts someone intentionally searched for information, by vehicle of information search}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{llllll}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{5}{c}{Dependent Variable} \\
\cmidrule(l{3pt}r{3pt}){2-6}
  & Doctor & Person & Online Forum & Social Networking Site & Online Search\\
\midrule
\cellcolor{gray!6}{Received Info, Doctor} & \cellcolor{gray!6}{\num{1.942}***} & \cellcolor{gray!6}{\num{1.124}***} & \cellcolor{gray!6}{\num{0.181}} & \cellcolor{gray!6}{\num{0.540}**} & \cellcolor{gray!6}{\num{0.430}**}\\
Received Info, Person & \num{0.800}*** & \num{1.199}*** & \num{0.728}*** & \num{0.281} & \num{0.365}*\\
\cellcolor{gray!6}{Received Info, News} & \cellcolor{gray!6}{\num{0.437}**} & \cellcolor{gray!6}{\num{0.100}} & \cellcolor{gray!6}{\num{0.359}*} & \cellcolor{gray!6}{\num{0.514}*} & \cellcolor{gray!6}{\num{1.091}***}\\
Received Info, Social Networking Site & \num{-0.130} & \num{0.437}** & \num{-0.603}** & \num{0.731}*** & \num{1.272}***\\
\cellcolor{gray!6}{Received Info, Online Forum} & \cellcolor{gray!6}{\num{0.412}*} & \cellcolor{gray!6}{\num{0.263}+} & \cellcolor{gray!6}{\num{1.266}***} & \cellcolor{gray!6}{\num{0.974}***} & \cellcolor{gray!6}{\num{0.695}***}\\
Age & \num{0.002} & \num{0.001} & \num{-0.007} & \num{-0.003} & \num{0.029}***\\
\cellcolor{gray!6}{Associate's Deg or above} & \cellcolor{gray!6}{\num{0.542}**} & \cellcolor{gray!6}{\num{0.154}} & \cellcolor{gray!6}{\num{1.086}***} & \cellcolor{gray!6}{\num{1.344}***} & \cellcolor{gray!6}{\num{-0.952}***}\\
White & \num{0.631} & \num{0.245} & \num{0.009} & \num{0.559} & \num{0.012}\\
\cellcolor{gray!6}{Black} & \cellcolor{gray!6}{\num{0.366}} & \cellcolor{gray!6}{\num{0.208}} & \cellcolor{gray!6}{\num{0.608}} & \cellcolor{gray!6}{\num{0.646}} & \cellcolor{gray!6}{\num{0.357}}\\
Native American & \num{0.309} & \num{-0.696} & \num{0.209} & \num{0.762} & \num{-0.831}\\
\cellcolor{gray!6}{Asian} & \cellcolor{gray!6}{\num{-0.294}} & \cellcolor{gray!6}{\num{-0.566}} & \cellcolor{gray!6}{\num{-2.496}**} & \cellcolor{gray!6}{\num{-0.568}} & \cellcolor{gray!6}{\num{0.634}}\\
Hispanic or Latino/x & \num{0.324} & \num{0.116} & \num{0.529}* & \num{0.632}** & \num{-0.585}*\\
\cellcolor{gray!6}{Num.Obs.} & \cellcolor{gray!6}{\num{948}} & \cellcolor{gray!6}{\num{948}} & \cellcolor{gray!6}{\num{948}} & \cellcolor{gray!6}{\num{948}} & \cellcolor{gray!6}{\num{948}}\\
\midrule
$R_{McFadden}^2$ & \num{0.193} & \num{0.121} & \num{0.145} & \num{0.154} & \num{0.221}\\
\cellcolor{gray!6}{BIC} & \cellcolor{gray!6}{\num{1152.2}} & \cellcolor{gray!6}{\num{1237.6}} & \cellcolor{gray!6}{\num{1048.0}} & \cellcolor{gray!6}{\num{864.8}} & \cellcolor{gray!6}{\num{1104.6}}\\
Log.Lik. & \num{-524.709} & \num{-567.376} & \num{-472.576} & \num{-380.971} & \num{-500.907}\\
\bottomrule
\multicolumn{6}{l}{\rule{0pt}{1em}Raw, Unexponentiated Coefficients}\\
\multicolumn{6}{l}{\rule{0pt}{1em}* p $<$ .05. ** p $<$ .01. *** p $<$ .001 (two-tailed test).}\\
\end{tabular}}
\end{table}

Results of each logistic regression are displayed in Table \ref{tab:table-model-2}.
Modeling each response as a separate formula is useful for interpretation, but
there are important caveats: because each logistic regression is on a different
scale, one must not compare the magnitude of coefficients between models. We
can, however, use the direction and significance of the coefficients to draw
conclusions about these different forms of information search vehicles.

The first model in Table \ref{tab:table-model-2} predicts whether a
respondent sought information intentionally about Covid-19 vaccinations by
asking their doctor or another health professional. First and foremost, I find
that those who received information about Covid-19 vaccinations were
6.97 times
more likely to seek out more information from their doctor than those who had
not ( \emph{p} \textless{} 0.001). However, receiving information from other vehicles also
increased the odds of seeking out information from medical professions. Those who
received information from a person like a friend or a relative were
2.23 times
more likely to ask their doctor ( \emph{p} \textless{} 0.001), while those who received
information from the news or television were
1.55
times more likely ( \emph{p} \textless{} 0.01). I also find that those who received information
from an online forum like a subreddit were
51\%
more likely to ask their doctors than those who hadn't ( \emph{p} \textless{} 0.05). Finally,
respondents with an associate's degree or higher were
72\%
more likely to ask their doctor for information on the Covid-19 vaccinations
than those who held less education ( \emph{p} \textless{} 0.01).

The second model predicts whether a respondent sought information about
Covid-19 vaccinations by asking a person like friend, neighbor, or family member
that they know. Only three coefficients in this model were significant and help
us draw any conclusions on who is most likely to activate their personal social
network for informational support. In this study, I find that receiving
information about the vaccine from a doctor, their personal network, or a social
networking site is associated with seeking out more information. Those who
received information from a doctor or other medical professional were
3.08
times more likely to seek information from a person like a friend ( \emph{p} \textless{} 0.001).
Moreover, it seems that receiving information from your personal social network,
like a friend or relative, is associated with seeking information from those
same people; in fact, I find that those who did are
3.32 more
likely to do so ( \emph{p} \textless{} 0.001). Finally, the respondents who received information
about the vaccine on a social networking site were
55\%
more likely to seek information from their personal network than those who hadn't
( \emph{p} \textless{} 0.01). The unexpected result of this model is that very few factors predict
personal social network activation, and this model has the lowest McFadden's R\^{}2,
indicating possible omitted variables.

I also wanted to see what was associated with posting in an online discussion
group, listserve, or other online forum like a Facebook Group or Subreddit about
Covid-19 vaccinations. This is conceptually different that posting a query on a
social networking site like Facebook or twitter where identities are involved,
but is theoretically more {[}costly?{]}{[}friction?{]} than searching on an internet
search engine. I found that having received information about the vaccine from
your personal social network (like a friend or relative), the news, or an online
forum was associated with higher odds of querying an online forum. Specifically,
receiving information from your personal network is associated with
2.07
higher odds ( \emph{p} \textless{} 0.001), from news or television media with 1.43 higher odds ( \emph{p} \textless{} 0.05), and
receiving information on an online forum associated with
3.55
higher odds ( \emph{p} \textless{} 0.001). Moreover, I found that those with an associate's
degree or above were
2.96 times
more likely to search for information on an online forum ( \emph{p} \textless{} 0.001). Finally,
I found a racial-ethnic with Hispanic-Latinos; I found that they were about
70\%
more likely to query an online forum than non-Hispanics ( \emph{p} \textless{} 0.05). However,
there were also a few variables that lowered the odds of posting in an online
discussion group. First, those who had received information from a social
networking site were
45\%
less likely to query a forum than those who hadn't (relative odds ratio =
\(1 - exp(\beta k)\), \emph{p} \textless{} 0.01). Moreover, I find more ethnoracial effects:
Respondents who claimed Asian ancestry were
92\%
less likely to query online forum ( \emph{p} \textless{} 0.01).

The fourth model predicts whether an individual sought information about
Covid-19 vaccinations through posted queries on a social networking site such
as Facebook timeline, Twitter status update, or LinkedIn. Receiving information
about Covid-19 seems to be quite related to posting on social media. Those who
received information from their doctor's had
1.72
higher odds of posting on a social networking site ( \emph{p} \textless{} 0.01), while those
who received their information from tv/news had 1.67 higher odds ( \emph{p} \textless{} 0.05).
Furthermore, those who received information on social networking sites were more
likely to post queries on social networking sites (\(\beta\) =
2.08, \emph{p} \textless{} 0.001).
The respondents in our sample who received information on online forums had
2.65
higher odds of posting queries on their social networking platforms ( \emph{p} \textless{} 0.001).
I found a relationship between education and posting on social networking sites
as well; specifically, those with an Associate's degree or above were 3.83 times more likely to post vaccination
queries on social networking sites than those with lower education ( \emph{p} \textless{} 0.001).
Finally, I find that Hispanic-Latinos were
88\%
more likely to ask their connections on a social networking site about the
Covid-19 vaccinations than non-Hispanics ( \emph{p} \textless{} 0.01).

Searching for information using an online search engine such as Google or Bing
is theoretically the search vehicle with the least amount of social or cognitive
friction. Our descriptive statistics showed that not everyone used this vehicle,
with only 41\% of our sample (See Table \ref{tab:table-1-desc}) having sought
information about the Covid-19 vaccines using online search engines. My model
reveals interesting patterns to help explain the variation. As with previous
models, receiving information of any kind increase the odds of online search,
though to varying magnitudes (Doctor:
1.54 odds;
Person:
1.44 odds;
News or Television:
2.98 odds;
Social Networking Site:
3.57 odds;
Online Forum:
2 odds).
I also find that older respondents were more likely to search online, with each
addition year aged to yield
3\%
higher odds of searching online ( \emph{p} \textless{} 0.001). The most interesting variations
come from what decreases the odds of online search. First, those with an
Associate's degree or higher were
61\%
less likely to search online for questions about Covid-19 than those with less
educational attainment ( \emph{p} \textless{} 0.001). In addition, I find that Hispanic-Latinos
had 44\%
lower odds of searching online than non-Hispanics ( \emph{p} \textless{} 0.05).

\hypertarget{vaccination-views}{%
\subsection{Vaccination Views}\label{vaccination-views}}

\begin{table}[!h]

\caption{\label{tab:table-model-3}Does receiving or searching for information predict vaccination status?}
\centering
\begin{tabular}[t]{lc}
\toprule
  & Model 1\\
\midrule
\cellcolor{gray!6}{Received Info, Doctor} & \cellcolor{gray!6}{\num{1.049}*** (\num{0.301})}\\
Received Info, Person & \num{-0.206} (\num{0.242})\\
\cellcolor{gray!6}{Received Info, News} & \cellcolor{gray!6}{\num{0.108} (\num{0.247})}\\
Received Info, Social Networking Site & \num{-0.794}*** (\num{0.240})\\
\cellcolor{gray!6}{Received Info, Online Forum} & \cellcolor{gray!6}{\num{-0.321} (\num{0.248})}\\
Sought Info, Doctor & \num{1.386}*** (\num{0.341})\\
\cellcolor{gray!6}{Sought Info, Person} & \cellcolor{gray!6}{\num{0.570}* (\num{0.285})}\\
Sought Info, Social Networking Site & \num{0.710} (\num{0.466})\\
\cellcolor{gray!6}{Sought Info, Online Forum} & \cellcolor{gray!6}{\num{0.354} (\num{0.342})}\\
Sought Info, Online Search & \num{0.085} (\num{0.260})\\
\cellcolor{gray!6}{Age} & \cellcolor{gray!6}{\num{-0.018}+ (\num{0.011})}\\
Associate's Deg or above & \num{1.281}*** (\num{0.234})\\
\cellcolor{gray!6}{White} & \cellcolor{gray!6}{\num{1.122} (\num{0.767})}\\
Black & \num{0.808} (\num{0.799})\\
\cellcolor{gray!6}{Native American} & \cellcolor{gray!6}{\num{0.126} (\num{0.829})}\\
Asian & \num{1.555}+ (\num{0.918})\\
\cellcolor{gray!6}{Hispanic or Latino/x} & \cellcolor{gray!6}{\num{1.039}* (\num{0.505})}\\
Num.Obs. & \num{936}\\
\midrule
\cellcolor{gray!6}{$R_{McFadden}^2$} & \cellcolor{gray!6}{\num{0.261}}\\
BIC & \num{669.2}\\
\cellcolor{gray!6}{Log.Lik.} & \cellcolor{gray!6}{\num{-266.187}}\\
\bottomrule
\multicolumn{2}{l}{\rule{0pt}{1em}Raw, Unexponentiated Coefficients}\\
\multicolumn{2}{l}{\rule{0pt}{1em}* p $<$ .05. ** p $<$ .01. *** p $<$ .001 (two-tailed test).}\\
\end{tabular}
\end{table}

Finally, in Table \ref{tab:table-model-3}, I investigate whether there is a
relationship between information receiving and information seeking behaviors and
the choice to get vaccinated against Covid-19 through a logistic regression
model predicting Vaccination Outlook. I find that receiving information from a
doctor or other medical profession is associated with
2.85 odds of receiving
a Covid-19 vaccinated ( \emph{p} \textless{} 0.001) and that seeking information from a doctor
also increases the odds of vaccination by
4 ( \emph{p} \textless{} 0.001).
I find that my respondents who received information on a social networking site
like Facebook or Twitter about the vaccines were
55\%
\textbf{less likely} to get vaccinated than those who received no information through
that vehicle ( \emph{p} \textless{} 0.001). However, I did find that those who reached out to
family or friends with their concerns were
77\% more likely
to become vaccinated ( \emph{p} \textless{} 0.05). Furthermore, my respondents who held an
Associate's degree or above had 3.6
higher odds of becoming immunized ( \emph{p} \textless{} 0.001). And finally, I found further
ethnoracial differences in my sample. I found that Hispanic-Latinos had
2.83 higher odds of vaccination
than non-Hispanics ( \emph{p} \textless{} 0.05) and that my Asian sample had
4.73 higher odds as well over
non-Asians ( \emph{p} = 0.09). See Figure \ref{fig:plot-model-3} for a visual
representation of how these different coefficients are related to vaccination
outlook.

\begin{figure}

{\centering \includegraphics[width=0.8\linewidth]{dissertation_files/figure-latex/plot-model-3-1}

}

\caption{Plot of Coefficients, Model 3}\label{fig:plot-model-3}
\end{figure}

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

Previous research in Sociology and Infodemiology has greatly failed to
distinguish between the activation of information seeking behaviors online and
offline. In this paper, I aim to uncover just how different various methods of
information search are and begin a line of research inquiry that investigates
the factors associated with each different vehicle. Finally, I also aimed to
uncover how the different fountains of information and information search
vehicles hold real world consequences through their associations with Covid-19
vaccination rates and intentions.

I first find that receiving information about Covid-19 vaccinations from any
outlined source increases the likelihood of searching out more information. I
also find important demographic differences in the overall propensity to seek
out information. First, I find that the older a respondent is, the more likely
they are to seek out information about Covid-19 vaccinations, possibly
indicating a larger information need by elderly populations overall, or a more
pressing need to search for information about the Covid-19 vaccinations because
of the higher risk of hospitalizations that older populations face
(Turner et al. 2018). Furthermore, I find that those who are college educated were
more likely to seek out information; for the most part this trend can be
observed in Table \ref{tab:table-model-2} as well. Human Capital Theory
(Mirowsky and Ross 1998) may help to explain this finding; this theory claims that
higher education can provides the skills to gain health-related knowledge and
use this knowledge to be proactive in their own lives. Finally, I find that my
respondents who identified as Black were more likely to seek out further
information; this may be explained by the maltreatment that African Americans
have endured in the US healthcare system (Bailey et al. 2017)
which has led to major distrust of the medical establishment among the
population (Bronson and Nuriddin 2014; Center 2019; Murray 2015).

Table \ref{tab:table-model-2} further demonstrated important takeaways about
how individuals seek information. First, I find that the different information
seeking vehicles queried in this survey are conceptually different and that the
utilization of different varies by demographic and supply (information fountain?
\textasciitilde{} source of having receiving information). Overall, receiving information about
Covid-19 vaccination generally is associated with information seeking behaviors,
though there are key variations. First, if you received information from a
doctor, you were likely to search from information from a doctor; this may
indicate an already existing trusting relationship between patient and
healthcare provider but it may also indicate the healthcare provider taking
initiaive and emphasizing the importance of the vaccine or the survey respondent
seeking out information from an expert. Another important finding is that if you
received information from a Social Networking Site like Facebook or Twitter, you
were less likely to query Online Forums like Reddit or Facebook Groups; this may
be an example of Uses and Gratification Theory
(Blumler and Katz 1974), where the two online platforms may act as
substitute sources of information and those who were satisfied with the
information they received on a Social Networking Site didn't have the need to
seek out more information. Finally, the ethnoracial variations exhibited in
Table \ref{tab:table-model-2} likely demonstrate how cultural attitudes around
the trustworthiness of different sources of information affect the utilization
of different methods; for example, Asians seem are less likely to use online
forums than non-Asians while Hispanics are more likely to use them than
non-Hispanics. The internal variations between the different information search
vehicles hint at different user profiles and may have major repercussions on the
quality of information they find and who is exposed to poor quality information.

Given the rampant misinformation around Covid-19, her related vaccinations
(Motta, Stecula, and Farhart 2020; Pathak, Agarawalla, and Gupta 2020; Shahsavari et al. 2020) and the slowed rate of vaccinations in the
United States, it is important to uncover what relationship the different
fountains of information and information search vehicles for Covid-19 vaccinations
are associated with compliance with public health recommendations. Table
\ref{tab:table-model-3} demonstrated just how these different fountains of
information and information search vehicles are associated with real world
consequences through Covid-19 vaccination rates and intentions. The first
takeaway is that receiving or seeking information from a doctor or other medical
profession was associated with higher likelihood of completed or planned vaccinations.
While blanket advice like ``Healthcare Providers should recommend the vaccine to
their patients'' would be ineffective because of the declining number of
Americans with a primary care doctor (Levine, Linder, and Landon 2020), increasing trust in the
institution of medicine seems to remain a strong predictor of vaccinations.
A second major takeaway is that receiving information from a Social Networking
Site like Facebook timeline or Twitter status update was significantly
associated with lower vaccination rates. While we don't know what exact
information was absorbed on these platforms, the lower odds of vaccination
indicate that it was not positive. Much has been attempted between 2020 and 2022
to curb vaccine misinformation on these social networking platforms (see Bowman 2020 for an early example); however, I find evidence that these social
networking platforms nevertheless have a measurable negative impact. Finally,
this study also contributes to the conversation on ethnoracial and
educational differences in vaccine hesitancy. I find in my sample that
Hispanic-Latinos and Asians were more likely than non-Hispanics and non-Asians
to receive or plan to receive a vaccination against Covid-19 (Table
\ref{tab:table-model-3}). Research in this area has mixed results, with some
studies showcasing consistent findings to these (Bagasra, Doan, and Allen 2021; King et al. 2021),
while others show that Whites have the lowest levels of vaccine hesitancy and
many minorities are much more hesitant (Foxworth 2021; Momplaisir et al. 2021). My finding that college-educated respondents were more likely seek
vaccination is largely consistent with the broader literature
(Khairat, Zou, and Adler-Milstein 2022), though again there are many variations depending on the vaccine
in question and study context (Siddiqui, Salmon, and Omer 2013).

\hypertarget{conclusion}{%
\section{Conclusion}\label{conclusion}}

Previous research has greatly failed to distinguish between the activation of
information seeking behaviors online and offline and largely focuses on the
information that is sent to consumers {[}push{]}, seeing people as passive receivers
of information. In this paper, I instead focus on individuals as active agents
in their search for information to begin a line of research inquiry that
investigates the factors associated with the various methods of information
search.

Given the large swaths of both misinformation and disinformation regarding
Covid-19 (Motta et al. 2020; Pathak et al. 2020; Shahsavari et al. 2020) and the measurable impacts this
misinformation has had on pandemic-related health behaviors
(Loomba et al. 2021), Covid-19 provides an ideal study to
investigate how we choose to search for information that affects both our own
lives and the lives of others.

This paper has provided several key findings that can be used to motivate policy
interventions for the Covid-19 vaccination campaigns and in the future for other
information campaigns. However, these findings are not to be taken out of the
context of their limitations. This paper is built off a small survey sample (
948) that was hosted online and anonymously through MTurk, a service
that provides people with micro-jobs. Because of how the website is set up,
respondents are incentivized to fill out surveys as quick as possible and there
were many responses that were poor quality and removed from the sample before
analysis. Because of this, there is no incentive for respondents to be honest in
these surveys. However, each of these limitations are often pointed to as
limitations of survey research as a whole. Even given these limitations,
the finding of this paper are interesting contributions to the literature.

Overall, this research project is important because the vehicles used in
information search impacts the information and quality of information found. By
looking at how individuals search, I aim to identified pain points and focus areas
for future interventions (receiving information online; ethnoracial variations; ) in the misinformation process.

### 2022-03-02 paper2appendix.tex
Initial Overleaf Import

\newpage

\hypertarget{appendix-1-survey-questions}{%
\section{Appendix 1: Survey Questions}\label{appendix-1-survey-questions}}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\emph{Q181}: Now, we're going to transition a bit to ask you about the information you received during the Covid-19 pandemic.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\emph{Q170}: In the past 12 months, without searching for it, did you receive information about the Covid-19 vaccine from \ldots{} (check all sources you received information from)

\begin{itemize}
\tightlist
\item
  your doctor or other health professional? (1)
\item
  a person like friend, neighbor, or family member that you know ? (9)
\item
  From television news channel or the newspaper? (10)
\item
  From an online discussion group, listserve, or other online forum including a Facebook group or subreddit? (11)
\item
  From a social networking site such as Facebook timeline, Twitter status update, or LinkedIn? (12)
\item
  Other (13) \_\_\_\_\_\_\_
\end{itemize}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\emph{Q171}: And how about you yourself intentionally looking for information about a Covid-19 vaccine? Such information can include things such as advice, clarification, facts, and experiences.

\begin{itemize}
\tightlist
\item
  Yes (4)
\item
  No (5)
\end{itemize}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\emph{Q172}: How did you look for information about the Covid-19 vaccine?

\begin{itemize}
\tightlist
\item
  Asking a person like friend, neighbor, or family member that I know (1)
\item
  Asking my doctor or another health professional (4)
\item
  Posted queries in an online discussion group, listserve, or other online forum like a Facebook Group or Subreddit (5)
\item
  Posted queries on a social networking site such as Facebook timeline, Twitter status update, or LinkedIn (6)
\item
  Searched for my question using an online search engine such as Google or Bing (7)
\item
  Other (8) \_\_\_\_\_\_\_\_\_\_\_
\end{itemize}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\emph{Q173}: What sort of information did you search for?
Separate different topics with a comma or semi-colon.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\emph{Q174}: How useful was the information you found?

\begin{itemize}
\tightlist
\item
  Extremely useful (22)
\item
  Very useful (23)
\item
  Moderately useful (24)
\item
  Slightly useful (25)
\item
  Not at all useful (26)
\end{itemize}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\emph{Q175}: Did the information you learned affect your decision to get vaccinated against Covid-19?

\begin{itemize}
\tightlist
\item
  Yes (39)
\item
  No (40)
\end{itemize}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\emph{Q179}: Did you receive a Covid-19 vaccine?

\begin{itemize}
\tightlist
\item
  Yes (9)
\item
  No (10)
\item
  I'm unsure or would not like to respond (11)
\end{itemize}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\emph{Q180}: Do you plan to receive a vaccine for the prevention of the Covid-19 virus?

\begin{itemize}
\tightlist
\item
  Definitely not (9)
\item
  Probably not (10)
\item
  Might or might not (11)
\item
  Probably yes (12)
\item
  Definitely yes (13)
\item
  I would not like to respond (14)
\end{itemize}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\emph{gender}: What is your gender?

\begin{itemize}
\tightlist
\item
  Male (1)
\item
  Female (2)
\item
  Other (3) \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
\item
  Prefer not to say (4)
\end{itemize}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\emph{hispanic}: Are you Hispanic, Latino/a/x, or Latin American Origin?

\begin{itemize}
\tightlist
\item
  Yes (1)
\item
  No (2)
\end{itemize}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\emph{race}: What is your race? If you are ``mixed race,'' select all that apply.

\begin{itemize}
\tightlist
\item
  White (1)
\item
  Black or African American (2)
\item
  American Indian or Alaskan Native (3)
\item
  Asian (please specify): (4) \_\_\_\_\_\_\_
\item
  Other (please specify): (5) \_\_\_\_\_\_\_
\item
  Prefer not to say (6)
\end{itemize}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\emph{educ}: What is the highest level of education that you have completed?

\begin{itemize}
\tightlist
\item
  Less than high school (1)
\item
  High school graduate (2)
\item
  Some college (3)
\item
  Associate's or Technical degree (4)
\item
  Bachelor's degree (5)
\item
  Graduate or professional degree (6)
\end{itemize}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\emph{income}: We would be interested to know roughly what your total household income
before taxes is. We mean income from all sources, including welfare, stock
dividends, other household members' income, etc. In 2020, in which bracket did your total family income fall?

\begin{itemize}
\tightlist
\item
  Under \$1,000 (1)
\item
  \$1,000 to \$9,999 (2)
\item
  \$10,000 to \$19,999 (3)
\item
  \$20,000 to \$29,999 (4)
\item
  \$30,000 to \$39,999 (5)
\item
  \$40,000 to \$49,999 (6)
\item
  \$50,000 to \$59,999 (7)
\item
  \$60,000 to \$74,999 (8)
\item
  \$75,000 to \$89,999 (9)
\item
  \$90,000 to \$109,999 (10)
\item
  \$110,000 to \$129,999 (11)
\item
  \$130,000 to \$149,999 (12)
\item
  \$150,000 or over (13)
\item
  Don't know (14)
\end{itemize}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\emph{age}: What is your age? (in years)

### 2022-03-02 paper3.tex
Initial Overleaf Import

\hypertarget{paper-3}{%
\chapter{Social Norms under Uncertain Times: A dynamic study of Stay-At-Home and Vaccination Rates During the Covid-19 Pandemic}\label{paper-3}}

\hypertarget{abstract-1}{%
\section{Abstract}\label{abstract-1}}

This paper examines how social norms are formed under conditions of uncertainty
using the case studies of stay-at-home and vaccination rates during the Covid-19
pandemic. I test fear-based models of behavioral adaption to public health
recommendations as well as patterns of complex social contagion using linear
mixed effects models. These models show that complex contagion is a valid
framework for the social contagion of new norms during Covid-19. However, I find
important moderating effect of signal discordance, the contextual diversity of
signals received by an ego.

Keywords: Social Networks, Social Norms, Health Behavior, Diffusion, Contagion

TODO
Mirbabaie et al. (2020)
@ TERNULLO

\hypertarget{background}{%
\section{Background}\label{background}}

After spreading around the world in a matter of months, the coronavirus
(COVID-19) became a leading cause of death in the United States. Although the
Centers for Disease Control and Prevention(CDC)
(2020) proposed several potential
mitigation strategies, the method of mitigation that received the most national
attention is the call to stay-at-home and social distance for non-essential
workers. CDC officials and frontline health care professionals advise that the
best way to prevent exposure to the virus is to stay at home and avoid close
contact with people.

A second strategy pushed by the CDC, once available, was to receive vaccination
to prevent the effects of the Covid-19 virus if infected. Vaccinations like
Pfizer-BioNTech (Comirnaty, tozinameran, BNT162b2), and Janssen/Johnson \&
Johnson, Moderna (mRNA-1273) started receiving approval for emergency use
authorization by the United States Food and Drug Administration (FDA) in
December 2020.

Although these public health interventions were pushed by policy makers
throughout 2020 and 2021, policy makers often struggle to promote public
adoption of policies that rely on the publics' willingness to adjust their
current `risky' behaviors to less-risk behaviors based on scientific facts. The
lack of adaption to newly recommended behaviors is partially due to the
variation in how individuals came to understand the threats of the disease
(Akpan et al. 2021; Bailey et al. 2020), but also due to habitus: the
ingrained habits, skills and dispositions of individuals and groups
(Bourdieu 1977). Habitus shapes how individuals perceive different social
interactions and norms and shape how they adopt different policies, leading to
different social outcomes and a divergence of attitudes (Madeira et al. 2018; Scott-Arthur, Brown, and Saukko 2021; Williams 1995).

There is little research on stay-at-home rates, especially in cases of pandemics
or disasters. Though research on the causes of population mobility did expand
after the onset of the Covid-19 pandemic (Bargain and Aminjonov 2020; Bourassa 2020; Bourassa et al. 2020; Grossman et al. 2020; Hagger et al. 2020; Hill, Gonzalez, and Burdette 2020; Hill, Gonzalez, and Davis 2021; Hill, Gonzalez, and Upenieks 2021; Huynh 2020), most research focused on unchanging cultural
determinants of the reduction in stay-at-home rates. For instance,
Gibbons, Yang, and Oren (2021) finds that social capital had spatially inconsistent effects on
stay-at-home rates. Instead of focusing on cultural relationships with
stay-at-home rates, this paper will instead focus on the dynamic nature of
population mobility across population networks.

There is more research on vaccine uptake
(Schmid et al. 2017) because of increased hesitancy and
anti-vaccination movements over previous decades
(Baumgaertner, Carlisle, and Justwan 2018; Hornsey et al. 2020; Johnson et al. 2020; Whitehead and Perry 2020). While some studies use social network analysis to
study the discussions for an against vaccinations online
(Milani, Weitkamp, and Webb 2020), vaccination rates are a great way to
investigate the establishment of new social norms. First, vaccination uptake is
measurable with stable information tracking infrastructure and vaccination
rates are varied across locations and time. Secondly, because vaccines have
become politicized (Motta 2021; Motta et al. 2021), the social contagion effects can be
studied.

This article researches the formation of social norms governing health behaviors
in cases of extreme uncertainty during the Covid-19 pandemic. Using theories of complex
contagion, associative diffusion and the integrated theoretical framework of
norms, I test how these health behaviors are outcomes of contagion and
discordance of signals, as well as other factors affecting associations like
religious and political conservatism, attention to television media sources,
and online norms as measured by information-search behaviors. Before outlining
my central hypotheses, I offer an overview of the current state of the social
contagion literature. After that, I will outline how I compiled this unique
longitudinal data set from Google, the CDC, Facebook and other sources and how I
define and calculate signal and discordance, two key independent variables for
this paper. To model stay-at-home and vaccination rates, I use linear mixed effects
models with random effects as a longitudinal model of contagion. After
interpreting the results of the models, I discuss the implications of these
findings for the sociological understanding of social contagion and the
formation of social norms.

\hypertarget{the-social-contagion-model}{%
\subsection{The Social Contagion Model}\label{the-social-contagion-model}}

Individuals engage with each other and their distributive ties to create
community contexts where norms, beliefs, and values circulate. These clusters of
interaction are called social networks, and if ``each person continues to
interact primarily with others nearby in space, the forces of conformity will be
strongest locally, leading to the emergence of clusters of people sharing
similar behavior'' (Kitts and Shi 2018). This community
interaction ultimately leads to converged communities of belief structures with
variations in how much they diverge from the norm (Cullum and Harton 2007; Latané and Bourgeois 1996; Okada 2017).

``Culture'' diffuses through communities and social networks. Information and
opinions spread (Robert M. Bond et al. 2012b; Fowler and Christakis 2010; Klar and Shmargad 2017), behaviors are adopted
(Aral and Nicolaides 2017; Centola 2010, 2011; Christakis and Fowler 2008; Rosenquist et al. 2010) , and there are patterns of health
contagion (Cacioppo, Fowler, and Christakis 2009; Christakis and Fowler 2007). However,
``different things spread in different ways and to different extents''
(Christakis and Fowler 2013, p 563) and when modeling diffusion and
contagion, we must be very specific about our scope conditions as they are
relevant to our theory and not to cross theories to infer connections where they
may not exist (Kitts and Quintane 2020).

Most of the diffusion literature does not focus on establishment of new norms
but the adoption of culture and specific deviant behaviors (see
Centola and Baronchelli (2015) for an exception). DellaPosta and
colleagues (2015) outline how the spread of culture
and behavior is tied to network autocorrelation, or ``the tendency for people to
resemble their network neighbors.'' They show that the distance between to agents
in sociocultural space can determine the likelihood of the adoption of a new
behavior. Like Axelrod (1997), this outlines
how the local convergence of close network actors becomes amplified and can
lead to global polarization between groups.

Outdated models found in early public health research claim that information
about the risks of behaviors will lead to changes in behaviors to mitigate those
said risks (e.g. Flay, DiTecco, and Schlegel 1980). However, while this model can be valid in specific
cases, more research has shown how the risks themselves do little to motivate
behavioral change (Witte and Allen 2000; Wolburg 2006). Often, an appeal to fear is
found to be a major driver of the adoption of information campaigns and some
research has shown that ``social network exposure to COVID-19 cases shapes
individuals'' beliefs and behaviors concerning the coronavirus''
(Bailey et al. 2020). Because of this, it is logical that higher local incidences of
infection would inspire fear and increase adherence to public health measures
according to this older model.

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\tightlist
\item
  \emph{Hypothesis 1} Relatively higher local rates of infection will lead to increased time spent in residence and increase vaccination uptake
\end{enumerate}

\hypertarget{complex-contagion-and-discordance}{%
\subsection{Complex Contagion and Discordance}\label{complex-contagion-and-discordance}}

Centola and Macy (2007) theorize that simple contagions are not
enough to spread behavioral change. Simple contagions are those in which only
one point of contact is needed to receive contagion, like with infectious
disease or to learn simple bits of information.
Centola and Macy (2007)'s large contribution was the theorizing
of complex contagions, those that require ``independent affirmation or
reinforcement from multiple sources'' (p 703) and is not based on the number of
exposures but the number of sources of exposure. In the case of behavioral
contagion, this means that the behavior must be reinforced through witnessing
multiple alters perform this behavior before contagion can take effect.

In the case of stay-at-home rates or vaccination rates, this theoretically means
that a person exposed to many sources of the same signal (high, medium, low
rates) will be more likely to adopt the behavior based on the reinforcement from
the multiple sources of exposure. As norms are inherently social, I theorize
that we can see complex contagion happening in real time with the following
hypothesis:

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\setcounter{enumi}{1}
\tightlist
\item
  \emph{Hypothesis 2} increased average time spent in residence (signal direction) from alters will have a positive effect on stay-at-home rates the ego-county; increased vaccine uptake by alters will have a positive effect on vaccine uptake for the ego-county
\end{enumerate}

To make the contagion more complex, different sources of exposure
(county-alters) adhere to CDC recommendations to stay-at-home at differing
rates. Whereas one county-alter may be greatly increasing its time in residence,
another may have made little change. When the majority of alters is in
concordance with each other, the signal to the ego is reinforced and more
impactful on the ego. When these signals are mixed with high variance from
different sources, agreement is low and makes the behavioral change less likely.
For this paper, I theorize that a new concept of `discordance' must be
considered as impacting complex contagion. discordance is the variance of
signals received by an alter; high discordance prevents reinforcement while low
discordance (concordance) enables complex contagion. Instead of adopting a
`majority' rules attitude, this means that the more discordance perceived by an
ego, the less likely the alters will have any effect on the ego. I theorize that
the behavior of a county-alter will be positively correlated with the behavior
of another county-ego if the county-ego receives highly discordant signals, as
seen in figure \ref{fig:dag}.

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\setcounter{enumi}{2}
\tightlist
\item
  \emph{Hypothesis 3} the effect of signal direction on time spent in residence and vaccine uptake will be moderated by diversity in signals (discordance)
\end{enumerate}

\begin{figure}

{\centering \includegraphics[width=0.8\linewidth]{G:/My Drive/R/My Projects/dissertation/figure/paper3/dag}

}

\caption{Elaboratory Theoretical Model of Health Behavior Norms}\label{fig:dag}
\end{figure}

\hypertarget{associative-diffusion}{%
\subsection{Associative Diffusion}\label{associative-diffusion}}

While much of the social contagion literature, like the theories above, focuses
on structural boundaries and homophily as causes of how diffusion occurs,
Goldberg and Stein (2018) propose a
disrupting alternative mechanism. They argue that what actually diffuses during
social contagion are the perceptions about which beliefs or behaviors are
compatible with one another, what they call ``associative diffusion.'' This
argument that culture does not spread like a virus but instead is dependent on
how belief structures are connected to each other is important to test because
norms around health behaviors became politicized issues during the Covid-19
pandemic. This means that the stay-at-home or vaccination behavior themselves
were not contagious, but the cognitive association of precisely what social
distancing or vaccination uptake \emph{meant} were spreading between populations of
individuals. Moreover, as Houghton (2021) outlines, diffusants - the things that are
diffusing through a population, are not independent of each other
(Mason, Conrey, and Smith 2007). When we take into account the interdependence between different
beliefs that are diffusing, such as Covid-19 is a hoax, social distancing saves
lives, the Covid-19 vaccine includes a microchip to control your thoughts, and lockdown
is against the rights guaranteed in the US constitution, we can imagine how
these various diffusants become associated together into structures of belief
through schemas of perception (Houghton 2021). While this cognitive theory of
cultural variation is difficult to test, the theory it supplies provides a solid
framework for how behavioral norms formed during the pandemic.

\begin{figure}

{\centering \includegraphics[width=0.8\linewidth]{G:/My Drive/R/My Projects/dissertation/figure/paper3/model}

}

\caption{Preliminary model of norm formation}\label{fig:norm-framework}
\end{figure}

The figure above illustrates how I interpret associative diffusion will impact
stay-at-home and vaccination rates in times of unsettled norms. An
individual enters this framework when they realize they don't have a normative
set of responses in their cultural toolkit to respond to an unfamiliar situation
they are presented with. Individuals look to norms to regulate behavior, avoid
deviance, and to maintain order (Horne and Mollborn 2020; Shepherd 2017); when they don't have a normative behavior
to follow (or rebel against), individuals look to the other sources in their
``community'' to mimic behavior, such as high-status individuals, institutions,
and members of their social network. I theorize that individuals look towards
their physical community, to their social network, popular media (which may
include government and science recommendations), established norms that they may
find online through search, and to the real threat of infection (what would
happen if I do nothing about this norm). Following both the Integrated
Theoretical Framework of Norms (Horne and Mollborn 2020) and
associative diffusion (DellaPosta et al. 2015; Goldberg and Stein 2018), I theorize that individuals interpret
signals from their ``community'' through their cognitive biases and behavioral
predispositions to determine their formation of new behavioral norms.

There is some evidence I can draw upon to support the associative diffusion
fraemwork. For instance, there is a central conflict between religious and
scientific ideologies which I theorize leads more religious counties to reject
the stay-at-home order and vaccines (Evans and Evans 2008)
because the associative diffusion of these behaviors pits public health
recommendations against religious ideologies.
Furthermore, as COVID-19 has become a politically polarizing issue, conservative
ideology and a general mistrust of ``big government'' (Frank 2007; Gauchat 2012) are likely to lead to resistance to the
government and scientific guidance.

\hypertarget{data-and-methods}{%
\section{Data and Methods}\label{data-and-methods}}

This article draws on two unique longitudinal datasets that I compiled for this
analysis from sources like Facebook, Google, CDC, and more. Because the
different datasets were on different scales (individual, zip-code, county,
state, designated market area) and time points (cross-sectional, longitudinal),
there was extensive data wrangling that had to be done to prepare these data for
statistical analysis. The steps taken to prepare each of the different model
features and where the data was sourced from is therefore covered in the
following sections before diving into modeling specifications.

\hypertarget{stay-at-home-rates}{%
\subsection{Stay at Home Rates}\label{stay-at-home-rates}}

\begin{table}[!h]

\caption{\label{tab:google-desc-table}Descriptive Statistics for Stay-at-Home Models (county-level)}
\centering
\begin{tabular}[t]{lrrrr}
\toprule
  & min & max & mean & sd\\
\midrule
Percent White & \num{0.14} & \num{0.98} & \num{0.81} & \num{0.15}\\
Percent College Graduates & \num{0.08} & \num{0.75} & \num{0.26} & \num{0.10}\\
Percent over 65 & \num{6.60} & \num{56.70} & \num{16.90} & \num{4.05}\\
Median Income & \num{28951.00} & \num{142299.00} & \num{59773.61} & \num{15264.50}\\
Monthly Unemployment Rate & \num{1.40} & \num{34.60} & \num{8.12} & \num{4.00}\\
Percent of GOP votes, 2016 & \num{0.08} & \num{0.90} & \num{0.57} & \num{0.15}\\
Percent Evangelical Christian & \num{0.00} & \num{0.67} & \num{0.20} & \num{0.14}\\
'Fox News' Trend & \num{0.00} & \num{204.08} & \num{29.59} & \num{16.94}\\
'Social Distancing' Trend & \num{0.00} & \num{500.00} & \num{20.64} & \num{25.36}\\
'Covid Conspiracy' Trend & \num{0.00} & \num{825.00} & \num{42.51} & \num{80.44}\\
Covid Case Rate & \num{0.00} & \num{343.71} & \num{21.17} & \num{27.44}\\
Week Number & \num{0.00} & \num{43.00} & \num{23.14} & \num{11.77}\\
Movement Signal & \num{-2.06} & \num{26.44} & \num{8.31} & \num{4.22}\\
Movement Discordance & \num{0.15} & \num{11.05} & \num{2.22} & \num{0.80}\\
\bottomrule
\multicolumn{5}{l}{\rule{0pt}{1em}Raw values presented in table. Values in models are normalized.}\\
\multicolumn{5}{l}{\rule{0pt}{1em}Notes: 1,375 counties, March 02 through December 28, 2020.}\\
\end{tabular}
\end{table}
\begin{figure}

{\centering \includegraphics[width=0.8\linewidth]{dissertation_files/figure-latex/plot-google-1}

}

\caption{Stay at Home Rates over Time}\label{fig:plot-google}
\end{figure}

My first dependent variable aims to operationalize behavioral norms as
stay-at-home rates with data from Google (Google 2020). While the Google
COVID-19 Community Mobility Reports include multiple measures of mobility based
on location and activity information, the change in time spent in residence
most closely aligns to an operationalization of an obedience to CDC and governor
orders, a new and emerging norm in 2020. The change in time spent in residence
variable represents percent change of time spent from Google Location History
within geographic areas that Google has designated as a residential area. These
data are aggregated to the county-level based on anonymized sets of data from
users who have turned on the Location History setting, which is off by default.
This means our sample is possibly skewed to people in the United States a) with
a mobile phone, b) with a Google account, and c) with knowledge of how to
synchronize their location history. Google has not made it clear whether there
are any weights in place to correct for these potential biases. Google
calculates the relative change in mobility in comparison to the median value of
movement in the area for the same the corresponding day of the week, during the
5-week period Jan 3--Feb 6, 2020. As Google did not provide data on certain US
counties if they did not have sufficient statistically significant levels of
data, my final county sample is \emph{n} = 1375
(compared to the total population of 3,107 US counties). Particular areas that
are excluded in this analysis include all counties in Alaska and DC, and over
half of the counties in North Dakota, South Dakota. A full list of excluded
counties available upon request. These data are longitudinal measures calculated
by creating a moving average of stay-at-home rates for each county (rolling
window width = 7 days) and then sampling every
Monday in the sample for 44 measures from March 02, 2020 through December 28,
2020.

\hypertarget{covid-vaccination-uptake}{%
\subsection{COVID vaccination uptake}\label{covid-vaccination-uptake}}

\begin{table}[!h]

\caption{\label{tab:vacc-desc-table}Descriptive Statistics for Vaccination Models (county-level)}
\centering
\begin{tabular}[t]{lrrrr}
\toprule
  & min & max & mean & sd\\
\midrule
Percent White & \num{0.08} & \num{1.00} & \num{0.83} & \num{0.17}\\
Percent College Graduates & \num{0.03} & \num{0.78} & \num{0.22} & \num{0.10}\\
Percent over 65 & \num{3.20} & \num{56.70} & \num{18.86} & \num{4.50}\\
Median Income & \num{21504.00} & \num{142299.00} & \num{53522.45} & \num{14312.25}\\
Monthly Unemployment Rate & \num{0.90} & \num{22.00} & \num{4.96} & \num{1.95}\\
Percent of GOP votes, 2020 & \num{0.09} & \num{0.94} & \num{0.64} & \num{0.16}\\
Percent Evangelical Christian & \num{0.00} & \num{1.31} & \num{0.22} & \num{0.16}\\
'Fox News' Trend & \num{5.00} & \num{405.88} & \num{72.12} & \num{27.38}\\
'Covid-19 vaccine' Trend & \num{0.00} & \num{755.56} & \num{74.67} & \num{70.33}\\
'Covid Conspiracy' Trend & \num{0.00} & \num{2000.00} & \num{56.05} & \num{189.61}\\
Covid Case Rate & \num{0.00} & \num{998.58} & \num{22.79} & \num{27.23}\\
Week Number & \num{1.00} & \num{35.00} & \num{18.00} & \num{10.10}\\
Vaccination Signal & \num{0.00} & \num{62.84} & \num{19.62} & \num{14.84}\\
Vaccination Discordance & \num{0.00} & \num{22.40} & \num{5.26} & \num{3.62}\\
\bottomrule
\multicolumn{5}{l}{\rule{0pt}{1em}Raw values presented in table. Values in Models are normalized.}\\
\multicolumn{5}{l}{\rule{0pt}{1em}Notes: 2,819 counties, January 04 through August 30, 2021.}\\
\end{tabular}
\end{table}
\begin{figure}

{\centering \includegraphics[width=0.8\linewidth]{dissertation_files/figure-latex/plot-vacc-1}

}

\caption{Vaccination Rates over Time}\label{fig:plot-vacc}
\end{figure}

The second dependent variable aims to operationalize vaccination uptake through
vaccination rate information in the United States from January 2021 through
August 30 2021 (CDC 2021). Data represents all vaccine partners including
jurisdictional partner clinics, retail pharmacies, long-term care facilities,
dialysis centers, Federal Emergency Management Agency and Health Resources and
Services Administration partner sites, and federal entity facilities.
Vaccination data is available for all US counties with the exception of parts of
California and Massachusetts, Hawaii, and Texas. In Texas and Hawaii, no county
level information is available, and California does not report the county of
residence for vaccinations when the county of residence has a population less
than 20,000 people. Finally, Massachusetts does not provide vaccination data for
Barnstable, Dukes, and Nantucket counties because of their small populations.
Therefore, my final county sample for vaccination rates is \emph{n} = 2819
(compared to the total population of 3,107 US counties). A list of included FIPS
are available upon request. Vaccination rates are scaled with a rolling mean
with a rolling window width of seven days to smooth out intra-week noise. I
sample every Monday between January 2021 through August 30, 2021 for 35 total
observations for each county.

\hypertarget{independent-variables-1}{%
\subsection{Independent Variables}\label{independent-variables-1}}

\hypertarget{network-signal}{%
\subsubsection{Network Signal}\label{network-signal}}

I utilize the likelihood of a friendship connection between counties
to create a county-level social network weighted by the probability of a tie.
Using this network and the two independent variables above, I examine how the
vaccination and stay-at-home rates of peer counties is contagious to the
ego-county. To do this, I first take the weighted average of each ego's network
signals using equation \eqref{eq:networksignal} where \texttt{x} denotes the
vaccination and stay-at-home rates of each alter county and \texttt{w} represents the
likelihood of a friendship connection between the ego county and each of their
alters, lagged by one week. This `signal' of norms gives us insight into the
coevolving contagion patterns of the new social norm being established. The
likelihood of friendship connection comes from the ``Social Connectedness Index''
(Bailey, Rachel Cao, et al. 2018; Facebook 2020) which indexes the social links between geographies by
the likelihood of Facebook friends. It is an aggregated measure of Facebook
friendship connections between counties. It corresponds to ``the (relative)
probability that two arbitrary Facebook users across two geographies are friends
with each other.'' The data is available at various geographic aggregation
levels, such as U.S. zip codes or entire countries. However, data is only
available at one time point because Facebook has found that although there are
individual changes in friendship connections over time, the aggregate
statistical probabilities of friendship remain stable. This measure is based on
user-provided information and real-time location-service data gathered by
Facebook. Facebook data has been shown to be highly representative of the U.S.
population and Facebook friendship links largely represent real-world
friendships (Bailey, Ruiqing Cao, et al. 2018; Jones et al. 2013). The data has been tested to show
how initial COVID-19 hotspots are related to subsequent virus spread to
non-hotspots, even after controlling for population density and geographic
distance (Kuchler, Russel, and Stroebel 2020).

\begin{equation}
signal = \frac{\sum_{i=1}^nw_ix_i}{\sum^n_{i=1}w_i} \label{eq:networksignal}
\end{equation}

\hypertarget{signal-discordance}{%
\subsubsection{Signal Discordance}\label{signal-discordance}}

The second independent variable, \emph{Signal Discordance}, builds on the network
signal but looks specifically at the extent to which a given ego-network
receives diverse contagion signals. Based on the hypothesis that when the
majority of alters is in concordance with each other, the signal to the ego is
reinforced and more impactful on the ego, a high discordance coefficient is
indicative of diverse signals which may prevent any clear interpretation of a
norm developing, whereas a low discordance coefficient would indicate reinforced
signaling. I use the formula to calculate weighted standard deviations, (see equation
\eqref{eq:signaldiscordance}) to provide a metric of a diversity of signals. In
this formula, \texttt{x} denotes the vaccination and stay-at-home rates of each alter
county and \texttt{w} represents the likelihood of a friendship connection between the
ego county and each of their alters, lagged by one week. Furthermore, \(\bar{x}^*\)
represents the weighted mean.

\begin{equation}
discordance = \sqrt{\frac{\sum_{i=1}^nw_i(x_i-\bar{x}^*)^2}{\sum^n_{i=1}w_i}} \label{eq:signaldiscordance}
\end{equation}

Figures \ref{fig:assortativity-vacc} and \ref{fig:discordancenetwork} provide
a visualization of both network signal and signal discordance for April 26, 2021
for 7 selected counties.\footnote{Figures in this paper were all created using ggplot2
  (Wickham 2011; Wickham et al. n.d.), patchwork (Pedersen n.d.), and ggridges (Wilke n.d.)}
While a county like Lake County, Ohio has low discordance meaning the signal of
vaccination rate is reinforced, Navajo County, Arizona receives very diverse
signals from their county-alters, negating any contagion effects. Figure
\ref{fig:discordancenetwork} explicitly outline how the weights and signals are
calculated for an ego with only 5 alters.

\begin{figure}

{\centering \includegraphics[width=0.7\linewidth]{dissertation_files/figure-latex/assortativity-vacc-1}

}

\caption{How Signal Mean and Signal Assortativity are Measured}\label{fig:assortativity-vacc}
\end{figure}

\begin{figure}

\begin{center}\includegraphics[width=0.5\linewidth,]{dissertation_files/figure-latex/discordancenetwork-1} \end{center}
  \begin{equation}
    w = \begin{bmatrix}0.0000015\\0.0000023\\0.0000527\\0.0000966\\0.0001119\end{bmatrix},  
    x = \begin{bmatrix}29.9\\20.4\\27.7\\24.6\\24.3\end{bmatrix} \longrightarrow
    \begin{matrix} \bar{x}, signal = 25.083\\ s, discordance = 1.41 \end{matrix} 
  \end{equation}
  \caption{Visualization of how Network Signal and Discordance are Calculated}
  \label{fig:discordancenetwork}
\end{figure}

\hypertarget{covid-19-case-rates}{%
\subsubsection{Covid-19 Case Rates}\label{covid-19-case-rates}}

To estimate the concept of `real threat of infection' in figure
\ref{fig:norm-framework}, the models use county-level Covid-19 case rates with
data compiled by The New York Times (2022). It is widely acknowledged that there are biases in
this data due to inconsistencies and availability in testing as well as
different community propensity to test (CDC 2020b; Gu n.d.) However, it is the best
measure we have of actual case rates. County data are scaled with a rolling mean
with a rolling window width of seven days to smooth out intra-week noise. Case
Rate is measured as number of cases per 100,000 population. Observations vary
from a minimum of 0 to a maximum of 1,565 across the two datasets.

\hypertarget{online-norms}{%
\subsubsection{Online Norms}\label{online-norms}}

To operationalize the search for online norms, I use Google search trends (Google 2022),
over the study period across individual designated media markets areas (DMAs), a
nonoverlapping aggregation of U.S. counties to 210 media markets based on
similar population clusters (Sood 2016). To investigate the rate of \emph{searching} for norms
online in both cases, I use the following search topics: `Social Distancing'
(2020, stay-at-home case only), `Covid-19 Vaccine' (2021, vaccination uptake case
only) and Covid Conspiracy (2020-2021, both cases). Search topics are a more
robust measurement than a single search term: topics are aggregations of the
rates of multiple, highly correlated search terms together into a cohesive
topic. For example, while `Beyoncé,' `Beyonce' and `beyonce knowles' are all
separate search terms, `Beyoncé Knowles' encompasses all of these into a single
search topic. While the data is originally on a scale of 0 to 100, with
100 being the maximum search popularity out of all DMAs, Google Search Trend are
now only available cross-sectionally (a single time period across a geography)
or time-series (a single geo-location across time). To remedy this and build a
longitudinal dataset of each search topic, I follow the method proposed in
Park, Kwak, and An (n.d.) (p.~5). This method involves building a dataset of unscaled
cross-sectional values, selecting a DMA to use to establish the rescaling ratio
(I use `Los Angeles CA'), and then finding the time-series values for the one
DMA. To find the rescaling ratio for each week in the time-series, you divide
the time-series value for each week by the cross-sectional value for each week,
resulting in a rescaling vector to be used for all weeks in the dataset across
geographies. To rescale each longitudinal value, multiply the respective week's
rescaling ratio by the cross-sectional value. Rescaled longitudinal data was
compared against time-series data for multiple test counties and was equivalent.
For a more in-depth explanation of this procedure, see Park et al. (n.d.) (p.~5).

\hypertarget{pillars-of-convervatism}{%
\subsubsection{Pillars of Convervatism}\label{pillars-of-convervatism}}

Research has shown that stay-at-home rates and other pandemic health behaviors
are related to various `pillars of conservatism' (Gonzalez et al. 2021; Hill et al. 2020; Hill et al. 2021, 2021). Namely, research shows that politically conservative
indicators, such as Republican political leadership, conservative Protestantism
and consumption of right-wing media are related to higher rates of movement and
lower rates of mask usage. Based on these findings, this article controls for
these factors in the following ways: to measure Republican political leadership,
I include percentage of votes for Donald Trump in the previous presidential
election; for the 2020 study, I use the 2016 results and for the 2021 study, I
use the 2020 results to infer proper time ordering. Second, to measure
conservative Protestantism, I employ the county's percentage of evangelical
Christians. These county-level data were collected through the 2010 U.S.
Religion Census: Religious Congregations and Membership Study
(Grammich et al. 2018). Finally, right-wing media consumption is assessed using
Google Search Trends to capture ``Fox News'' searches over the study period across
individual designated media markets areas (DMAs). I use this measure to indicate
active interest in and attention toward Fox News. Google Search Trends have been
validated for use in a range of research contexts and for use with survey data,
voting data, and ecological data (Bail, Brown, and Wimmer 2019; Reyes, Majluf, and Ibáñez 2018; Scheitle 2011; Stephens-Davidowitz 2014; Swearingen and Ripberger 2014).

\hypertarget{demographics}{%
\subsubsection{Demographics}\label{demographics}}

These models also control for (1) percent of the population that is above 65
years old (those most at risk of hospitalization), (2) percent of the population
that identifies as white, (3) percent of the population that holds a college
degree, (4) median income, and (5) monthly county unemployment rate. Measures 1
through 4 are obtained from the 2018 American Community Survey: 5-Year Estimates
(US Census Bureau 2018); unemployment rates are gathered
from the U.S. Bureau of Labor Statistics (Labor Statistics 2021).

\hypertarget{analysis-and-results}{%
\section{Analysis and Results}\label{analysis-and-results}}

My analytic strategy proceeds in four steps. In Tables
\ref{tab:google-desc-table} (Stay-at-Home) and \ref{tab:vacc-desc-table}
(Vaccination Uptake), I present descriptive statistics for all study variables,
including variable ranges, means, and standard deviations across the two cases.
Then, in Tables \ref{tab:google-tab} - \ref{tab:vacc-tab}, I fit a series of
three linear mixed effects regression models using the nlme package in R
(Pinheiro et al. 2021; Pinheiro and Bates 2000) for our two cases, Stay-at-Home rates and
Vaccination rates. Linear mixed effects models are a form of hierarchical linear
models that contain both random and fixed effects. These models treat the
dependent variables as continuous. The following strategies I will outline are
identical for both case studies. Models 1 through 3 address hypotheses 1 through
3 respectively. Each model utilizes normalized independent variables, i.e.
variables that have been centered and scaled to have a mean of 0 and standard
deviation 1. The first model is a baseline linear mixed effects model that
employs all basic controls to predict the dependent variable, allowing both
time-varying and county-level variables to predict the outcome. All variables
have fixed effects, meaning that the county-level exogenous effects are
controlled for when estimating the coefficient. In addition, models are
specified with a random intercept per county. The lme models are set with a
autoregressive correlation structure (\texttt{correlation\ =\ corAR1()}) to control for
temporally autocorrelated error structures; models are also optimized using
Nelder--Mead, quasi-Newton and conjugate-gradient algorithms for box-constrained
optimization and simulated annealing (\texttt{control\ =\ lmeControl(opt\ =\ "optim")}).
This first model will address Hypothesis 1. To test hypothesis 2, I estimate
model 2 which builds on model 1 by first introducing vaccination signal. Because
the signal varies by week, I estimate this model with an interaction between
week and signal. And finally, because signal may have divergent effects across
counties, I set a random effect for signal nested by county. A visual
representation of this interaction can be seen in figures
\ref{fig:plot-google-h2} and \ref{fig:plot-vacc-h2}. Model 3 further
elaborates on the previous model by introducing both a fixed effect for signal
discordance and an interaction term between signal and discordance. Figures
\ref{fig:plot-google-h3} and \ref{fig:plot-vacc-h3} depict just how signal and
discordance interact across these two cases.

\hypertarget{stay-at-home-rate-results}{%
\subsection{Stay-at-Home Rate results}\label{stay-at-home-rate-results}}

\begin{table}[!h]

\caption{\label{tab:google-tab}Linear Mixed Effects Regression Results for Stay-At-Home Rates}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{lccc}
\toprule
  & Model 1 & Model 2 & Model 3\\
\midrule
Percent White & \num{0.088}*** & \num{0.058}** & \num{0.060}**\\
 & (\num{0.023}) & (\num{0.019}) & (\num{0.019})\\
Percent College Graduates & \num{-0.016} & \num{0.010} & \num{0.020}\\
 & (\num{0.028}) & (\num{0.023}) & (\num{0.024})\\
Percent over 65 & \num{-0.034}+ & \num{-0.031}* & \num{-0.037}*\\
 & (\num{0.018}) & (\num{0.015}) & (\num{0.015})\\
Median Income & \num{-0.042} & \num{-0.032} & \num{0.015}\\
 & (\num{0.030}) & (\num{0.024}) & (\num{0.025})\\
Monthly Unemployment Rate & \num{0.087}*** & \num{0.012}*** & \num{0.065}***\\
 & (\num{0.003}) & (\num{0.003}) & (\num{0.004})\\
Percent of GOP votes, 2016 & \num{0.077}* & \num{0.043} & \num{0.017}\\
 & (\num{0.032}) & (\num{0.026}) & (\num{0.027})\\
Percent Evangelical Christian & \num{-0.016} & \num{-0.008} & \num{-0.014}\\
 & (\num{0.022}) & (\num{0.018}) & (\num{0.019})\\
'Fox News' Trend & \num{-0.030}*** & \num{-0.028}*** & \num{-0.026}***\\
 & (\num{0.001}) & (\num{0.001}) & \vphantom{1} (\num{0.001})\\
'Social Distancing' Trend & \num{0.011}*** & \num{0.004}* & \num{0.001}\\
 & (\num{0.002}) & (\num{0.002}) & \vphantom{1} (\num{0.002})\\
'Covid Conspiracy' Trend & \num{0.024}*** & \num{0.006}*** & \num{0.010}***\\
 & (\num{0.002}) & (\num{0.002}) & (\num{0.002})\\
Covid Case Rate & \num{0.000} & \num{-0.009}* & \num{-0.007}+\\
 & (\num{0.004}) & (\num{0.004}) & (\num{0.004})\\
Week Number & \num{-0.002}+ & \num{-0.002}* & \num{-0.004}***\\
 & (\num{0.001}) & (\num{0.001}) & (\num{0.001})\\
Stay at Home Rate, county mean & \num{0.898}*** & \num{0.873}*** & \num{0.846}***\\
 & (\num{0.059}) & (\num{0.048}) & (\num{0.050})\\
Signal &  & \num{0.473}*** & \num{0.550}***\\
 &  & (\num{0.005}) & (\num{0.008})\\
Signal x Week &  & \num{-0.016}*** & \num{-0.018}***\\
 &  & (\num{0.000}) & (\num{0.000})\\
Signal Discordance &  &  & \num{-0.101}***\\
 &  &  & (\num{0.004})\\
Signal x Signal Discordance &  &  & \num{-0.092}***\\
 &  &  & (\num{0.002})\\
\midrule
Log.Lik. & \num{-23007.044} & \num{-19555.920} & \num{-18655.837}\\
\bottomrule
\multicolumn{4}{l}{\rule{0pt}{1em}N = 57,356, N of random Effects = 1375}\\
\multicolumn{4}{l}{\rule{0pt}{1em}Models 2-3 include a random effect for Movement Signal by FIPS}\\
\multicolumn{4}{l}{\rule{0pt}{1em}Model 1 includes a random intercept for FIPS,}\\
\multicolumn{4}{l}{\rule{0pt}{1em}* p $<$ .05. ** p $<$ .01. *** p $<$ .001 (two-tailed test).}\\
\end{tabular}
\end{table}

In Table \ref{tab:google-tab} and Figures \ref{fig:plot-google-h2} -
\ref{fig:plot-google-h3}, I present the elaboratory county-level models that
predict stay-at-home rates, or, time spent in residence. Model 1 addresses
hypothesis 1, that relatively higher local rates of infection will lead to
increased time spent in residence. This model's phi paramter is 0.933, which is
a good indicator that adjacent time points for each county are related and the
model is specified correctly (Finch, Bolin, and Kelley 2014). In this first model, many controls
have an impact on the outcome. For instance, when controlling for everything
else, the percent of GOP votes in 2016, the percentage of residents who identify
racially as White, and higher rates of unemployment increased the stay-at-home
rate while Searches for norms online seems to
have an effect on the outcome: searches for `Fox News' are associated with
decreased stay-at-home rates, while searching for both `Social Distancing' and
`Covid Conspiracy' tend to increase time spent in residence. Interestingly, the
perceived threat of the virus, measured through Covid-19 case rates, were not
significantly related to stay-at-home rates in model 1. In other words, for
every 1 standard deviation increase in Covid-19 case rates, stay-at-home rates
actually decreased by
0.0003 (\emph{p} = 0.936),
a very small and insignificant effect. In this case, I fail to reject the null
hypothesis that relatively higher local rates of infection will lead to
increased time spent in residence.

Table \ref{tab:google-tab} Model 2 investigates Hypothesis 2, that increased
average time spent in residence (signal direction) from alters will have a
positive effect on stay-at-home rates for the ego-county. This model builds on
model 1 by adding in the variable for Movement Signal (see \protect\hyperlink{network-signal}{Network
Signal} for specifications). For every one standard deviation
increase in the average time spent in residence of the county alters, an ego tends to also increase its' own stay-at-home rate by
0.473
(\emph{p} \textless{} 0.001). I am therefore able to reject my null hypothesis for hypothesis
2, that an increased average time spent in residence (signal direction) from
alters will have a positive effect on time spent in residence for the
ego-county.

\begin{figure}

{\centering \includegraphics[width=0.8\linewidth]{dissertation_files/figure-latex/plot-google-h2-1}

}

\caption{Predicted Values of Stay at Home Rate by Movement Signal}\label{fig:plot-google-h2}
\end{figure}

However, this coefficient is inadequate alone because the effect varies over
time; the interaction between week and movement signal is negative, meaning that
week partially moderates the effect of the signal. Figure
\ref{fig:plot-google-h2} illustrates this interaction. In the early days of the
Covid-19 pandemic, seeing a high rate of time spent in residence by alters led
to a high rate of staying-at-home for county egos. However, as the pandemic
progressed, these signals switched. In other words, towards the end of 2020,
other factors may have come into play and if a county saw its' alters social
distancing and spending time in residence, ego counties spent less time at home.
Theoretically, this may be because individuals saw their adjacent communities
with strong public health norms and felt safe and justified their own deviance.
However, if an ego county received signals that
others were failing to social distance, they were more likely to stay-at-home.
In this case, the threat of the virus may have been more evident for
individuals.

\begin{figure}

{\centering \includegraphics[width=0.8\linewidth]{dissertation_files/figure-latex/plot-google-h3-1}

}

\caption{Predicted Values of Stay at Home Rate Moderated}\label{fig:plot-google-h3}
\end{figure}

Model 3 then adds the concept of Signal Discordance to investigate Hypothesis 3,
that the effect of signal direction on stay-at-home rates will be moderated by a
diversity in signals (\emph{discordance}). Many of the controls remain consistent
throughout the models, with the exception of `Social Distancing' Trend whose
effect has been completely mediated by the inclusion of signal discordance.
Importantly, signal discordance has a negative effect on stay-at-home rates,
where every one standard deviation increase in discordance lowers stay-at-home rates by
-0.101
(\emph{p} \textless{} 0.001). The interaction between signal and signal discordance have a
coefficient of a similar magnitude, with every one standard deviation increase
in discordance and signal resulting in
-0.092
lower rates of time spent in residence, indicating moderation. Figure
\ref{fig:plot-google-h3} illustrates the moderating effect that signal
discordance has on signal. Under high discordance, the social influence effect
is almost completely moderated because there is no clear story or norm forming.
However, under low discordance, the signal is condensed, allowing for social
influence to have an effect. Explicitly, if a county is receiving a wide array
of low and high signals, their stay at home rates won't be affected by social
contagion. When a signal is concentrated or in agreement, the theoretical effect
of movement signaling on the ego are the strongest. With this, I am able to
reject the null hypothesis of no relationship for hypothesis 3 and find that the
effect of signal direction on time spent in residence is moderated by diversity
in signals.

\hypertarget{vaccination-rate-results}{%
\subsection{Vaccination Rate results}\label{vaccination-rate-results}}

\begin{table}[!h]

\caption{\label{tab:vacc-tab}Linear Mixed Effects Regression Results for Vaccination Rates}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{lccc}
\toprule
  & Model 1 & Model 2 & Model 3\\
\midrule
Percent White & \num{0.023}+ & \num{-0.029}*** & \num{-0.027}***\\
 & (\num{0.012}) & (\num{0.003}) & (\num{0.003})\\
Percent College Graduates & \num{-0.004} & \num{0.009}* & \num{0.010}*\\
 & (\num{0.013}) & (\num{0.004}) & (\num{0.004})\\
Percent over 65 & \num{-0.012} & \num{-0.002} & \num{0.000}\\
 & (\num{0.008}) & (\num{0.002}) & (\num{0.002})\\
Median Income & \num{0.002} & \num{-0.017}*** & \num{-0.016}***\\
 & (\num{0.011}) & (\num{0.003}) & (\num{0.003})\\
Monthly Unemployment Rate & \num{-0.031}*** & \num{-0.014}*** & \num{-0.013}***\\
 & (\num{0.001}) & (\num{0.001}) & (\num{0.001})\\
Percent of GOP votes, 2020 & \num{-0.070}*** & \num{0.031}*** & \num{0.028}***\\
 & (\num{0.014}) & (\num{0.004}) & (\num{0.004})\\
Percent Evangelical Christian & \num{0.000} & \num{0.000} & \num{-0.001}\\
 & (\num{0.009}) & (\num{0.003}) & (\num{0.003})\\
'Fox News' Trend & \num{0.002}*** & \num{0.000} & \num{0.000}*\\
 & (\num{0.000}) & (\num{0.000}) & \vphantom{4} (\num{0.000})\\
'Vaccine' Trend & \num{-0.001}*** & \num{0.000} & \num{0.000}+\\
 & (\num{0.000}) & (\num{0.000}) & \vphantom{3} (\num{0.000})\\
'Covid Conspiracy' Trend & \num{0.000}* & \num{0.001}*** & \num{0.001}***\\
 & (\num{0.000}) & (\num{0.000}) & \vphantom{2} (\num{0.000})\\
Covid Case Rate & \num{-0.008}*** & \num{0.001}*** & \num{0.001}***\\
 & (\num{0.000}) & (\num{0.000}) & \vphantom{1} (\num{0.000})\\
Week Number & \num{0.067}*** & \num{0.011}*** & \num{0.011}***\\
 & (\num{0.000}) & (\num{0.000}) & (\num{0.000})\\
Vaccination Rate, county mean & \num{0.800}*** & \num{0.201}*** & \num{0.170}***\\
 & (\num{0.018}) & (\num{0.005}) & (\num{0.005})\\
Vaccination Signal &  & \num{0.854}*** & \num{0.865}***\\
 &  & (\num{0.005}) & (\num{0.006})\\
Vaccination Signal x Week &  & \num{-0.005}*** & \num{-0.003}***\\
 &  & (\num{0.000}) & (\num{0.000})\\
Vaccination Discordance &  &  & \num{-0.072}***\\
 &  &  & \vphantom{1} (\num{0.002})\\
Vaccination Signal x Discordance &  &  & \num{-0.051}***\\
 &  &  & (\num{0.002})\\
\midrule
Log.Lik. & \num{118677.013} & \num{160000.978} & \num{160638.703}\\
\bottomrule
\multicolumn{4}{l}{\rule{0pt}{1em}N = 99,890, N of random Effects = 2819}\\
\multicolumn{4}{l}{\rule{0pt}{1em}Models 2-3 include a random effect for Movement Signal by FIPS}\\
\multicolumn{4}{l}{\rule{0pt}{1em}Model 1 includes a random intercept for FIPS,}\\
\multicolumn{4}{l}{\rule{0pt}{1em}* p $<$ .05. ** p $<$ .01. *** p $<$ .001 (two-tailed test).}\\
\end{tabular}
\end{table}

In Table \ref{tab:vacc-tab} and Figures \ref{fig:plot-vacc-h2} -
\ref{fig:plot-vacc-h3}, I present the elaboratory county-level models that
predict vaccination uptake rates. The parameter phi in model 1 is .985, which is
a good indicator that adjacent time points for each county are related and this
is an appropriate modeling technique for the data (Finch et al. 2014). Table
\ref{tab:vacc-tab} Model 1 addresses hypothesis 1, that relatively higher local
rates of infection will lead to increased vaccination uptake. In this first
model, we see various controls impacting vaccination rates. For instance, when
controlling for everything else, higher income areas lead to higher vaccination
uptake. On the other hand, counties with higher unemployment and higher votes
for Donald J. Trump in the 2020 election are associated with lower vaccination
rates. Interestingly, counties that search for Fox News are more likely to have
higher vaccination rates while those performing Google searches for information
about the vaccine are likely to have lower rates of vaccination. The test of
Hypothesis 1 also returns surprising results: every 1 standard deviation
increase in county Covid-19 case rates is expected to yield a
-0.008
decrease in vaccination rates. This may be due to time ordering or reverse
causality, where individuals in counties who have higher rates of vaccination
are less likely to take tests to Covid-19 infections because of the higher
likelihood of asymptomaticity. However, it is important to note that the Case
Rate variable actually becomes distorted with the addition of Vaccination Signal
and Vaccination Discordance in models 2 and 3. Distortion occurs when the
direction of a focal relationship reverses sign once a third (distorter)
variable is controlled, in this case, those related to signal. Therefore, the
results of hypothesis 1 are quite inconclusive.

\begin{figure}

{\centering \includegraphics[width=0.8\linewidth]{dissertation_files/figure-latex/plot-vacc-h2-1}

}

\caption{Predicted Values of Vaccination Rate}\label{fig:plot-vacc-h2}
\end{figure}

Table \ref{tab:vacc-tab} model 2 tests the hypothesis 2 that increase vaccine
uptake by alters will have a positive effect on vaccine uptake for the
ego-county. The results are incredibly clear: seeing alter counties receiving
vaccines is associated with higher vaccination rates. Specifically, a 1 standard
deviation increase in vaccine signal, the average rate of vaccination of a
county's alters, is associated with a
0.854
percent increase of vaccination rates for the ego county. The strength of this
result leads me to reject the null hypothesis for hypothesis 2 and find that
increased average time spent in residence (signal direction) from alters will
have a positive effect on time spent in residence for the ego-county. The
interaction of vaccine signal can be seen in Figure \ref{fig:plot-vacc-h2}.
While the interaction is not as extreme as the results for Hypothesis 2 for
Stay-at-Home rates, there is still a distinction between high and low
vaccination signals over time. The slope for Higher Vaccination Signal is less
pronounced than Low Vaccination Signal. This is likely an artifact where some
counties vaccinated broadly early on, so their vaccination rate stays rather
constant in later weeks. However, overall, the message is clear: ego-counties
who `see' high levels of vaccinations among their alters have higher vaccination
rates; those who don't see that social norm forming are much less likely to
vaccinate.

\begin{figure}

{\centering \includegraphics[width=0.8\linewidth]{dissertation_files/figure-latex/plot-vacc-h3-1}

}

\caption{Predicted Values of Vaccination Rate}\label{fig:plot-vacc-h3}
\end{figure}

Table \ref{tab:vacc-tab} Model 3 then models the moderation of signal direction
for vaccine uptake by diversity in signals (\emph{Discordance}). This is a second
test of Hypothesis 3, that the effect of signal direction on vaccine uptake will
be moderated by diversity in signals. The coefficients in model 3 are largely
consistent with model 2 and there is very little change in the magnitude
or significance of the coefficients. Vaccination signal maintains to have a positive
effect on the alter's vaccination rates, while vaccination discordance has a negative effect on vaccination rates, where every one standard deviation increase in discordance lowers rates by
-0.072
(\emph{p} \textless{} 0.001). The interaction between signal and signal discordance have a
coefficient of a similar magnitude, with every one standard deviation increase
in discordance \emph{and} signal resulting in\\
lower rates of vaccination. Figure \ref{fig:plot-vacc-h3} illustrates this
relationship, where there is slight moderation of the effect on vaccine signal
on vaccination rates. If a county receives consistently high signals, they are
more likely to have more residents vaccinated. If a county receives high but
inconsistent signals, they are still decently likely to raise vaccination rates
but to a lesser extent. While not as strong of moderation the the findings for
Stay-at-Home Rates for hypothesis 3, I also reject the null hypothesis and find
a moderation of the relationship between signal direction and vaccine uptake by
discordance.

\hypertarget{discussion-and-conclusion}{%
\section{Discussion and Conclusion}\label{discussion-and-conclusion}}

This paper examines how social norms are formed under conditions of uncertainty
using the case studies of stay-at-home rates and vaccination rates during the
Covid-19 pandemic. I test fear-based models of behavioral adaption to public
health recommendations as well as patterns of complex social contagion. This
article demonstrates that the establishment of social norms under patterns of
uncertainty in my two cases do follow the theorized framework of complex
contagion; however, I find a moderating effect of signal discordance to be an
overlooked factor in theories of contagion.

This study is sensitive to aggregation error and sampling error derived from the
multiple big-data sources (Facebook 2020; Google 2020). The aggregation errors are
potentially linked to the assumption that the average stay-at-home behavior of a
county is a good representation of the diversity in behaviors within that
county. If stay-at-home rates are normally distributed, this is a correct
assumption to make; however, little is known about each county's underlying
distribution of behaviors that lead to the aggregate measures.

Regardless of limitations, this article is a unique and compelling contribution
to the academic study of social contagion and social norms. First, this article
demonstrates that it is possible to link, at least at a community level,
information search by individuals, social relationships, and observed health
behaviors without being limited to self-report measures of perceptions,
attitudes, or intentions about behavior. Sociological research has long debated
about the agency of individuals and the social and institutional structure in
which individuals are immersed. In this study, I aggregate beyond the individual
case to explore overall patterns of movement and vaccination which summarizes
individual agency of health behaviors together.

This article also provides a new adaption of the theory of complex contagion
using big data from the natural experiment of Covid-19. Because most studies of
complex contagion utilize agent-based modeling or studies of social media
(Aral and Nicolaides 2017; Robert M. Bond et al. 2012a; Latané, Nowak, and Liu 1994; Sprague and House 2017), combining measures of actual behavioral outcomes with data from
social media websites provides a further test of ecological and external
validity for the theory.

Researchers of contagion and social networks should be interested in this study.
My theory of discordance, or a diversity of signals received, is not found in
the literature on complex contagion; complex contagion focuses on the number of
reinforcing actors, while other theories focus on how different diffusants
interact with each other (Goldberg and Stein 2018; Houghton 2021; Mason et al. 2007). Discordance, on the other hand, looks specifically at the
context of the reinforcing actors among the other signals. This study finds that
indeed the context of the signals matters for diffusion.

### 2022-03-02 ch1.tex
Updates

@@
 From a networks
-perspective, "people rarely act on mass-media information unless it is also transmitted thro\citep[p.
+perspective, "people rarely act on mass-media information unless it is also transmitted through personal ties" \citep[p.
 1374]{granovetterStrengthWeakTies1973}.
-Lazarsfeld's first study focused on politics \citeyearpar{lazarsfeldPeopleChoice1944} but follow up studies from \citep{katzPersonalInfluencePart1955} showed that this model matched information flows beyond the political realm.
+Lazarsfeld  \citeyearpar{lazarsfeldPeopleChoice1944}'s first study focused on politics but follow up studies from \citep{katzPersonalInfluencePart1955} showed that this model matched information flows beyond the political realm.
 In contrast to the one-step flow, where media directly influences the masses, Lazarsfeld's theory remains in prominence today.
-While many scholars assumed that
-modern micro-targeted marketing strategies would provide evidence for a one-step flow perspective \citep{bennettOneStepFlowCommunication2006}, many scholars find that "opinion leaders" (often influencers and celebrities) still create a two-step flow of information transmission \citep{choi15, hilbertOneStepTwo2017}.
+While many scholars assumed that modern micro-targeted marketing strategies would provide evidence for a one-step flow perspective \citep{bennettOneStepFlowCommunication2006}, many scholars find that "opinion leaders" (often influencers and celebrities) still create a two-step flow of information transmission \citep{choi15, hilbertOneStepTwo2017}.
 
@@
 
-\subsubsection{Uses and Gratification Theory}
+\subsection{Uses and Gratification Theory}
 
@@
 
-\subsubsection{Social Norms}
+\subsection{Social Norms}
 
@@
 
-\subsection{Broader Impact}
+\section{Broader Impact}
 
@@
 
-This dissertation also contributes to computational social science &
+This dissertation also contributes to computational social science \&
 critical big data studies. I base much of my dissertation around Google
@@
 
-\subsection{Three Empirical Articles}
+\section{Three Empirical Articles}
 
@@
 
-\subsubsection{Article 1: Construct Validity and Correspondence of Google Trends}
+\subsection{Article 1: Construct Validity and Correspondence of Google Trends}
 % TODO Double check name
@@
 
-\subsubsection{Article 2: Information-Seeking Behaviors for Information on Covid-19 Vaccinations}
+\subsection{Article 2: Information-Seeking Behaviors for Information on Covid-19 Vaccinations}
 % TODO Double check name
@@
 
-\subsubsection{Article 3: Social Norms under Uncertain Times: A dynamic study of Stay-At-Home and Vaccination Rates During the Covid-19 Pandemic}
+\subsection{Article 3: Social Norms under Uncertain Times: A dynamic study of Stay-At-Home and Vaccination Rates During the Covid-19 Pandemic}
 % TODO Double check name

### 2022-03-02 paper1.tex
Updates

@@
 research because they are bigger, cheaper, and already available
-\citep{kingEnsuringDataRichFuture2011, lazerComputationalSocialScience2009,
-salganikBitBitSocial2017}. Before overenthusiastically embracing these
+\citep{kingEnsuringDataRichFuture2011,lazerComputationalSocialScience2009,salganikBitBitSocial2017}. Before overenthusiastically embracing these
 sources into our workflows, social scientists must clearly establish
@@
 reliability and dependencies among data" \citep[p. 1203]{lazerParableGoogleFlu2014}. Building on this prior research outlining these various
-issues with big data \citep{boydCriticalQuestionsBig2012,
-lazerIssuesConstructValidity2015}, this paper tests the construct
+issues with big data \citep{boydCriticalQuestionsBig2012,lazerIssuesConstructValidity2015}, this paper tests the construct
 validity of Google Search Trends as an indicator of three different
@@
 social science research. From research on mass shootings and firearms
-\citep{brownsteinInternetSearchPatterns2020,
-semenzaInformationseekingWakeTragedy2020}, protest and anti-Muslim
-sentiment \citep{bailUsingInternetSearch2018,
-barrieSearchingRacismGeorge2020, grossThereFergusonEffect2017}, to
-analyzing country-level changes in social perception \citep{reyes_etal18},
+\citep{brownsteinInternetSearchPatterns2020,semenzaInformationseekingWakeTragedy2020}, protest and anti-Muslim sentiment \citep{bailUsingInternetSearch2018,barrieSearchingRacismGeorge2020,grossThereFergusonEffect2017}, to analyzing country-level changes in social perception \citep{reyes_etal18},
 Google search trends are a new and innovative indicator of cultural
-interest. Extending into social networks and culture,
-\citet{bailPrestigeProximityPrejudice2019} even used Google trends to measure
+interest. Extending into social networks and culture, \citet{bailPrestigeProximityPrejudice2019} even used Google trends to measure
 how culture spreads around the globe.
@@
 Medical Internet Research. While much of this research has focused on
-the Covid-19 pandemic \citep{jimenez_etal20,
-jimenezCOVID19SymptomGoogle2020,
-limEstimatingInformationSeekingBehaviour2020,
-mavraganiCOVID19PredictabilityUnited2020,
-nguyenGoogleTrendsAnalysis2020, todorovaInternetBasedData2021} , other
+the Covid-19 pandemic \citep{jimenez_etal20,jimenezCOVID19SymptomGoogle2020,limEstimatingInformationSeekingBehaviour2020,mavraganiCOVID19PredictabilityUnited2020,nguyenGoogleTrendsAnalysis2020, todorovaInternetBasedData2021} , other
 research has investigated Google Trends as an indicator of wellbeing
-\citep{brodeurCOVID19LockdownsWellbeing2021,
-carpiTwitterSubjectiveWellBeing2020, duCOVID19IncreasesOnline2020},
+\citep{brodeurCOVID19LockdownsWellbeing2021,carpiTwitterSubjectiveWellBeing2020, duCOVID19IncreasesOnline2020},
 suicidality \citep{burnettTimeTrendsPublic2020}, vaccination uptake
@@
 sources to address the three areas of inquiry for this paper.  Table
-\@ref(tab:data-sources-table) outlines which data sources are used for this
+\ref{tab:data-sources-table} outlines which data sources are used for this
 project and which trends are matched to each source.
 
-TABLE HERE
+\input{tables/paper1/data-sources-table}
 
@@
 of x observations, one for each U.S. County. The variable
-measures the precent of adults in the county who describe themselves as
+measures the percent of adults in the county who describe themselves as
 “unsure”, “probably not”, or “definitely not” going to get a COVID-19 vaccine
@@
 represents the percent of adults in the county who never or rarely wear a mask
-(range = x to x)
+(range = x to x).
 
@@
 cases, resulting from x observations of x counties. Missing data were interpolated using
-`zoo::na.approx()` \citep{zoo}. Measures range from x to x.
+zoo::na.approx() \citep{zoo}. Measures range from x to x.
 
@@
 time, percent of households living under the poverty line, and percent above 65
-years old. In addition, some models employ the U.S. Current Population Survey &
+years old. In addition, some models employ the U.S. Current Population Survey \&
 American Community Survey Geographic Estimates of Internet Use, 1997-2018
@@
 individual indicator based on County FIPS Codes and date. After creating these
-different datasets, I use the Pearson correlation formula (formula
-%\@ref(eq:pearsoncorr)
+different datasets, I use the Pearson correlation formula (formula \eqref{eq:pearsoncorr}
 ) for cross-sectional numeric data to calculate the
@@
   \frac{ \sum_{i=1}^{n}(x_i-\bar{x})(y_i-\bar{y}) }{
-        \sqrt{\sum_{i=1}^{n}(x_i-\bar{x})^2}\sqrt{\sum_{i=1}^{n}(y_i-\bar{y})^2}} %(\#eq:pearsoncorr)
+        \sqrt{\sum_{i=1}^{n}(x_i-\bar{x})^2}\sqrt{\sum_{i=1}^{n}(y_i-\bar{y})^2}} \label{eq:pearsoncorr}
 \end{equation}
@@
 measures across time and counties. Results of these correlations can be seen in 
-table %\@ref(tab:corr-results).
+table \ref{tab:corr-results}.
 
@@
 
+\input{tables/paper1/corr-results}
+
 The first attitudinal indicators is Vaccine Hesitancy for COVID-19 vaccines
@@
 correlations in multiple linear regression (see the results in table
-% \@ref(tab:vacc_hes_analysis)
-), I see an $r^2$ of 0.233 (Model 1) and 0.411
+\ref{tab:vacc_hes_analysis}), I see an $r^2$ of 0.233 (Model 1) and 0.411
 (Model 2), indicating that the Google Trends are able to explain about 23% of
@@
 percentage of households with broadband internet and the population density are
-able to explain about 35% of the variation (model 2), outperforming the first
+able to explain about 35\% of the variation (model 2), outperforming the first
 models. The Trend coefficients themselves, however, are significant and remain
@@
 
+\input{tables/paper1/vacc_hes_analysis}
+
 The second attitudinal measure I test is how Google Trends relates to rare mask
@@
 common rules of thumb. I introduce these trends in multiple linear regression in
-table 
-% \@ref(tab:mask_analysis)
-. Model 1 demonstrates that these five Google
+table \ref{tab:mask_analysis}. Model 1 demonstrates that these five Google
 Search Trends can explain about 7\% of the variance in mask usage across U.S.
@@
 
+\input{tables/paper1/mask_analysis}
+
 \subsection{Validating Google Trends as metrics of health outcomes}
@@
 include the three trends in random intercept hierarchical linear models. Model 1
-of table 
-% \@ref(tab:covid_analysis)
-indicates that the trends themselves are able
+of table \ref{tab:covid_analysis} indicates that the trends themselves are able
 to explain about 20\% of the variation in Covid-19 rates ($r^2$ = 0.201). Few
@@
 
+\input{tables/paper1/covid_analysis}
+
 Another indicator of health outcomes I test to validate Google Trends as
@@
 negligible. I introduce these trends into a random intercept model to control
-for inter-group variation over time in table 
-% \@ref(tab:suicide_analysis)
-. While
-table 
-% \@ref(tab:suicide_analysis)
-model 1 reveals a significant relationship
+for inter-group variation over time in table \ref{tab:suicide_analysis}. While
+table \ref{tab:suicide_analysis} model 1 reveals a significant relationship
 between suicide hotline trends and suicide rates, the effect is small and the
@@
 Trends should not be used as indicators of suicide rates or intentions.
+
+\input{tables/paper1/suicide_analysis}
 
@@
 
-In table 
-% \@ref(tab:pres_2016_analysis)
-, I outline the results for the model
+In table \ref{tab:pres_2016_analysis}, I outline the results for the model
 predicting the county percentage of votes for Hillary Clinton. Model 1
@@
 fit quite well, bringing the $r^2$ up to 0.313 in model 2 and $r^2$ 0.327 in
-model 3. In table 
-% \@ref(tab:pres_2020_analysis)
-shows this same analysis for the
+model 3. In table \ref{tab:pres_2020_analysis} shows this same analysis for the
 2020 election and predicts the percentage of votes for Joe Biden. While this
-model is largely similar to those in table 
-% \@ref(tab:pres_2016_analysis)
-, this
+model is largely similar to those in table \ref{tab:pres_2016_analysis}, this
 model 1 demonstrates how unrelated Google Trends can be from actual outcomes. In
@@
 political support.
+
+\input{tables/paper1/pres_2016_analysis}
+\input{tables/paper1/pres_2020_analysis}
 

### 2022-03-02 paper2.tex
Updates

@@
 “the receiver as an active information seeker and processor." \citep{johnsonComprehensiveModelCancerRelated1993},
-though there are always exceptions \cite{ysenbach09}
+though there are always exceptions \citep{eysenbach09}
 
@@
 Active, directed searching by individuals to obtain information is sparsely
-discussed in the sociological literature. Pejtersen \citet{pejtersen1984}, a scholar
+discussed in the sociological literature. Pejtersen \citet{pejtersenDesignComputeraidedUsersystem1984}, a scholar
 of library and information science, theorized that there are 5 strategies for
@@
 
-%%% STOPED PASTING CITATIONS HERE
-
 There are three computer-mediated vehicles I consider for this analysis: online
@@
 Modern-day theorists have extended UGT theory and classified the uses and
-gratifications of the internet and of social media. \cite{staffordDeterminingUsesGratifications2004} theorize that the internet
+gratifications of the internet and of social media. \citet{staffordDeterminingUsesGratifications2004} theorize that the internet
 provides gratification through useful content that meets expectations,
 gratification from purposeful navigating or random browsing as a process, and
-social gratification from forming and deepening social ties. \cite{leungGenerationalDifferencesContent201} theorizes that social media is
+social gratification from forming and deepening social ties. \citet{leungGenerationalDifferencesContent2013} theorizes that social media is
 gratifying for users because it allows for venting of negative feelings,
@@
 potential avoidance of embarrassment and other negative social interactions,
-especially in the case on search engines. Stephen Rains
-(2018) finds that patients tend to search for
+especially in the case on search engines. \citet{rainsCopingIllnessDigitally2018}
+finds that patients tend to search for
 technical information about an illness online but they then turn to their social
@@
 activate informational support among their social network or turn to online
-groups that validate their worldview (Bogers and Wernersen 2014). Finally, UGT and
-Brasher's definition of social support
-(2002) help us to theorize that the
-psychosocial needs like identity management or relational maintenance
-(Brashers et al. 2002) of an individual may influence their
-chosen information search vehicle: when the informational need is related to
+groups that validate their worldview \citep{bogersHowSocialAre2014}. Finally, UGT and
+Brasher's definition of social support \citeyearpar{brashersInformationSeekingAvoiding2002} help us to theorize that the
+psychosocial needs like identity management or relational maintenance of an individual may influence their chosen information search vehicle: when the informational need is related to
 forming and deepening social ties search is likely to be done from network ties.
@@
 is slighted gender unbalanced, slightly skewing towards a male sample. For the
-respondents who provided their zip code (p =
-0.98), the
-sample is quite balanced with a slight skew towards MTurkers in the South (p =
-0.41).
-The survey took an average of 24.48 minutes with a
-standard deviation of 13.23 minutes. The shortest
-valid survey took 3.75 minutes and the longest took
-111.08 minutes. Participants were paid \$6.00 for their
-time after Amazon administrative fees, funded by a Grant awarded to Kelsey E.
+respondents who provided their zip code (p = 0.98), the sample is quite balanced with a slight skew towards MTurkers in the South (p = 0.41).
+
+The survey took an average of 24.48 minutes with a standard deviation of 13.23 minutes.
+The shortest valid survey took 3.75 minutes and the longest took 111.08 minutes.
+Participants were paid \$6.00 for their time after Amazon administrative fees, funded by a Grant awarded to Kelsey E.
 Gonzalez and Nicolas Legewie by the Summer Institute in Computational Social
-Science and the Russell Sage Foundation. The main portion of this survey
-replicates the book, Someone to Talk To (Small 2017) by expanding on
-Small's finding that people draw on much broader sources than ``important people''
-for support by segregating weak-tie social support into instrumental, emotional,
-and informational support (see House et al. 1988). The latter
+Science and the Russell Sage Foundation.
+The main portion of this survey replicates the book, Someone to Talk To \citep{smallSomeoneTalk2017} by expanding on Small's finding that people draw on much broader sources than ``important people'' for support by segregating weak-tie social support into instrumental, emotional, and informational support \citep[see][]{houseStructuresProcessesSocial1988}.
+The latter
 part of the survey focuses on resource activation for the specific case-study of
@@
 
-\begin{table}[!h]
-
-\caption{\label{tab:table-1-desc}Descriptive Statistics for Dichotomous and Numeric Variables}
-\centering
-\begin{tabular}[t]{lrr}
-\toprule
-  & Mean & SD\\
-\midrule
-\cellcolor{gray!6}{Received info} & \cellcolor{gray!6}{\num{0.66}} & \cellcolor{gray!6}{\num{0.47}}\\
-Received info, Doctor & \num{0.47} & \num{0.50}\\
-\cellcolor{gray!6}{Received info, Person} & \cellcolor{gray!6}{\num{0.67}} & \cellcolor{gray!6}{\num{0.47}}\\
-Received info, News & \num{0.65} & \num{0.48}\\
-\cellcolor{gray!6}{Received info, Social Networking Site} & \cellcolor{gray!6}{\num{0.40}} & \cellcolor{gray!6}{\num{0.49}}\\
-Received info, Online Forum & \num{0.35} & \num{0.48}\\
-\cellcolor{gray!6}{Sought Info} & \cellcolor{gray!6}{\num{0.78}} & \cellcolor{gray!6}{\num{0.41}}\\
-Sought Info, Doctor & \num{0.44} & \num{0.50}\\
-\cellcolor{gray!6}{Sought Info, Person} & \cellcolor{gray!6}{\num{0.42}} & \cellcolor{gray!6}{\num{0.49}}\\
-Sought Info, Social Networking Site & \num{0.18} & \num{0.39}\\
-\cellcolor{gray!6}{Sought Info, Online Forum} & \cellcolor{gray!6}{\num{0.27}} & \cellcolor{gray!6}{\num{0.44}}\\
-Sought Info, Online Search & \num{0.41} & \num{0.49}\\
-\cellcolor{gray!6}{Vaccination Status} & \cellcolor{gray!6}{\num{0.84}} & \cellcolor{gray!6}{\num{0.36}}\\
-Vaccination Outlook & \num{0.87} & \num{0.34}\\
-\cellcolor{gray!6}{Age} & \cellcolor{gray!6}{\num{37.76}} & \cellcolor{gray!6}{\num{10.75}}\\
-Hispanic or Latino/x & \num{0.15} & \num{0.36}\\
-\cellcolor{gray!6}{Race, White} & \cellcolor{gray!6}{\num{0.88}} & \cellcolor{gray!6}{\num{0.33}}\\
-Race, Black & \num{0.08} & \num{0.27}\\
-\cellcolor{gray!6}{Race, Native American} & \cellcolor{gray!6}{\num{0.03}} & \cellcolor{gray!6}{\num{0.16}}\\
-Race, Asian or Pacific Islander & \num{0.04} & \num{0.20}\\
-\cellcolor{gray!6}{Associate's Deg or above} & \cellcolor{gray!6}{\num{0.74}} & \cellcolor{gray!6}{\num{0.44}}\\
-\bottomrule
-\multicolumn{3}{l}{\rule{0pt}{1em}Notes: 948 Surveyed, Conducted December 03 through December 12, 2021.}\\
-\end{tabular}
-\end{table}
+\input{tables/paper2/table-1-desc}
 
@@
 posed with 5 responses and `other,' of which they could select multiple. The
-largest proportion, 44\%, asked their
-`doctor or another health professional' (95\% Confidence Interval =
-\{41\%, 47\%\}).
-About 42\% said they asked, `a person
+largest proportion, 44\%, asked their `doctor or another health professional' (95\% Confidence Interval = \{41\%, 47\%\}). About 42\% said they asked, `a person
 like friend, neighbor, or family member that {[}they{]} know' (95\% Confidence
-Interval = \{39\%, 45\%\}). An additional
-41\% searched `for {[}their{]} question
+Interval = \{39\%, 45\%\}). An additional 41\% searched `for {[}their{]} question
 using an online search engine such as Google or Bing' (95\% Confidence Interval
-= \{38\%, 45\%\}). About a quarter of the
-sample, 27\%, `posted queries in an
+= \{38\%, 45\%\}). About a quarter of the sample, 27\%, `posted queries in an
 online discussion group, listserve, or other online forum like a Facebook Group
 or Subreddit' (95\% Confidence Interval = \{24\%, 30\%\}).
-And finally, 18\% of the sample `posted queries
-on a social networking site such as Facebook timeline, Twitter status update, or
-LinkedIn' (95\% Confidence Interval = \{16\%, 21\%\}).
+And finally, 18\% of the sample `posted queries on a social networking site such as Facebook timeline, Twitter status update, or LinkedIn' (95\% Confidence Interval = \{16\%, 21\%\}).
 Much of the question wording and the specific categories of search were inspired
-by ICPSR project 37220 (Scanlon 2019).
+by ICPSR project 37220 \citep{scanlon19}.
 
-\begin{table}[!h]
-
-\caption{\label{tab:table-2-desc}Descriptive Statistics for Categorical Variables}
-\centering
-\begin{tabular}[t]{llrr}
-\toprule
-  &    & N & Percent\\
-\midrule
-\cellcolor{gray!6}{Gender} & \cellcolor{gray!6}{Female} & \cellcolor{gray!6}{418} & \cellcolor{gray!6}{\num{44.09}}\\
- & Male & 524 & \num{55.27}\\
-\cellcolor{gray!6}{} & \cellcolor{gray!6}{Other} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{\num{0.63}}\\
-Highest Education Level & Graduate or professional degree & 145 & \num{15.30}\\
-\cellcolor{gray!6}{} & \cellcolor{gray!6}{Bachelor's degree} & \cellcolor{gray!6}{560} & \cellcolor{gray!6}{\num{59.07}}\\
- & Associate's or Technical degree & 72 & \num{7.59}\\
-\cellcolor{gray!6}{} & \cellcolor{gray!6}{Some college} & \cellcolor{gray!6}{100} & \cellcolor{gray!6}{\num{10.55}}\\
- & High school graduate & 68 & \num{7.17}\\
-\cellcolor{gray!6}{} & \cellcolor{gray!6}{Less than high school} & \cellcolor{gray!6}{3} & \cellcolor{gray!6}{\num{0.32}}\\
-Plan to be Vaccinated if not & Probably not & 38 & \num{4.01}\\
-\cellcolor{gray!6}{} & \cellcolor{gray!6}{Definitely yes} & \cellcolor{gray!6}{13} & \cellcolor{gray!6}{\num{1.37}}\\
- & Definitely not & 61 & \num{6.43}\\
-\cellcolor{gray!6}{} & \cellcolor{gray!6}{Might or might not} & \cellcolor{gray!6}{22} & \cellcolor{gray!6}{\num{2.32}}\\
- & Probably yes & 13 & \num{1.37}\\
-\cellcolor{gray!6}{Found Info Sought Useful} & \cellcolor{gray!6}{Very useful} & \cellcolor{gray!6}{345} & \cellcolor{gray!6}{\num{36.39}}\\
- & Moderately useful & 112 & \num{11.81}\\
-\cellcolor{gray!6}{} & \cellcolor{gray!6}{Extremely useful} & \cellcolor{gray!6}{264} & \cellcolor{gray!6}{\num{27.85}}\\
- & Slightly useful & 18 & \num{1.90}\\
-\cellcolor{gray!6}{} & \cellcolor{gray!6}{Not at all useful} & \cellcolor{gray!6}{2} & \cellcolor{gray!6}{\num{0.21}}\\
-Census Region & Midwest & 171 & \num{18.04}\\
-\cellcolor{gray!6}{} & \cellcolor{gray!6}{Northeast} & \cellcolor{gray!6}{170} & \cellcolor{gray!6}{\num{17.93}}\\
- & South & 365 & \num{38.50}\\
-\cellcolor{gray!6}{} & \cellcolor{gray!6}{West} & \cellcolor{gray!6}{223} & \cellcolor{gray!6}{\num{23.52}}\\
-\bottomrule
-\multicolumn{4}{l}{\rule{0pt}{1em}Notes: 948 Surveyed, Conducted December 03 through December 12, 2021.}\\
-\end{tabular}
-\end{table}
+\input{tables/paper2/table-2-desc}
 
@@
 84\% of the sample said that
-they had indeed received a vaccination (95\% Confidence Interval = \{82\%, 87\%\}). As the national vaccination rate is
-closer to 75\% (CDC 2020a), this indicates some bias in our sample that must be
+they had indeed received a vaccination (95\% Confidence Interval = \{82\%, 87\%\}).
+As the national vaccination rate is closer to 75\% \citep{cdc20}, this indicates some bias in our sample that must be
 acknowledged: either MTurkers are more likely to be vaccinated that the normal
@@
 plan to receive a vaccine for the prevention of the Covid-19 virus?' Of those
-who were asked this question (n = 147),
-9\%
-said they were `definitely yes' getting the vaccine;
-9\%
-said they were `probably yes' going to receive vaccine. The rest of the sample was more unsure:
-15\%
-said they `Might or might not,'
-26\%
-said `Probably not,' and finally
-41\%
-said they would `definitely not' receive the vaccine. The variable `Vaccination
-Outlook' indicates that either the respondent received a Covid-19 vaccine or
+who were asked this question (n = 147), 9\% said they were `definitely yes' getting the vaccine;
+9\% said they were `probably yes' going to receive vaccine.
+The rest of the sample was more unsure: 15\% said they `Might or might not,' 26\% said `Probably not,' and finally 41\% said they would `definitely not' receive the vaccine.
+The variable `Vaccination Outlook' indicates that either the respondent received a Covid-19 vaccine or
 either probably or definitely will in the future.
@@
 average age of our sample was 37.76.
-Our sample was 44\%
-female, and 55\%
-male. The sample is diverse racially though some ethnic groups are underrepresented compared to national averages. Race was evaluated using the
+Our sample was 44\% female, and 55\% male.
+The sample is diverse racially though some ethnic groups are underrepresented compared to national averages.
+Race was evaluated using the
 question, `What is your race? If you are ``mixed race,'' select all that apply.'
@@
 paper, I rely heavily on logistic regression, modeled in \texttt{r}; specifically, I
-fit a series of Binomial Generalized Linear Models (Venables and Ripley 2002).
-In Table \ref{tab:table-model-1}\footnote{All tables in this paper were created with the modelsummary package in \texttt{r} (Arel-Bundock 2022)}
+fit a series of Binomial Generalized Linear Models \citep{venables2002a}.
+In Table \ref{tab:table-model-1}\footnote{All tables in this paper were created with the modelsummary package in \texttt{r} \citep{modelsummary}}
 , I fit a logistic regression model predicting
@@
 age, education level and race. Figure \ref{fig:plot-model-1} then illustrates
-the relationship between the coefficients and information seeking.\footnote{Figures in
-  this paper were all created using the \texttt{r} packages jtools (Long 2020) and ggplot2 (Wickham 2011; Wickham, Chang, and Henry n.d.)}.
+the relationship between the coefficients and information seeking.\footnote{Figures in this paper were all created using the \texttt{r} packages jtools \citep{jtools} and ggplot2 \citep{wickham_etal, wickham11}}.
 In Table \ref{tab:model-2-phi} I disaggregate information seeking behaviors by
@@
 online forum, on a social networking site, or using an online search tool. I
-investigate these differences through a phi coefficient (Warrens 2008), otherwise
+investigate these differences through a phi coefficient \citep{warrens08}, otherwise
 known as a mean square contingency coefficient which is used to investigate the
 degree of association between two binary variables.\footnote{To calculate the Phi
-  Coefficient, I utilize the Psych \texttt{r} package (Revelle 2015)} I then investigate the
+  Coefficient, I utilize the Psych \texttt{r} package \citep{psych}} I then investigate the
 associations between my predictors and the 5 information search vehicles by
@@
 
-\begin{table}[!h]
-
-\caption{\label{tab:table-model-1}What predicts someone intentionally searched for information}
-\centering
-\begin{tabular}[t]{lc}
-\toprule
-  & Model 1\\
-\midrule
-\cellcolor{gray!6}{Received Info, Doctor} & \cellcolor{gray!6}{\num{1.037}*** (\num{0.181})}\\
-Received Info, Person & \num{0.624}*** (\num{0.171})\\
-\cellcolor{gray!6}{Received Info, News} & \cellcolor{gray!6}{\num{0.316}+ (\num{0.175})}\\
-Received Info, Social Networking Site & \num{0.320}+ (\num{0.187})\\
-\cellcolor{gray!6}{Received Info, Online Forum} & \cellcolor{gray!6}{\num{0.873}*** (\num{0.203})}\\
-Age & \num{0.025}** (\num{0.009})\\
-\cellcolor{gray!6}{Associate's Deg or above} & \cellcolor{gray!6}{\num{0.456}* (\num{0.192})}\\
-White & \num{0.857} (\num{0.575})\\
-\cellcolor{gray!6}{Black} & \cellcolor{gray!6}{\num{1.274}* (\num{0.625})}\\
-Native American & \num{0.405} (\num{0.710})\\
-\cellcolor{gray!6}{Asian} & \cellcolor{gray!6}{\num{0.105} (\num{0.588})}\\
-Hispanic or Latino/x & \num{0.425} (\num{0.271})\\
-\cellcolor{gray!6}{Num.Obs.} & \cellcolor{gray!6}{\num{948}}\\
-\midrule
-$R_{McFadden}^2$ & \num{0.110}\\
-\cellcolor{gray!6}{BIC} & \cellcolor{gray!6}{\num{988.1}}\\
-Log.Lik. & \num{-442.618}\\
-\bottomrule
-\multicolumn{2}{l}{\rule{0pt}{1em}Raw, Unexponentiated Coefficients}\\
-\multicolumn{2}{l}{\rule{0pt}{1em}* p $<$ .05. ** p $<$ .01. *** p $<$ .001 (two-tailed test).}\\
-\end{tabular}
-\end{table}
+\input{tables/paper2/table-model-1}
 
 \begin{figure}
-
-{\centering \includegraphics[width=0.8\linewidth]{dissertation_files/figure-latex/plot-model-1-1}
-
-}
-
+{\centering \includegraphics[width=0.8\linewidth]{figs/paper2/plot-model-1-1}}
 \caption{Plot of Coefficients, Model 1}\label{fig:plot-model-1}
@@
 
-\begin{table}[!h]
-
-\caption{\label{tab:model-2-phi}Phi Coefficient ($\phi$) of binary association between each Information Search Vehicle}
-\centering
-\begin{tabular}[t]{l|l|r|r|r|r}
-\hline
- & Person & Dr & Online Forum & Social Networking Site & Online Search\\
-\hline
-\cellcolor{gray!6}{Person} & \cellcolor{gray!6}{NA} & \cellcolor{gray!6}{0.28} & \cellcolor{gray!6}{0.172} & \cellcolor{gray!6}{0.275} & \cellcolor{gray!6}{0.216}\\
-\hline
-Dr & NA & NA & 0.192 & 0.152 & 0.098\\
-\hline
-\cellcolor{gray!6}{Online Forum} & \cellcolor{gray!6}{NA} & \cellcolor{gray!6}{NA} & \cellcolor{gray!6}{NA} & \cellcolor{gray!6}{0.371} & \cellcolor{gray!6}{-0.073}\\
-\hline
-Social Networking Site & NA & NA & NA & NA & 0.057\\
-\hline
-\cellcolor{gray!6}{Online Search} & \cellcolor{gray!6}{NA} & \cellcolor{gray!6}{NA} & \cellcolor{gray!6}{NA} & \cellcolor{gray!6}{NA} & \cellcolor{gray!6}{NA}\\
-\hline
-\end{tabular}
-\end{table}
+\input{tables/paper2/model-2-phi}
 
@@
 various information seeking vehicles: Around 40\% of the sample has inquired for
-information from a doctor, a person, or using online search tool (
-44\%,
-42\%,
-41\%) while my
-respondents used vehicles like online forums (
-27\%) and social
-networking sites (18\%)
+information from a doctor, a person, or using online search tool (44\%, 42\%, 41\%) while my
+respondents used vehicles like online forums (27\%) and social networking sites (18\%)
 to seek out information at significantly lower rates. To investigate how each
@@
 
-\begin{table}[!h]
-
-\caption{\label{tab:table-model-2}What predicts someone intentionally searched for information, by vehicle of information search}
-\centering
-\resizebox{\linewidth}{!}{
-\begin{tabular}[t]{llllll}
-\toprule
-\multicolumn{1}{c}{ } & \multicolumn{5}{c}{Dependent Variable} \\
-\cmidrule(l{3pt}r{3pt}){2-6}
-  & Doctor & Person & Online Forum & Social Networking Site & Online Search\\
-\midrule
-\cellcolor{gray!6}{Received Info, Doctor} & \cellcolor{gray!6}{\num{1.942}***} & \cellcolor{gray!6}{\num{1.124}***} & \cellcolor{gray!6}{\num{0.181}} & \cellcolor{gray!6}{\num{0.540}**} & \cellcolor{gray!6}{\num{0.430}**}\\
-Received Info, Person & \num{0.800}*** & \num{1.199}*** & \num{0.728}*** & \num{0.281} & \num{0.365}*\\
-\cellcolor{gray!6}{Received Info, News} & \cellcolor{gray!6}{\num{0.437}**} & \cellcolor{gray!6}{\num{0.100}} & \cellcolor{gray!6}{\num{0.359}*} & \cellcolor{gray!6}{\num{0.514}*} & \cellcolor{gray!6}{\num{1.091}***}\\
-Received Info, Social Networking Site & \num{-0.130} & \num{0.437}** & \num{-0.603}** & \num{0.731}*** & \num{1.272}***\\
-\cellcolor{gray!6}{Received Info, Online Forum} & \cellcolor{gray!6}{\num{0.412}*} & \cellcolor{gray!6}{\num{0.263}+} & \cellcolor{gray!6}{\num{1.266}***} & \cellcolor{gray!6}{\num{0.974}***} & \cellcolor{gray!6}{\num{0.695}***}\\
-Age & \num{0.002} & \num{0.001} & \num{-0.007} & \num{-0.003} & \num{0.029}***\\
-\cellcolor{gray!6}{Associate's Deg or above} & \cellcolor{gray!6}{\num{0.542}**} & \cellcolor{gray!6}{\num{0.154}} & \cellcolor{gray!6}{\num{1.086}***} & \cellcolor{gray!6}{\num{1.344}***} & \cellcolor{gray!6}{\num{-0.952}***}\\
-White & \num{0.631} & \num{0.245} & \num{0.009} & \num{0.559} & \num{0.012}\\
-\cellcolor{gray!6}{Black} & \cellcolor{gray!6}{\num{0.366}} & \cellcolor{gray!6}{\num{0.208}} & \cellcolor{gray!6}{\num{0.608}} & \cellcolor{gray!6}{\num{0.646}} & \cellcolor{gray!6}{\num{0.357}}\\
-Native American & \num{0.309} & \num{-0.696} & \num{0.209} & \num{0.762} & \num{-0.831}\\
-\cellcolor{gray!6}{Asian} & \cellcolor{gray!6}{\num{-0.294}} & \cellcolor{gray!6}{\num{-0.566}} & \cellcolor{gray!6}{\num{-2.496}**} & \cellcolor{gray!6}{\num{-0.568}} & \cellcolor{gray!6}{\num{0.634}}\\
-Hispanic or Latino/x & \num{0.324} & \num{0.116} & \num{0.529}* & \num{0.632}** & \num{-0.585}*\\
-\cellcolor{gray!6}{Num.Obs.} & \cellcolor{gray!6}{\num{948}} & \cellcolor{gray!6}{\num{948}} & \cellcolor{gray!6}{\num{948}} & \cellcolor{gray!6}{\num{948}} & \cellcolor{gray!6}{\num{948}}\\
-\midrule
-$R_{McFadden}^2$ & \num{0.193} & \num{0.121} & \num{0.145} & \num{0.154} & \num{0.221}\\
-\cellcolor{gray!6}{BIC} & \cellcolor{gray!6}{\num{1152.2}} & \cellcolor{gray!6}{\num{1237.6}} & \cellcolor{gray!6}{\num{1048.0}} & \cellcolor{gray!6}{\num{864.8}} & \cellcolor{gray!6}{\num{1104.6}}\\
-Log.Lik. & \num{-524.709} & \num{-567.376} & \num{-472.576} & \num{-380.971} & \num{-500.907}\\
-\bottomrule
-\multicolumn{6}{l}{\rule{0pt}{1em}Raw, Unexponentiated Coefficients}\\
-\multicolumn{6}{l}{\rule{0pt}{1em}* p $<$ .05. ** p $<$ .01. *** p $<$ .001 (two-tailed test).}\\
-\end{tabular}}
-\end{table}
+\input{tables/paper2/table-model-2}
 
@@
 received information from a person like a friend or a relative were
-2.23 times
-more likely to ask their doctor ( \emph{p} \textless{} 0.001), while those who received
-information from the news or television were
-1.55
-times more likely ( \emph{p} \textless{} 0.01). I also find that those who received information
-from an online forum like a subreddit were
-51\%
-more likely to ask their doctors than those who hadn't ( \emph{p} \textless{} 0.05). Finally,
-respondents with an associate's degree or higher were
-72\%
+2.23 times more likely to ask their doctor ( \emph{p} \textless{} 0.001), while those who received
+information from the news or television were 1.55 times more likely ( \emph{p} \textless{} 0.01).
+I also find that those who received information from an online forum like a subreddit were 51\% more likely to ask their doctors than those who hadn't ( \emph{p} \textless{} 0.05).
+Finally, respondents with an associate's degree or higher were 72\%
 more likely to ask their doctor for information on the Covid-19 vaccinations
@@
 networking site is associated with seeking out more information. Those who
-received information from a doctor or other medical professional were
-3.08
+received information from a doctor or other medical professional were 3.08
 times more likely to seek information from a person like a friend ( \emph{p} \textless{} 0.001).
@@
 like a friend or relative, is associated with seeking information from those
-same people; in fact, I find that those who did are
-3.32 more
+same people; in fact, I find that those who did are 3.32 more
 likely to do so ( \emph{p} \textless{} 0.001). Finally, the respondents who received information
-about the vaccine on a social networking site were
-55\%
+about the vaccine on a social networking site were 55\%
 more likely to seek information from their personal network than those who hadn't
@@
 forum was associated with higher odds of querying an online forum. Specifically,
-receiving information from your personal network is associated with
-2.07
-higher odds ( \emph{p} \textless{} 0.001), from news or television media with 1.43 higher odds ( \emph{p} \textless{} 0.05), and
-receiving information on an online forum associated with
-3.55
+receiving information from your personal network is associated with 2.07
+higher odds ( \emph{p} \textless{} 0.001), from news or television media with 1.43 higher odds ( \emph{p} \textless{} 0.05), and receiving information on an online forum associated with 3.55
 higher odds ( \emph{p} \textless{} 0.001). Moreover, I found that those with an associate's
-degree or above were
-2.96 times
+degree or above were 2.96 times 
 more likely to search for information on an online forum ( \emph{p} \textless{} 0.001). Finally,
-I found a racial-ethnic with Hispanic-Latinos; I found that they were about
-70\%
+I found a racial-ethnic with Hispanic-Latinos; I found that they were about 70\%
 more likely to query an online forum than non-Hispanics ( \emph{p} \textless{} 0.05). However,
 there were also a few variables that lowered the odds of posting in an online
-discussion group. First, those who had received information from a social
-networking site were
-45\%
+discussion group. First, those who had received information from a social networking site were 45\%
 less likely to query a forum than those who hadn't (relative odds ratio =
 \(1 - exp(\beta k)\), \emph{p} \textless{} 0.01). Moreover, I find more ethnoracial effects:
-Respondents who claimed Asian ancestry were
-92\%
+Respondents who claimed Asian ancestry were 92\%
 less likely to query online forum ( \emph{p} \textless{} 0.01).
@@
 about Covid-19 seems to be quite related to posting on social media. Those who
-received information from their doctor's had
-1.72
+received information from their doctor's had 1.72
 higher odds of posting on a social networking site ( \emph{p} \textless{} 0.01), while those
@@
 Furthermore, those who received information on social networking sites were more
-likely to post queries on social networking sites (\(\beta\) =
-2.08, \emph{p} \textless{} 0.001).
-The respondents in our sample who received information on online forums had
-2.65
+likely to post queries on social networking sites (\(\beta\) = 2.08, \emph{p} \textless{} 0.001).
+The respondents in our sample who received information on online forums had 2.65
 higher odds of posting queries on their social networking platforms ( \emph{p} \textless{} 0.001).
@@
 queries on social networking sites than those with lower education ( \emph{p} \textless{} 0.001).
-Finally, I find that Hispanic-Latinos were
-88\%
+Finally, I find that Hispanic-Latinos were 88\%
 more likely to ask their connections on a social networking site about the
@@
 models, receiving information of any kind increase the odds of online search,
-though to varying magnitudes (Doctor:
-1.54 odds;
-Person:
-1.44 odds;
-News or Television:
-2.98 odds;
-Social Networking Site:
-3.57 odds;
-Online Forum:
-2 odds).
+though to varying magnitudes (Doctor: 1.54 odds; Person: 1.44 odds; News or Television: 2.98 odds; Social Networking Site: 3.57 odds; Online Forum: 2 odds).
 I also find that older respondents were more likely to search online, with each
-addition year aged to yield
-3\%
+addition year aged to yield 3\%
 higher odds of searching online ( \emph{p} \textless{} 0.001). The most interesting variations
 come from what decreases the odds of online search. First, those with an
-Associate's degree or higher were
-61\%
+Associate's degree or higher were 61\%
 less likely to search online for questions about Covid-19 than those with less
 educational attainment ( \emph{p} \textless{} 0.001). In addition, I find that Hispanic-Latinos
-had 44\%
-lower odds of searching online than non-Hispanics ( \emph{p} \textless{} 0.05).
+had 44\% lower odds of searching online than non-Hispanics ( \emph{p} \textless{} 0.05).
 
@@
 
-\begin{table}[!h]
-
-\caption{\label{tab:table-model-3}Does receiving or searching for information predict vaccination status?}
-\centering
-\begin{tabular}[t]{lc}
-\toprule
-  & Model 1\\
-\midrule
-\cellcolor{gray!6}{Received Info, Doctor} & \cellcolor{gray!6}{\num{1.049}*** (\num{0.301})}\\
-Received Info, Person & \num{-0.206} (\num{0.242})\\
-\cellcolor{gray!6}{Received Info, News} & \cellcolor{gray!6}{\num{0.108} (\num{0.247})}\\
-Received Info, Social Networking Site & \num{-0.794}*** (\num{0.240})\\
-\cellcolor{gray!6}{Received Info, Online Forum} & \cellcolor{gray!6}{\num{-0.321} (\num{0.248})}\\
-Sought Info, Doctor & \num{1.386}*** (\num{0.341})\\
-\cellcolor{gray!6}{Sought Info, Person} & \cellcolor{gray!6}{\num{0.570}* (\num{0.285})}\\
-Sought Info, Social Networking Site & \num{0.710} (\num{0.466})\\
-\cellcolor{gray!6}{Sought Info, Online Forum} & \cellcolor{gray!6}{\num{0.354} (\num{0.342})}\\
-Sought Info, Online Search & \num{0.085} (\num{0.260})\\
-\cellcolor{gray!6}{Age} & \cellcolor{gray!6}{\num{-0.018}+ (\num{0.011})}\\
-Associate's Deg or above & \num{1.281}*** (\num{0.234})\\
-\cellcolor{gray!6}{White} & \cellcolor{gray!6}{\num{1.122} (\num{0.767})}\\
-Black & \num{0.808} (\num{0.799})\\
-\cellcolor{gray!6}{Native American} & \cellcolor{gray!6}{\num{0.126} (\num{0.829})}\\
-Asian & \num{1.555}+ (\num{0.918})\\
-\cellcolor{gray!6}{Hispanic or Latino/x} & \cellcolor{gray!6}{\num{1.039}* (\num{0.505})}\\
-Num.Obs. & \num{936}\\
-\midrule
-\cellcolor{gray!6}{$R_{McFadden}^2$} & \cellcolor{gray!6}{\num{0.261}}\\
-BIC & \num{669.2}\\
-\cellcolor{gray!6}{Log.Lik.} & \cellcolor{gray!6}{\num{-266.187}}\\
-\bottomrule
-\multicolumn{2}{l}{\rule{0pt}{1em}Raw, Unexponentiated Coefficients}\\
-\multicolumn{2}{l}{\rule{0pt}{1em}* p $<$ .05. ** p $<$ .01. *** p $<$ .001 (two-tailed test).}\\
-\end{tabular}
-\end{table}
+\input{tables/paper2/table-model-3}
 
@@
 I find that my respondents who received information on a social networking site
-like Facebook or Twitter about the vaccines were
-55\%
+like Facebook or Twitter about the vaccines were 55\%
 \textbf{less likely} to get vaccinated than those who received no information through
@@
 family or friends with their concerns were
-77\% more likely
-to become vaccinated ( \emph{p} \textless{} 0.05). Furthermore, my respondents who held an
+77\% more likely to become vaccinated ( \emph{p} \textless{} 0.05). Furthermore, my respondents who held an
 Associate's degree or above had 3.6
@@
 non-Asians ( \emph{p} = 0.09). See Figure \ref{fig:plot-model-3} for a visual
-representation of how these different coefficients are related to vaccination
-outlook.
+representation of how these different coefficients are related to vaccination outlook.
 
 \begin{figure}
-
-{\centering \includegraphics[width=0.8\linewidth]{dissertation_files/figure-latex/plot-model-3-1}
-
-}
-
+{\centering \includegraphics[width=0.8\linewidth]{figs/paper2/plot-model-3-1}}
 \caption{Plot of Coefficients, Model 3}\label{fig:plot-model-3}
@@
 of the higher risk of hospitalizations that older populations face
-(Turner et al. 2018). Furthermore, I find that those who are college educated were
+\citep{turner_etal18}. Furthermore, I find that those who are college educated were
 more likely to seek out information; for the most part this trend can be
 observed in Table \ref{tab:table-model-2} as well. Human Capital Theory
-(Mirowsky and Ross 1998) may help to explain this finding; this theory claims that
+\citep{mirowsky_ross98} may help to explain this finding; this theory claims that
 higher education can provides the skills to gain health-related knowledge and
@@
 information; this may be explained by the maltreatment that African Americans
-have endured in the US healthcare system (Bailey et al. 2017)
+have endured in the US healthcare system \citep{baileyStructuralRacismHealth2017}
 which has led to major distrust of the medical establishment among the
-population (Bronson and Nuriddin 2014; Center 2019; Murray 2015).
+population \citep{center2019, murray15, bronson2014don}.
 
@@
 seeking vehicles queried in this survey are conceptually different and that the
-utilization of different varies by demographic and supply (information fountain?
-\textasciitilde{} source of having receiving information). Overall, receiving information about
+utilization of different varies by demographic and supply 
+% TODO (information fountain? \textasciitilde{} source of having receiving information). 
+Overall, receiving information about
 Covid-19 vaccination generally is associated with information seeking behaviors,
@@
 be an example of Uses and Gratification Theory
-(Blumler and Katz 1974), where the two online platforms may act as
+\citep{blumlerUsesMassCommunications1974}, where the two online platforms may act as
 substitute sources of information and those who were satisfied with the
@@
 Given the rampant misinformation around Covid-19, her related vaccinations
-(Motta, Stecula, and Farhart 2020; Pathak, Agarawalla, and Gupta 2020; Shahsavari et al. 2020) and the slowed rate of vaccinations in the
+\citep{pathakInfodemicsCOVID19Role2020, mottaHowRightLeaningMedia2020, shahsavariConspiracyTimeCorona2020}
+and the slowed rate of vaccinations in the
 United States, it is important to uncover what relationship the different
@@
 their patients'' would be ineffective because of the declining number of
-Americans with a primary care doctor (Levine, Linder, and Landon 2020), increasing trust in the
+Americans with a primary care doctor \citep{levine_etal20}, increasing trust in the
 institution of medicine seems to remain a strong predictor of vaccinations.
@@
 \ref{tab:table-model-3}). Research in this area has mixed results, with some
-studies showcasing consistent findings to these (Bagasra, Doan, and Allen 2021; King et al. 2021),
+studies showcasing consistent findings to these \citep{bagasra_etal21,king_etal21},
 while others show that Whites have the lowest levels of vaccine hesitancy and
-many minorities are much more hesitant (Foxworth 2021; Momplaisir et al. 2021). My finding that college-educated respondents were more likely seek
-vaccination is largely consistent with the broader literature
-(Khairat, Zou, and Adler-Milstein 2022), though again there are many variations depending on the vaccine
-in question and study context (Siddiqui, Salmon, and Omer 2013).
+many minorities are much more hesitant \citep{momplaisir_etal21, foxworth21}.
+My finding that college-educated respondents were more likely seek vaccination is largely consistent with the broader literature
+\citep{khairat_etal22}, though again there are many variations depending on the vaccine
+in question and study context \citep{siddiqui_etal13}.
 
@@
 Given the large swaths of both misinformation and disinformation regarding
-Covid-19 (Motta et al. 2020; Pathak et al. 2020; Shahsavari et al. 2020) and the measurable impacts this
-misinformation has had on pandemic-related health behaviors
-(Loomba et al. 2021), Covid-19 provides an ideal study to
+Covid-19 \citep{pathakInfodemicsCOVID19Role2020, mottaHowRightLeaningMedia2020, shahsavariConspiracyTimeCorona2020} and the measurable impacts this misinformation has had on pandemic-related health behaviors
+\citep{loombaMeasuringImpactCOVID192021, greene_murphy21}, Covid-19 provides an ideal study to
 investigate how we choose to search for information that affects both our own
@@
 looking at how individuals search, I aim to identified pain points and focus areas
-for future interventions (receiving information online; ethnoracial variations; ) in the misinformation process.
+for future interventions (receiving information online; ethnoracial variations) in the misinformation process.

### 2022-03-02 paper3.tex
Updates

@@
 
-TODO
-Mirbabaie et al. (2020)
-@ TERNULLO
+% TODO
+\citep{mirbabaie_etal20, ternullo22}
 
@@
 (COVID-19) became a leading cause of death in the United States. Although the
-Centers for Disease Control and Prevention(CDC)
-(2020) proposed several potential
-mitigation strategies, the method of mitigation that received the most national
+Centers for Disease Control and Prevention (CDC) \citeyearpar{centersfordiseasecontrolandpreventionHowProtectYourself2020} proposed several potential mitigation strategies, the method of mitigation that received the most national
 attention is the call to stay-at-home and social distance for non-essential
@@
 variation in how individuals came to understand the threats of the disease
-(Akpan et al. 2021; Bailey et al. 2020), but also due to habitus: the
+\citep{akpanAssociationWhatPeople2021, bailey_etal20}, but also due to habitus: the
 ingrained habits, skills and dispositions of individuals and groups
-(Bourdieu 1977). Habitus shapes how individuals perceive different social
+\citep{bourdieu77}. Habitus shapes how individuals perceive different social
 interactions and norms and shape how they adopt different policies, leading to
-different social outcomes and a divergence of attitudes (Madeira et al. 2018; Scott-Arthur, Brown, and Saukko 2021; Williams 1995).
+different social outcomes and a divergence of attitudes \citep{scottarthur_etal21, williams95, madeira_etal18}.
 
@@
 or disasters. Though research on the causes of population mobility did expand
-after the onset of the Covid-19 pandemic (Bargain and Aminjonov 2020; Bourassa 2020; Bourassa et al.
-2020; Grossman et al.
-2020; Hagger et al.
-2020; Hill, Gonzalez, and Burdette 2020; Hill, Gonzalez, and Davis 2021; Hill, Gonzalez, and Upenieks 2021; Huynh 2020), most research focused on unchanging cultural
-determinants of the reduction in stay-at-home rates. For instance,
-Gibbons, Yang, and Oren (2021) finds that social capital had spatially inconsistent effects on
+after the onset of the Covid-19 pandemic 
+\citep{bargainTrustCompliancePublic2020, bourassaStatelevelStayathomeOrders2020, bourassaSocialDistancingHealth2020, grossmanPoliticalPartisanshipInfluences2020, haggerPredictingSocialDistancing2020, hillBloodChristCompels2020, hillNastiestQuestion, hillLoveThyAged2021,huynhDoesCultureMatter2020}, most research focused on unchanging cultural
+determinants of the reduction in stay-at-home rates. For instance, \citet{gibbons_etal21}
+ finds that social capital had spatially inconsistent effects on
 stay-at-home rates. Instead of focusing on cultural relationships with
@@
 
-There is more research on vaccine uptake
-(Schmid et al. 2017) because of increased hesitancy and
-anti-vaccination movements over previous decades
-(Baumgaertner, Carlisle, and Justwan 2018; Hornsey et al. 2020; Johnson et al. 2020; Whitehead and Perry 2020). While some studies use social network analysis to
-study the discussions for an against vaccinations online
-(Milani, Weitkamp, and Webb 2020), vaccination rates are a great way to
+There is more research on vaccine uptake \citep{schmidBarriersInfluenzaVaccination2017}
+ because of increased hesitancy and
+anti-vaccination movements over previous decades \citep{baumgaertnerInfluencePoliticalIdeology2018, hornseyDonaldTrumpVaccination2020, johnsonOnlineCompetitionPro2020, whiteheadHowCultureWars2020}.
+While some studies use social network analysis to
+study the discussions for an against vaccinations online \citep{milaniVisualVaccineDebate2020}, vaccination rates are a great way to
 investigate the establishment of new social norms. First, vaccination uptake is
@@
 rates are varied across locations and time. Secondly, because vaccines have 
-become politicized (Motta 2021; Motta et al. 2021), the social contagion effects can be
+become politicized \citep{mottaRepublicansNotDemocrats2021, mottaIdentifyingPrevalenceCorrelates2021}, the social contagion effects can be
 studied.
@@
 strongest locally, leading to the emergence of clusters of people sharing
-similar behavior'' (Kitts and Shi 2018). This community
+similar behavior'' \citep{kitts_shi18}. This community
 interaction ultimately leads to converged communities of belief structures with
-variations in how much they diverge from the norm (Cullum and Harton 2007; Latané and Bourgeois 1996; Okada 2017).
+variations in how much they diverge from the norm \citep{cullumCulturalEvolutionInterpersonal2007, lataneExperimentalEvidenceDynamic1996, okadaStructureCulturalRejection2017}.
 
 ``Culture'' diffuses through communities and social networks. Information and
-opinions spread (Robert M. Bond et al. 2012b; Fowler and Christakis 2010; Klar and Shmargad 2017), behaviors are adopted
-(Aral and Nicolaides 2017; Centola 2010, 2011; Christakis and Fowler 2008; Rosenquist et al. 2010) , and there are patterns of health
-contagion (Cacioppo, Fowler, and Christakis 2009; Christakis and Fowler 2007). However,
+opinions spread \citep{bond_etal12, fowler2010cooperative,klarEffectNetworkStructure2017}, behaviors are adopted \citep{aralExerciseContagionGlobal2017, centolaSpreadBehaviorOnline2010, centolaExperimentalStudyHomophily2011,christakis2008collective,rosenquist2010spread}, and there are patterns of health contagion \citep{cacioppo2009alone,christakisSpreadObesityLarge2007}.
+However,
 ``different things spread in different ways and to different extents''
-(Christakis and Fowler 2013, p 563) and when modeling diffusion and
+\citep[p. 563]{christakisSocialContagionTheory2013} and when modeling diffusion and
 contagion, we must be very specific about our scope conditions as they are
 relevant to our theory and not to cross theories to infer connections where they
-may not exist (Kitts and Quintane 2020).
+may not exist \citep{kitts_quintane20}.
 
 Most of the diffusion literature does not focus on establishment of new norms
-but the adoption of culture and specific deviant behaviors (see
-Centola and Baronchelli (2015) for an exception). DellaPosta and
-colleagues (2015) outline how the spread of culture
+but the adoption of culture and specific deviant behaviors 
+\citep[see][for an exception]{centolaSpontaneousEmergenceConventions2015}. 
+\citet{dellapostaWhyLiberalsDrink2015} outline how the spread of culture
 and behavior is tied to network autocorrelation, or ``the tendency for people to
@@
 in sociocultural space can determine the likelihood of the adoption of a new
-behavior. Like Axelrod (1997), this outlines
+behavior. Like \citet{axelrodDisseminationCultureModel1997}, this outlines
 how the local convergence of close network actors becomes amplified and can
@@
 about the risks of behaviors will lead to changes in behaviors to mitigate those
-said risks (e.g. Flay, DiTecco, and Schlegel 1980). However, while this model can be valid in specific
+said risks \citep[e.g.][]{flay_etal80}. However, while this model can be valid in specific
 cases, more research has shown how the risks themselves do little to motivate
-behavioral change (Witte and Allen 2000; Wolburg 2006). Often, an appeal to fear is
+behavioral change \citep{witte_allen00,wolburg06}. Often, an appeal to fear is
 found to be a major driver of the adoption of information campaigns and some
 research has shown that ``social network exposure to COVID-19 cases shapes
-individuals'' beliefs and behaviors concerning the coronavirus''
-(Bailey et al. 2020). Because of this, it is logical that higher local incidences of
+individuals'' beliefs and behaviors concerning the coronavirus'' \citep{bailey_etal20}. Because of this, it is logical that higher local incidences of
 infection would inspire fear and increase adherence to public health measures
@@
 
-Centola and Macy (2007) theorize that simple contagions are not
+\citep{centolaComplexContagionsWeakness2007} theorize that simple contagions are not
 enough to spread behavioral change. Simple contagions are those in which only
@@
 disease or to learn simple bits of information.
-Centola and Macy (2007)'s large contribution was the theorizing
+Centola and Macy \citeyearpar{centolaComplexContagionsWeakness2007}'s large contribution was the theorizing
 of complex contagions, those that require ``independent affirmation or
-reinforcement from multiple sources'' (p 703) and is not based on the number of
+reinforcement from multiple sources'' (p. 703) and is not based on the number of
 exposures but the number of sources of exposure. In the case of behavioral
@@
 \begin{figure}
-
-{\centering \includegraphics[width=0.8\linewidth]{G:/My Drive/R/My Projects/dissertation/figure/paper3/dag}
-
-}
-
+{\centering \includegraphics[width=0.8\linewidth]{figs/paper3/dag}}
 \caption{Elaboratory Theoretical Model of Health Behavior Norms}\label{fig:dag}
@@
 on structural boundaries and homophily as causes of how diffusion occurs,
-Goldberg and Stein (2018) propose a
+\citet{goldbergSocialContagionAssociative2018} propose a
 disrupting alternative mechanism. They argue that what actually diffuses during
@@
 distancing or vaccination uptake \emph{meant} were spreading between populations of
-individuals. Moreover, as Houghton (2021) outlines, diffusants - the things that are
-diffusing through a population, are not independent of each other
-(Mason, Conrey, and Smith 2007). When we take into account the interdependence between different
-beliefs that are diffusing, such as Covid-19 is a hoax, social distancing saves
+individuals. Moreover, as \citet{houghtonSocialContagionInteracting2021} outlines, diffusants - the things that are
+diffusing through a population, are not independent of each other \citep{mason_etal07}.
+When we take into account the interdependence between different beliefs that are diffusing, such as Covid-19 is a hoax, social distancing saves
 lives, the Covid-19 vaccine includes a microchip to control your thoughts, and lockdown
@@
 these various diffusants become associated together into structures of belief
-through schemas of perception (Houghton 2021). While this cognitive theory of
-cultural variation is difficult to test, the theory it supplies provides a solid
-framework for how behavioral norms formed during the pandemic.
+through schemas of perception \citep{houghtonSocialContagionInteracting2021}.
+While this cognitive theory of cultural variation is difficult to test, the theory it supplies provides a solid framework for how behavioral norms formed during the pandemic.
 
 \begin{figure}
-
-{\centering \includegraphics[width=0.8\linewidth]{G:/My Drive/R/My Projects/dissertation/figure/paper3/model}
-
-}
-
+{\centering \includegraphics[width=0.8\linewidth]{figs/paper3/model}}
 \caption{Preliminary model of norm formation}\label{fig:norm-framework}
@@
 they are presented with. Individuals look to norms to regulate behavior, avoid
-deviance, and to maintain order (Horne and Mollborn 2020; Shepherd 2017); when they don't have a normative behavior
+deviance, and to maintain order \citep{horneNormsIntegratedFramework2020, shepherdStructurePerceptionHow2017}; when they don't have a normative behavior
 to follow (or rebel against), individuals look to the other sources in their
@@
 happen if I do nothing about this norm). Following both the Integrated
-Theoretical Framework of Norms (Horne and Mollborn 2020) and
-associative diffusion (DellaPosta et al. 2015; Goldberg and Stein 2018), I theorize that individuals interpret
+Theoretical Framework of Norms \citep{horneNormsIntegratedFramework2020} and
+associative diffusion \citep{dellapostaWhyLiberalsDrink2015, goldbergSocialContagionAssociative2018}, I theorize that individuals interpret
 signals from their ``community'' through their cognitive biases and behavioral
@@
 scientific ideologies which I theorize leads more religious counties to reject
-the stay-at-home order and vaccines (Evans and Evans 2008)
+the stay-at-home order and vaccines \citep{evansReligionScienceEpistemological2008}
 because the associative diffusion of these behaviors pits public health
@@
 Furthermore, as COVID-19 has become a politically polarizing issue, conservative
-ideology and a general mistrust of ``big government'' (Frank 2007; Gauchat 2012) are likely to lead to resistance to the
+ideology and a general mistrust of ``big government'' \citep{frank2007, gauchat2008} are likely to lead to resistance to the
 government and scientific guidance.
@@
 
-\begin{table}[!h]
+\input{tables/paper3/google-desc-table}
 
-\caption{\label{tab:google-desc-table}Descriptive Statistics for Stay-at-Home Models (county-level)}
-\centering
-\begin{tabular}[t]{lrrrr}
-\toprule
-  & min & max & mean & sd\\
-\midrule
-Percent White & \num{0.14} & \num{0.98} & \num{0.81} & \num{0.15}\\
-Percent College Graduates & \num{0.08} & \num{0.75} & \num{0.26} & \num{0.10}\\
-Percent over 65 & \num{6.60} & \num{56.70} & \num{16.90} & \num{4.05}\\
-Median Income & \num{28951.00} & \num{142299.00} & \num{59773.61} & \num{15264.50}\\
-Monthly Unemployment Rate & \num{1.40} & \num{34.60} & \num{8.12} & \num{4.00}\\
-Percent of GOP votes, 2016 & \num{0.08} & \num{0.90} & \num{0.57} & \num{0.15}\\
-Percent Evangelical Christian & \num{0.00} & \num{0.67} & \num{0.20} & \num{0.14}\\
-'Fox News' Trend & \num{0.00} & \num{204.08} & \num{29.59} & \num{16.94}\\
-'Social Distancing' Trend & \num{0.00} & \num{500.00} & \num{20.64} & \num{25.36}\\
-'Covid Conspiracy' Trend & \num{0.00} & \num{825.00} & \num{42.51} & \num{80.44}\\
-Covid Case Rate & \num{0.00} & \num{343.71} & \num{21.17} & \num{27.44}\\
-Week Number & \num{0.00} & \num{43.00} & \num{23.14} & \num{11.77}\\
-Movement Signal & \num{-2.06} & \num{26.44} & \num{8.31} & \num{4.22}\\
-Movement Discordance & \num{0.15} & \num{11.05} & \num{2.22} & \num{0.80}\\
-\bottomrule
-\multicolumn{5}{l}{\rule{0pt}{1em}Raw values presented in table. Values in models are normalized.}\\
-\multicolumn{5}{l}{\rule{0pt}{1em}Notes: 1,375 counties, March 02 through December 28, 2020.}\\
-\end{tabular}
-\end{table}
 \begin{figure}
-
-{\centering \includegraphics[width=0.8\linewidth]{dissertation_files/figure-latex/plot-google-1}
-
-}
-
+{\centering \includegraphics[width=0.8\linewidth]{figs/paper3/plot-google-1}}
 \caption{Stay at Home Rates over Time}\label{fig:plot-google}
@@
 My first dependent variable aims to operationalize behavioral norms as
-stay-at-home rates with data from Google (Google 2020). While the Google
+stay-at-home rates with data from Google \citep{google2020}. While the Google
 COVID-19 Community Mobility Reports include multiple measures of mobility based
@@
 
-\begin{table}[!h]
+\input{tables/paper3/vacc-desc-table}
 
-\caption{\label{tab:vacc-desc-table}Descriptive Statistics for Vaccination Models (county-level)}
-\centering
-\begin{tabular}[t]{lrrrr}
-\toprule
-  & min & max & mean & sd\\
-\midrule
-Percent White & \num{0.08} & \num{1.00} & \num{0.83} & \num{0.17}\\
-Percent College Graduates & \num{0.03} & \num{0.78} & \num{0.22} & \num{0.10}\\
-Percent over 65 & \num{3.20} & \num{56.70} & \num{18.86} & \num{4.50}\\
-Median Income & \num{21504.00} & \num{142299.00} & \num{53522.45} & \num{14312.25}\\
-Monthly Unemployment Rate & \num{0.90} & \num{22.00} & \num{4.96} & \num{1.95}\\
-Percent of GOP votes, 2020 & \num{0.09} & \num{0.94} & \num{0.64} & \num{0.16}\\
-Percent Evangelical Christian & \num{0.00} & \num{1.31} & \num{0.22} & \num{0.16}\\
-'Fox News' Trend & \num{5.00} & \num{405.88} & \num{72.12} & \num{27.38}\\
-'Covid-19 vaccine' Trend & \num{0.00} & \num{755.56} & \num{74.67} & \num{70.33}\\
-'Covid Conspiracy' Trend & \num{0.00} & \num{2000.00} & \num{56.05} & \num{189.61}\\
-Covid Case Rate & \num{0.00} & \num{998.58} & \num{22.79} & \num{27.23}\\
-Week Number & \num{1.00} & \num{35.00} & \num{18.00} & \num{10.10}\\
-Vaccination Signal & \num{0.00} & \num{62.84} & \num{19.62} & \num{14.84}\\
-Vaccination Discordance & \num{0.00} & \num{22.40} & \num{5.26} & \num{3.62}\\
-\bottomrule
-\multicolumn{5}{l}{\rule{0pt}{1em}Raw values presented in table. Values in Models are normalized.}\\
-\multicolumn{5}{l}{\rule{0pt}{1em}Notes: 2,819 counties, January 04 through August 30, 2021.}\\
-\end{tabular}
-\end{table}
 \begin{figure}
-
-{\centering \includegraphics[width=0.8\linewidth]{dissertation_files/figure-latex/plot-vacc-1}
-
-}
-
+{\centering \includegraphics[width=0.8\linewidth]{figs/paper3/plot-vacc-1}}
 \caption{Vaccination Rates over Time}\label{fig:plot-vacc}
@@
 vaccination rate information in the United States from January 2021 through
-August 30 2021 (CDC 2021). Data represents all vaccine partners including
+August 30 2021 \citep{cdcCOVID19Vaccination2021}. Data represents all vaccine partners including
 jurisdictional partner clinics, retail pharmacies, long-term care facilities,
@@
 likelihood of friendship connection comes from the ``Social Connectedness Index''
-(Bailey, Rachel Cao, et al. 2018; Facebook 2020) which indexes the social links between geographies by
+\citep{Bailey2018, facebook20} which indexes the social links between geographies by
 the likelihood of Facebook friends. It is an aggregated measure of Facebook
@@
 population and Facebook friendship links largely represent real-world
-friendships (Bailey, Ruiqing Cao, et al. 2018; Jones et al. 2013). The data has been tested to show
+friendships \citep{bailey_etal18, jones_etal13}. The data has been tested to show
 how initial COVID-19 hotspots are related to subsequent virus spread to
 non-hotspots, even after controlling for population density and geographic
-distance (Kuchler, Russel, and Stroebel 2020).
+distance \citep{Kuchler2020}.
 
@@
 for 7 selected counties.\footnote{Figures in this paper were all created using ggplot2
-  (Wickham 2011; Wickham et al. n.d.), patchwork (Pedersen n.d.), and ggridges (Wilke n.d.)}
+\citep{wickham_etal, wickham11}, patchwork \citep{pedersen20}, and ggridges \citep{ggridges}}
 While a county like Lake County, Ohio has low discordance meaning the signal of
@@
 \begin{figure}
-
-{\centering \includegraphics[width=0.7\linewidth]{dissertation_files/figure-latex/assortativity-vacc-1}
-
-}
-
+{\centering \includegraphics[width=0.7\linewidth]{figs/paper3/assortativity-vacc-1}}
 \caption{How Signal Mean and Signal Assortativity are Measured}\label{fig:assortativity-vacc}
@@
 \begin{figure}
-
-\begin{center}\includegraphics[width=0.5\linewidth,]{dissertation_files/figure-latex/discordancenetwork-1} \end{center}
+\begin{center}\includegraphics[width=0.5\linewidth,]{figs/paper3/discordancenetwork-1} 
   \begin{equation}
@@
   \label{fig:discordancenetwork}
+  \end{center}
 \end{figure}
@@
 \ref{fig:norm-framework}, the models use county-level Covid-19 case rates with
-data compiled by The New York Times (2022). It is widely acknowledged that there are biases in
-this data due to inconsistencies and availability in testing as well as
-different community propensity to test (CDC 2020b; Gu n.d.) However, it is the best
+data compiled by The New York Times \citeyearpar{covid_data}. It is widely acknowledged that there are biases in this data due to inconsistencies and availability in testing as well as
+different community propensity to test \citep{gu22, cdc20a}. However, it is the best
 measure we have of actual case rates. County data are scaled with a rolling mean
@@
 
-To operationalize the search for online norms, I use Google search trends (Google 2022),
+To operationalize the search for online norms, I use Google search trends \citep{googletrends},
 over the study period across individual designated media markets areas (DMAs), a
 nonoverlapping aggregation of U.S. counties to 210 media markets based on
-similar population clusters (Sood 2016). To investigate the rate of \emph{searching} for norms
+similar population clusters \citep{dma_key}. To investigate the rate of \emph{searching} for norms
 online in both cases, I use the following search topics: `Social Distancing'
@@
 compared against time-series data for multiple test counties and was equivalent.
-For a more in-depth explanation of this procedure, see Park et al. (n.d.) (p.~5).
+For a more in-depth explanation of this procedure, see \citet[p. 5]{park_etal}.
 
@@
 Research has shown that stay-at-home rates and other pandemic health behaviors
-are related to various `pillars of conservatism' (Gonzalez et al. 2021; Hill et al. 2020; Hill et al. 2021, 2021). Namely, research shows that politically conservative
+are related to various `pillars of conservatism' \citep{gonzalez_etal21,hillBloodChristCompels2020,hillLoveThyAged2021, hillNastiestQuestion}. Namely, research shows that politically conservative
 indicators, such as Republican political leadership, conservative Protestantism
@@
 Christians. These county-level data were collected through the 2010 U.S.
-Religion Census: Religious Congregations and Membership Study
-(Grammich et al. 2018). Finally, right-wing media consumption is assessed using
+Religion Census: Religious Congregations and Membership Study \citep{grammich_etal18}. Finally, right-wing media consumption is assessed using
 Google Search Trends to capture ``Fox News'' searches over the study period across
@@
 validated for use in a range of research contexts and for use with survey data,
-voting data, and ecological data (Bail, Brown, and Wimmer 2019; Reyes, Majluf, and Ibáñez 2018; Scheitle 2011; Stephens-Davidowitz 2014; Swearingen and Ripberger 2014).
+voting data, and ecological data \citep{bailPrestigeProximityPrejudice2019, reyesUsingInternetSearch2018, scheitleGoogleInsightsSearch2011, stephensdavidowitzCostRacialAnimus2014, swearingenGoogleInsightsSenate2014}.
 
@@
 degree, (4) median income, and (5) monthly county unemployment rate. Measures 1
-through 4 are obtained from the 2018 American Community Survey: 5-Year Estimates
-(US Census Bureau 2018); unemployment rates are gathered
-from the U.S. Bureau of Labor Statistics (Labor Statistics 2021).
+through 4 are obtained from the 2018 American Community Survey: 5-Year Estimates \citep{uscensusbureauAmericanCommunitySurvey2018}; unemployment rates are gathered
+from the U.S. Bureau of Labor Statistics \citep{labor2020a}.
 
@@
 three linear mixed effects regression models using the nlme package in R
-(Pinheiro et al. 2021; Pinheiro and Bates 2000) for our two cases, Stay-at-Home rates and
+\citep{pinheiro_etal21, pinheiro_bates00} for our two cases, Stay-at-Home rates and
 Vaccination rates. Linear mixed effects models are a form of hierarchical linear
@@
 
-\begin{table}[!h]
-
-\caption{\label{tab:google-tab}Linear Mixed Effects Regression Results for Stay-At-Home Rates}
-\centering
-\fontsize{8}{10}\selectfont
-\begin{tabular}[t]{lccc}
-\toprule
-  & Model 1 & Model 2 & Model 3\\
-\midrule
-Percent White & \num{0.088}*** & \num{0.058}** & \num{0.060}**\\
- & (\num{0.023}) & (\num{0.019}) & (\num{0.019})\\
-Percent College Graduates & \num{-0.016} & \num{0.010} & \num{0.020}\\
- & (\num{0.028}) & (\num{0.023}) & (\num{0.024})\\
-Percent over 65 & \num{-0.034}+ & \num{-0.031}* & \num{-0.037}*\\
- & (\num{0.018}) & (\num{0.015}) & (\num{0.015})\\
-Median Income & \num{-0.042} & \num{-0.032} & \num{0.015}\\
- & (\num{0.030}) & (\num{0.024}) & (\num{0.025})\\
-Monthly Unemployment Rate & \num{0.087}*** & \num{0.012}*** & \num{0.065}***\\
- & (\num{0.003}) & (\num{0.003}) & (\num{0.004})\\
-Percent of GOP votes, 2016 & \num{0.077}* & \num{0.043} & \num{0.017}\\
- & (\num{0.032}) & (\num{0.026}) & (\num{0.027})\\
-Percent Evangelical Christian & \num{-0.016} & \num{-0.008} & \num{-0.014}\\
- & (\num{0.022}) & (\num{0.018}) & (\num{0.019})\\
-'Fox News' Trend & \num{-0.030}*** & \num{-0.028}*** & \num{-0.026}***\\
- & (\num{0.001}) & (\num{0.001}) & \vphantom{1} (\num{0.001})\\
-'Social Distancing' Trend & \num{0.011}*** & \num{0.004}* & \num{0.001}\\
- & (\num{0.002}) & (\num{0.002}) & \vphantom{1} (\num{0.002})\\
-'Covid Conspiracy' Trend & \num{0.024}*** & \num{0.006}*** & \num{0.010}***\\
- & (\num{0.002}) & (\num{0.002}) & (\num{0.002})\\
-Covid Case Rate & \num{0.000} & \num{-0.009}* & \num{-0.007}+\\
- & (\num{0.004}) & (\num{0.004}) & (\num{0.004})\\
-Week Number & \num{-0.002}+ & \num{-0.002}* & \num{-0.004}***\\
- & (\num{0.001}) & (\num{0.001}) & (\num{0.001})\\
-Stay at Home Rate, county mean & \num{0.898}*** & \num{0.873}*** & \num{0.846}***\\
- & (\num{0.059}) & (\num{0.048}) & (\num{0.050})\\
-Signal &  & \num{0.473}*** & \num{0.550}***\\
- &  & (\num{0.005}) & (\num{0.008})\\
-Signal x Week &  & \num{-0.016}*** & \num{-0.018}***\\
- &  & (\num{0.000}) & (\num{0.000})\\
-Signal Discordance &  &  & \num{-0.101}***\\
- &  &  & (\num{0.004})\\
-Signal x Signal Discordance &  &  & \num{-0.092}***\\
- &  &  & (\num{0.002})\\
-\midrule
-Log.Lik. & \num{-23007.044} & \num{-19555.920} & \num{-18655.837}\\
-\bottomrule
-\multicolumn{4}{l}{\rule{0pt}{1em}N = 57,356, N of random Effects = 1375}\\
-\multicolumn{4}{l}{\rule{0pt}{1em}Models 2-3 include a random effect for Movement Signal by FIPS}\\
-\multicolumn{4}{l}{\rule{0pt}{1em}Model 1 includes a random intercept for FIPS,}\\
-\multicolumn{4}{l}{\rule{0pt}{1em}* p $<$ .05. ** p $<$ .01. *** p $<$ .001 (two-tailed test).}\\
-\end{tabular}
-\end{table}
+\input{tables/paper3/google-tab}
 
@@
 \begin{figure}
-
-{\centering \includegraphics[width=0.8\linewidth]{dissertation_files/figure-latex/plot-google-h2-1}
-
-}
-
+{\centering \includegraphics[width=0.8\linewidth]{figs/paper3/plot-google-h2-1}}
 \caption{Predicted Values of Stay at Home Rate by Movement Signal}\label{fig:plot-google-h2}
@@
 \begin{figure}
-
-{\centering \includegraphics[width=0.8\linewidth]{dissertation_files/figure-latex/plot-google-h3-1}
-
-}
-
+{\centering \includegraphics[width=0.8\linewidth]{figs/paper3/plot-google-h3-1}}
 \caption{Predicted Values of Stay at Home Rate Moderated}\label{fig:plot-google-h3}
@@
 
-\begin{table}[!h]
-
-\caption{\label{tab:vacc-tab}Linear Mixed Effects Regression Results for Vaccination Rates}
-\centering
-\fontsize{8}{10}\selectfont
-\begin{tabular}[t]{lccc}
-\toprule
-  & Model 1 & Model 2 & Model 3\\
-\midrule
-Percent White & \num{0.023}+ & \num{-0.029}*** & \num{-0.027}***\\
- & (\num{0.012}) & (\num{0.003}) & (\num{0.003})\\
-Percent College Graduates & \num{-0.004} & \num{0.009}* & \num{0.010}*\\
- & (\num{0.013}) & (\num{0.004}) & (\num{0.004})\\
-Percent over 65 & \num{-0.012} & \num{-0.002} & \num{0.000}\\
- & (\num{0.008}) & (\num{0.002}) & (\num{0.002})\\
-Median Income & \num{0.002} & \num{-0.017}*** & \num{-0.016}***\\
- & (\num{0.011}) & (\num{0.003}) & (\num{0.003})\\
-Monthly Unemployment Rate & \num{-0.031}*** & \num{-0.014}*** & \num{-0.013}***\\
- & (\num{0.001}) & (\num{0.001}) & (\num{0.001})\\
-Percent of GOP votes, 2020 & \num{-0.070}*** & \num{0.031}*** & \num{0.028}***\\
- & (\num{0.014}) & (\num{0.004}) & (\num{0.004})\\
-Percent Evangelical Christian & \num{0.000} & \num{0.000} & \num{-0.001}\\
- & (\num{0.009}) & (\num{0.003}) & (\num{0.003})\\
-'Fox News' Trend & \num{0.002}*** & \num{0.000} & \num{0.000}*\\
- & (\num{0.000}) & (\num{0.000}) & \vphantom{4} (\num{0.000})\\
-'Vaccine' Trend & \num{-0.001}*** & \num{0.000} & \num{0.000}+\\
- & (\num{0.000}) & (\num{0.000}) & \vphantom{3} (\num{0.000})\\
-'Covid Conspiracy' Trend & \num{0.000}* & \num{0.001}*** & \num{0.001}***\\
- & (\num{0.000}) & (\num{0.000}) & \vphantom{2} (\num{0.000})\\
-Covid Case Rate & \num{-0.008}*** & \num{0.001}*** & \num{0.001}***\\
- & (\num{0.000}) & (\num{0.000}) & \vphantom{1} (\num{0.000})\\
-Week Number & \num{0.067}*** & \num{0.011}*** & \num{0.011}***\\
- & (\num{0.000}) & (\num{0.000}) & (\num{0.000})\\
-Vaccination Rate, county mean & \num{0.800}*** & \num{0.201}*** & \num{0.170}***\\
- & (\num{0.018}) & (\num{0.005}) & (\num{0.005})\\
-Vaccination Signal &  & \num{0.854}*** & \num{0.865}***\\
- &  & (\num{0.005}) & (\num{0.006})\\
-Vaccination Signal x Week &  & \num{-0.005}*** & \num{-0.003}***\\
- &  & (\num{0.000}) & (\num{0.000})\\
-Vaccination Discordance &  &  & \num{-0.072}***\\
- &  &  & \vphantom{1} (\num{0.002})\\
-Vaccination Signal x Discordance &  &  & \num{-0.051}***\\
- &  &  & (\num{0.002})\\
-\midrule
-Log.Lik. & \num{118677.013} & \num{160000.978} & \num{160638.703}\\
-\bottomrule
-\multicolumn{4}{l}{\rule{0pt}{1em}N = 99,890, N of random Effects = 2819}\\
-\multicolumn{4}{l}{\rule{0pt}{1em}Models 2-3 include a random effect for Movement Signal by FIPS}\\
-\multicolumn{4}{l}{\rule{0pt}{1em}Model 1 includes a random intercept for FIPS,}\\
-\multicolumn{4}{l}{\rule{0pt}{1em}* p $<$ .05. ** p $<$ .01. *** p $<$ .001 (two-tailed test).}\\
-\end{tabular}
-\end{table}
+\input{tables/paper3/vacc-tab}
 
@@
 a good indicator that adjacent time points for each county are related and this
-is an appropriate modeling technique for the data (Finch et al. 2014). Table
+is an appropriate modeling technique for the data \citep{finch_etal14}. Table
 \ref{tab:vacc-tab} Model 1 addresses hypothesis 1, that relatively higher local
@@
 Hypothesis 1 also returns surprising results: every 1 standard deviation
-increase in county Covid-19 case rates is expected to yield a
--0.008
-decrease in vaccination rates. This may be due to time ordering or reverse
+increase in county Covid-19 case rates is expected to yield a -0.008 decrease in vaccination rates. This may be due to time ordering or reverse
 causality, where individuals in counties who have higher rates of vaccination
@@
 \begin{figure}
-
-{\centering \includegraphics[width=0.8\linewidth]{dissertation_files/figure-latex/plot-vacc-h2-1}
-
-}
-
+{\centering \includegraphics[width=0.8\linewidth]{figs/paper3/plot-vacc-h2-1}}
 \caption{Predicted Values of Vaccination Rate}\label{fig:plot-vacc-h2}
@@
 \begin{figure}
-
-{\centering \includegraphics[width=0.8\linewidth]{dissertation_files/figure-latex/plot-vacc-h3-1}
-
-}
-
+{\centering \includegraphics[width=0.8\linewidth]{figs/paper3/plot-vacc-h3-1}}
 \caption{Predicted Values of Vaccination Rate}\label{fig:plot-vacc-h3}
@@
 or significance of the coefficients. Vaccination signal maintains to have a positive
-effect on the alter's vaccination rates, while vaccination discordance has a negative effect on vaccination rates, where every one standard deviation increase in discordance lowers rates by
--0.072
-(\emph{p} \textless{} 0.001). The interaction between signal and signal discordance have a
-coefficient of a similar magnitude, with every one standard deviation increase
-in discordance \emph{and} signal resulting in\\
+effect on the alter's vaccination rates, while vaccination discordance has a negative effect on vaccination rates, where every one standard deviation increase in discordance lowers rates by -0.072 (\emph{p} \textless{} 0.001).
+The interaction between signal and signal discordance have a coefficient of a similar magnitude, with every one standard deviation increase
+in discordance \emph{and} signal resulting in 
 lower rates of vaccination. Figure \ref{fig:plot-vacc-h3} illustrates this
@@
 This study is sensitive to aggregation error and sampling error derived from the
-multiple big-data sources (Facebook 2020; Google 2020). The aggregation errors are
+multiple big-data sources \citep{facebook20, google2020}. The aggregation errors are
 potentially linked to the assumption that the average stay-at-home behavior of a
@@
 using big data from the natural experiment of Covid-19. Because most studies of
-complex contagion utilize agent-based modeling or studies of social media
-(Aral and Nicolaides 2017; Robert M. Bond et al. 2012a; Latané, Nowak, and Liu 1994; Sprague and House 2017), combining measures of actual behavioral outcomes with data from
+complex contagion utilize agent-based modeling or studies of social media \citep{aralExerciseContagionGlobal2017,sprague_house17,bond_etal12,latane_etal94}, combining measures of actual behavioral outcomes with data from
 social media websites provides a further test of ecological and external
@@
 reinforcing actors, while other theories focus on how different diffusants
-interact with each other (Goldberg and Stein 2018; Houghton 2021; Mason et al. 2007). Discordance, on the other hand, looks specifically at the
-context of the reinforcing actors among the other signals. This study finds that
-indeed the context of the signals matters for diffusion.
+interact with each other \citep{houghton20,goldbergSocialContagionAssociative2018,mason_etal07}.
+Discordance, on the other hand, looks specifically at the context of the reinforcing actors among the other signals.
+This study finds that indeed the context of the signals matters for diffusion.

### 2022-03-02 tables/paper1/data-sources-table.tex
Updates

\begin{table}[!h]
\caption{\label{tab:data-sources-table}}
\centering
\begin{tabular}[t]{}
\end{tabular}
\end{table}

### 2022-03-02 tables/paper2/model-2-phi.tex
Updates

\begin{table}[!h]

\caption{\label{tab:model-2-phi}Phi Coefficient ($\phi$) of binary association between each Information Search Vehicle}
\centering
\begin{tabular}[t]{p{0.25\linewidth} p{0.10\linewidth} p{0.08\linewidth} p{0.12\linewidth} p{0.15\linewidth} p{0.12\linewidth}}
\hline
 & Person & Dr & Online Forum & Social Networking Site & Online Search\\
\hline
\cellcolor{gray!6}{Person} & \cellcolor{gray!6}{NA} & \cellcolor{gray!6}{0.28} & \cellcolor{gray!6}{0.172} & \cellcolor{gray!6}{0.275} & \cellcolor{gray!6}{0.216}\\

Dr & NA & NA & 0.192 & 0.152 & 0.098\\

\cellcolor{gray!6}{Online Forum} & \cellcolor{gray!6}{NA} & \cellcolor{gray!6}{NA} & \cellcolor{gray!6}{NA} & \cellcolor{gray!6}{0.371} & \cellcolor{gray!6}{-0.073}\\

Social Networking Site & NA & NA & NA & NA & 0.057\\

\cellcolor{gray!6}{Online Search} & \cellcolor{gray!6}{NA} & \cellcolor{gray!6}{NA} & \cellcolor{gray!6}{NA} & \cellcolor{gray!6}{NA} & \cellcolor{gray!6}{NA}\\
\hline
\end{tabular}
\end{table}

### 2022-03-02 tables/paper2/table-1-desc.tex
Updates

\begin{table}[!h]

\caption{\label{tab:table-1-desc}Descriptive Statistics for Dichotomous and Numeric Variables}
\centering
\begin{tabular}[t]{lrr}
\toprule
  & Mean & SD\\
\midrule
\cellcolor{gray!6}{Received info} & \cellcolor{gray!6}{\num{0.66}} & \cellcolor{gray!6}{\num{0.47}}\\
Received info, Doctor & \num{0.47} & \num{0.50}\\
\cellcolor{gray!6}{Received info, Person} & \cellcolor{gray!6}{\num{0.67}} & \cellcolor{gray!6}{\num{0.47}}\\
Received info, News & \num{0.65} & \num{0.48}\\
\cellcolor{gray!6}{Received info, Social Networking Site} & \cellcolor{gray!6}{\num{0.40}} & \cellcolor{gray!6}{\num{0.49}}\\
Received info, Online Forum & \num{0.35} & \num{0.48}\\
\cellcolor{gray!6}{Sought Info} & \cellcolor{gray!6}{\num{0.78}} & \cellcolor{gray!6}{\num{0.41}}\\
Sought Info, Doctor & \num{0.44} & \num{0.50}\\
\cellcolor{gray!6}{Sought Info, Person} & \cellcolor{gray!6}{\num{0.42}} & \cellcolor{gray!6}{\num{0.49}}\\
Sought Info, Social Networking Site & \num{0.18} & \num{0.39}\\
\cellcolor{gray!6}{Sought Info, Online Forum} & \cellcolor{gray!6}{\num{0.27}} & \cellcolor{gray!6}{\num{0.44}}\\
Sought Info, Online Search & \num{0.41} & \num{0.49}\\
\cellcolor{gray!6}{Vaccination Status} & \cellcolor{gray!6}{\num{0.84}} & \cellcolor{gray!6}{\num{0.36}}\\
Vaccination Outlook & \num{0.87} & \num{0.34}\\
\cellcolor{gray!6}{Age} & \cellcolor{gray!6}{\num{37.76}} & \cellcolor{gray!6}{\num{10.75}}\\
Hispanic or Latino/x & \num{0.15} & \num{0.36}\\
\cellcolor{gray!6}{Race, White} & \cellcolor{gray!6}{\num{0.88}} & \cellcolor{gray!6}{\num{0.33}}\\
Race, Black & \num{0.08} & \num{0.27}\\
\cellcolor{gray!6}{Race, Native American} & \cellcolor{gray!6}{\num{0.03}} & \cellcolor{gray!6}{\num{0.16}}\\
Race, Asian or Pacific Islander & \num{0.04} & \num{0.20}\\
\cellcolor{gray!6}{Associate's Deg or above} & \cellcolor{gray!6}{\num{0.74}} & \cellcolor{gray!6}{\num{0.44}}\\
\bottomrule
\multicolumn{3}{l}{\rule{0pt}{1em}Notes: 948 Surveyed, Conducted December 03 through December 12, 2021.}\\
\end{tabular}
\end{table}

### 2022-03-02 tables/paper2/table-2-desc.tex
Updates

\begin{table}[!h]

\caption{\label{tab:table-2-desc}Descriptive Statistics for Categorical Variables}
\centering
\begin{tabular}[t]{llrr}
\toprule
  &    & N & Percent\\
\midrule
\cellcolor{gray!6}{Gender} & \cellcolor{gray!6}{Female} & \cellcolor{gray!6}{418} & \cellcolor{gray!6}{\num{44.09}}\\
 & Male & 524 & \num{55.27}\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Other} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{\num{0.63}}\\
Highest Education Level & Graduate or professional degree & 145 & \num{15.30}\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Bachelor's degree} & \cellcolor{gray!6}{560} & \cellcolor{gray!6}{\num{59.07}}\\
 & Associate's or Technical degree & 72 & \num{7.59}\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Some college} & \cellcolor{gray!6}{100} & \cellcolor{gray!6}{\num{10.55}}\\
 & High school graduate & 68 & \num{7.17}\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Less than high school} & \cellcolor{gray!6}{3} & \cellcolor{gray!6}{\num{0.32}}\\
Plan to be Vaccinated if not & Probably not & 38 & \num{4.01}\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Definitely yes} & \cellcolor{gray!6}{13} & \cellcolor{gray!6}{\num{1.37}}\\
 & Definitely not & 61 & \num{6.43}\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Might or might not} & \cellcolor{gray!6}{22} & \cellcolor{gray!6}{\num{2.32}}\\
 & Probably yes & 13 & \num{1.37}\\
\cellcolor{gray!6}{Found Info Sought Useful} & \cellcolor{gray!6}{Very useful} & \cellcolor{gray!6}{345} & \cellcolor{gray!6}{\num{36.39}}\\
 & Moderately useful & 112 & \num{11.81}\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Extremely useful} & \cellcolor{gray!6}{264} & \cellcolor{gray!6}{\num{27.85}}\\
 & Slightly useful & 18 & \num{1.90}\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Not at all useful} & \cellcolor{gray!6}{2} & \cellcolor{gray!6}{\num{0.21}}\\
Census Region & Midwest & 171 & \num{18.04}\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{Northeast} & \cellcolor{gray!6}{170} & \cellcolor{gray!6}{\num{17.93}}\\
 & South & 365 & \num{38.50}\\
\cellcolor{gray!6}{} & \cellcolor{gray!6}{West} & \cellcolor{gray!6}{223} & \cellcolor{gray!6}{\num{23.52}}\\
\bottomrule
\multicolumn{4}{l}{\rule{0pt}{1em}Notes: 948 Surveyed, Conducted December 03 through December 12, 2021.}\\
\end{tabular}
\end{table}

### 2022-03-02 tables/paper2/table-model-2.tex
Updates

\begin{table}[!h]

\caption{\label{tab:table-model-2}What predicts someone intentionally searched for information, by vehicle of information search}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{llllll}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{5}{c}{Dependent Variable} \\
\cmidrule(l{3pt}r{3pt}){2-6}
  & Doctor & Person & Online Forum & Social Networking Site & Online Search\\
\midrule
\cellcolor{gray!6}{Received Info, Doctor} & \cellcolor{gray!6}{\num{1.942}***} & \cellcolor{gray!6}{\num{1.124}***} & \cellcolor{gray!6}{\num{0.181}} & \cellcolor{gray!6}{\num{0.540}**} & \cellcolor{gray!6}{\num{0.430}**}\\
Received Info, Person & \num{0.800}*** & \num{1.199}*** & \num{0.728}*** & \num{0.281} & \num{0.365}*\\
\cellcolor{gray!6}{Received Info, News} & \cellcolor{gray!6}{\num{0.437}**} & \cellcolor{gray!6}{\num{0.100}} & \cellcolor{gray!6}{\num{0.359}*} & \cellcolor{gray!6}{\num{0.514}*} & \cellcolor{gray!6}{\num{1.091}***}\\
Received Info, Social Networking Site & \num{-0.130} & \num{0.437}** & \num{-0.603}** & \num{0.731}*** & \num{1.272}***\\
\cellcolor{gray!6}{Received Info, Online Forum} & \cellcolor{gray!6}{\num{0.412}*} & \cellcolor{gray!6}{\num{0.263}+} & \cellcolor{gray!6}{\num{1.266}***} & \cellcolor{gray!6}{\num{0.974}***} & \cellcolor{gray!6}{\num{0.695}***}\\
Age & \num{0.002} & \num{0.001} & \num{-0.007} & \num{-0.003} & \num{0.029}***\\
\cellcolor{gray!6}{Associate's Deg or above} & \cellcolor{gray!6}{\num{0.542}**} & \cellcolor{gray!6}{\num{0.154}} & \cellcolor{gray!6}{\num{1.086}***} & \cellcolor{gray!6}{\num{1.344}***} & \cellcolor{gray!6}{\num{-0.952}***}\\
White & \num{0.631} & \num{0.245} & \num{0.009} & \num{0.559} & \num{0.012}\\
\cellcolor{gray!6}{Black} & \cellcolor{gray!6}{\num{0.366}} & \cellcolor{gray!6}{\num{0.208}} & \cellcolor{gray!6}{\num{0.608}} & \cellcolor{gray!6}{\num{0.646}} & \cellcolor{gray!6}{\num{0.357}}\\
Native American & \num{0.309} & \num{-0.696} & \num{0.209} & \num{0.762} & \num{-0.831}\\
\cellcolor{gray!6}{Asian} & \cellcolor{gray!6}{\num{-0.294}} & \cellcolor{gray!6}{\num{-0.566}} & \cellcolor{gray!6}{\num{-2.496}**} & \cellcolor{gray!6}{\num{-0.568}} & \cellcolor{gray!6}{\num{0.634}}\\
Hispanic or Latino/x & \num{0.324} & \num{0.116} & \num{0.529}* & \num{0.632}** & \num{-0.585}*\\
\cellcolor{gray!6}{Num.Obs.} & \cellcolor{gray!6}{\num{948}} & \cellcolor{gray!6}{\num{948}} & \cellcolor{gray!6}{\num{948}} & \cellcolor{gray!6}{\num{948}} & \cellcolor{gray!6}{\num{948}}\\
\midrule
$R_{McFadden}^2$ & \num{0.193} & \num{0.121} & \num{0.145} & \num{0.154} & \num{0.221}\\
\cellcolor{gray!6}{BIC} & \cellcolor{gray!6}{\num{1152.2}} & \cellcolor{gray!6}{\num{1237.6}} & \cellcolor{gray!6}{\num{1048.0}} & \cellcolor{gray!6}{\num{864.8}} & \cellcolor{gray!6}{\num{1104.6}}\\
Log.Lik. & \num{-524.709} & \num{-567.376} & \num{-472.576} & \num{-380.971} & \num{-500.907}\\
\bottomrule
\multicolumn{6}{l}{\rule{0pt}{1em}* p $<$ .05. ** p $<$ .01. *** p $<$ .001 (two-tailed test).}\\
\multicolumn{6}{l}{\rule{0pt}{1em}Raw, Unexponentiated Coefficients}\\
\end{tabular}}
\end{table}

### 2022-03-03 paper1.tex
even more bib fixes
fix paper 1 tables, finish most of writing

@@
 \hypertarget{paper-1}{%
-\chapter{Digital Trace Data as Indicators of Social Data Validating Google Trends for  use in Scientific Research}\label{paper-1}}
-
-Possible titles Digital Trace Data as Social Indicators: Indicators of
-Attention Rather Than Support
-
-Digital Trace Data as Indicators of Social Data: Validating Google Trends for
- use in Scientific Research
+\chapter{Digital Trace Data as Indicators of the Social World: Validating Google Trends for use in Scientific Research}\label{paper-1}}
 
 \section{Abstract}
+I will first investigate how Google Search Trends can be operationalized
+as cultural attitudes, disease prevalence and voting behaviors through
+comparing trends data to observed valid indicators of these cases.
+Specifically, I will test cultural indicators from the NORC General
+Social Survey, United States county-level suicide rates from National
+Center for Health Statistics, US case rates of Covid-19 from The New
+York Times, historical US Presidential Election results, and the
+American National Election Survey against selected Google Trends terms
+and analyze the data using correlation methods. The aim of this article
+is to assess the construct validity and will contribute to critical big
+data studies and sociological methodology.
 
@@
 research because they are bigger, cheaper, and already available
-\citep{kingEnsuringDataRichFuture2011,lazerComputationalSocialScience2009,salganikBitBitSocial2017}. Before overenthusiastically embracing these
+\citep{kingEnsuringDataRichFuture2011,lazerComputationalSocialScience2009,salganikBitBitSocial2017}.
+Before overenthusiastically embracing these
 sources into our workflows, social scientists must clearly establish
-parameters under which these data sources could be operationalized
+parameters under which these data sources should be operationalized
 \citep{bailCulturalEnvironmentMeasuring2014, lazerParableGoogleFlu2014}. As
@@
 can ignore foundational issues of measurement and construct validity and
-reliability and dependencies among data" \citep[p. 1203]{lazerParableGoogleFlu2014}. Building on this prior research outlining these various
-issues with big data \citep{boydCriticalQuestionsBig2012,lazerIssuesConstructValidity2015}, this paper tests the construct
-validity of Google Search Trends as an indicator of three different
-cases, namely cultural attitudes, disease prevalence and voting
-behavior. These three cases will be tested using cultural indicators
-from the NORC General Social Survey, United States county-level suicide
-rates from National Center for Health Statistics, US cases rates of
-Covid-19 from The New York Times, historical US Presidential Election
-results, and the American National Election Survey. Data will be
-analyzed against corresponding operationalized Google Trends
-longitudinal data using Pearson's r for pairwise correlations, testing
-for the strength of relationships between the Google Trend indicator and
-the respective comparison indicator. This paper will contribute to the
-creation of methodological norms and standards of how to use Google
-Trends as a big data source for societal research and serve as a
-critical inquiry into the adoption of big data without a critical eye
-for the ecological validity of the sources.
+reliability and dependencies among data" 
+\citep[p. 1203]{lazerParableGoogleFlu2014}.
 
-With the expansion of big data, some research has shown extremely
-innovative methods that lead to groundbreaking results that are shown to
+With the expansion of big data, some computational social science research has developed extremely
+innovative methods that lead to groundbreaking results using big data that are shown to
 be reliable. As an example, \citet{blumenstockPredictingPovertyWealth2015} use
 county-level cell-phone records to construct the distribution of poverty
-and wealth in Rwanda, a country where national surveys and censes are
+and wealth in Rwanda, a country where national surveys and censuses are
 rare and costly. However, \citet{blumenstockPredictingPovertyWealth2015} go to
@@
 methodological guidelines of how to use sources of big data
-\citep{asseoTrackingCOVID19Using2020, stilesAssessingCriterionValidity2018}.
+\citep[For exceptions, see ][]{asseoTrackingCOVID19Using2020, stilesAssessingCriterionValidity2018}.
 However, research has shown the small adjustments to an algorithm or
 metric may void any research insight we are able to pull from such data
-\citep{lazerParableGoogleFlu2014}. Because of this, I propose a
-methodological validation study of the Google Search Trends source of
-big data to investigate how it is advisable to utilize this data in
-social scientific research.
+\citep{lazerParableGoogleFlu2014}.
+
+\subsection{Google Trends}
+
+One source of big data that has yet to be widely utilized are Google Search Trends. 
+Google Trends is an open data resource provided by Google, a major internet search
+engine worldwide, that analyzes the top search queries across different localities, languages, and time. 
+While Google Trends is freely available and holds a breadth of online activities that could potentially 
+be of use in social science, few social scientists have used this resource. Because of this, 
+I set out to establish how can we operationalize Google Search Trends as
+validated indicator for uses in social science research to provide guidance to social scientists as they
+adapt different sources of big data into their toolboxes.
+
+Building on this prior research outlining various issues with different sources of big data
+\citep{boydCriticalQuestionsBig2012,lazerIssuesConstructValidity2015},
+this paper tests the construct validity of Google Search Trends as an indicator of three different
+cases, namely attitudes, disease prevalence and political preferences.
+These three cases will be tested using attitudinal indicators from the %NORC General Social Survey, 
+CDC \citeyearpar{vaches_data} and New York Times \citeyearpar{mask_data}, 
+health indicators from the CDC \citeyearpar{suic_data}, 
+US cases rates of Covid-19 from The New York Times \citeyearpar{covid_data},  
+and political indicators from the historical US Presidential Election results \citeyearpar{pres_data}, 
+and the American National Election Survey \citeyearpar{anes_data}. This paper will contribute to the
+creation of methodological norms and standards of how to use Google
+Trends as a big data source for societal research and serve as a
+critical inquiry into the adoption of big data without a critical eye
+for the ecological validity of the sources.
+
+\subsection{Google Trends and research on attitudes}
 
@@
 be operationalized for social scientific usage. First, I'll test Google
-Trends as an operationalization of cultural attitudes with the General
-Social Survey. After \citet{bailCulturalEnvironmentMeasuring2014}'s call for
+Trends as an operationalization of attitudinal indicators. 
+After \citet{bailCulturalEnvironmentMeasuring2014}'s call for
 cultural sociologists to utilize the ever-expanding world of big data,
-Google trends as a data source began appearing in sociological and
-social science research. From research on mass shootings and firearms
-\citep{brownsteinInternetSearchPatterns2020,semenzaInformationseekingWakeTragedy2020}, protest and anti-Muslim sentiment \citep{bailUsingInternetSearch2018,barrieSearchingRacismGeorge2020,grossThereFergusonEffect2017}, to analyzing country-level changes in social perception \citep{reyes_etal18},
-Google search trends are a new and innovative indicator of cultural
-interest. Extending into social networks and culture, \citet{bailPrestigeProximityPrejudice2019} even used Google trends to measure
-how culture spreads around the globe.
+Google trends began appearing as a data source in sociological and
+social science research. From research on mass shootings and firearms \citep{brownsteinInternetSearchPatterns2020, semenzaInformationseekingWakeTragedy2020}, 
+protest and anti-Muslim sentiment \citep{bailUsingInternetSearch2018,barrieSearchingRacismGeorge2020,grossThereFergusonEffect2017},
+to analyzing country-level changes in social perception \citep{reyes_etal18},
+Google search trends are a new and innovative indicator of cultural interest.
+Extending into social networks and culture, \citet{bailPrestigeProximityPrejudice2019}
+even used Google trends to measure how 'culture' spreads around the globe.
 
-Google Search Trends have also been used continuously in estimations of
+\subsection{Google Trends and research on health behaviors}
+
+Google Search Trends have been used continuously in estimations of
 disease prevalence and population health in journals like the Journal of
 Medical Internet Research. While much of this research has focused on
-the Covid-19 pandemic \citep{jimenez_etal20,jimenezCOVID19SymptomGoogle2020,limEstimatingInformationSeekingBehaviour2020,mavraganiCOVID19PredictabilityUnited2020,nguyenGoogleTrendsAnalysis2020, todorovaInternetBasedData2021} , other
-research has investigated Google Trends as an indicator of wellbeing
-\citep{brodeurCOVID19LockdownsWellbeing2021,carpiTwitterSubjectiveWellBeing2020, duCOVID19IncreasesOnline2020},
-suicidality \citep{burnettTimeTrendsPublic2020}, vaccination uptake
-\citep{dalumhansenEnsembleLearnedVaccination2016}, obesity
-\citep{sarigulNowcastingObesityUsing2014}, and even insomnia
-\citep{zittingGoogleTrendsReveal2020}, to cover a few examples. For a partial
-review of other utilizations, see \citet{nutiUseGoogleTrends2014}. According to
+the Covid-19 pandemic \citep{jimenez_etal20, jimenezCOVID19SymptomGoogle2020, limEstimatingInformationSeekingBehaviour2020, mavraganiCOVID19PredictabilityUnited2020, nguyenGoogleTrendsAnalysis2020, todorovaInternetBasedData2021},
+other research has investigated Google Trends as indicators of wellbeing
+\citep{brodeurCOVID19LockdownsWellbeing2021, carpiTwitterSubjectiveWellBeing2020, duCOVID19IncreasesOnline2020},
+suicidality \citep{burnettTimeTrendsPublic2020}, 
+vaccination uptake \citep{dalumhansenEnsembleLearnedVaccination2016}, 
+obesity \citep{sarigulNowcastingObesityUsing2014}, 
+and even insomnia \citep{zittingGoogleTrendsReveal2020},
+to cover a few examples. For a partial review of other utilizations, see \citet{nutiUseGoogleTrends2014}. According to
 \citet{jaidkaInformationseekingVsSharing2021}, the majority of studies profess
@@
 assumptions that individuals search because of self-diagnosis and to
-identify possible courses of treatment
-\citep{dechoudhurySeekingSharingHealth2014}.
+identify possible courses of treatment \citep{dechoudhurySeekingSharingHealth2014}.
 
-% <!-- Following reports say that Google searches can predict covid  -->
+\citet{mingUnderstandingHealthCommunication2021}
 
-% <!-- 14. Brunori, P. & Resce, G. Searching for the peak Google Trends and the Covid-19 outbreak in Italy. SERIES working papers N. 04/2020 -->
-
-% <!-- Lampos, V. et al. Tracking COVID-19 using online search. Preprint at https://arxiv.org/abs/2003.08086 (2020). -->
-
-% <!-- 16. Walker, A., Hopkins, C. & Surda, P. The use of google trends to investigate the loss of smell related searches during COVID‐19 outbreak. Int. Forum Allergy Rh. 10, 839–847 (2020). -->
-
-% <!-- 17.
-Stephens-Davidowitz, S.
-Google Searches Can Help Us Find Emerging Covid-19 Outbreaks.
-The New York Times https://www.nytimes.com/2020/04/05/opinion/coronavirus-google-searches.html (2020).
--->
-
-% <!-- 18.
-Frank, T.
-Goldman says fewer ‘loss of smell’ Google queries suggest better COVID outlook.
-Consumer News and Business Channel.
-CNBC https://www.cnbc.com/2020/04/15/goldman-says-fewer-loss-of-smell-google-searches-is-a-positive-sign-for-pandemic.html (2020) -->
+\subsection{Google Trends and research on politics}
 
@@
 America \citep{montoyaUsingGoogleData2020}. 
+% TODO what are the results of these papers? do they show promise?
 
-Research Question - How can we operationalize Google Search Trends as a
-valid indicator for uses in social science research?
+\subsection{Causes for concern}
+summarize
+\citet{jungherr_etal17}
 
-<https://journals.sagepub.com/doi/10.1177/0894439316631043> What
-constructs might google trends capture and not capture well? Capture
+What constructs might google trends capture and not capture well? Capture
 attention but not attitudes
 
-Also Asseo - "we assumed that media coverage may potentially decouple
-the search popularity from the number of cases, since searches would
+In contrast to the papers mentioned above, there are researchers who have cautioned against
+the wide usage of Google Search Trends. For instance, \citet{asseoTrackingCOVID19Using2020} 
+concludes in their research on Covid-19 case rates and Google searches that the correlation 
+is often spurious and due to confounding. They even explain that "searches would
 result not only from self-symptoms, but also from interest elicited by
-media coverage."
+media coverage" \citep[][TODO ADD Page here]{asseoTrackingCOVID19Using2020}.
+
+\citet{rovetta21}
+
+\citet{cebrian_domenech22}
 
@@
 \subsubsection{Attitudinal}
-<!-- \citep{gss_data} (let's see if I get access first) -->
+
+% <!-- \citep{gss_data} (let's see if I get access first) -->
 
@@
 vaccine if available during May 26, 2021 – June 7, 2021. This dataset consists
-of x observations, one for each U.S. County. The variable
+of 3,148 observations, one for each U.S. County. The variable
 measures the percent of adults in the county who describe themselves as
 “unsure”, “probably not”, or “definitely not” going to get a COVID-19 vaccine
-once one is available to them. The variable ranges from x to y.
+once one is available to them. The variable ranges from 4.99\% to 32.33\%.
 
@@
 sometimes, frequently, and always wore a mask when in public. This dataset
-consists of x observations, one for each U.S. County. This measure
+consists of 3,148 observations, one for each U.S. County included in the sample. This measure
 represents the percent of adults in the county who never or rarely wear a mask
-(range = x to x).
+(range = 0.10\% to 55.80\%).
 
@@
 Case Rate is measured as number of cases per 100,000 population. Observations
-vary from a minimum of 0 to a maximum of x for each 
-Monday from x through x. There are x cases across x counties and x dates. Missing data were interpolated using `zoo::na.approx()` \citep{zoo}.
+vary from a minimum of 0 to a maximum of 1460.46 for each Monday from January 27, 2020 through
+December 27, 2021. There are 285,986 cases across 3,136 counties and 101
+dates. Missing data were interpolated using `zoo::na.approx()` \citep{zoo}.
 
@@
 rates are scaled by population size for each year and can be interpreted as the
-death rate by suicide for every 1000 people. There are x total
-cases, resulting from x observations of x counties. Missing data were interpolated using
-zoo::na.approx() \citep{zoo}. Measures range from x to x.
+death rate by suicide for every 1000 people. There are 34,683 total
+cases, resulting from 34,617 observations of 3,147 counties. Missing data were interpolated using
+zoo\:\:na\.approx() \citep{zoo}. Measures range from 0.034 to 53.254.
 
@@
 results from Townhall.com, Fox News, Politico, and the New York Times. Data on 
-presidential outcomes were available for x counties in 2016 and
-x counties in 2020. Each variable measures the percent of votes
-for the candidate, with the lowest percent at x and the highest at x.
+presidential outcomes were available for 3,147 counties in 2016 and
+3,118 counties in 2020. Each variable measures the percent of votes
+for the candidate, with the lowest percent at 3.09\% and the highest at 92.15\%.
 
@@
 
-\section{Discussion}
+\section{Discussion and Conclusion}
+This paper provides a critical test of Google Trends for use in Social Science. 
+I failed to find moderate or strong correlation among any of the Google 
+Trends tested and their validated indicators.
+While some Google Trends tested were significantly associated with the outcome in the linear regression model,
+effects tended to be small and the total model explainability remained low,
+even when controlling for demographic variables.
 
-The external validity of these voting
+Some previous research has shown strong innovation in the computational social sciences
+to gather sociodemographic data when survey or other research methods are too costly
+\citep{blumenstockPredictingPovertyWealth2015}. Google Trends, in theory, sounds like 
+a promising data source to 'nowcast' attitidinal, health, and political indicators;
+not only would the data be easily and freely accessible, it would also provide 
+indicators for areas where conducting research may be too costly. The demand for this 
+sort of indicator is clear and fields like the health sciences have freely utilized
+this data source. However, this article shows that there is no 
+no external validity of Google Trends for this specific use and social scientists
+will find no replacement for high quality survey data with Google Trends.
 
-While I expect these tests to show high correlation between observed
-indicators and Google search trends, there will be three important
-questions that surface. First, just because something is correlated,
-does that mean it can replace the collection of other types of data?
-Second, how correlated does a trend need to be for social scientists to
-justifiably rely on it to indicate some outcome? And finally, how can we
-construct analyses like this to be robust to changes in the terms used
-across time and location?
-
-The purpose of this paper is more methodological than theoretical, and I
-see this paper having an impact on the social sciences and computational
-social science as researchers pursue more projects using this source of
-big data. Google Trends are relatively underutilized in the field
-compared to in the health sciences and business. Once I assess how this
-data can be used, I would like to be able to join
-\citet{bailCulturalEnvironmentMeasuring2014} in encouraging social scientists
-to pursue more research with big data while taking into account the
-potential pitfalls with any source of big data
-\citep{mcfarlandBigDataDanger2015}.
-
-\section{Conclusion}
+As social scientists it is our responsibility to deeply investigate the validity 
+of the data that we use in order to be confident in our research findings. As with any
+source of data, we must take into account the potential pitfalls, especially in research on big data
+\citep{mcfarlandBigDataDanger2015}. In the case of Google Search Trends, precaution was 
+warranted. While I would like to be able to join \citet{bailCulturalEnvironmentMeasuring2014} 
+in encouraging social scientists to pursue more research with the many new sources of big data, 
+I emphasize that testing out data to verify what it actually corrresponds to is an essential step 
+to making impactful research as a discipline going forward.

### 2022-03-03 paper3.tex
fix paper 1 tables, finish most of writing

@@
 distancing or vaccination uptake \emph{meant} were spreading between populations of
-individuals. Moreover, as \citet{houghtonSocialContagionInteracting2021} outlines, diffusants - the things that are
+individuals. Moreover, as \citet{houghton20} outlines, diffusants - the things that are
 diffusing through a population, are not independent of each other \citep{mason_etal07}.
@@
 these various diffusants become associated together into structures of belief
-through schemas of perception \citep{houghtonSocialContagionInteracting2021}.
+through schemas of perception \citep{houghton20}.
 While this cognitive theory of cultural variation is difficult to test, the theory it supplies provides a solid framework for how behavioral norms formed during the pandemic.
@@
 or time-series (a single geo-location across time). To remedy this and build a
-longitudinal dataset of each search topic, I follow the method proposed in
-Park, Kwak, and An (n.d.) (p.~5). This method involves building a dataset of unscaled
+longitudinal dataset of each search topic, I follow the method proposed in \citet[p. 5]{park_etal}.
+This method involves building a dataset of unscaled
 cross-sectional values, selecting a DMA to use to establish the rescaling ratio

### 2022-03-03 tables/paper1/data-sources-table.tex
fix paper 1 tables, finish most of writing

@@
+\newcolumntype{L}{>{\raggedright\arraybackslash}X}
+
+\definecolor{Gray}{gray}{0.9}
+\definecolor{lightblue}{HTML}{bad7db}
+
+\renewcommand{\arraystretch}{1.2}
+
 \begin{table}[!h]
-\caption{\label{tab:data-sources-table}}
+\caption{\label{tab:data-sources-table}Data Sources}
 \centering
-\begin{tabular}[t]{}
-\end{tabular}
+\fontsize{8}{10}\selectfont
+\setlength{\extrarowheight}{2pt}
+\begin{tabularx}{\linewidth}{@{}L c c L@{}}
+\toprule
+\textbf{Validated Data Source} & \textbf{Type} & \textbf{Dates} & \textbf{Google Trends Used}\citep{googletrends} \\ \midrule
+% \rowcolor{lightblue}
+\multicolumn{4}{l}{\textbf{Behaviors and Attitudes}} \\\hline
+% General Social Survey & Cross-Sectional & 2010 - 2020 & NA \\
+Vaccine Hesitancy for COVID-19 \citep{vaches_data}& Cross-Sectional & March 3 - 15, 2021 & Search Topics: 'Covid-19 vaccine', 'Coronavirus (Disease)', 'Coronavirus   (Virus)', 'Vaccine' \\
+Mask-Wearing Survey Data \citep{mask_data} & Cross-Sectional & July 2 - 14, 2020 & Search Topics: 'Coronavirus (Disease)', 'Coronavirus (Virus)', 'Cloth   Face Mask', 'Mask', 'Civil and Political Rights' \\
+American National Election Survey \citep{anes_data}& Cross-Sectional & 2020 & NA \\
+% \rowcolor{lightblue}
+\multicolumn{4}{l}{\textbf{Health}} \\\hline
+Covid Rates \citep{covid_data}& Longitudinal & Every Monday, 2020 - 2021 & 'Covid-19', 'Coronavirus', 'Taste Loss', 'Smell Loss' \\
+Suicide Rates \citep{suic_data} & Longitudinal & Yearly 2010-2020 & Search Topics: 'Suicide', 'Depression', Search Term:' Suicide Hotline' \\
+% \rowcolor{lightblue}
+\multicolumn{4}{l}{\textbf{Political}} \\\hline
+American National Election Survey \citep{anes_data}& Cross-Sectional & 2020 & NA \\
+Presidential Election Results \citep{pres_data}& Cross Sectional & 2016 \& 2020 & Search Topics: 'Hilary Clinton', 'Donald Trump', 'Joe Biden' \\ \bottomrule
+\end{tabularx}
 \end{table}

### 2022-03-03 tables/paper2/model-2-phi.tex
fix paper 1 tables, finish most of writing

@@
-\begin{table}[!h]
+\begin{table}[ht]
 
@@
 \centering
-\begin{tabular}[t]{p{0.25\linewidth} p{0.10\linewidth} p{0.08\linewidth} p{0.12\linewidth} p{0.15\linewidth} p{0.12\linewidth}}
+\begin{tabular}{p{0.25\linewidth} p{0.10\linewidth} p{0.08\linewidth} p{0.12\linewidth} p{0.15\linewidth} p{0.12\linewidth}}
 \hline
@@
 \hline
-\cellcolor{gray!6}{Person} & \cellcolor{gray!6}{NA} & \cellcolor{gray!6}{0.28} & \cellcolor{gray!6}{0.172} & \cellcolor{gray!6}{0.275} & \cellcolor{gray!6}{0.216}\\
+Person& NA& 0.28& 0.172& 0.275& 0.216\\
 
-Dr & NA & NA & 0.192 & 0.152 & 0.098\\
+Dr & & & 0.192 & 0.152 & 0.098\\
 
-\cellcolor{gray!6}{Online Forum} & \cellcolor{gray!6}{NA} & \cellcolor{gray!6}{NA} & \cellcolor{gray!6}{NA} & \cellcolor{gray!6}{0.371} & \cellcolor{gray!6}{-0.073}\\
+Online Forum& NA& NA& NA& 0.371& -0.073\\
 
-Social Networking Site & NA & NA & NA & NA & 0.057\\
+Social Networking Site & & & & & 0.057\\
 
-\cellcolor{gray!6}{Online Search} & \cellcolor{gray!6}{NA} & \cellcolor{gray!6}{NA} & \cellcolor{gray!6}{NA} & \cellcolor{gray!6}{NA} & \cellcolor{gray!6}{NA}\\
+Online Search& NA& NA& NA& NA& NA\\
 \hline

### 2022-03-03 tables/paper2/table-1-desc.tex
fix paper 1 tables, finish most of writing

@@
 \centering
-\begin{tabular}[t]{lrr}
+\begin{tabular}{lrr}
 \toprule
@@
 \midrule
-\cellcolor{gray!6}{Received info} & \cellcolor{gray!6}{\num{0.66}} & \cellcolor{gray!6}{\num{0.47}}\\
+Received info & \num{0.66} & \num{0.47}\\
 Received info, Doctor & \num{0.47} & \num{0.50}\\
-\cellcolor{gray!6}{Received info, Person} & \cellcolor{gray!6}{\num{0.67}} & \cellcolor{gray!6}{\num{0.47}}\\
+Received info, Person & \num{0.67} & \num{0.47}\\
 Received info, News & \num{0.65} & \num{0.48}\\
-\cellcolor{gray!6}{Received info, Social Networking Site} & \cellcolor{gray!6}{\num{0.40}} & \cellcolor{gray!6}{\num{0.49}}\\
+Received info, Social Networking Site & \num{0.40} & \num{0.49}\\
 Received info, Online Forum & \num{0.35} & \num{0.48}\\
-\cellcolor{gray!6}{Sought Info} & \cellcolor{gray!6}{\num{0.78}} & \cellcolor{gray!6}{\num{0.41}}\\
+Sought Info & \num{0.78} & \num{0.41}\\
 Sought Info, Doctor & \num{0.44} & \num{0.50}\\
-\cellcolor{gray!6}{Sought Info, Person} & \cellcolor{gray!6}{\num{0.42}} & \cellcolor{gray!6}{\num{0.49}}\\
+Sought Info, Person & \num{0.42} & \num{0.49}\\
 Sought Info, Social Networking Site & \num{0.18} & \num{0.39}\\
-\cellcolor{gray!6}{Sought Info, Online Forum} & \cellcolor{gray!6}{\num{0.27}} & \cellcolor{gray!6}{\num{0.44}}\\
+Sought Info, Online Forum & \num{0.27} & \num{0.44}\\
 Sought Info, Online Search & \num{0.41} & \num{0.49}\\
-\cellcolor{gray!6}{Vaccination Status} & \cellcolor{gray!6}{\num{0.84}} & \cellcolor{gray!6}{\num{0.36}}\\
+Vaccination Status & \num{0.84} & \num{0.36}\\
 Vaccination Outlook & \num{0.87} & \num{0.34}\\
-\cellcolor{gray!6}{Age} & \cellcolor{gray!6}{\num{37.76}} & \cellcolor{gray!6}{\num{10.75}}\\
+Age & \num{37.76} & \num{10.75}\\
 Hispanic or Latino/x & \num{0.15} & \num{0.36}\\
-\cellcolor{gray!6}{Race, White} & \cellcolor{gray!6}{\num{0.88}} & \cellcolor{gray!6}{\num{0.33}}\\
+Race, White & \num{0.88} & \num{0.33}\\
 Race, Black & \num{0.08} & \num{0.27}\\
-\cellcolor{gray!6}{Race, Native American} & \cellcolor{gray!6}{\num{0.03}} & \cellcolor{gray!6}{\num{0.16}}\\
+Race, Native American & \num{0.03} & \num{0.16}\\
 Race, Asian or Pacific Islander & \num{0.04} & \num{0.20}\\
-\cellcolor{gray!6}{Associate's Deg or above} & \cellcolor{gray!6}{\num{0.74}} & \cellcolor{gray!6}{\num{0.44}}\\
+Associate's Deg or above & \num{0.74} & \num{0.44}\\
 \bottomrule

### 2022-03-03 tables/paper2/table-2-desc.tex
fix paper 1 tables, finish most of writing

@@
 \centering
-\begin{tabular}[t]{llrr}
+\begin{tabular}{llrr}
 \toprule
@@
 \midrule
-\cellcolor{gray!6}{Gender} & \cellcolor{gray!6}{Female} & \cellcolor{gray!6}{418} & \cellcolor{gray!6}{\num{44.09}}\\
+Gender & Female & 418 & \num{44.09}\\
  & Male & 524 & \num{55.27}\\
-\cellcolor{gray!6}{} & \cellcolor{gray!6}{Other} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{\num{0.63}}\\
+ & Other & 6 & \num{0.63}\\
 Highest Education Level & Graduate or professional degree & 145 & \num{15.30}\\
-\cellcolor{gray!6}{} & \cellcolor{gray!6}{Bachelor's degree} & \cellcolor{gray!6}{560} & \cellcolor{gray!6}{\num{59.07}}\\
+ & Bachelor's degree & 560 & \num{59.07}\\
  & Associate's or Technical degree & 72 & \num{7.59}\\
-\cellcolor{gray!6}{} & \cellcolor{gray!6}{Some college} & \cellcolor{gray!6}{100} & \cellcolor{gray!6}{\num{10.55}}\\
+ & Some college & 100 & \num{10.55}\\
  & High school graduate & 68 & \num{7.17}\\
-\cellcolor{gray!6}{} & \cellcolor{gray!6}{Less than high school} & \cellcolor{gray!6}{3} & \cellcolor{gray!6}{\num{0.32}}\\
+ & Less than high school & 3 & \num{0.32}\\
 Plan to be Vaccinated if not & Probably not & 38 & \num{4.01}\\
-\cellcolor{gray!6}{} & \cellcolor{gray!6}{Definitely yes} & \cellcolor{gray!6}{13} & \cellcolor{gray!6}{\num{1.37}}\\
+ & Definitely yes & 13 & \num{1.37}\\
  & Definitely not & 61 & \num{6.43}\\
-\cellcolor{gray!6}{} & \cellcolor{gray!6}{Might or might not} & \cellcolor{gray!6}{22} & \cellcolor{gray!6}{\num{2.32}}\\
+ & Might or might not & 22 & \num{2.32}\\
  & Probably yes & 13 & \num{1.37}\\
-\cellcolor{gray!6}{Found Info Sought Useful} & \cellcolor{gray!6}{Very useful} & \cellcolor{gray!6}{345} & \cellcolor{gray!6}{\num{36.39}}\\
+Found Info Sought Useful & Very useful & 345 & \num{36.39}\\
  & Moderately useful & 112 & \num{11.81}\\
-\cellcolor{gray!6}{} & \cellcolor{gray!6}{Extremely useful} & \cellcolor{gray!6}{264} & \cellcolor{gray!6}{\num{27.85}}\\
+ & Extremely useful & 264 & \num{27.85}\\
  & Slightly useful & 18 & \num{1.90}\\
-\cellcolor{gray!6}{} & \cellcolor{gray!6}{Not at all useful} & \cellcolor{gray!6}{2} & \cellcolor{gray!6}{\num{0.21}}\\
+ & Not at all useful & 2 & \num{0.21}\\
 Census Region & Midwest & 171 & \num{18.04}\\
-\cellcolor{gray!6}{} & \cellcolor{gray!6}{Northeast} & \cellcolor{gray!6}{170} & \cellcolor{gray!6}{\num{17.93}}\\
+ & Northeast & 170 & \num{17.93}\\
  & South & 365 & \num{38.50}\\
-\cellcolor{gray!6}{} & \cellcolor{gray!6}{West} & \cellcolor{gray!6}{223} & \cellcolor{gray!6}{\num{23.52}}\\
+ & West & 223 & \num{23.52}\\
 \bottomrule

### 2022-03-04 paper1.tex
finish paper 1

@@
 \section{Abstract}
-I will first investigate how Google Search Trends can be operationalized
-as cultural attitudes, disease prevalence and voting behaviors through
-comparing trends data to observed valid indicators of these cases.
-Specifically, I will test cultural indicators from the NORC General
-Social Survey, United States county-level suicide rates from National
-Center for Health Statistics, US case rates of Covid-19 from The New
-York Times, historical US Presidential Election results, and the
-American National Election Survey against selected Google Trends terms
-and analyze the data using correlation methods. The aim of this article
-is to assess the construct validity and will contribute to critical big
-data studies and sociological methodology.
+
+Computational social science and other disciplines are quick to 
+adopt new sources of digital trace data for use in academic research. 
+In this article, I examine the validity of Google Search Trends 
+as potential indicator of three different cases, namely attitudes, 
+disease prevalence and political preferences using eight %TODO double check number
+different validated data sources. I use Pearson and Repeated Measures Correlations 
+between the Google Trends and the validated indicators as well as multiple linear regression
+(for cross-sectional datasets) and random intercept hierarchical linear models
+(for longitudinal datasets) as an additional test of the data. 
+I fail to find moderate or strong correlation among any of the Google 
+Trends tested and their validated indicators. While some Google Trends 
+tested were significantly associated with the outcome in the regression models,
+effects tended to be small and the total model explainability remained low,
+even when controlling for demographic variables. This article shows that there is no 
+no external validity of Google Trends for these uses and social scientists
+will find no replacement for high quality survey data with Google Trends.
+
+\textbf{Keywords}: Social Science Methodology, Digital Trace Data, Information-Seeking Behavior, Google Trends, Information and communications technology, Validity
 
@@
 
-With the expansion of big data, some computational social science research has developed extremely
-innovative methods that lead to groundbreaking results using big data that are shown to
-be reliable. As an example, \citet{blumenstockPredictingPovertyWealth2015} use
+With the expansion of big data, some computational social science research has
+developed extremely innovative methods that lead to groundbreaking results using 
+big data that are shown to be reliable. As an example,
+\citet{blumenstockPredictingPovertyWealth2015} use
 county-level cell-phone records to construct the distribution of poverty
@@
 Google Trends is an open data resource provided by Google, a major internet search
-engine worldwide, that analyzes the top search queries across different localities, languages, and time. 
-While Google Trends is freely available and holds a breadth of online activities that could potentially 
-be of use in social science, few social scientists have used this resource. Because of this, 
-I set out to establish how can we operationalize Google Search Trends as
-validated indicator for uses in social science research to provide guidance to social scientists as they
-adapt different sources of big data into their toolboxes.
+engine worldwide, that analyzes the top search queries across different localities, 
+languages, and time. While Google Trends is freely available and holds a breadth of 
+online activities that could potentially be of use in social science, few social 
+scientists outside of economics \citep[see][for examples]{choi2012predicting, jun2018ten,da2011search} have used this resource.
+Because of this, I set out to establish how can we operationalize Google Search Trends as
+validated indicator for uses in social science research to provide guidance to social 
+scientists as they adapt different sources of big data into their toolboxes.
 
@@
 Medical Internet Research. While much of this research has focused on
-the Covid-19 pandemic \citep{jimenez_etal20, jimenezCOVID19SymptomGoogle2020, limEstimatingInformationSeekingBehaviour2020, mavraganiCOVID19PredictabilityUnited2020, nguyenGoogleTrendsAnalysis2020, todorovaInternetBasedData2021},
+the Covid-19 pandemic \citep{jimenez_etal20, jimenezCOVID19SymptomGoogle2020, limEstimatingInformationSeekingBehaviour2020, mavraganiCOVID19PredictabilityUnited2020, nguyenGoogleTrendsAnalysis2020, todorovaInternetBasedData2021, mingUnderstandingHealthCommunication2021},
 other research has investigated Google Trends as indicators of wellbeing
@@
 identify possible courses of treatment \citep{dechoudhurySeekingSharingHealth2014}.
-
-\citet{mingUnderstandingHealthCommunication2021}
 
@@
 \subsection{Causes for concern}
-summarize
-\citet{jungherr_etal17}
 
-What constructs might google trends capture and not capture well? Capture
-attention but not attitudes
-
+While Google Trends has not been widely used or tested in social science,
+I am not the first author to investigate its validity.
 In contrast to the papers mentioned above, there are researchers who have cautioned against
@@
 result not only from self-symptoms, but also from interest elicited by
-media coverage" \citep[][TODO ADD Page here]{asseoTrackingCOVID19Using2020}.
+media coverage" \citep[][p.1]{asseoTrackingCOVID19Using2020}.
 
-\citet{rovetta21}
+\citet{rovetta21} also investigate the reliability of Covid-19 searches to investigate the quality of the data and find that there are various issues with missing data in smaller regions and significant variation in correlations between regions throughout the study period, which they indicated was a cause for concern more than a product of behavioral changes.
 
-\citet{cebrian_domenech22}
+\citet{cebrian_domenech22} emphasize in their research that there are some 
+non-negligible issues with the measurement of Google Trends, pointing to 
+errors within the purview of accuracy, completeness, consistency, and validity \citep{KarrDataQuality}. \citet{cebrian_domenech22} point not only to 
+meta issues like the lack of transparency into the sampling methods 
+and population coverage, but they identify real differences 
+in the data provided by the Google Trends API for the same query, pointing
+to likely internal process used by Google to sample their data to compute the trends.
+These authors show that the variability of the results over time for the same query
+can alter the results of analysis and forecasting significantly; they propose
+caution in the use of the digital trace data for other researchers until
+further research can determine the cause for the inaccuracies.
+
+Finally, it is important to note that a majority of research using 
+Google Trends as digital trace data do so to indicate
+populations \textit{attention} to a search query. Because
+searches can be done with many different intentions, such as 
+information gathering, ridicule, navigational purposes, it may
+be hard to declare that an overall level of engagement with a topic
+on Google Search may be indicative of anything more than interest \citep{da2011search}. 
+\citet{jungherr_etal17} explore this topic deeply with data from
+Twitter on German federal election candidates and find that there is no
+indication that tweets about candidates are indicative of or can predict 
+political support. Instead, they conclude that tweets merely indicate the
+temporal dynamics of public attention toward politics.
+
+Building on this previous research in the reliability and accuracy of the trends, 
+it is imperative that, as a discipline, we are able to provide a framework for
+how to use different sources of digital trace data. This aim of this paper is
+to take the first step to build that framework. I will attempt to validate 
+Google Search Trends for use outside of mere interest or attention using the
+methods that follow; specifically, to verify whether
+trends can be used to indicate attitudes, health outcomes, or political support.
 
@@
 datapoints in longitudinal datasets were filled in with interpolated values
-using `zoo::na.approx()` \citep{zoo}.
+using \texttt{zoo\:\:na.approx()} \citep{zoo}.
 
@@
 \subsection{Analysis}
-Google Search Trends data and additional demographic data are merged with each
-individual indicator based on County FIPS Codes and date. After creating these
-different datasets, I use the Pearson correlation formula (formula \eqref{eq:pearsoncorr}
-) for cross-sectional numeric data to calculate the
+Google Search Trends data and additional demographic data were merged with each
+individual indicator based on County FIPS Codes and date using \texttt{dplyr} in \texttt{r}, version 4.1.2 \citep{tidyverse}. After creating these
+different datasets, I use the Pearson correlation formula (formula \eqref{eq:pearsoncorr}) for cross-sectional numeric data to calculate the
 strength of the relationship between each Google Trend and the respective
@@
 To address longitudinal correlations, I employ Repeated Measures Correlation
-using the `rmcorr` package in R \citep{bland1995, bakdash2017}. Repeated Measures
-Correlation is useful for determining the within-county association for paired
-measures across time and counties. Results of these correlations can be seen in 
-table \ref{tab:corr-results}.
+using the `rmcorr` package in \texttt{r} \citep{bland1995, bakdash2017}. 
+Repeated Measures Correlation is useful for determining the within-county
+association for paired measures across time and counties. Results of these 
+correlations can be seen in table \ref{tab:corr-results}.
 
@@
 \citep{pinheiro_etal21} (for longitudinal datasets) to identify the strength of
-relationships across locales: I include city-data like county population size,
+relationships across locales. I include city-data like county population size,
 broadband rates, and median income to attempt to disentangle possible
@@
 variables, i.e.variables have been centered and scaled to have a mean of 0 and
-standard deviation 1.
+standard deviation 1. Results of these models can be seen in tables \ref{tab:vacc_hes_analysis} through \ref{tab:pres_2020_analysis}.
 

### 2022-03-04 paper2.tex
finish paper 1

@@
 
-\begin{figure}
+\begin{figure}[h]
 {\centering \includegraphics[width=0.8\linewidth]{figs/paper2/plot-model-1-1}}
-\caption{Plot of Coefficients, Model 1}\label{fig:plot-model-1}
+\caption{What predicts someone intentionally searched for information, Plot of Coefficients}\label{fig:plot-model-1}
 \end{figure}
@@
 
-\begin{figure}
+% <!-- TODO: watch out about saying vaccinated, this variable is about opinion -->
+
+\begin{figure}[h]
 {\centering \includegraphics[width=0.8\linewidth]{figs/paper2/plot-model-3-1}}
-\caption{Plot of Coefficients, Model 3}\label{fig:plot-model-3}
+\caption{Does receiving or searching for information predict vaccination status? Plot of Coefficients}\label{fig:plot-model-3}
 \end{figure}

### 2022-03-04 paper3.tex
finish paper 1

@@
 signals received by an ego.
+
+% need to explain a little bit more what diversity of signals etc means (since this is the first look)
 
@@
 
-\begin{figure}
-{\centering \includegraphics[width=0.8\linewidth]{figs/paper3/model}}
-\caption{Preliminary model of norm formation}\label{fig:norm-framework}
-\end{figure}
-
 The figure above illustrates how I interpret associative diffusion will impact
@@
 
-To estimate the concept of `real threat of infection' in figure
-\ref{fig:norm-framework}, the models use county-level Covid-19 case rates with
+To estimate the concept of `real threat of infection' for a fear-based model of
+health behaviors, the models use county-level Covid-19 case rates with
 data compiled by The New York Times \citeyearpar{covid_data}. It is widely acknowledged that there are biases in this data due to inconsistencies and availability in testing as well as

### 2022-03-05 paper1.tex
Edits on Paper 1

@@
 In this article, I examine the validity of Google Search Trends 
-as potential indicator of three different cases, namely attitudes, 
+as potential indicators of three different cases, namely attitudes, 
 disease prevalence and political preferences using eight %TODO double check number
@@
 (for cross-sectional datasets) and random intercept hierarchical linear models
-(for longitudinal datasets) as an additional test of the data. 
-I fail to find moderate or strong correlation among any of the Google 
+(for longitudinal datasets) as additional tests of the data. 
+I fail to find correlation among any of the Google 
 Trends tested and their validated indicators. While some Google Trends 
 tested were significantly associated with the outcome in the regression models,
-effects tended to be small and the total model explainability remained low,
+effects tended to be small and the total model interpretability remained low,
 even when controlling for demographic variables. This article shows that there is no 
-no external validity of Google Trends for these uses and social scientists
+external validity of Google Trends for these uses and social scientists
 will find no replacement for high quality survey data with Google Trends.
 
-\textbf{Keywords}: Social Science Methodology, Digital Trace Data, Information-Seeking Behavior, Google Trends, Information and communications technology, Validity
+\textbf{Keywords}: Google Trends, Social Science Methodology, Digital Trace Data, Information-Seeking Behavior, Information and communications technology, Validity
 
@@
 Before overenthusiastically embracing these
-sources into our workflows, social scientists must clearly establish
+sources and integrating them into our big data toolkits, social scientists must clearly establish
 parameters under which these data sources should be operationalized
@@
 With the expansion of big data, some computational social science research has
-developed extremely innovative methods that lead to groundbreaking results using 
-big data that are shown to be reliable. As an example,
-\citet{blumenstockPredictingPovertyWealth2015} use
-county-level cell-phone records to construct the distribution of poverty
+developed extremely innovative methods that have lead to groundbreaking results using 
+reliable sources of big data. As an example,\citet{blumenstockPredictingPovertyWealth2015}
+use county-level cell-phone records to construct the distribution of poverty
 and wealth in Rwanda, a country where national surveys and censuses are
@@
 However, research has shown the small adjustments to an algorithm or
-metric may void any research insight we are able to pull from such data
+metric may void any research insight we can pull from such data
 \citep{lazerParableGoogleFlu2014}.
@@
 
-One source of big data that has yet to be widely utilized are Google Search Trends. 
+Social scientists have yet to widely utilize Google Search Trends as a source of big data.
 Google Trends is an open data resource provided by Google, a major internet search
@@
 online activities that could potentially be of use in social science, few social 
-scientists outside of economics \citep[see][for examples]{choi2012predicting, jun2018ten,da2011search} have used this resource.
-Because of this, I set out to establish how can we operationalize Google Search Trends as
-validated indicator for uses in social science research to provide guidance to social 
-scientists as they adapt different sources of big data into their toolboxes.
+scientists outside of economics have used this resource \citep[see][for examples]{choi2012predicting, jun2018ten,da2011search}. 
+Because of this, I set out to provide guidance to social scientists as they introduce
+the data source into their toolboxes on how we can operationalize Google Search Trends
+as validated indicators and under what circumstances.
 
-Building on this prior research outlining various issues with different sources of big data
+Building on prior research outlining the various issues with different sources of big data
 \citep{boydCriticalQuestionsBig2012,lazerIssuesConstructValidity2015},
-this paper tests the construct validity of Google Search Trends as an indicator of three different
+this paper evaluates the construct validity of Google Search Trends as an indicator of three different
 cases, namely attitudes, disease prevalence and political preferences.
@@
 I will use three categorizations of ways I propose Google Trends could
-be operationalized for social scientific usage. First, I'll test Google
+be operationalized for social scientific usage. First, I test Google
 Trends as an operationalization of attitudinal indicators. 
@@
 cultural sociologists to utilize the ever-expanding world of big data,
-Google trends began appearing as a data source in sociological and
+Google trends began slowly appearing as a data source in sociological and
 social science research. From research on mass shootings and firearms \citep{brownsteinInternetSearchPatterns2020, semenzaInformationseekingWakeTragedy2020}, 
@@
 
-Google Search Trends have been used continuously in estimations of
-disease prevalence and population health in journals like the Journal of
+Google Search Trends have been utilized to estimate disease prevalence
+and population health in journals like the Journal of
 Medical Internet Research. While much of this research has focused on
@@
 and even insomnia \citep{zittingGoogleTrendsReveal2020},
-to cover a few examples. For a partial review of other utilizations, see \citet{nutiUseGoogleTrends2014}. According to
-\citet{jaidkaInformationseekingVsSharing2021}, the majority of studies profess
+to cover a few examples. For a partial review of other utilizations, see \citet{nutiUseGoogleTrends2014}. According to \citet{jaidkaInformationseekingVsSharing2021}, the majority of studies profess
 a correlation of \> .70, "demonstrating the vast potential of Google
@@
 
-Various sources have also used Google Trends as a way to forecast
+Various sources have also used Google Trends to forecast
 political elections and political attitudes
@@
 Elections relate to attention measured by search traffic.
-\citet{prado-romanGoogleTrendsPredictor2020} compare how Google Search trends
-are able to predict presidential election results in both the United
+\citet{prado-romanGoogleTrendsPredictor2020} demonstrate how Google Search trends
+successfully predicts presidential election results in both the United
 States and Canada. Finally, the OECD Development Centre is investigating
@@
 
-While Google Trends has not been widely used or tested in social science,
+While Google Trends has not been widely used or validated by social scientists,
 I am not the first author to investigate its validity.
@@
 
-\citet{rovetta21} also investigate the reliability of Covid-19 searches to investigate the quality of the data and find that there are various issues with missing data in smaller regions and significant variation in correlations between regions throughout the study period, which they indicated was a cause for concern more than a product of behavioral changes.
+\citet{rovetta21} also investigates the reliability of Covid-19 searches to infer 
+the quality of the data; the author finds that there are various issues with missing data in 
+smaller regions and significant variation in correlations between the sampled regions throughout
+the study period. Rovetta indicates that this is a cause for concern and is undoubtedly due to more 
+serious causes than behavioral changes among the population or changes in the underlying product algorithm.
 
@@
 
-Finally, it is important to note that a majority of research using 
+Finally, it is important to note that most of the research using 
 Google Trends as digital trace data do so to indicate
@@
 searches can be done with many different intentions, such as 
-information gathering, ridicule, navigational purposes, it may
+information gathering, ridicule, navigational purposes, etc., it may
 be hard to declare that an overall level of engagement with a topic
@@
 political support. Instead, they conclude that tweets merely indicate the
-temporal dynamics of public attention toward politics.
+temporal dynamics of public attention toward politics. The same may
+be true about Google Trends.
 
 Building on this previous research in the reliability and accuracy of the trends, 
-it is imperative that, as a discipline, we are able to provide a framework for
-how to use different sources of digital trace data. This aim of this paper is
+it is imperative that we provide a framework for how to use diverse sources
+of digital trace data as a discipline. The aim of this paper is
 to take the first step to build that framework. I will attempt to validate 
@@
 methods that follow; specifically, to verify whether
-trends can be used to indicate attitudes, health outcomes, or political support.
+trends should be used to indicate attitudes, health outcomes, or political support.
 
@@
 sources to address the three areas of inquiry for this paper.  Table
-\ref{tab:data-sources-table} outlines which data sources are used for this
+\ref{tab:data-sources-table} outlines which data sources I use in this
 project and which trends are matched to each source.
@@
 counties to 210 media markets based on similar population clusters \citep{dma_key}.
-Raw data is on a scale from 0 to 100, with 100 being the maximum search
+Raw data is on a scale from zero to one hundred, with one hundred being the maximum search
 popularity out of all DMAs. When available, I use Google search topics to
@@
 search terms, 'Beyoncé Knowles' encompasses all of these into a single search
-topic. Google Search Trend are only available cross-sectionally (a single time
+topic. Google Search Trends are only available cross-sectionally (a single 
 period across a geography) or as time-series (a single geo-location across
-time). To remedy this and build a longitudinal dataset of each search topic for
-the longitudinal datasets, I follow the method proposed in \citet[p. 5]{park_etal}.
+time). To remedy this and build a longitudinal dataset of each search topic 
+to match the longitudinal validated measures, I follow the method proposed in \citet[p. 5]{park_etal}.
 This method involves building a dataset of unscaled cross-sectional values,
@@
 rescale each longitudinal value, multiply the respective week's rescaling ratio
-by the cross-sectional value. Rescaled longitudinal data was compared against
-time-series data for multiple test counties and was equivalent. For a more
-in-depth explanation of this procedure, see \citet[p. 5]{park_etal}. Missing
-datapoints in longitudinal datasets were filled in with interpolated values
-using \texttt{zoo\:\:na.approx()} \citep{zoo}.
+by the cross-sectional value. To validate this method, I compared the rescaled
+longitudinal data against multiple samples of time-series data. For a more
+in-depth explanation of this procedure, see \citet[p. 5]{park_etal}. I interpolate 
+missing datapoints in the longitudinal datasets using \texttt{zoo\:\:na\.approx\(\)} \citep{zoo}.
 
@@
 I also use U.S. Covid-19 rates to validate health and disease related topics. I
-retrieve U.S. county-level Covid-19 rates from by \citet{covid_data}, who compile this
+retrieve U.S. county-level Covid-19 rates from \citet{covid_data}, who compile this
 data based on reports from state and local health agencies. It is widely
@@
 Case Rate is measured as number of cases per 100,000 population. Observations
-vary from a minimum of 0 to a maximum of 1460.46 for each Monday from January 27, 2020 through
+vary from a minimum of zero to a maximum of 1460.46 for each Monday from January 27, 2020, through
 December 27, 2021. There are 285,986 cases across 3,136 counties and 101
-dates. Missing data were interpolated using `zoo::na.approx()` \citep{zoo}.
+dates. Missing data were interpolated using \texttt{zoo\:\:na\.approx\(\)} \citep{zoo}.
 
@@
 rates are scaled by population size for each year and can be interpreted as the
-death rate by suicide for every 1000 people. There are 34,683 total
-cases, resulting from 34,617 observations of 3,147 counties. Missing data were interpolated using
-zoo\:\:na\.approx() \citep{zoo}. Measures range from 0.034 to 53.254.
+death rate by suicide for every one thousand people. There are 34,683 total
+cases, resulting from 10 observations of 3,147 counties. Missing data were interpolated using
+\texttt{zoo\:\:na\.approx\(\)} \citep{zoo}. Measures range from 0.034 to 53.254.
 
@@
 
-Finally, I test Google Trends as an operationalization of political
+Finally, I evaluate Google Trends as an operationalization of political
 attitudes by first looking at actual voting outcomes in historical US
@@
 
-In addition, I use data on political opinions from the the American National
+In addition, I use data on political opinions from the American National
 Election Survey 2020 Time-Series Study \citep{anes_data}. This data is paired with
 restricted data provided by ICPSR, the Inter-university Consortium for Political
-and Social Research, that contains the geo-ids of the 5,441
+and Social Research, which contains the geo-ids of the 5,441
 survey respondents. The study interviewed respondents in a pre-election survey
-that was conducted between August 18, 2020 and the day of the US Presidential
-election day, November 3, 2020.
+that was conducted between August 18, 2020, and the day of the US Presidential
+election, November 3, 2020.  %TODO
+I will write about actual variables when my data extract request is approved.
 
@@
 These data include total population, population density,
-unemployment rate for those 16 and over, median county income, average commute
+unemployment rate for those sixteen years old and over, median county income, average commute
 time, percent of households living under the poverty line, and percent above 65
@@
 Google Search Trends data and additional demographic data were merged with each
-individual indicator based on County FIPS Codes and date using \texttt{dplyr} in \texttt{r}, version 4.1.2 \citep{tidyverse}. After creating these
-different datasets, I use the Pearson correlation formula (formula \eqref{eq:pearsoncorr}) for cross-sectional numeric data to calculate the
-strength of the relationship between each Google Trend and the respective
-data source.
+individual indicator based on County FIPS Codes and date using \texttt{dplyr} in \texttt{r},
+version 4.1.2 \citep{tidyverse}. After creating these different datasets, I use the 
+Pearson correlation formula (\eqref{eq:pearsoncorr}) for cross-sectional 
+numeric data to calculate the strength of the relationship between each Google
+Trend and the respective data source.
 
@@
 To address longitudinal correlations, I employ Repeated Measures Correlation
-using the `rmcorr` package in \texttt{r} \citep{bland1995, bakdash2017}. 
+using the \texttt{rmcorr} package in \texttt{r} \citep{bland1995, bakdash2017}. 
 Repeated Measures Correlation is useful for determining the within-county
 association for paired measures across time and counties. Results of these 
-correlations can be seen in table \ref{tab:corr-results}.
+correlations are in table \ref{tab:corr-results}.
 
-As an additional test of the relationships, I employ multiple linear regression
+As an additional criteria to evaluate the strength of the relationships, 
+I employ multiple linear regression
 (for cross-sectional datasets) and random intercept hierarchical linear models
@@
 relationships across locales. I include city-data like county population size,
-broadband rates, and median income to attempt to disentangle possible
-confounders of the relationship between Google search Trends and verified
+broadband rates, and median income to disentangle potentially
+confounded relationships between Google search Trends and verified
 indicators. Identifying these possible confounded relationships will help to
@@
 while others did not. For linear regression models, I normalize independent
-variables, i.e.variables have been centered and scaled to have a mean of 0 and
-standard deviation 1. Results of these models can be seen in tables \ref{tab:vacc_hes_analysis} through \ref{tab:pres_2020_analysis}.
+variables; in other words, variables have been centered and scaled to have a mean of zero and
+standard deviation of one. Results of these models are in tables \ref{tab:vacc_hes_analysis} through \ref{tab:pres_2020_analysis}.
 
@@
 
-The first attitudinal indicators is Vaccine Hesitancy for COVID-19 vaccines
+The first attitudinal indicator is Vaccine Hesitancy for COVID-19 vaccines
 \citep{vaches_data}. When comparing the measure of vaccine hesitancy to four
@@
 ('Coronavirus (Disease)' and vaccine hesitancy). Correlation's under |0.40| are 
-considered to be weak according to the common rules of thumb. When running these
+weak according to the common rules of thumb. With only one correlation 
+above that threshold, I conclude that the overall trends are at best weakly
+correlated with these attitudes. When running these
 correlations in multiple linear regression (see the results in table
-\ref{tab:vacc_hes_analysis}), I see an $r^2$ of 0.233 (Model 1) and 0.411
-(Model 2), indicating that the Google Trends are able to explain about 23% of
+\ref{tab:vacc_hes_analysis}), I see an $r^2$ of 0.233 (Model 1),
+indicating that the Google Trends explains about 23\% of
 the variation in Vaccine Hesitancy alone. Demographic characteristics like the
@@
 able to explain about 35\% of the variation (model 2), outperforming the first
-models. The Trend coefficients themselves, however, are significant and remain
-significant when controlling for demographics. This reinforces the finding from
-the Pearson Correlation that there is a significant but weak relationship
-between the Google Trends and Vaccine Hesitancy.
+models. The Trend coefficients for the trends themselves, however, are
+significant and remain significant when controlling for demographics.
+This reinforces the finding from the Pearson Correlation that there is a significant but weak relationship between the Google Trends and Vaccine Hesitancy.
 
@@
 usage. As with vaccine hesitancy, the Pearson correlations are negligible.
-Correlation's under |0.20| are considered to be negigible according to the
+Correlation's under |0.20| are negligible according to the
 common rules of thumb. I introduce these trends in multiple linear regression in
 table \ref{tab:mask_analysis}. Model 1 demonstrates that these five Google
-Search Trends can explain about 7\% of the variance in mask usage across U.S.
+Search Trends can explain about 8\% of the variance in mask usage across U.S.
 counties, reinforcing the conclusion that the relationship is quite weak. The
-coefficients themselves are somewhat significant in Model 1. However, after
+coefficients themselves are significant in Model 1. However, after
 including the demographic variables in Models 2 and 3, we see that the
 relationship between the Google Search Trends and mask usage is strengthened in
-magnitude and in significance, likely indicating a suppression effect due to
+magnitude and in significance, indicating a suppression effect due to
 underlying relationships between the trends and demographic variables. While the
@@
 In addition to attitudinal measures, I attempt to validate Google Trends for
-uses in the measurements of health indicators. The first indicator I test is
+uses in the measurements of health indicators. The first indicator I assess is
 Covid-19 case rates from 2020 through 2021. The Pearson correlation results
@@
 correlations, reveals similarly weak results with a maximum correlation of 0.32
-between 'smell loss' and rates of Covid-19. To further test the relationship, I
+between 'smell loss' and rates of Covid-19. To further investigate the relationship, I
 include the three trends in random intercept hierarchical linear models. Model 1
@@
 to explain about 20\% of the variation in Covid-19 rates ($r^2$ = 0.201). Few
-of the demographic variables have an effect on Covid-19 rates in models 2 or 3,
-though it seems there is some suppression for median income, unemployment rates,
+of the demographic variables influence Covid-19 rates in models 2 or 3,
+though there is some suppression for median income, unemployment rates,
 and population density. Model 3 has an $r^2$ of 0.200. I conclude that the
 Google Trends are slightly related to Covid-19 rates, but that this relationship
-is weak and we should not attempt to use Google Trends as an indicator of actual
+is weak, and we should not attempt to use Google Trends as an indicator of actual
 health outcomes.
@@
 
-Another indicator of health outcomes I test to validate Google Trends as
-possible health indicators are county suicide rates. As with previous cases,
+Another health outcome I test is county suicide rates. As with previous cases,
 there is only negligible correlation between actual suicide rates and Google
@@
 for inter-group variation over time in table \ref{tab:suicide_analysis}. While
-table \ref{tab:suicide_analysis} model 1 reveals a significant relationship
-between suicide hotline trends and suicide rates, the effect is small and the
+table \ref{tab:suicide_analysis} model 1 reveals a statistically significant relationship
+between suicide hotline trends and suicide rates, the effect is small, and the
 entire model only has an $r^2$ of 0.058. Adding in demographic features in model
-2 improves the $r^2$ quite a lot. In model 3, the inclusion of Google Trends
-actually decreases the overall amount of suicide rate variance explained
+2 improves the $r^2$ to 0.56. In model 3, the inclusion of Google Trends
+decreases the overall amount of suicide rate variance explained
 compared to model 2. These analyses lead me to conclude that Google Search
-Trends should not be used as indicators of suicide rates or intentions.
+Trends should not be used by researchers as indicators of suicide rates or intentions.
 
@@
 
-Previous research has showed some relationship between Google Search Trends and
-political election results. I test here the relationships between search trends
+Previous research has shown some relationship between Google Search Trends and
+political election results. I investigate the relationships between search trends
 and U.S. Presidential Election results in 2016 and 2020. In 2016, Pearson
@@
 predicting the county percentage of votes for Hillary Clinton. Model 1
-demonstrates how well Google Trends are able to predict the votes; while the
+demonstrates how well Google Trends predict the votes; while the
 trend for 'Hillary Clinton' is significantly associated with votes, the model's
@@
 fit quite well, bringing the $r^2$ up to 0.313 in model 2 and $r^2$ 0.327 in
-model 3. In table \ref{tab:pres_2020_analysis} shows this same analysis for the
+model 3. Table \ref{tab:pres_2020_analysis} shows this same analysis for the
 2020 election and predicts the percentage of votes for Joe Biden. While this
-model is largely similar to those in table \ref{tab:pres_2016_analysis}, this
+model is analogous to those in table \ref{tab:pres_2016_analysis}, this
 model 1 demonstrates how unrelated Google Trends can be from actual outcomes. In
@@
 \section{Discussion and Conclusion}
-This paper provides a critical test of Google Trends for use in Social Science. 
-I failed to find moderate or strong correlation among any of the Google 
-Trends tested and their validated indicators.
-While some Google Trends tested were significantly associated with the outcome in the linear regression model,
-effects tended to be small and the total model explainability remained low,
-even when controlling for demographic variables.
+This paper provides a critique of Google Trends for use in Social Science. 
+I failed to find correlation between the Google Trends and their 
+validated indicators. While some Google Trends tested were significantly 
+associated with the outcome in the linear regression model, effects tended
+to be small and the total model interpretability remained low, even when 
+controlling for demographic variables.
 
@@
 \citep{blumenstockPredictingPovertyWealth2015}. Google Trends, in theory, sounds like 
-a promising data source to 'nowcast' attitidinal, health, and political indicators;
-not only would the data be easily and freely accessible, it would also provide 
+a promising data source to 'nowcast' attitudinal, health, and political indicators.
+Not only would the data be easily and freely accessible, but it would also provide 
 indicators for areas where conducting research may be too costly. The demand for this 
 sort of indicator is clear and fields like the health sciences have freely utilized
-this data source. However, this article shows that there is no 
-no external validity of Google Trends for this specific use and social scientists
+this data source. However, this article shows that there is
+no external validity of Google Trends for these specific uses and social scientists
 will find no replacement for high quality survey data with Google Trends.
@@
 As social scientists it is our responsibility to deeply investigate the validity 
-of the data that we use in order to be confident in our research findings. As with any
-source of data, we must take into account the potential pitfalls, especially in research on big data
+of the data that we use so we can be confident in our research findings. As with any
+source of data, we must consider the potential pitfalls, especially in research on big data
 \citep{mcfarlandBigDataDanger2015}. In the case of Google Search Trends, precaution was 
@@
 in encouraging social scientists to pursue more research with the many new sources of big data, 
-I emphasize that testing out data to verify what it actually corrresponds to is an essential step 
+I emphasize that testing out data to verify what it actually corresponds to is an essential step 
 to making impactful research as a discipline going forward.

### 2022-03-05 tables/paper2/model-2-phi.tex
finish paper 1
Edits on Paper 1

@@
 \centering
-\begin{tabular}{p{0.25\linewidth} p{0.10\linewidth} p{0.08\linewidth} p{0.12\linewidth} p{0.15\linewidth} p{0.12\linewidth}}
-\hline
- & Person & Dr & Online Forum & Social Networking Site & Online Search\\
-\hline
-Person& NA& 0.28& 0.172& 0.275& 0.216\\
+\begin{tabular}{p{0.25\linewidth} p{0.10\linewidth} p{0.08\linewidth} p{0.12\linewidth} p{0.15\linewidth} p{0.12\linewidth}}\toprule
+ & Person & Dr & Online Forum & SNS & Online Search \\\toprule
+Person & \- &  0.28& 0.172& 0.275& 0.216 \\
+Dr & \- &  \- &  0.192 & 0.152 & 0.098 \\
+Online Forum& \- &  \- &  \- &  0.371& -0.073 \\
+SNS & \- &  \- &  \- &  \- &  0.057 \\
+Online Search& \- &  \- &  \- &  \- &  \\
+\bottomrule
+\multicolumn{6}{l}{\rule{0pt}{1em}Notes: SNS = Social Networking Site}\\
 
-Dr & & & 0.192 & 0.152 & 0.098\\
-
-Online Forum& NA& NA& NA& 0.371& -0.073\\
-
-Social Networking Site & & & & & 0.057\\
-
-Online Search& NA& NA& NA& NA& NA\\
-\hline
 \end{tabular}

### 2022-03-08 ch1.tex
even more bib fixes
fix paper 1 tables, finish most of writing
finish paper 1
haven't commited in a while.

@@
 
+\begin{center}
+    \texttt{UNDERGOING CHANGES}
+\end{center}
+
 This dissertation focuses on how people search for information and how
-people rely on this information and other cues to inform their
+people rely on this information and to inform their
 health-behaviors and develop norms. I will investigate the following
 questions:
-
-- How can we operationalize Google Search Trends as a valid indicator for uses in social science research?    
-- How do computer-mediated or interpersonal information-seeking strategies vary
-across populations?
-- What factors lead people to perform health information search on the Covid-19 vaccine online versus among social network ties? 
-- How are new health behavior norms regarding public health recommendations formed during the Covid-19 pandemic?  
-- How are patterns of information-search related to social norm stabilization during the Covid-19 pandemic?
 
@@
 
-\emph{need to cite \citep{bayer_etal20, bossetta18}}
+\citep{sparrow2011google} - memory is worse, reliance on technology
+
+\section{Background}
+
+\subsection{Information Flow}
 
@@
 \citep{granovetterStrengthWeakTies1973}, how social ties spread information about job
-opportunities \citep{granovetterGettingJobStudy1995, montgomeryJobSearchNetwork1992}, how information
-spreads best when weak and strong ties are balanced (embeddedness) \citep{uzziSocialStructureCompetition1997}, and more recent innovations in the stickiness of complex contagion \citep{centolaComplexContagionsWeakness2007}.
+opportunities \citep{granovetterGettingJobStudy1995, montgomeryJobSearchNetwork1992}, how 
+information spreads best when weak and strong ties are balanced (embeddedness) \citep{uzziSocialStructureCompetition1997}, and more recent innovations in the stickiness of complex contagion \citep{centolaComplexContagionsWeakness2007}.
 
@@
 opposite behavior: active directed searching by individuals to obtain
-information. \citep{pejtersenDesignComputeraidedUsersystem1984}, a scholar of library and information
+information. \citep{pejtersenDesignComputeraidedUsersystem1984}, a
+scholar of library and information
 science, theorized that there are 5 strategies for searching for
@@
 library setting, scholars have extended the theory to other fields and
-validated the framework \citep{fidelHumanInformationInteraction2012}; the frame is a useful beginning
-point for my theories of information search through network activation
-or through computer-mediated communication.
+validated the framework \citep{fidelHumanInformationInteraction2012}; the frame is a
+useful beginning point for my theories of information search through 
+network activation or through computer-mediated communication.
+
+\subsection{Information Search in The Digital Age}
+computer-mediated information search - as in the pre-internet age, you could find information without asking a friend or an expert. encyclopedias.. etc.
+
+computer mediated communication
+
+Social media...  \citep{bayer_etal20}
+"“Social media are Internet-based, disentrained, and persistent channels of
+masspersonal communication facilitating perceptions of interactions 
+among users, deriving value primarily from user-generated content.” \citep[][p. 50]{carr2015social}
+
+Social Networking Site - profile, stream , network, messaging \citep{boyd2007social, ellison2013sociality}
+
+integration of the one-to-one communication formations (face-to-face, letters, texting) within the context of one-to-many forms of communication (television, radio) \citep{o2018masspersonal}
+
+\subsection{Theory of Uncertainty Management}
 
@@
 
+\citep{sparrow2011google} - memory is worse, reliance on technology
+
+\subsection{Social Support}
+
 One way to find information is to activate network ties to find out
@@
 social ties and have strong and measurable association with health
-outcomes \citep{houseMeasuresConceptsSocial1985, thoitsMechanismsLinkingSocial2011}. Informational support is
+outcomes \citep{houseMeasuresConceptsSocial1985, thoitsMechanismsLinkingSocial2011}.
+Informational support is
 the process of seeking "help in defining, understanding, and coping with
@@
 people are likely to choose to search online.
+
+% TODO where to put this?
+Indeed, much research has revealed the higher levels of social capital of Facebook users \citep{liu2016meta}, with findings indicating that using SNSs to find information and relationship maintenance indicating the highest levels of bridging capital.
 
@@
 deepening social ties. \citet{leungGenerationalDifferencesContent2013} theorizes that 
-social media is
-gratifying for users because it allows for venting of negative feelings,
+social media is gratifying for users because it allows for venting of negative feelings,
 provides recognition, provides entertainment, promotes social affection,
@@
 when the informational need is related to forming and deepening social
-ties but search will be conducted online when information is needed but
+ties \citep{baumeister,grieve2013face} but search will be conducted online when 
+information is needed but
 an individual does not have an additional cognitive need to fill through
@@
 need to be balanced and will determine where search is conducted.
+
+\subsection{new literature to add}
+
+\citet{bayer_etal20}
+profiles and self-presentation
+networks and social mobilization
+streams and social comparison
+messages and social connectedness
+
+\citet{bossetta18}
+"tools that are easy to use and functional to the demands of varying using demographics"
+"digital architecture - the technical protocols that enable, constrain and shape user behavior in a virtual space"
+Different platforms deliver different user experiences along the dimensions of searchability, connectivity, and privacy
+
+\citet{boyd2010social}
+"Networked publics serve many of the same functions as other types of publics – they allow people to gather for social, cultural, and civic purposes and they help people connect with a world beyond their close friends and family.
+" p 39
+• Persistence: online expressions are automatically recorded and archived
+• Replicability: content made out of bits can be duplicated.
+• Scalability: the potential visibility of content in networked publics is great.
+• Searchability: content in networked publics can be accessed through search
 
@@
 people likely to rely on the behavior of others' to set their own norms
-for behavior \citep{alvarez2018, horneNormsIntegratedFramework2020}. This project will investigate how search contributes to the
-development of said spontaneous norms.
+for behavior \citep{alvarez2018, horneNormsIntegratedFramework2020}. 
+This project will investigate how search contributes to the development of said spontaneous norms.
 
@@
 integration \citep{durkheimDivisionLaborSociety1933, durkheimSuicide1897}.
-Weber, on the other hand,
-distinguished social behavior from social action, which was an action a
-person takes through subjective understanding and interpretation of
-actions of others. % TODO CITE ME
+Weber, on the other hand, distinguished social behavior from social action,
+which was an action a person takes through subjective understanding and
+interpretation of actions of others \citep{weber1978economy}.
 
@@
 by all parties of what is harmful and beneficial -- a critical question
-for the research question in Part 4: Paper 3. The Relational argument % TODO ADD LINK
+for the research question in \hyperlink{paper-3}{Paper 3}. The Relational argument 
+% TODO check if link works
 for norms is based on the value people place on their relationships and
@@
 \citep{robalinoPeerEffectsAdolescent2018, tankardEffectSupremeCourt2017}.
+
+\subsection{Social Networks}
 
@@
 \section{Broader Impact}
+\begin{center}
+    \texttt{UNDERGOING CHANGES}
+\end{center}
 
@@
 
+\begin{center}
+    \texttt{all three of these are UNDERGOING CHANGES}
+\end{center}
+
+\begin{figure}
+{\centering \includegraphics[width=\linewidth]{figs/ch1/Dissertation Concept Map - Color.pdf}}
+\caption{Theoretical Framework for the Dissertation}\label{fig:concept-map}
+\end{figure}
+
 To make my intended contributions to the literatures on computational
@@
 
+% TODO integrate research questions
+- How can we operationalize Google Search Trends as a valid indicator for uses in social science research?    
+- How do computer-mediated or interpersonal information-seeking strategies vary
+across populations?
+- What factors lead people to perform health information search on the Covid-19 vaccine online versus among social network ties? 
+- How are new health behavior norms regarding public health recommendations formed during the Covid-19 pandemic?  
+- How are patterns of information-search related to social norm stabilization during the Covid-19 pandemic?
+
 \subsection{Article 1: Construct Validity and Correspondence of Google Trends}
@@
 % TODO link to article
+
+\hyperlink{paper-1}{Paper 1}
 I will first investigate how Google Search Trends can be operationalized
@@
 % TODO link to article  
+\hyperlink{paper-2}{Paper 2}
 The second article in my dissertation investigates the question "what
@@
 % TODO link to article  
+\hyperlink{paper-3}{Paper 3}
+
 My final article takes a deeper dive into the formation of social norms

### 2022-03-09 ch1.tex
Finish Background theory

--- 2022-03-02 ch1.tex
@@
 
-This dissertation focuses on how people search for information and how
-people rely on this information and other cues to inform their
-health-behaviors and develop norms. I will investigate the following
-questions:
+% TODO entire dissertation Covid vs COVID vs Coronavirus
 
-- How can we operationalize Google Search Trends as a valid indicator for uses in social science research?    
-- How do computer-mediated or interpersonal information-seeking strategies vary
-across populations?
-- What factors lead people to perform health information search on the Covid-19 vaccine online versus among social network ties? 
-- How are new health behavior norms regarding public health recommendations formed during the Covid-19 pandemic?  
-- How are patterns of information-search related to social norm stabilization during the Covid-19 pandemic?
+This dissertation focuses on how people search for information and how people
+rely on this information and to inform their health-behaviors and develop social
+norms. Information permeates every facet of human society, from the hordes of
+data gathered through digital trace data or the passing gossip between friends.
+Human communication and human society are based on the circulation of
+information and knowledge. Information can be shared and promoted by others
+through information campaigns and consumed by an individual, called information
+push, or intentionally sought out by individuals, called information pull
+\citep{cybenkoFoundationsInformationPush1999}.
 
-Information is all around us and permeates every facet of human society,
-from the hordes of data gathered during the internet age or passing
-gossip between friends. Human communication and human society are based
-on the circulation of information and knowledge. Information can be
-shared by others through information campaigns and consumed by an
-individual, called information push, or intentionally sought out by
-individuals, called information pull \citep{cybenkoFoundationsInformationPush1999}.
+We must understand the information individuals receive and seek out in order
+to develop a well functioning society. The information that
+one consumes consolidates to create the entire worldview of every individual,
+leading to how they understand the world and behave civilly therein. New and
+emerging social norms must align with one's worldview to anticipate any sort of 
+behavioral change, for better or for worse.
 
-\emph{need to cite \citep{bayer_etal20, bossetta18}}
+The importance of reputable information and misinformation was clearly evident
+in the recent and ongoing Covid-19 pandemic. While the vaccines against the
+Covid-19 virus prevent severe illness, hospitalization, and death, only 60\% of
+Arizonans over 12 years old are fully vaccinated against the virus. We know that
+people exposed to misinformation are much less likely to receive vaccinations
+against the virus \citep{loombaMeasuringImpactCOVID192021}. It is not an
+exaggeration to claim that misinformation has been deadly for Arizona
+\citep{pathakInfodemicsCOVID19Role2020, greene_murphy21}.
 
-A critical turning point in the study of the flow information was put forth by renowned Sociologist Paul Lazarsfeld \citeyearpar{lazarsfeldPeopleChoice1944}.
-Lazarsfeld and others theorized that the media did not directly influence the masses, but that a "Two-Step Flow" was occurring where "opinion leaders" interpreted messages from mass media and then, in turn, promoted their opinions to the masses \citep{katzPersonalInfluencePart1955}.
-The opinion leaders interpret, explain, and diffuse contents to "opinion followers".
-From a networks
-perspective, "people rarely act on mass-media information unless it is also transmitted through personal ties" \citep[p.
-1374]{granovetterStrengthWeakTies1973}.
-Lazarsfeld  \citeyearpar{lazarsfeldPeopleChoice1944}'s first study focused on politics but follow up studies from \citep{katzPersonalInfluencePart1955} showed that this model matched information flows beyond the political realm.
-In contrast to the one-step flow, where media directly influences the masses, Lazarsfeld's theory remains in prominence today.
-While many scholars assumed that modern micro-targeted marketing strategies would provide evidence for a one-step flow perspective \citep{bennettOneStepFlowCommunication2006}, many scholars find that "opinion leaders" (often influencers and celebrities) still create a two-step flow of information transmission \citep{choi15, hilbertOneStepTwo2017}.
+This dissertation on information search and norm development provides clear and
+timely social implications for Arizona and the United States. This dissertation
+uncovers how norms are created during periods of norm uncertainty and builds the
+foundation to theorize and test interventions that promote positive norms in
+times of disasters and uncertainty. Specifically, I investigate how local
+diffusion leads to social norms through information search which will have
+strong implications for the prevention of global polarization and the spread of
+misinformation.
 
-The spread of information has also been studied thoroughly from the
-prospective of social networks. Individuals engage with each other and
-their distributive ties to create community contexts where norms,
-beliefs, and values circulate. Information diffuses through communities
-and social networks \citep{fowler2010cooperative, bond_etal12, klarEffectNetworkStructure2017}.
-However, "different things spread in different ways and to
-different extents" \citep[p. 563]{christakisSocialContagionTheory2013} and information can
-spread differently than a virus or behavior. Important studies in the
-spread of information through networks include the study of adoption of
-innovations by physicians \citep{colemanDiffusionInnovationPhysicians1957}, how new
-inventions are adopted from early adopters to laggards \citep{rogersDiffusionInnovations1962},
-how weak ties help cohere networks and diffuse information
-\citep{granovetterStrengthWeakTies1973}, how social ties spread information about job
-opportunities \citep{granovetterGettingJobStudy1995, montgomeryJobSearchNetwork1992}, how information
-spreads best when weak and strong ties are balanced (embeddedness) \citep{uzziSocialStructureCompetition1997}, and more recent innovations in the stickiness of complex contagion \citep{centolaComplexContagionsWeakness2007}.
+In academia and policy, the main focus in research on information has always
+been the information that is sent to consumers, seeing people as passive
+receivers of information. My dissertation instead focuses on individuals as
+active agents in their search for information which helps me uncover the
+information individuals are exposed to. By looking at how individuals search, I
+aim to identify pain points and focus areas for future interventions in the
+misinformation process.
 
-So far, I have only been discussing the way that information is
-passively consumed through push efforts by opinion leaders and social
-networks. However, sociological literature is really sparse on the
-opposite behavior: active directed searching by individuals to obtain
-information. \citep{pejtersenDesignComputeraidedUsersystem1984}, a scholar of library and information
-science, theorized that there are 5 strategies for searching for
-information. The most common strategy is browsing, where people follow
-leads based on associations without planning ahead. Another strategy is
-analytical, which includes an explicit consideration of all facets of
-the question to guide a search. The empirical method guides the search
-based on tactics that were successful in past research. The known site
-strategy is to go to the direct source of the information if known. And
-finally, the similarity method is to find information based on another
-similar question that already has an answer. These 5 strategies vary in
-their demands for prior knowledge, cognitive processing, memory, and
-time spent. While this theory is aimed at finding information in a
-library setting, scholars have extended the theory to other fields and
-validated the framework \citep{fidelHumanInformationInteraction2012}; the frame is a useful beginning
-point for my theories of information search through network activation
-or through computer-mediated communication.
+The information that spread to communities in Arizona led to the health
+behaviors exhibited today by Arizonans. While the information spread in various
+ways, like through diffusion and polarization, it contributed to our newly
+established norms in the Spring of 2020 and since. By uncovering how norms were
+created during this time of norm uncertainty, my research will contribute to the
+recommended interventions to promote effective health-related behavioral norms
+before politicization and misinformation occurs. This will create a healthier,
+happier Arizona.
 
-Some communication theorists ask why an answer to a question is sought
-in the first place. The Theory of Uncertainty Management \citep{brashersCommunicationUncertaintyManagement2001}
-professes that people search for information when their uncertainty
-around the subject leads to anxiety or other cognitive harms. The Theory
-of Motivated Information Management \citep{afifiSeekingInformationSexual2006, afifiTheoryMotivatedInformation2004}
-extends the prior by adding that uncertainty itself is not the catalyst
-for information-search; rather, it is driven by a discrepancy between
-the current level of uncertainty on a subject and desired level of
-uncertainty.
+\section{Background}
 
-One way to find information is to activate network ties to find out
-information through a form of social support. Social support, while
-previously used interchangeably with the term social networks and social
-integration \citep{houseStructuresProcessesSocial1988}, are the emotional,
-informational, and instrumental assistance functions performed between
-social ties and have strong and measurable association with health
-outcomes \citep{houseMeasuresConceptsSocial1985, thoitsMechanismsLinkingSocial2011}. Informational support is
-the process of seeking "help in defining, understanding, and coping with
-problematic events and include education, advice, or referral to another
-source of support" \citep[p. 640]{winemiller_etal93}. Brashers, a health
-communications researcher, defines informational support slightly
-differently, focusing on the exchange of information that "facilitates
-coping with life stresses... that may be exchanged among members of a
-support network" \citeyearpar[p. 260]{brashersInformationSeekingAvoiding2002}.
-Both of these definitions provide important
-lenses for my question of how computer-mediated or interpersonal
-information-seeking strategies vary. If information is needed but there
-is no search for coping or deeper understanding of important matters,
-people are likely to choose to search online.
+\subsection{Information Flow}
+% what happened before this point? 
+A critical turning point in the study of the flow information was put forth by
+renowned Sociologist Paul Lazarsfeld \citeyearpar{lazarsfeldPeopleChoice1944}.
+Lazarsfeld and others theorized that the media did not directly influence the
+masses, but that a "Two-Step Flow" was occurring where "opinion leaders"
+interpreted messages from mass media and then, in turn, promoted their opinions
+to the masses \citep{katzPersonalInfluencePart1955}. The opinion leaders
+interpret, explain, and diffuse contents to "opinion followers". From a networks
+perspective, "people rarely act on mass-media information unless it is also
+transmitted through personal ties" \citep[p. 1374]{granovetterStrengthWeakTies1973}. 
+Lazarsfeld \citeyearpar{lazarsfeldPeopleChoice1944}'s first study focused on
+politics but follow up studies from \citep{katzPersonalInfluencePart1955} showed
+that this model matched information flows beyond the political realm. In
+contrast to the one-step flow, where media directly influences the masses,
+Lazarsfeld's theory remains in prominence today. While many scholars assumed
+that modern micro-targeted marketing strategies would provide evidence for a
+one-step flow perspective \citep{bennettOneStepFlowCommunication2006}, many
+scholars find that "opinion leaders" (often influencers and celebrities) still
+create a two-step flow of information transmission \citep{choi15,
+hilbertOneStepTwo2017}.
+
+The spread of information has been thoroughly studied from the prospective
+of social networks. Individuals engage with each other and their distributive
+ties to create community contexts where norms, beliefs, and values circulate.
+Information diffuses through communities and social networks
+\citep{fowler2010cooperative, bond_etal12, klarEffectNetworkStructure2017}.
+However, "different things spread in different ways and to different extents"
+\citep[p. 563]{christakisSocialContagionTheory2013} and information can spread
+differently than a virus or behavior. Important studies in the spread of
+information through networks include the study of adoption of innovations by
+physicians \citep{colemanDiffusionInnovationPhysicians1957}, how new inventions
+are adopted from early adopters to laggards
+\citep{rogersDiffusionInnovations1962}, how weak ties help bind networks and
+diffuse information \citep{granovetterStrengthWeakTies1973}, how social ties
+spread information about job opportunities
+\citep{granovetterGettingJobStudy1995, montgomeryJobSearchNetwork1992}, how
+information spreads best when weak and strong ties are balanced (embeddedness)
+\citep{uzziSocialStructureCompetition1997}, and more recent innovations in the
+stickiness of complex contagion \citep{centolaComplexContagionsWeakness2007}.
+
+\subsection{Information Search}
+I only discussed the way that information is passively
+consumed through push efforts by opinion leaders and social networks. However,
+sociological literature is really sparse on the opposite behavior: active
+directed searching by individuals to obtain information.
+\citep{pejtersenDesignComputeraidedUsersystem1984}, a scholar of library and
+information science, theorized that there are 5 strategies for searching for
+information. The most common strategy is browsing, where people follow leads
+based on associations without planning ahead. Another strategy is analytical,
+which includes an explicit consideration of all facets of the question to guide
+a search. The empirical method guides the search based on tactics that were
+successful in past research. The known site strategy is to go to the direct
+source of the information if known. And finally, the similarity method is to
+find information based on another similar question that already has an answer.
+These 5 strategies vary in their demands for prior knowledge, cognitive
+processing, memory, and time spent. While this theory is aimed at finding
+information in a library setting, scholars have extended the theory to other
+fields and validated the framework \citep{fidelHumanInformationInteraction2012};
+the frame is a useful beginning point for the theories of information search
+through network activation or through computer-mediated communication.
+
+\subsection{Information Search in The Digital Age}
+
+The introduction of the internet and digital technologies introduced an epochal
+disruption in the communication and informational-search mediums that people had
+available to them. Computer-mediated communication was the largest communication
+revolution in a century, changing the speed and availability of communication
+between individuals by electronic mail, instant messaging, two-way interactive
+video calls, discussion forums, blogs, and social networking
+\citep{rainie2012networked}. Computer-mediated communication encompasses any
+sort of communication through computers connected to the internet; the umbrella
+term involves both synchronous and asynchronous communication as well as
+one-to-one, one-to-many, or many-to-many exchanges. Social media, on the other
+hand, are more specific, and are "Internet-based, disentrained, and persistent
+channels of mass personal communication facilitating perceptions of interactions
+among users, deriving value primarily from user-generated content.” \citep[][p.
+50]{carr2015social}. While an email between colleagues is computer-mediated
+communication, it is not social media as there is only one interaction between
+users and there is no value derived from the user-generated content outside the
+pair \citep{bayer_etal20}. Even more restrictive still is the social networking
+site, which consists of a profile, a network, and a stream or a feed
+\citep{boyd2007social, ellison2013sociality,},  often also involving a messaging
+component  \citep{bayer_etal20}. Social networking sites are also interesting
+because they often uniquely combine one-to-one communication within the context
+of one-to-many communication, like resharing a television news story to your
+facebook feed and chatting with others about the content in the comments
+section. But what do these classifications mean for the information-seeking
+behaviors of individuals in the 21st century? Not only is it quicker to perform
+network activation and seek support, but people are "permanently online,
+permanently connected" making activation easy \citep{vorderer2017permanently}.
+The constant connectedness facilitates communication, but also presents people
+with overchoice, or the difficulty in making a decision because simply every
+network connection you may want to activate is permanently connected and easy to
+reach. In other words, constant connection may be debilitating to many who are
+seeking information. \citet{smallSomeoneTalk2017} provides many examples of this
+when he demonstrates that more often than not, graduate students who needed
+support simply asked "miscellaneous classmates encountered down the hall" (p.
+176) rather than their trusted, long-term confidants. It seems that network
+activation may rely on more than just trust; namely: convenience.
+
+The digital age did not only revolutionize communication. It also
+revoluitionized information search \citep{ramirez2002information}. Just as prior
+to the digital age you could open an encyclopedia or peruse the library to find
+the information you seek, much of the computer-mediated information search
+surely occurs outside of social network activation contexts. While searching in
+an encyclopedia is far less common today, internet search engines have
+revolutionizes the speed and ease at which we can find information. Early web
+search engines allowed information seekers to browse web directories and early
+engines like Yahoo! and Altavista found success using keyword-based search,
+though the early algorithms were limited in what they could find and relied
+heavily on the wording of the queries. Google, the major web search engine used
+today, introduced the disrputive PageRank algorithm in the early 2000s, securing
+its place as the information hegemon of the 21st century
+\citep{brin1998anatomy}. Not only has computer-mediated information search
+revolutionized the ease of obtaining information, but it has also changed out
+brains. \citet{sparrow2011google} show that the digital age has led to worse
+memory and higher reliance on technology to keep track of information for us.
+These search engines have also shaped our cultures by controlling, whether
+through algorithm or intentionally, the information the engine provides. For
+example, Google will not show results for various neo-Nazi websies in countries
+where holocaust denial is illegal, like France and Germany. This is illustrative
+of the control engines have over information and how this control may introduce
+various political, economic, and social biases in the information they provide
+\citep{segev2010google}. When 99Firms \citeyearpar{99firms22} compiled the data
+from sources like NetMarketShare, Statista, DuckDuckGo, Yahoo Finance, Google,
+and Pew Research they find that about about Around 93\% of all web traffic is
+via a search engine and that 78.39\% of all internet search use Google. Because
+computer-mediated information search is instantaneous and only requires mobile
+data or wifi, there is virtually no cost to seeking information on one of these
+mediums.
+
+\subsection{Theory of Uncertainty Management}
+
+Some communication theorists ask why an answer to a question is sought in the
+first place. The Theory of Uncertainty Management
+\citep{brashersCommunicationUncertaintyManagement2001} professes that people
+search for information when their uncertainty around the subject leads to
+anxiety or other cognitive harms. The Theory of Motivated Information Management
+\citep{afifiSeekingInformationSexual2006, afifiTheoryMotivatedInformation2004}
+extends the prior by adding that uncertainty itself is not the catalyst for
+information-search; rather, it is driven by a discrepancy between the current
+level of uncertainty on a subject and desired level of uncertainty.
+
+\subsection{Social Support}
+
+One way to find information is to activate network ties to find out information
+through a form of social support. Social support, while previously used
+interchangeably with the term social networks and social integration
+\citep{houseStructuresProcessesSocial1988}, are the emotional, informational,
+and instrumental assistance functions performed between social ties and have
+strong and measurable association with health outcomes
+\citep{houseMeasuresConceptsSocial1985, thoitsMechanismsLinkingSocial2011}.
+Informational support is the process of seeking "help in defining,
+understanding, and coping with problematic events and include education, advice,
+or referral to another source of support" \citep[p. 640]{winemiller_etal93}.
+Brashers, a health communications researcher, defines informational support
+slightly differently, focusing on the exchange of information that "facilitates
+coping with life stresses... that may be exchanged among members of a support
+network" \citeyearpar[p. 260]{brashersInformationSeekingAvoiding2002}. Both of
+these definitions provide important lenses for my question of how
+computer-mediated or interpersonal information-seeking strategies vary. 
+Some research has revealed that Facebook users who utilize the platform to 
+find information and to maintain relationships have high levels of bridging
+social capital \citep{liu2016meta}. However, this leaves the question 
+of who activates their social networks for information using social networking 
+sites like Facebook over activating these networks in face-to-face interactions.
 
@@
 From studies of mass communication, uses and gratifications theory (UGT)
-\citep{blumlerUsesMassCommunications1974, tanMassCommunicationTheories1985}
-may also lend itself to theorizing why
-computer-mediated or interpersonal information-seeking strategies vary.
-UGT posits that users are not passive consumers of media and that people
-have an active role in choosing different sources of media based on
-their satisfaction of specific needs on an individual basis. UGT is
-based on Maslow's \citeyearpar{maslowTheoryHumanMotivation1943}
-hierarchy of needs and is compatible with
-Lazarsfeld and Katz's theory of two-step flow because people can choose
-their media and the opinion leaders they follow. Modern-day theorists
-have extended UGT theory and classified the uses and gratifications of
-the internet and of social media. \citet{staffordDeterminingUsesGratifications2004}
-theorize that the internet provides gratification through useful content
-that meets expectations, gratification from purposeful navigating or
-random browsing as a process, and social gratification from forming and
-deepening social ties. \citet{leungGenerationalDifferencesContent2013} theorizes that 
-social media is
+\citep{blumlerUsesMassCommunications1974, tanMassCommunicationTheories1985} may
+lend itself to theorizing why information-seeking strategies vary among different
+platforms and activation types. UGT posits that users are not passive
+consumers of media and that people have an active role in choosing different
+sources of media based on their satisfaction of specific needs on an individual
+basis. UGT is based on Maslow's \citeyearpar{maslowTheoryHumanMotivation1943}
+hierarchy of needs and is compatible with Lazarsfeld and Katz's theory of
+two-step flow because people can choose their media and the opinion leaders they
+follow. Modern-day theorists have extended UGT theory and classified the uses
+and gratifications of the internet and of social media.
+\citet{staffordDeterminingUsesGratifications2004} theorize that the internet
+provides gratification through useful content that meets expectations,
+gratification from purposeful navigating or random browsing as a process, and
+social gratification from forming and deepening social ties.
+\citet{leungGenerationalDifferencesContent2013} theorizes that social media is
 gratifying for users because it allows for venting of negative feelings,
-provides recognition, provides entertainment, promotes social affection,
-and fulfills cognitive needs. Adapting UGT to my own purposes, I
-theorize that informational support will be activated from network ties
-when the informational need is related to forming and deepening social
-ties but search will be conducted online when information is needed but
-an individual does not have an additional cognitive need to fill through
-social interaction. Alternative goals such as identity management or
-relational maintenance \citep{brashersInformationSeekingAvoiding2002}
-need to be balanced and will determine where search is conducted.
+provides recognition, provides entertainment, promotes social affection, and
+fulfills cognitive needs.
+
+There has been some research into how different platforms allow for different user 
+experiences or "affordances" \citep{boyd2010social}. For example, \citet{bossetta18} first show
+that all social media platforms must provide "tools that are easy to use and 
+functional to the demands of varying using demographics" (p. 473). They also
+explain how each digital architecture enables, contstrains and shapes how users
+behave on their platform and in virtual space, leading to many different experiences 
+along the dimensions of searchability, connectivity, and privacy.
+
+Adapting UGT to my own purposes, I theorize that
+informational support will be activated from network ties when the informational
+need is related to forming and deepening social ties
+\citep{baumeister,grieve2013face} but search will be conducted outside of network
+activation when information is needed but an individual does not have an additional cognitive
+need to fill through social interaction. Alternative goals such as identity
+management or relational maintenance
+\citep{brashersInformationSeekingAvoiding2002} need to be balanced and may also
+influence where search is conducted.
 
 \subsection{Social Norms}
+I showed the levels of uncertainty may direct how and when people
+search for information. However, in situations of rapidly changing norms,
+uncertainty is prevalent. This dissertation will also focus on developing
+new social norms in situations of uncertainty about how to behave. 
+Minimal research exists in quickly emerging
+norms in times of emergency, but shows that people likely to rely on the
+behavior of others' to set their own norms for behavior \citep{alvarez2018,
+horneNormsIntegratedFramework2020}. This project will investigate how search
+contributes to the development of said spontaneous norms.
 
-One area previously mentioned that motivates information search is to
-minimize uncertainty based on the Theory of Motivated Information
-Management; this dissertation will also focus on developing new social
-norms in situations of uncertainty about how to behave. Minimal research
-exists in quickly emerging norms in times of emergency, but shows that
-people likely to rely on the behavior of others' to set their own norms
-for behavior \citep{alvarez2018, horneNormsIntegratedFramework2020}. This project will investigate how search contributes to the
-development of said spontaneous norms.
+Social norms form the building blocks of social organization and have been a
+focus of sociology since the beginning. In a recent Annual Review of Sociology
+piece focused on social norms, Horne and Mollborn define norms as "group-level
+evaluations of behavior ... [or] when people have expectations about how others
+evaluate behaviors" \citeyearpar[p. 468-69]{horneNormsIntegratedFramework2020}.
+One of the principal architects of sociology, \'{E}mile Durkheim, saw that
+society exerted powerful forces on individuals and classified people's norms,
+beliefs, and values as parts of collective consciousness that provide for
+societal integration \citeyearpar{durkheimSuicide1897, durkheimDivisionLaborSociety1933}.
+For Durkheim, norms were therefore the glue that held society together in cohesion.
 
-Social norms form the building blocks of social organization and have
-been a focus of sociology since the beginning. In a recent Annual Review
-of Sociology piece focused on social norms, Horne and Mollborn define
-norms as "group-level evaluations of behavior ... [or] when people
-have expectations about how others evaluate behaviors" \citeyearpar[p. 468-69]{horneNormsIntegratedFramework2020}. Durkheim saw that society exerted powerful
-forces on individuals and classified people's norms, beliefs, and values
-as parts of collective consciousness that provide for societal
-integration \citep{durkheimDivisionLaborSociety1933, durkheimSuicide1897}.
-Weber, on the other hand,
-distinguished social behavior from social action, which was an action a
-person takes through subjective understanding and interpretation of
-actions of others. % TODO CITE ME
+Max Weber, another founding architect of sociology saw social norms differently.
+Weber distinguished social behavior from social action, which was an action a
+person takes through subjective understanding and interpretation of actions of
+others \citeyearpar{weber1978economy}. Weber therefore saw social norms through
+the lens of the subjective meanings behind every action. Actions that were not
+considered by an individual were not the focus of Weber. New spontaneous norms
+that are emerging in a society under upheaval, like the health behaviors that
+emerged during the Covid-19 pandemic, emerged with new subjective meanings and
+cognitive associations that held consequences for the individuals who adopted
+the social actions.
 
@@
 \citep{horneNormsIntegratedFramework2020}. One of the main critiques of the
-consequentialist argument is that it relies on the same interpretation
-by all parties of what is harmful and beneficial -- a critical question
-for the research question in Part 4: Paper 3. The Relational argument % TODO ADD LINK
+consequentialist argument is that it relies on the same interpretation of the perceived action
+by all parties of what is harmful and beneficial. The Relational argument 
 for norms is based on the value people place on their relationships and
@@
 
-Norms are formed in social networks; "Networks operate in a larger
-cultural context that can facilitate or inhibit acceptance of general
-cultural norms and beliefs \citep{pescosolidoDurkheimSuicideReligion1989, whiteSocialStructureMultiple1976}. Because of this, people tend to resemble
+\subsection{Social Networks}
+
+Norms are formed inside of social networks; "Networks operate in a larger cultural
+context that can facilitate or inhibit acceptance of general cultural norms and
+beliefs" \citep[][p. 44]{pescosolidoDurkheimSuicideReligion1989}. 
+Because of this, people tend to resemble
 their network as a form of network autocorrelation and homophily
 \citep{dellapostaWhyLiberalsDrink2015}. While "birds of a feather flock
-together" in homophily \citep{mcphersonBirdsFeatherHomophily2001},
-attitudes and behaviors are shaped by peers, creating filter bubbles of
-social influence \citep{dellapostaWhyLiberalsDrink2015}.
+together" in homophily \citep{mcphersonBirdsFeatherHomophily2001}, attitudes and
+behaviors are shaped by peers, creating filter bubbles of social influence
+\citep{dellapostaWhyLiberalsDrink2015}.
 
-\citet{goldbergSocialContagionAssociative2018} argue that the state of the literature on
-diffusion and social contagion, discussed above, is erroneous. They
-propose an important linkage that had been missed in previous research
-of the diffusion of behavior (or, as I interpret it, the creation of new
-norms). They argue that what actually diffuses during social contagion
-are the perceptions about which beliefs or behaviors are compatible with
-one another, what they call "associative diffusion". In times of
-behavioral uncertainty, I theorize that individuals strategically look
-towards other high-status individuals, institutions, and perform
-regimented searches to establish for themselves the behavior that is
-compatible with other cognitive biases they hold.
+\citet{goldbergSocialContagionAssociative2018} argue that the state of the
+literature on diffusion and social contagion, discussed above, is erroneous.
+They propose an important linkage that had been missed in previous research of
+the diffusion of behavior (or, as I interpret it, the creation of new norms).
+They argue that what actually diffuses during social contagion are the
+perceptions about which beliefs or behaviors are compatible with one another,
+what they call "associative diffusion". 
+This relates back to the theory of relational norms, where individuals assume
+what their peers will approve and disapprove of. In order for these assumptions 
+to take place, they must have an understanding of which behaviors and beliefs
+are possessed by whom in their network and how new associations may influence
+or disrupt the expected actions. 
+In times of behavioral uncertainty, I
+theorize that individuals strategically look towards other high-status
+individuals, institutions, and perform regimented searches to establish for
+themselves the behavior that is compatible with other cognitive biases they
+hold.
 
 \section{Broader Impact}
+\begin{center}
+    \texttt{UNDERGOING CHANGES}
+\end{center}
 
-% from Marshall Foundation
-
-The vaccines against the COVID-19 coronavirus prevent severe illness,
-hospitalization, and death. However, as I'm writing this, less than 55%
-of Arizonans over 12 years old are fully vaccinated against the virus.
-We know that people exposed to misinformation are much less likely to
-receive vaccinations against the virus \citep{loombaMeasuringImpactCOVID192021}. It is not
-an exaggeration to claim that misinformation has been deadly for Arizona
-\citep{pathakInfodemicsCOVID19Role2020}.
-
-misinformation \citep{greene_murphy21}
-
-My research on information search and norm development provides clear
-and timely social implications for Arizona and the United States. This
-dissertation uncovers how norms are created during periods of norm
-uncertainty and builds the foundation to theorize and test interventions
-that promote positive norms in times of disasters and uncertainty.
-Specifically, I investigate how local diffusion leads to social norms
-through information search which will have strong implications for the
-prevention of global polarization and the spread of misinformation.
-
-In academia and policy, the main focus is on the information that is
-sent to consumers, seeing people as passive receivers of information. My dissertation instead
-focuses on individuals as active agents in their search for information
-which helps me uncover the information individuals are exposed to. By
-looking at how individuals search, I aim to identify pain points and focus areas for
-future interventions in the misinformation process.
-
-The information that spread to communities in Arizona led to the health
-behaviors exhibited today by Arizonans. While the information spread in
-various ways, like through diffusion and polarization, it contributed to
-our newly established norms. By uncovering how norms were created during
-this time of norm uncertainty, my research will contribute to the recommended interventions to promote effective health-related behavioral norms before politicization and
-misinformation occurs. This will create a healthier, happier Arizona
-
-This dissertation researches information search and norm development,
-both of which have implications for academic research and communities.
-
+% TODO make Broader Impact more relevant to actual findings
 % Original
@@
 
-\subsection{Article 1: Construct Validity and Correspondence of Google Trends}
-% TODO Double check name
-% TODO link to article  
+% todo, go over fig:conceptmap
+
+\hyperlink{paper-1}{\subsection{Article 1: Digital Trace Data as Indicators of the Social World: Validating Google Trends for use in Scientific Research}}
+
+- How can we operationalize Google Search Trends as a valid indicator for uses in social science research?
+
 I will first investigate how Google Search Trends can be operationalized
@@
 data studies and sociological methodology.
-% TODO ADD IN ARTICLE 1 ABSTRACT
 
-\subsection{Article 2: Information-Seeking Behaviors for Information on Covid-19 Vaccinations}
-% TODO Double check name
-% TODO link to article  
+Computational social science and other disciplines are quick to 
+adopt new sources of digital trace data for use in academic research. 
+In this article, I examine the validity of Google Search Trends 
+as potential indicators of three different cases, namely attitudes, 
+disease prevalence and political preferences using eight %TODO double check number
+different validated data sources. I use Pearson and Repeated Measures Correlations 
+between the Google Trends and the validated indicators as well as multiple linear regression
+(for cross-sectional datasets) and random intercept hierarchical linear models
+(for longitudinal datasets) as additional tests of the data. 
+I fail to find correlation among any of the Google 
+Trends tested and their validated indicators. While some Google Trends 
+tested were significantly associated with the outcome in the regression models,
+effects tended to be small and the total model interpretability remained low,
+even when controlling for demographic variables. This article shows that there is no 
+external validity of Google Trends for these uses and social scientists
+will find no replacement for high quality survey data with Google Trends.
+
+\hyperlink{paper-2}{\subsection{Article 2: Information-Seeking Behaviors for Information on Covid-19 Vaccinations}}
+
+- How do computer-mediated or interpersonal information-seeking strategies vary
+across populations?
+- What factors lead people to perform health information search on the Covid-19 vaccine online versus among social network ties?
+
 The second article in my dissertation investigates the question "what
@@
 
-\subsection{Article 3: Social Norms under Uncertain Times: A dynamic study of Stay-At-Home and Vaccination Rates During the Covid-19 Pandemic}
-% TODO Double check name
-% TODO link to article  
+\hyperlink{paper-3}{\subsection{Article 3: Social Norms under Uncertain Times: A dynamic study of Stay-At-Home and Vaccination Rates During the Covid-19 Pandemic}}
+
+- How are new health behavior norms regarding public health recommendations formed during the Covid-19 pandemic?  
+- How are patterns of information-search related to social norm stabilization during the Covid-19 pandemic?
+
 My final article takes a deeper dive into the formation of social norms
-governing health behaviors in cases of extreme uncertainty using the
-cases of both a) population mobility during early 2020 and b)
-vaccination rates during early 2021, both as responses to public health
-recommendations to mitigate the Covid-19 pandemic. Using theories of
-associative diffusion and the integrated theoretical framework of norms,
-I test how these health behaviors are outcomes of assortative signaling
-from networks and other sources, such as social isolation and connection
-between communities, religious and political conservativism, and
-attention to media sources, and online norms as measured by
+governing health behaviors in cases of extreme uncertainty using the cases of
+both a) population mobility during early 2020 and b) vaccination rates during
+early 2021, both as responses to public health recommendations to mitigate the
+Covid-19 pandemic. Using theories of associative diffusion and the integrated
+theoretical framework of norms, I test how these health behaviors are outcomes
+of assortative signaling from networks and other sources, such as social
+isolation and connection between communities, religious and political
+conservativism, and attention to media sources, and online norms as measured by
 information-search behaviors. To investigate this, I conduct statistical
-modelling on a dataset I compiled from multiple sources, including
-Google, Facebook, and the Center for Disease Control and Prevention.
+modelling on a dataset I compiled from multiple sources, including Google,
+Facebook, and the Center for Disease Control and Prevention.
 

### 2022-03-09 paper1.tex
Finish Background theory

@@
 in-depth explanation of this procedure, see \citet[p. 5]{park_etal}. I interpolate 
-missing datapoints in the longitudinal datasets using \texttt{zoo\:\:na\.approx\(\)} \citep{zoo}.
+missing datapoints in the longitudinal datasets using \texttt{na.approx()} \citep{zoo}.
 
@@
 December 27, 2021. There are 285,986 cases across 3,136 counties and 101
-dates. Missing data were interpolated using \texttt{zoo\:\:na\.approx\(\)} \citep{zoo}.
+dates. Missing data were interpolated using \texttt{na.approx()} \citep{zoo}.
 
@@
 cases, resulting from 10 observations of 3,147 counties. Missing data were interpolated using
-\texttt{zoo\:\:na\.approx\(\)} \citep{zoo}. Measures range from 0.034 to 53.254.
+\texttt{na.approx()} \citep{zoo}. Measures range from 0.034 to 53.254.
 

### 2022-03-10 ch1.tex
3 article summaries

@@
 
-\section{Background}
+\section{Theoretical Underpinnings}
 
 \subsection{Information Flow}
-% what happened before this point? 
+% TODO what happened before this point? 
 A critical turning point in the study of the flow information was put forth by
@@
 from sources like NetMarketShare, Statista, DuckDuckGo, Yahoo Finance, Google,
-and Pew Research they find that about about Around 93\% of all web traffic is
+and Pew Research they found that about about Around 93\% of all web traffic is
 via a search engine and that 78.39\% of all internet search use Google. Because
@@
 are possessed by whom in their network and how new associations may influence
-or disrupt the expected actions. 
-In times of behavioral uncertainty, I
+or disrupt the expected actions. In times of behavioral uncertainty, I
 theorize that individuals strategically look towards other high-status
@@
 
-\section{Broader Impact}
+\section{Three Empirical Articles}
+
+To investigate information-seeking behaviors, online search tools, and how
+new norms in health behaviors form, I first provide an outline of the 
+information push and pull process in figure \ref{fig:concept-map}. After 
+being exposed to new information, an actor can choose to further investigate
+the information online or offline and, in turn, further share the 
+information they were exposed to.
+
+\begin{figure}
+{\centering \includegraphics[width=\linewidth]{figs/ch1/Dissertation Concept Map - Color.pdf}}
+\caption{Theoretical Framework for the Dissertation}\label{fig:concept-map}
+\end{figure}
+
+This dissertation uses three articles to investigate different parts of
+the aforementioned theoretical framework (figure \ref{fig:concept-map}).
+The dissertation is divided into three parts, with Article 1 focusing 
+on online information search, Article 2 focusing on online and offline
+information search, and Article 3 investigating the entire information
+push and pull process in the context of establishing new norms.
+
+\hyperlink{paper-1}{\subsection{Article 1: Digital Trace Data as Indicators of the Social World: Validating Google Trends for use in Scientific Research}}
+
+Computational social science and other disciplines are quick to adopt new
+sources of digital trace data for use in academic research. In this article, I
+examine the validity of one of these new sources, Google Search Trends. I
+validate how Google Trends can be used to demonstrate three different cases,
+namely attitudes, disease prevalence and political preferences using eight %TODO double check number
+different validated data sources. This paper asks, "How can we operationalize
+Google Search Trends as a valid indicator for uses in social science research?"
+I use Pearson and Repeated Measures Correlations between the Google Trends and
+the validated indicators as well as multiple linear regression (for
+cross-sectional datasets) and random intercept hierarchical linear models (for
+longitudinal datasets) as additional tests of the data.
+
+I fail to find correlation among any of the Google Trends tested and their
+validated indicators. While some Google Trends tested were significantly
+associated with the outcome in the regression models, effects tended to be small
+and the total model interpretability remained low, even when controlling for
+demographic variables. This article shows that there is no external validity of
+Google Trends for these uses and social scientists will find no replacement for
+high quality survey data with Google Trends.
+
+\hyperlink{paper-2}{\subsection{Article 2: Information-Seeking Behaviors for Information on Covid-19 Vaccinations}}
+
+Knowing that Google trends data only encompasses a small portion of the
+information-seeking done by modern humans, it is important to
+investigate what leads individuals to search for a question online using
+a search engine (contributing to macro-level trends data) versus more
+traditional means of information gathering, such as network activation
+(asking someone in their social network for informational support). 
+Previous research has greatly failed to distinguish between the activation of
+information seeking behaviors online and offline. Using theories of social
+support and uses and gratifications theory, I investigate the factors associated
+with each vehicle type when on information seeking vehicle: personal connection,
+doctor, social networking site, online forum, and online search engine. I use
+original survey data of 948 Americans to investigate their experiences seeking out
+information about the Covid-19 vaccines.
+
+This paper aims to address two main questions:
+\begin{itemize}
+  \item How do computer-mediated or interpersonal information-seeking strategies vary
+across populations?
+  \item How does the information search vehicle utilized affect Covid-19 Vaccination uptake? 
+\end{itemize}
+
+In this article, I find little evidence that online search is more utilized than
+seeking social support from personal network connections or health professionals
+as I hypothesize based on uses and gratifications theory. I find evidence that
+the categorizations of vehicles queried in this survey are indeed conceptually
+different from each other and that the utilization of different vehicles varies
+by demography and information exposure points. Finally, I find that different
+exposure points and information search vehicles hold real world consequences
+through their associations with Covid-19 vaccination rates and intentions, as
+information from a doctor increased the Covid-19 vaccination uptake while
+receiving information from a Social Networking Site like Facebook or Twitter was
+associated with lower odds of vaccination.
+
+\hyperlink{paper-3}{\subsection{Article 3: Social Norms under Uncertain Times: A dynamic study of Stay-At-Home and Vaccination Rates During the Covid-19 Pandemic}}
+
+My final article takes a deeper dive into the formation of social norms
+governing health behaviors in cases of extreme uncertainty using the cases of
+both stay-at-home rates and vaccination rates as responses to public health recommendations to mitigate the Covid-19 pandemic. Using theories of associative diffusion and the integrated
+theoretical framework of norms, I test models of behavioral adaption to public health
+recommendations as well as patterns of complex social contagion using linear
+mixed effects models.
+
+These models show that complex contagion is a valid 
+framework for the social contagion of new norms during Covid-19. Importantly, I find
+important moderating effect of signal discordance, the contextual diversity of
+signals received by an ego. This paper shows that the contagion process is not
+fully understood without looking at the context of each exposure point within the
+range of exposures one experiences.
+
+\section{Contributions and Future Directions}
 \begin{center}
@@
 
-\section{Three Empirical Articles}
-
+\section{Conclusions}
 \begin{center}
-    \texttt{all three of these are UNDERGOING CHANGES}
+    \texttt{UNDERGOING CHANGES}
 \end{center}
 
-\begin{figure}
-{\centering \includegraphics[width=\linewidth]{figs/ch1/Dissertation Concept Map - Color.pdf}}
-\caption{Theoretical Framework for the Dissertation}\label{fig:concept-map}
-\end{figure}
-
-To make my intended contributions to the literatures on computational
-social science, sociological methodology, social norms, social networks,
-and diffusion, my dissertation will take the following format:
-
-% todo, go over fig:conceptmap
-
-\hyperlink{paper-1}{\subsection{Article 1: Digital Trace Data as Indicators of the Social World: Validating Google Trends for use in Scientific Research}}
-
-- How can we operationalize Google Search Trends as a valid indicator for uses in social science research?
-
-I will first investigate how Google Search Trends can be operationalized
-as cultural attitudes, disease prevalence and voting behaviors through
-comparing trends data to observed valid indicators of these cases.
-Specifically, I will test cultural indicators from the NORC General
-Social Survey, United States county-level suicide rates from National
-Center for Health Statistics, US case rates of Covid-19 from The New
-York Times, historical US Presidential Election results, and the
-American National Election Survey against selected Google Trends terms
-and analyze the data using correlation methods. The aim of this article
-is to assess the construct validity and will contribute to critical big
-data studies and sociological methodology.
-
-Computational social science and other disciplines are quick to 
-adopt new sources of digital trace data for use in academic research. 
-In this article, I examine the validity of Google Search Trends 
-as potential indicators of three different cases, namely attitudes, 
-disease prevalence and political preferences using eight %TODO double check number
-different validated data sources. I use Pearson and Repeated Measures Correlations 
-between the Google Trends and the validated indicators as well as multiple linear regression
-(for cross-sectional datasets) and random intercept hierarchical linear models
-(for longitudinal datasets) as additional tests of the data. 
-I fail to find correlation among any of the Google 
-Trends tested and their validated indicators. While some Google Trends 
-tested were significantly associated with the outcome in the regression models,
-effects tended to be small and the total model interpretability remained low,
-even when controlling for demographic variables. This article shows that there is no 
-external validity of Google Trends for these uses and social scientists
-will find no replacement for high quality survey data with Google Trends.
-
-\hyperlink{paper-2}{\subsection{Article 2: Information-Seeking Behaviors for Information on Covid-19 Vaccinations}}
-
-- How do computer-mediated or interpersonal information-seeking strategies vary
-across populations?
-- What factors lead people to perform health information search on the Covid-19 vaccine online versus among social network ties?
-
-The second article in my dissertation investigates the question "what
-are the behavioral processes that lead to macro-level outcomes" (in this
-case, Google Trends results) proposed by \citet{breigerScaling2015}. Knowing that
-Google trends data only encompasses a small portion of the
-information-seeking done by modern humans, it is important to
-investigate what leads individuals to search for a question online using
-a search engine (contributing to macro-level trends data) versus more
-traditional means of information gathering, such as network activation
-(asking someone in their social network for informational support). To
-investigate this, I use the case of receiving, requesting, and sharing
-information about the Covid-19 vaccine in a survey I received funding to
-conduct of 900 Adults in the United States.
-
-Previous research has greatly failed to distinguish between the activation of
-information seeking behaviors online and offline. Using theories of social
-support and uses and gratifications theory I investigate the factors associated
-with each vehicle type when on information seeking vehicle: personal connection,
-doctor, social networking site, online forum, and online search engine. Using
-novel survey data of % TODO  nrow(rain) Americans and their experience seeking out
-information about the Covid-19 vaccines, I find little evidence that online
-search is more utilized than seeking social support from personal network
-connections or health professionals. I find evidence that the vehicles queried
-in this survey are conceptually different and that the utilization of different
-vehicles varies by demography and information sources. Finally, I find that
-different fountains of information and information search vehicles hold real
-world consequences through their associations with Covid-19 vaccination rates
-and intentions, as information from a doctor increased the Covid-19 vaccination
-uptake while receiving information from a Social Networking Site like Facebook
-or Twitter was associated with lower odds of vaccination.
-
-\hyperlink{paper-3}{\subsection{Article 3: Social Norms under Uncertain Times: A dynamic study of Stay-At-Home and Vaccination Rates During the Covid-19 Pandemic}}
-
-- How are new health behavior norms regarding public health recommendations formed during the Covid-19 pandemic?  
-- How are patterns of information-search related to social norm stabilization during the Covid-19 pandemic?
-
-My final article takes a deeper dive into the formation of social norms
-governing health behaviors in cases of extreme uncertainty using the cases of
-both a) population mobility during early 2020 and b) vaccination rates during
-early 2021, both as responses to public health recommendations to mitigate the
-Covid-19 pandemic. Using theories of associative diffusion and the integrated
-theoretical framework of norms, I test how these health behaviors are outcomes
-of assortative signaling from networks and other sources, such as social
-isolation and connection between communities, religious and political
-conservativism, and attention to media sources, and online norms as measured by
-information-search behaviors. To investigate this, I conduct statistical
-modelling on a dataset I compiled from multiple sources, including Google,
-Facebook, and the Center for Disease Control and Prevention.
-
-This paper examines how social norms are formed under conditions of uncertainty
-using the case studies of stay-at-home and vaccination rates during the Covid-19
-pandemic.  I test fear-based models of behavioral adaption to public health
-recommendations as well as patterns of complex social contagion using linear
-mixed effects models. These models show that complex contagion is a valid
-framework for the social contagion of new norms during Covid-19. However, I find
-important moderating effect of signal discordance, the contextual diversity of
-signals received by an ego.
+what do these papers come TOGERTHER to tell us about information search?

### 2022-03-11 ch1.tex
finish contributions and future directions

@@
 \section{Contributions and Future Directions}
-\begin{center}
-    \texttt{UNDERGOING CHANGES}
-\end{center}
 
-% TODO make Broader Impact more relevant to actual findings
-% Original
-
-This research will first and foremost impact sociology. While the spread
-of information is investigated in the discipline (diffusion, mass
-communication, social influence), it is almost always from a structural
+% search as an agentic process
+This research will make contributions to multiple subfields and literatures. 
+First and foremost, these articles make a contribution to the sociological literature.
+The spread of information has long been investigated in the discipline (diffusion, mass
+communication, social influence). However, it is almost always researched from a structural
 perspective which disregards individual agency and choice in the
-acquisition of new information. This perspective aligns with Uses and
-Gratifications Theory, discussed in Section B: Background, and sees
-people as active agents in their search for information instead of just
+acquisition of new information. This dissertation adopts the second perspective,
+centering people as active agents in their search for information algined
+with their own preferences and gratifications instead of just
 passive receivers of information signals.
-
 Taking this agentic perspective is critical in the study of information
@@
 Goldberg and Stein (2018). How people search for information determines
-the information that they find; the information they uncover is filtered
+the information that they find. The information they uncover is filtered
 through cognitive biases and predispositions to how they interpret and
@@
 search and will change how people are organized and how people behave.
+\hyperlink{paper-2}{Article 2} importantly shows that 
+the vehicles uses to search for information have a significant impact on the choice to get vaccinated against Covid-19, a real-world consequence to the minutiae of individual information search.
 
-Additionally, this dissertation will investigate how social norms are
-formed in situations of uncertainty, an area that is less developed in
-sociology. While sociologists have studied social norms since the
-formation of the discipline, focus on the quick formation of social
-norms has implications for social behavioral outcomes, cultural change,
-organizational reactions to unrest and disasters, and many more areas
-that influence humanity.
-
-This dissertation will also have implications for the study of social
-networks and social support. Not only is this work situated in the
-sociological study of social support and social influence, but I utilize
-rarely-used-in-sociology sources of big data to better understand these
-mechanisms and test existing theories.
-
+% CSS & big data
 This dissertation also contributes to computational social science \&
@@
 Search Trends, which are relatively underutilized in the social sciences
-compared to health sciences and business. Not only does this project
-introduce Google Search Trends in new ways, but I perform explicit tests
-of how this data should be used in the social sciences, providing the
-groundwork for this exciting source of big data for future computational
-social scientists. Because my research takes a critical big data studies
-approach, I take into account the potential pitfalls with any source of
-big data (McFarland and McFarland 2015) and attempt to explicitly answer
-questions posed by this field, such as "what are the behavioral
-processes that lead to macro-level outcomes" proposed by \citet{breigerScaling2015}.
+compared to health sciences and business. Because \hyperlink{paper-1}{Article 1} 
+takes a critical big data studies approach, I take into account the potential
+pitfalls with any source of big data \citep{mcfarlandBigDataDanger2015} and explicitly
+test just how well Google Trends can be used as an indicator for different concepts. 
+Importantly, I find that there is no replacement for high quality survey data with Google Trends. 
+This is a large contribution to the field of critical big data studies but also provides
+the groundwork for future tests of external validity for big data for future computational
+social scientists.
 
+% micro behaviors to macro processes
+Bridging the contribution of search as an agentic process 
+and critical big data studies, this dissertation contributes to the question posed by 
+\citet{breigerScaling2015}, "what are the behavioral processes that 
+lead to macro-level outcomes?" With the exponentially growing size of digital-trace data
+that is available, it is important to not only uncover the external validity of 
+the data and correspondence to real world behaviors (see \hyperlink{paper-1}{Article 1})
+but also important to understand the social forces that leads to the big data. 
+One of the contributions of \hyperlink{paper-2}{Article 2} dives deep
+into this question, uncovering why some people choose to use web search engines over other
+information-vehicles. These papers are a first step in validating and establishing
+a deeper understanding of who the users are that contribute to macro-level aggregate trends.
+
+% social norms
+Additionally, this dissertation investigates how social norms are
+formed in situations of uncertainty, an area that is far less developed in
+sociology. While sociologists have studied social norms since the
+formation of the discipline, norms are most often studied under the lens
+of the emergence of norms and transmission of norms between groups, 
+deviance and social control, the interaction of norms as "mental representations of appropriate behavior" \citep{aarts2003silence}, and research categorizing different types of norms (e.g.
+descriptive versus injunctive, prescriptive versus proscriptive).
+The focus on the formation of new social norms during times of upheaval 
+has implications for interventions in social behavioral outcomes, 
+research on cultural change, and the spread of cognitive associations. 
+Moreover, \hyperlink{paper-3}{Article 3} focuses on how how conflicting
+behaviors become settled into cognitive associations, providing
+a relevant framework for research on unrest and disasters.
+
+% social networks / diffusion
+This dissertation will also have implications for the study of social
+networks and diffusion. \citet{centolaComplexContagionsWeakness2007}
+introduced a pivotal disruption to the diffusion literature when
+they developed complex contagion, the need for reinforcement through multiple
+exposures.  \hyperlink{paper-3}{Article 3} in this dissertation
+takes this disruption one step further to demonstrate that the concordance
+of the exposure affects the contagion process; in other words, being exposed to a 
+diversity of diffusants (discordance) can prevent the diffusant from spreading. 
+This critical finding provides many fields of exploration for scholars 
+to further the interdependence between different beliefs that are diffusing and
+under what contexts the discordance matters.
+
+% social epidemiology
 I also make important contributions to social epidemiology through this
 research. Each of the three papers in this dissertation use health case
-studies for questions of sociological interest. Because of this, I will
-contribute to social epidemiological questions on vaccine hesitancy,
+studies for questions of sociological interest. Because of this, I 
+contribute to the social epidemiological conversation on vaccine hesitancy,
 health communication, and diffusion of high-risk health behaviors. While
-all of these areas are important to social epidemiology, there are
+all of these areas are important to social epidemiology, there hold
 potential important health implications for these contributions on
-outside of the academy.
+outside of the academy, covered in the first paragraphs of this chapter.
 
-Outside of the academic research impacts that this dissertation makes,
-there are clear and timely social implications that will stem from this
-work. First, by uncovering how norms are created during norm
-uncertainty, I may be able to establish recommendations for
-interventions to be applied during disasters and other times of unrest
-to promote effective positive norms. Second, my research may have
-implications for how to optimize gratifications in search processes to
-promote healthy social relationships and improved online algorithm
-deployment.
-
-This work also relates to polarization and misinformation, two major
-social issues of our time. \citet{axelrodDisseminationCultureModel1997} shows that network structure,
-autocorrelation, and diffusion create local convergence of attitudes and
-culture which then leads to global polarization \citep{dellapostaWhyLiberalsDrink2015}. In investigating how local diffusion leads to social norms
-through information search, some of my findings may have strong
-implications and interventions for the prevention of global
-polarization. Relatedly, understanding where and how people search for
-information has implications for the information they are exposed to and
-the norms they develop. This project will attempt to relate to where
-misinformation is uncovered and how to intervene in its absorption.
+%  polarization misinformation
+% This work also relates to polarization and misinformation, two major
+% social issues of our time. \citet{axelrodDisseminationCultureModel1997} shows that network structure,
+% autocorrelation, and diffusion create local convergence of attitudes and
+% culture which then leads to global polarization \citep{dellapostaWhyLiberalsDrink2015}. In investigating how local diffusion leads to social norms
+% through information search, some of my findings may have strong
+% implications and interventions for the prevention of global
+% polarization. Relatedly, understanding where and how people search for
+% information has implications for the information they are exposed to and
+% the norms they develop. This project will attempt to relate to where
+% misinformation is uncovered and how to intervene in its absorption.
 

### 2022-03-12 ch1.tex
Finish copyediting ch 1

@@
 This dissertation focuses on how people search for information and how people
-rely on this information and to inform their health-behaviors and develop social
+rely on this information to inform their health-behaviors and develop social
 norms. Information permeates every facet of human society, from the hordes of
-data gathered through digital trace data or the passing gossip between friends.
+data gathered through digital-trace data or the passing gossip between friends.
 Human communication and human society are based on the circulation of
@@
 through information campaigns and consumed by an individual, called information
-push, or intentionally sought out by individuals, called information pull
-\citep{cybenkoFoundationsInformationPush1999}.
+push, or information can be intentionally sought out by individuals, 
+called information pull \citep{cybenkoFoundationsInformationPush1999}.
 
-We must understand the information individuals receive and seek out in order
-to develop a well functioning society. The information that
+We must understand the information individuals receive and seek out 
+to develop a well-functioning society. The information that
 one consumes consolidates to create the entire worldview of every individual,
@@
 
-The importance of reputable information and misinformation was clearly evident
+The importance of reputable information and misinformation was clear
 in the recent and ongoing Covid-19 pandemic. While the vaccines against the
@@
 This dissertation on information search and norm development provides clear and
-timely social implications for Arizona and the United States. This dissertation
+timely social implications for Arizona and the United States. I
 uncovers how norms are created during periods of norm uncertainty and builds the
@@
 
-In academia and policy, the main focus in research on information has always
+In academia and policy, the focus in research on information has always
 been the information that is sent to consumers, seeing people as passive
 receivers of information. My dissertation instead focuses on individuals as
-active agents in their search for information which helps me uncover the
-information individuals are exposed to. By looking at how individuals search, I
-aim to identify pain points and focus areas for future interventions in the
-misinformation process.
+active agents in their search for information. By looking at how individuals 
+search, I aim to identify pain points and focus areas for future interventions
+in the misinformation process.
 
@@
 \subsection{Information Flow}
-% TODO what happened before this point? 
-A critical turning point in the study of the flow information was put forth by
+Humans have long been interested in how to persuade the masses. With the 
+rise of democracy, the need of the powerful to persuade and appease the
+masses dramatically increased. And for a while, behavioral scientists 
+adopted really simplistic models of persuasion like the hypodermic needle model
+\citep{bineham1988historical}. This simplistic perception of human behavior 
+thought that the media basically injects messages into passive consumers
+who wholly accept the message and are affected by its contents \citep{lasswellpropaganda}.
+
+A critical turning point in the study of the flow of information was put forth by
 renowned Sociologist Paul Lazarsfeld \citeyearpar{lazarsfeldPeopleChoice1944}.
@@
 
-The spread of information has been thoroughly studied from the prospective
+The spread of information has been thoroughly studied from the perspective
 of social networks. Individuals engage with each other and their distributive
@@
 \subsection{Information Search}
-I only discussed the way that information is passively
+I have only discussed the way that information is passively
 consumed through push efforts by opinion leaders and social networks. However,
-sociological literature is really sparse on the opposite behavior: active
+sociological literature is sparse on the opposite behavior: active
 directed searching by individuals to obtain information.
@@
 information. The most common strategy is browsing, where people follow leads
-based on associations without planning ahead. Another strategy is analytical,
+based on associations without planning. Another strategy is analytical,
 which includes an explicit consideration of all facets of the question to guide
@@
 site, which consists of a profile, a network, and a stream or a feed
-\citep{boyd2007social, ellison2013sociality,},  often also involving a messaging
+\citep{boyd2007social, ellison2013sociality},  often also involving a messaging
 component  \citep{bayer_etal20}. Social networking sites are also interesting
@@
 of one-to-many communication, like resharing a television news story to your
-facebook feed and chatting with others about the content in the comments
+Facebook feed and chatting with others about the content in the comments
 section. But what do these classifications mean for the information-seeking
@@
 The constant connectedness facilitates communication, but also presents people
-with overchoice, or the difficulty in making a decision because simply every
+with overchoice, or the difficulty in deciding because simply every
 network connection you may want to activate is permanently connected and easy to
@@
 seeking information. \citet{smallSomeoneTalk2017} provides many examples of this
-when he demonstrates that more often than not, graduate students who needed
+when he demonstrates that often, graduate students who needed
 support simply asked "miscellaneous classmates encountered down the hall" (p.
@@
 The digital age did not only revolutionize communication. It also
-revoluitionized information search \citep{ramirez2002information}. Just as prior
+revolutionized information search \citep{ramirez2002information}. Just as prior
 to the digital age you could open an encyclopedia or peruse the library to find
@@
 an encyclopedia is far less common today, internet search engines have
-revolutionizes the speed and ease at which we can find information. Early web
+revolutionized the speed and ease at which we can find information. Early web
 search engines allowed information seekers to browse web directories and early
@@
 heavily on the wording of the queries. Google, the major web search engine used
-today, introduced the disrputive PageRank algorithm in the early 2000s, securing
+today, introduced the disruptive PageRank algorithm in the early 2000s, securing
 its place as the information hegemon of the 21st century
 \citep{brin1998anatomy}. Not only has computer-mediated information search
-revolutionized the ease of obtaining information, but it has also changed out
+revolutionized the ease of obtaining information, but it has also changed our
 brains. \citet{sparrow2011google} show that the digital age has led to worse
@@
 through algorithm or intentionally, the information the engine provides. For
-example, Google will not show results for various neo-Nazi websies in countries
+example, Google will not show results for various neo-Nazi websites in countries
 where holocaust denial is illegal, like France and Germany. This is illustrative
@@
 from sources like NetMarketShare, Statista, DuckDuckGo, Yahoo Finance, Google,
-and Pew Research they found that about about Around 93\% of all web traffic is
-via a search engine and that 78.39\% of all internet search use Google. Because
-computer-mediated information search is instantaneous and only requires mobile
-data or wifi, there is virtually no cost to seeking information on one of these
-mediums.
+and Pew Research they found that about Around 93\% of all web traffic is
+via a search engine and that 78.39\% of all internet searches performed are done
+so using Google. Because computer-mediated information search is instantaneous 
+and only requires mobile data or WiFi, there is virtually no cost to seeking
+information on one of these mediums.
 
@@
 coping with life stresses... that may be exchanged among members of a support
-network" \citeyearpar[p. 260]{brashersInformationSeekingAvoiding2002}. Both of
-these definitions provide important lenses for my question of how
+network" \citeyearpar[p. 260]{brashersInformationSeekingAvoiding2002}. Both
+definitions provide important lenses for my question of how
 computer-mediated or interpersonal information-seeking strategies vary. 
@@
 of who activates their social networks for information using social networking 
-sites like Facebook over activating these networks in face-to-face interactions.
+sites like Facebook instead of activating these networks in face-to-face
+interactions.
 
@@
 that all social media platforms must provide "tools that are easy to use and 
-functional to the demands of varying using demographics" (p. 473). They also
-explain how each digital architecture enables, contstrains and shapes how users
+functional to the demands of varying user demographics" (p. 473). They also
+explain how each digital architecture enables, constrains and shapes how users
 behave on their platform and in virtual space, leading to many different experiences 
@@
 \subsection{Social Norms}
-I showed the levels of uncertainty may direct how and when people
+I showed that the levels of uncertainty may direct how and when people
 search for information. However, in situations of rapidly changing norms,
@@
 Minimal research exists in quickly emerging
-norms in times of emergency, but shows that people likely to rely on the
-behavior of others' to set their own norms for behavior \citep{alvarez2018,
+norms in times of emergency but shows that people are likely to rely on the
+behavior of others to set their own norms for behavior \citep{alvarez2018,
 horneNormsIntegratedFramework2020}. This project will investigate how search
@@
 developed when individuals make inferences from their social worlds
-\citep{fryeCulturalMeaningsAggregation2017}.
-
-Importantly, people look to others performing an action and often
+\citep{fryeCulturalMeaningsAggregation2017}. Importantly,
+people look to others performing an action and often
 interpret that performance as an indication that an action is approved,
@@
 This relates back to the theory of relational norms, where individuals assume
-what their peers will approve and disapprove of. In order for these assumptions 
-to take place, they must have an understanding of which behaviors and beliefs
+what their peers will approve and disapprove of. For these assumptions 
+to take place, they must understand which behaviors and beliefs
 are possessed by whom in their network and how new associations may influence
@@
 individuals, institutions, and perform regimented searches to establish for
-themselves the behavior that is compatible with other cognitive biases they
-hold.
+themselves the behavior that is compatible with other cognitive associations
+and biases they hold.
 
@@
 This dissertation uses three articles to investigate different parts of
-the aforementioned theoretical framework (figure \ref{fig:concept-map}).
+the theoretical framework (figure \ref{fig:concept-map}).
 The dissertation is divided into three parts, with Article 1 focusing 
@@
 Google Trends for these uses and social scientists will find no replacement for
-high quality survey data with Google Trends.
+high quality survey data with Google Trends. Instead, we must only use 
+Google Trends to demonstrate interest or attention.
 
@@
 investigate what leads individuals to search for a question online using
-a search engine (contributing to macro-level trends data) versus more
+a search engine versus more
 traditional means of information gathering, such as network activation
@@
 support and uses and gratifications theory, I investigate the factors associated
-with each vehicle type when on information seeking vehicle: personal connection,
+with each information seeking vehicle: personal connection,
 doctor, social networking site, online forum, and online search engine. I use
@@
 through their associations with Covid-19 vaccination rates and intentions, as
-information from a doctor increased the Covid-19 vaccination uptake while
+information from a doctor increases the Covid-19 vaccination uptake while
 receiving information from a Social Networking Site like Facebook or Twitter was
@@
 framework for the social contagion of new norms during Covid-19. Importantly, I find
-important moderating effect of signal discordance, the contextual diversity of
+a novel moderating effect of signal discordance, the contextual diversity of
 signals received by an ego. This paper shows that the contagion process is not
@@
 This research will make contributions to multiple subfields and literatures. 
-First and foremost, these articles make a contribution to the sociological literature.
+First and foremost, these articles contribute to the sociological literature.
 The spread of information has long been investigated in the discipline (diffusion, mass
@@
 acquisition of new information. This dissertation adopts the second perspective,
-centering people as active agents in their search for information algined
+centering people as active agents in their search for information aligned
 with their own preferences and gratifications instead of just
@@
 \hyperlink{paper-2}{Article 2} importantly shows that 
-the vehicles uses to search for information have a significant impact on the choice to get vaccinated against Covid-19, a real-world consequence to the minutiae of individual information search.
+the vehicles used to search for information have a significant impact on the choice to get vaccinated against Covid-19, a real-world consequence to the minutiae of individual information search.
 
@@
 compared to health sciences and business. Because \hyperlink{paper-1}{Article 1} 
-takes a critical big data studies approach, I take into account the potential
-pitfalls with any source of big data \citep{mcfarlandBigDataDanger2015} and explicitly
+takes a critical big data studies approach, I consider the potential
+pitfalls that any source of big data face \citep{mcfarlandBigDataDanger2015} and explicitly
 test just how well Google Trends can be used as an indicator for different concepts. 
@@
 of the emergence of norms and transmission of norms between groups, 
-deviance and social control, the interaction of norms as "mental representations of appropriate behavior" \citep{aarts2003silence}, and research categorizing different types of norms (e.g.
-descriptive versus injunctive, prescriptive versus proscriptive).
+deviance and social control, the interaction of norms as "mental 
+representations of appropriate behavior" \citep{aarts2003silence}, 
+and research categorizing different types of norms (e.g., descriptive 
+versus injunctive, prescriptive versus proscriptive).  
 The focus on the formation of new social norms during times of upheaval 
@@
 research on cultural change, and the spread of cognitive associations. 
-Moreover, \hyperlink{paper-3}{Article 3} focuses on how how conflicting
+Moreover, \hyperlink{paper-3}{Article 3} focuses on how conflicting
 behaviors become settled into cognitive associations, providing
@@
 diversity of diffusants (discordance) can prevent the diffusant from spreading. 
-This critical finding provides many fields of exploration for scholars 
-to further the interdependence between different beliefs that are diffusing and
-under what contexts the discordance matters.
+This critical finding provides many new areas of exploration for scholars 
+to further investigate the interdependence between different beliefs that
+are diffusing and under what contexts the discordance matters.
 
@@
 health communication, and diffusion of high-risk health behaviors. While
-all of these areas are important to social epidemiology, there hold
+all these areas are important to social epidemiology, there hold
 potential important health implications for these contributions on
@@
 % misinformation is uncovered and how to intervene in its absorption.
-
-\section{Conclusions}
-\begin{center}
-    \texttt{UNDERGOING CHANGES}
-\end{center}
-
-what do these papers come TOGERTHER to tell us about information search?

### 2022-03-15 abstract.tex
finish paper 1
Finish paper 2 revisions

@@
-The online world presents new avenues for the spread of information in addition to the traditional word of mouth effects of social networks.
-It also provides new big data sources for social science research because they are bigger, cheaper, and already available.
-In my dissertation, I combine these two areas of inquiry by examining the differences between the social network contagion of ideas (push) and information seeking (pull) and their relation to the creation of social norms.
-My first article tests the construct validity of the Google Search Trends source of big data as an indicator of three different cases, namely cultural attitudes, disease prevalence and voting behavior, using pairwise correlations .
-My second article establishes how individuals perform information search, whether through interpersonal networks or online, using my original survey data of 900 Adults in the United States.
-My final article builds on these by investigating how new health-behavior social norms form in the face of assortative signals through associative cognitive diffusion.
-This research will be a contribution to methodology of computational social science as it tests the reliability of a big data source, questions what behavioral processes lead to macro-level outcomes recorded in big data sources, and uses novel combinations of data sources and methodology to investigate questions of sociological interest.
-This research will also contribute to the sociology study of information technologies in the digital age, medical sociology, and social networks.
+% at least 150 words, generally no more than 500 words
+
+This dissertation focuses on how people search for information and how people
+rely on this information to inform their health-behaviors and develop social
+norms. Information can be shared and promoted by others
+through information campaigns and consumed by an individual, called information
+push, or information can be intentionally sought out by individuals, 
+called information pull, and their relation to the creation of social norms.
+
+The first article tests the construct validity of the Google Search Trends source,
+an online indicator of computer-mediated information search. I attempt to
+validate Google Search Trends for use as indicators of attitudes, disease prevalence
+and political preferences using eight different validated data sources. %TODO double check number
+I fail to find correlation among any of the Google Trends tested and their
+validated indicators and show that there is no external validity of
+Google Trends for these uses and social scientists will find no replacement for
+high quality survey data with Google Trends. Instead, we must only use 
+Google Trends to demonstrate interest or attention.
+
+Knowing that Google trends data only encompasses a small portion of the
+information-seeking done by modern humans, my second article 
+is motivated by the research question: How do computer-mediated or interpersonal 
+information-seeking strategies vary across populations? Using original survey data
+of 948 Americans, I investigate their experiences seeking out information about 
+the Covid-19 vaccines among the following information seeking vehicles: 
+personal connection, doctor, social networking site, online forum, and online search engine. 
+I find little evidence that online search is more utilized than
+seeking social support from personal network connections or health professionals
+as I hypothesize based on uses and gratifications theory. I find that different
+exposure points and information search vehicles hold real world consequences
+through their associations with Covid-19 vaccination rates and intentions, as
+information from a doctor increases the Covid-19 vaccination uptake while
+receiving information from a Social Networking Site like Facebook or Twitter was
+associated with lower odds of vaccination.
+
+My final article takes a deeper dive into the formation of social norms
+governing health behaviors in cases of extreme uncertainty using the cases of
+both stay-at-home rates and vaccination rates as responses to public health recommendations to mitigate the Covid-19 pandemic. Using theories of associative diffusion and the integrated
+theoretical framework of norms, I test models of behavioral adaption to public health
+recommendations as well as patterns of complex social contagion using linear
+mixed effects models. These models show that complex contagion is a valid 
+framework for the social contagion of new norms during Covid-19. Importantly, I find
+a novel moderating effect of signal discordance, the contextual diversity of
+signals received by an ego. This paper shows that the contagion process is not
+fully understood without looking at the context of each exposure point within the
+range of exposures one experiences.
+
+The introductory chapter provides a summary of the research and an explanation of how this
+research contributes to the sociology, social science, and society.

### 2022-03-15 ch1.tex
Finish paper 2 revisions

@@
 The importance of reputable information and misinformation was clear
-in the recent and ongoing Covid-19 pandemic. While the vaccines against the
-Covid-19 virus prevent severe illness, hospitalization, and death, only 60\% of
+in the recent and ongoing COVID-19 pandemic. While the vaccines against the
+COVID-19 virus prevent severe illness, hospitalization, and death, only 60\% of
 Arizonans over 12 years old are fully vaccinated against the virus. We know that
@@
 that are emerging in a society under upheaval, like the health behaviors that
-emerged during the Covid-19 pandemic, emerged with new subjective meanings and
+emerged during the COVID-19 pandemic, emerged with new subjective meanings and
 cognitive associations that held consequences for the individuals who adopted
@@
 
-\hyperlink{paper-2}{\subsection{Article 2: Information-Seeking Behaviors for Information on Covid-19 Vaccinations}}
+\hyperlink{paper-2}{\subsection{Article 2: Information-Seeking Behaviors for Information on COVID-19 Vaccinations}}
 
@@
 original survey data of 948 Americans to investigate their experiences seeking out
-information about the Covid-19 vaccines.
+information about the COVID-19 vaccines.
 
@@
 across populations?
-  \item How does the information search vehicle utilized affect Covid-19 Vaccination uptake? 
+  \item How does the information search vehicle utilized affect COVID-19 Vaccination uptake? 
 \end{itemize}
@@
 exposure points and information search vehicles hold real world consequences
-through their associations with Covid-19 vaccination rates and intentions, as
-information from a doctor increases the Covid-19 vaccination uptake while
+through their associations with COVID-19 vaccination rates and intentions, as
+information from a doctor increases the COVID-19 vaccination uptake while
 receiving information from a Social Networking Site like Facebook or Twitter was
@@
 
-\hyperlink{paper-3}{\subsection{Article 3: Social Norms under Uncertain Times: A dynamic study of Stay-At-Home and Vaccination Rates During the Covid-19 Pandemic}}
+\hyperlink{paper-3}{\subsection{Article 3: Social Norms under Uncertain Times: A dynamic study of Stay-At-Home and Vaccination Rates During the COVID-19 Pandemic}}
 
@@
 governing health behaviors in cases of extreme uncertainty using the cases of
-both stay-at-home rates and vaccination rates as responses to public health recommendations to mitigate the Covid-19 pandemic. Using theories of associative diffusion and the integrated
+both stay-at-home rates and vaccination rates as responses to public health recommendations to mitigate the COVID-19 pandemic. Using theories of associative diffusion and the integrated
 theoretical framework of norms, I test models of behavioral adaption to public health
@@
 These models show that complex contagion is a valid 
-framework for the social contagion of new norms during Covid-19. Importantly, I find
+framework for the social contagion of new norms during COVID-19. Importantly, I find
 a novel moderating effect of signal discordance, the contextual diversity of
@@
 \hyperlink{paper-2}{Article 2} importantly shows that 
-the vehicles used to search for information have a significant impact on the choice to get vaccinated against Covid-19, a real-world consequence to the minutiae of individual information search.
+the vehicles used to search for information have a significant impact on the choice to get vaccinated against COVID-19, a real-world consequence to the minutiae of individual information search.
 

### 2022-03-15 paper1.tex
3 article summaries
Finish paper 2 revisions

@@
 \chapter{Digital Trace Data as Indicators of the Social World: Validating Google Trends for use in Scientific Research}\label{paper-1}}
+
+% TODO: should I add in some figures to outline these relationships?
 
@@
 health indicators from the CDC \citeyearpar{suic_data}, 
-US cases rates of Covid-19 from The New York Times \citeyearpar{covid_data},  
+US cases rates of COVID-19 from The New York Times \citeyearpar{covid_data},  
 and political indicators from the historical US Presidential Election results \citeyearpar{pres_data}, 
@@
 Medical Internet Research. While much of this research has focused on
-the Covid-19 pandemic \citep{jimenez_etal20, jimenezCOVID19SymptomGoogle2020, limEstimatingInformationSeekingBehaviour2020, mavraganiCOVID19PredictabilityUnited2020, nguyenGoogleTrendsAnalysis2020, todorovaInternetBasedData2021, mingUnderstandingHealthCommunication2021},
+the COVID-19 pandemic \citep{jimenez_etal20, jimenezCOVID19SymptomGoogle2020, limEstimatingInformationSeekingBehaviour2020, mavraganiCOVID19PredictabilityUnited2020, nguyenGoogleTrendsAnalysis2020, todorovaInternetBasedData2021, mingUnderstandingHealthCommunication2021},
 other research has investigated Google Trends as indicators of wellbeing
@@
 the wide usage of Google Search Trends. For instance, \citet{asseoTrackingCOVID19Using2020} 
-concludes in their research on Covid-19 case rates and Google searches that the correlation 
+concludes in their research on COVID-19 case rates and Google searches that the correlation 
 is often spurious and due to confounding. They even explain that "searches would
@@
 
-\citet{rovetta21} also investigates the reliability of Covid-19 searches to infer 
+\citet{rovetta21} also investigates the reliability of COVID-19 searches to infer 
 the quality of the data; the author finds that there are various issues with missing data in 
@@
 
-I also use U.S. Covid-19 rates to validate health and disease related topics. I
-retrieve U.S. county-level Covid-19 rates from \citet{covid_data}, who compile this
+I also use U.S. COVID-19 rates to validate health and disease related topics. I
+retrieve U.S. county-level COVID-19 rates from \citet{covid_data}, who compile this
 data based on reports from state and local health agencies. It is widely
@@
 uses in the measurements of health indicators. The first indicator I assess is
-Covid-19 case rates from 2020 through 2021. The Pearson correlation results
+COVID-19 case rates from 2020 through 2021. The Pearson correlation results
 indicate negligible to weak relationships between the search terms and the
@@
 correlations, reveals similarly weak results with a maximum correlation of 0.32
-between 'smell loss' and rates of Covid-19. To further investigate the relationship, I
+between 'smell loss' and rates of COVID-19. To further investigate the relationship, I
 include the three trends in random intercept hierarchical linear models. Model 1
 of table \ref{tab:covid_analysis} indicates that the trends themselves are able
-to explain about 20\% of the variation in Covid-19 rates ($r^2$ = 0.201). Few
-of the demographic variables influence Covid-19 rates in models 2 or 3,
+to explain about 20\% of the variation in COVID-19 rates ($r^2$ = 0.201). Few
+of the demographic variables influence COVID-19 rates in models 2 or 3,
 though there is some suppression for median income, unemployment rates,
 and population density. Model 3 has an $r^2$ of 0.200. I conclude that the
-Google Trends are slightly related to Covid-19 rates, but that this relationship
+Google Trends are slightly related to COVID-19 rates, but that this relationship
 is weak, and we should not attempt to use Google Trends as an indicator of actual

### 2022-03-15 paper2.tex
haven't commited in a while.
Finish paper 2 revisions

@@
 \hypertarget{paper-2}{%
-\chapter{Information-Seeking Behaviors for Information on Covid-19 Vaccinations}\label{paper-2}}
+\chapter{Information-Seeking Behaviors for Information on COVID-19 Vaccinations}\label{paper-2}}
 
@@
 Previous research has greatly failed to distinguish between the activation of
-information seeking behaviors online and offline. Using theories of social
-support and uses and gratifications theory I investigate the factors associated
-with each vehicle type when on information seeking vehicle: personal connection,
+information-seeking behaviors online and offline. Using theories of 1) social
+support and 2) uses and gratifications theory I investigate the factors associated
+with each vehicle type when on information-seeking vehicle: personal connection,
 doctor, social networking site, online forum, and online search engine. Using
 novel survey data of 948 Americans and their experience seeking out
-information about the Covid-19 vaccines, I find little evidence that online
+information about the COVID-19 vaccines, I find little evidence that online
 search is more utilized than seeking social support from personal network
@@
 vehicles varies by demography and information sources. Finally, I find that
-different fountains of information and information search vehicles hold real
-world consequences through their associations with Covid-19 vaccination rates
-and intentions, as information from a doctor increased the Covid-19 vaccination
+different sources of information exposure and information search vehicles hold real
+world consequences through their associations with COVID-19 vaccination rates
+and intentions, as information from a doctor increased the COVID-19 vaccination
 uptake while receiving information from a Social Networking Site like Facebook
@@
 
-\textbf{Keywords}: Information-Seeking Behavior, Covid-19, Vaccine Hesitancy, Social Networks, Social Support, Information \& Communication Technologies
+\textbf{Keywords}: Information-Seeking Behavior, COVID-19, Vaccine Hesitancy, Social Networks, Social Support, Information \& Communication Technologies
 
@@
 harmless \citep{douglas21} some discredited theories such as 'vaccines cause autism'
-have major ramifications for both the individual and the social world that
-surrounds them. For example, a newfound public resistance to vaccination
+have major ramifications for both the individual and public health.
+For example, a newfound public resistance to vaccination
 against Measles by so-called 'anti-vaxxers' caused a 17\% increase in rates
@@
 \citep{johnsonOnlineCompetitionPro2020, broniatowski_etal20}.
-% cite something else here
+% TODO cite something else here
 
@@
 \citep{mertonManifestLatentFunctions1968, katzPersonalInfluencePart1955, lazarsfeldPeopleChoice1944},
-rather than on
-“the receiver as an active information seeker and processor." \citep{johnsonComprehensiveModelCancerRelated1993},
-though there are always exceptions \citep{eysenbach09}
+rather than on “the receiver as an active information seeker and processor." 
+\citep{johnsonComprehensiveModelCancerRelated1993}
+\citep[for an exception, see]{eysenbach09}.
 
-I use the case of information around Covid-19 vaccinations to explore the
+I use the case of information around COVID-19 vaccinations to explore the
 variation of usage of information search vehicles. In doing so, I seek to answer
 how computer-mediated or interpersonal information-seeking strategies vary
-across populations in their search for information about Covid-19 vaccinations
-and investigate how these strategies affect vaccination uptake.
+across populations in their search for information about COVID-19 vaccinations
+and investigate how these strategies affect vaccination uptake. Specifically, this article 
+answers two research questions: (1) How do computer-mediated or interpersonal information-seeking
+strategies vary across populations? (2) How does the information search vehicle utilized 
+affect COVID-19 Vaccination uptake?
 
-Before addressing my central research questions, I offer an overview of the
+Before addressing the results to these research questions, I offer an overview of the
 current state of social science literature in regards to information-seeking
-strategies before providing a description of the research methodology and
-analytic sample. I discuss the implications of these findings for the
+strategies and providing a description of the research methodology and
+analytic sample. I then discuss the implications of these findings for the
 sociological understanding of information search and vaccination uptake.
@@
 discussed in the sociological literature. Pejtersen \citet{pejtersenDesignComputeraidedUsersystem1984}, a scholar
-of library and information science, theorized that there are 5 strategies for
-searching for information. The most common strategy is browsing, where people
+of library and information science, theorized that there are five strategies for
+searching for information: browsing, analytical, empirical, known site, and similarity. 
+The most common strategy is browsing, where people
 follow leads based on associations without premeditation. Another strategy is
@@
 method is to find information based on another similar question that already has
-an answer. These 5 strategies vary in their demands for prior knowledge,
+an answer. These five strategies vary in their demands for prior knowledge,
 cognitive processing, memory, and time spent. While this theory is aimed at
@@
 
-One way to find information is to activate network ties to find out information
+One way to find information is to activate network ties to secure information
 through a form of social support. Social support, while previously used
-interchangeably with the term social networks and social integration
+interchangeably with the terms social networks and social integration
 \citep{houseStructuresProcessesSocial1988}, are the emotional, informational, and
@@
 understanding, and coping with problematic events and include education, advice,
-or referral to another source of support” \citep{winemiller_etal93}[p. 640].
+or referral to another source of support” \citep[][p. 640]{winemiller_etal93}.
 Brashers, a health communications researcher, defines informational support
@@
 coping with life stresses… that may be exchanged among members of a support
-network” \citet{brashersInformationSeekingAvoiding2002}[p. 260].These definitions
+network” \citet[][p. 260]{brashersInformationSeekingAvoiding2002}.These definitions
 help to differentiate between seeking information through social ties or through
@@
 Social support has long been theorized to stem from core discussion networks and
-much of the historical social support surveys only looked at these core
+much of the historical social support surveys only examined these core
 networks. The underlying assumption is that individuals reach out to a handful
@@
 context, namely via computer-mediated information search tools such as the
-process of “Googling”. As the online environment began penetrating all facets of
+process of “Googling”, or the utilization of internet search engines. 
+As the online environment began penetrating all facets of
 modern human life, it makes sense that performing online search has become one
-of the most convenient vehicles for information search. While Small
-\citet{smallSomeoneTalk2017} focuses on how support can depend on a network tie
-simply "happened to be there", online search is theoretically the most
-frictionless and costless mode of support. No social capital or relationship is
-necessary when choosing to utilize a search engine.
+of the most convenient vehicles for information search. Small
+\citet{smallSomeoneTalk2017} showed that Graduate students often
+confided in a "miscellaneous classmates encountered down the hall" (p.
+176) instead of established and trusted confidants because they
+simply were there at the right time. I theorize that online search engines
+may be the most frictionless and costless mode of support. 
+No social capital or relationship is necessary when choosing to utilize a search engine.
 
@@
 subreddits or Facebook groups, and posting a status update online via Facebook
-or Twitter. While the first two are largely anonymous and don't require a
+or Twitter. While the first two are largely anonymous and do not require a
 personal network, the third is a unique hybrid between personal network
@@
 borrow uses and gratifications theory (UGT) from studies of mass communication
-\citep{blumlerUsesMassCommunications1974, tanMassCommunicationTheories1985}
-. UGT
-posits that users are not passive consumers of media and that people have an
+\citep{blumlerUsesMassCommunications1974, tanMassCommunicationTheories1985}. 
+UGT posits that users are not passive consumers of media and that people have an
 active role in choosing different sources of media based on their satisfaction
-of specific needs on an individual basis. UGT is based on Maslow’s  \citeyear{maslowTheoryHumanMotivation1943} hierarchy of needs and is compatible with
+of specific needs on an individual basis. UGT is based on Maslow’s  
+\citeyear{maslowTheoryHumanMotivation1943} hierarchy of needs and is compatible with
 Lazarsfeld and Katz’s theory of two-step flow \cite{katzPersonalInfluencePart1955}
@@
 Modern-day theorists have extended UGT theory and classified the uses and
-gratifications of the internet and of social media. \citet{staffordDeterminingUsesGratifications2004} theorize that the internet
+gratifications of the internet and of social media. 
+\citet{staffordDeterminingUsesGratifications2004} theorize that the internet
 provides gratification through useful content that meets expectations,
 gratification from purposeful navigating or random browsing as a process, and
-social gratification from forming and deepening social ties. \citet{leungGenerationalDifferencesContent2013} theorizes that social media is
+social gratification from forming and deepening social ties. 
+\citet{leungGenerationalDifferencesContent2013} theorizes that social media is
 gratifying for users because it allows for venting of negative feelings,
@@
 fulfills cognitive needs.
+
+\begin{hyp}[H\ref{hyp:online-vs-network}] \label{hyp:online-vs-network}
+The proportion of survey respondents who seek information
+using an online search engine will be significantly higher than those who
+need to activate network resources, like asking a friend.
+\end{hyp}
 
@@
 groups that validate their worldview \citep{bogersHowSocialAre2014}. Finally, UGT and
-Brasher's definition of social support \citeyearpar{brashersInformationSeekingAvoiding2002} help us to theorize that the
-psychosocial needs like identity management or relational maintenance of an individual may influence their chosen information search vehicle: when the informational need is related to
-forming and deepening social ties search is likely to be done from network ties.
+Brasher's definition of social support \citeyearpar{brashersInformationSeekingAvoiding2002}
+help us to theorize that the psychosocial needs like identity management or relational
+maintenance of an individual may influence their chosen information search vehicle: 
+when the informational need is related to forming and deepening social ties search 
+is likely to be done from network ties.
+
+\begin{hyp}[H\ref{hyp:drgooglefriend}] \label{hyp:drgooglefriend}
+Seeking information from experts, search engines, and other people
+will be the most common modes of information search. 
+\end{hyp}
 
@@
 The data used for this research project are based on original survey data
-sampled between December 03, 2021 through
-December 12, 2021. This survey was hosted on Qualtrics and
-participants were paid and recruited using Amazon Turk (MTurk). The total valid
+collected between December 03, 2021 through December 12, 2021.
+This survey was hosted on Qualtrics and participants were paid and 
+recruited using Amazon Turk (MTurk). Potential MTurkers were invited
+to participate if they were located in the United States, had a task
+rate approval of over 95 percent, had completed 50 tasks, and had not 
+completed this survey in previous sessions. The total valid 
 survey responses (\emph{n} = 948) were selected from a total of 1,066
@@
 responses), poor quality typed responses (e.g., social network alters
-consistently named random nouns), or taking the survey more than once. The same
-is slighted gender unbalanced, slightly skewing towards a male sample. For the
-respondents who provided their zip code (p = 0.98), the sample is quite balanced with a slight skew towards MTurkers in the South (p = 0.41).
+consistently named random nouns), or taking the survey more than once. The sample
+is slightly gender unbalanced, skewing towards male respondents. For the
+respondents who provided their zip code (p = 0.98), the sample is quite balanced with
+a slight skew towards MTurkers in the South (p = 0.41).
 
@@
 The shortest valid survey took 3.75 minutes and the longest took 111.08 minutes.
-Participants were paid \$6.00 for their time after Amazon administrative fees, funded by a Grant awarded to Kelsey E.
-Gonzalez and Nicolas Legewie by the Summer Institute in Computational Social
-Science and the Russell Sage Foundation.
-The main portion of this survey replicates the book, Someone to Talk To \citep{smallSomeoneTalk2017} by expanding on Small's finding that people draw on much broader sources than ``important people'' for support by segregating weak-tie social support into instrumental, emotional, and informational support \citep[see][]{houseStructuresProcessesSocial1988}.
-The latter
-part of the survey focuses on resource activation for the specific case-study of
-information during the Covid-19 pandemic analyzed in this paper.
+Participants received \$6.00 in compensation for their participation in the survey
+\footnote{All funding for this survey was provided by a Grant awarded to Kelsey E. 
+Gonzalez and Nicolas Legewie by the Summer Institute in Computational Social Science
+and the Russell Sage Foundation.}. The survey consisted of two main parts. The
+first portion of the survey is a replication of they survey conducted by 
+\citet{smallSomeoneTalk2017}. In this section, we expand Small's research on 
+support activation by segregating weak-tie social support into instrumental, 
+emotional, and informational categories \citep[see][]{houseStructuresProcessesSocial1988}.
+The second part of the survey focuses on network resource activation and 
+information-seeking behaviors of individuals regarding COVID-19 vaccinations
+for this paper.
 
-\input{tables/paper2/table-1-desc}
+\input{tables/paper2/table-1-ind}
 
@@
 variable is a dichotomous indicator of whether someone intentionally sought out
-information about Covid-19 vaccinations. The survey asked, ``And how about you
-yourself intentionally looking for information about a Covid-19 vaccine? Such
+information about COVID-19 vaccinations. The survey asked, ``And how about you
+yourself intentionally looking for information about a COVID-19 vaccine? Such
 information can include things such as advice, clarification, facts, and
 experiences.'' About 78\% (\(\widehat{p}\))
-of respondents had intentionally sought out information about Covid-19
+of respondents had intentionally sought out information about COVID-19
 vaccinations (95\% Confidence Interval = \{76\%, 81\%\}).
@@
 Further dependent variables segment the above question into multiple options;
-``How did you look for information about the Covid-19 vaccine?'' Respondents were
+``How did you look for information about the COVID-19 vaccine?'' Respondents were
 posed with 5 responses and `other,' of which they could select multiple. The
-largest proportion, 44\%, asked their `doctor or another health professional' (95\% Confidence Interval = \{41\%, 47\%\}). About 42\% said they asked, `a person
-like friend, neighbor, or family member that {[}they{]} know' (95\% Confidence
-Interval = \{39\%, 45\%\}). An additional 41\% searched `for {[}their{]} question
-using an online search engine such as Google or Bing' (95\% Confidence Interval
-= \{38\%, 45\%\}). About a quarter of the sample, 27\%, `posted queries in an
-online discussion group, listserve, or other online forum like a Facebook Group
-or Subreddit' (95\% Confidence Interval = \{24\%, 30\%\}).
-And finally, 18\% of the sample `posted queries on a social networking site such as Facebook timeline, Twitter status update, or LinkedIn' (95\% Confidence Interval = \{16\%, 21\%\}).
+largest proportion, 44\%, asked their `doctor or another health professional'.
+About 42\% said they asked, `a person like friend, neighbor, or family member 
+that [they] know'. An additional 41\% searched `for [their] question
+using an online search engine such as Google or Bing'. About a quarter of the
+sample, 27\%, `posted queries in an online discussion group, listserv, or 
+other online forum like a Facebook Group or Subreddit'. And finally, 18\% of 
+the sample `posted queries on a social networking site such as Facebook timeline, 
+Twitter status update, or LinkedIn'.
 Much of the question wording and the specific categories of search were inspired
 by ICPSR project 37220 \citep{scanlon19}.
-
-\input{tables/paper2/table-2-desc}
 
@@
 
+\input{tables/paper2/table-2-dep}
+
 Another Dependent variable for this analysis is a dichotomous variable
-indicating whether the respondent has received or plans to receive a vaccination against Covid-19. For this survey, the number of doses or timeline of receipt were less
+indicating whether the respondent has received or plans to receive a vaccination against
+COVID-19. For this survey, the number of doses or timeline of receipt were less
 relevant to the research question. This variable instead focuses on intent or
@@
 of two survey items. The first item is actual vaccination status, obtained through
-the question `Did you receive a Covid-19 vaccine?'
+the question `Did you receive a COVID-19 vaccine?'
 84\% of the sample said that
 they had indeed received a vaccination (95\% Confidence Interval = \{82\%, 87\%\}).
-As the national vaccination rate is closer to 75\% \citep{cdc20}, this indicates some bias in our sample that must be
+As the national vaccination rate is closer to 75\% \citep{cdc20}, this indicates 
+some bias in our sample that must be
 acknowledged: either MTurkers are more likely to be vaccinated that the normal
@@
 contributes to `Vaccination Outlook' was only given to those who had not
-responded `yes' to the to their vaccination status. These respondents were asked `Do you
-plan to receive a vaccine for the prevention of the Covid-19 virus?' Of those
+responded `yes' to the to their vaccination status. These respondents were asked 
+`Do you plan to receive a vaccine for the prevention of the COVID-19 virus?' Of those
 who were asked this question (n = 147), 9\% said they were `definitely yes' getting the vaccine;
-9\% said they were `probably yes' going to receive vaccine.
-The rest of the sample was more unsure: 15\% said they `Might or might not,' 26\% said `Probably not,' and finally 41\% said they would `definitely not' receive the vaccine.
-The variable `Vaccination Outlook' indicates that either the respondent received a Covid-19 vaccine or
+9\% said they were `probably yes' going to receive vaccine. The rest of the sample was
+more unsure: 15\% said they `Might or might not,' 26\% said `Probably not,' and finally
+41\% said they would `definitely not' receive the vaccine. The variable `Vaccination 
+Outlook' indicates that either the respondent received a COVID-19 vaccine or
 either probably or definitely will in the future.
@@
 `In the past 12 months, without searching for it, did you receive information
-about the Covid-19 vaccine from \ldots{} (check all sources you received information
+about the COVID-19 vaccine from \ldots{} (check all sources you received information
 from).' This differs from the `How did you look for information' question above
 because this is based on passive reception of information. The largest proportion
-of respondents had received information from a person like friend, neighbor, or
-family member that {[}they{]} know (\(\widehat{p}\) = 67\%
-). Respondents also commonly received information from a television news channel
+of respondents had received information from "a person like friend, neighbor, or
+family member that [they] know" (\(\widehat{p}\) = 67\%). Respondents
+also commonly received information from a television news channel
 or a newspaper, about 65\% of the sample.
 47\% of the sample had received information from
-their doctor or other health professional while 40\%
+their doctor or other health professional, while 40\%
 received information from a social networking site such as Facebook timeline,
 Twitter status update, or LinkedIn. Finally, the lowest proportion of the sample
-had received information from an online discussion group, listserve, or other
+had received information from an online discussion group, listserv, or other
 online forum like a Facebook group or subreddit
@@
 
-We also asked various demographic questions to understand our sample. The
-average age of our sample was 37.76.
-Our sample was 44\% female, and 55\% male.
-The sample is diverse racially though some ethnic groups are underrepresented compared to national averages.
-Race was evaluated using the
+We also asked various demographic questions to describe our sample. The
+average age of our sample was 37.76. 44\% of our sample self-identified as female, 
+while 55\% self-identified as male. The sample is diverse racially though some ethnic
+groups are underrepresented compared to national averages. Race was evaluated using the
 question, `What is your race? If you are ``mixed race,'' select all that apply.'
@@
 
-My analytic strategy proceeds in four steps. In Tables \ref{tab:table-1-desc}
-\& \ref{tab:table-2-desc}, I present descriptive statistics for all study
+My analytic strategy proceeds in four steps. In Tables \ref{tab:table-1-ind}
+\& \ref{tab:table-2-dep}, I present descriptive statistics for all study
 variables, including variable ranges, means, and standard deviations. For this
 paper, I rely heavily on logistic regression, modeled in \texttt{r}; specifically, I
-fit a series of Binomial Generalized Linear Models \citep{venables2002a}.
-In Table \ref{tab:table-model-1}\footnote{All tables in this paper were created with the modelsummary package in \texttt{r} \citep{modelsummary}}
-, I fit a logistic regression model predicting
-whether someone sought information about Covid-19 using their sources of
+fit a series of binomial generalized linear models with a logit link \citep{venables2002a},
+otherwise known as logistic regression model \citep{hothorn2006handbook}.
+This approach is appropriate because the data
+are non-nested, cross-sectional data with binary independent variables. In Table \ref{tab:table-model-1}
+\footnote{All tables in this paper were created with the modelsummary package in \texttt{r} 
+\citep{modelsummary}},I fit a logistic regression model predicting
+whether someone sought information about COVID-19 using their sources of
 information (`Received info') as well as various demographic variables such as
 age, education level and race. Figure \ref{fig:plot-model-1} then illustrates
-the relationship between the coefficients and information seeking.\footnote{Figures in this paper were all created using the \texttt{r} packages jtools \citep{jtools} and ggplot2 \citep{wickham_etal, wickham11}}.
-In Table \ref{tab:model-2-phi} I disaggregate information seeking behaviors by
+the relationship between the coefficients and information-seeking.\footnote{Figures 
+in this paper were all created using the \texttt{r} packages jtools \citep{jtools}
+and ggplot2 \citep{wickham_etal, wickham11}}.
+In Table \ref{tab:model-2-phi}, I disaggregate information-seeking behaviors by
 investigating the difference in proportions of each of the 5 different avenues
-of seeking information about Covid-19: from another person, from a doctor, on an
+of seeking information about COVID-19: from another person, from a doctor, on an
 online forum, on a social networking site, or using an online search tool. I
 investigate these differences through a phi coefficient \citep{warrens08}, otherwise
-known as a mean square contingency coefficient which is used to investigate the
+known as a mean square contingency coefficient, which is used to investigate the
 degree of association between two binary variables.\footnote{To calculate the Phi
   Coefficient, I utilize the Psych \texttt{r} package \citep{psych}} I then investigate the
-associations between my predictors and the 5 information search vehicles by
+associations between my predictors and the five information search vehicles by
 modelling a series of logistic regressions in Table \ref{tab:table-model-2}.
 Finally, in Table \ref{tab:table-model-3}, I investigate whether there is a
-relationship between information receiving and information seeking behaviors and
-the choice to get vaccinated against Covid-19 through a logistic regression
+relationship between information exposure sources, information-seeking behaviors and
+the choice to get vaccinated against COVID-19 through a logistic regression
 model predicting Vaccination Outlook. Figure \ref{fig:plot-model-3} then
@@
 \hypertarget{information-seeking}{%
-\subsection{Information Seeking}\label{information-seeking}}
+\subsection{information-seeking}\label{information-seeking}}
 
@@
 {\centering \includegraphics[width=0.8\linewidth]{figs/paper2/plot-model-1-1}}
-\caption{What predicts someone intentionally searched for information, Plot of Coefficients}\label{fig:plot-model-1}
+\caption{What predicts someone intentionally searched for information, Plot of Coefficients?}\label{fig:plot-model-1}
 \end{figure}
@@
 Table \ref{tab:table-model-1} provides the results of my logistic regression
-analysis predicting whether someone sought information about Covid-19. These
+analysis predicting whether someone sought information about COVID-19. These
 initial results suggest similar results for each vehicle of information
@@
 seeking out information. For example, respondents who had received information
-from a doctor or other medical professional were 2.82
-(relative odds ratio = \(exp(\beta k)\), \emph{p} \textless{} 0.001) times more likely to seek
-out information over someone who hadn't. Similarly, respondents who had received
-information from `a person like friend, neighbor, or family member that {[}they{]} know'
-were 1.87
-( \emph{p} \textless{} 0.001) times more likely to seek out information over someone who hadn't
-received information from a person like that. Interesting, those who had
-received information from an online discussion group, listserve, or other online
-forum including a Facebook group or subreddit were
-2.39 ( \emph{p} \textless{} 0.001)
-times more likely to search out more information than someone who hadn't. While
-most demographic variables don't seem to have a strong effect on whether someone
-sought out information about the Covid-19 vaccine, a few key variables had strong
-associations. Age, for instance, is associated with seeking information; every
-additional year of age a person holds they are
-3\%
-more likely to search for information, possibly indicating a generational effect
-of information seeking patterns ( \emph{p} \textless{} 0.01). Additionally, those who were more
-educated, that is those with an associate's degree or higher, were
-1.58
-more likely to seek additional information than those without the degree
-( \emph{p} \textless{} 0.05). And finally, there is evidence to suggest that the Black or
+from a doctor or other medical professional were 2.82 (odds ratio = \(exp(\beta k)\),
+\emph{p} \textless{} 0.001) times more likely to seek out information over someone
+who had not. Similarly, respondents who had received information from `a
+person like friend, neighbor, or family member that [they] know' were 1.87
+(\emph{p} \textless{} 0.001) times more likely to seek out information over 
+someone who had not received information from a person like that. Interesting, 
+those who had received information from an online discussion group, listserv,
+or other online forum including a Facebook group or subreddit were 2.39 (\emph{p}
+\textless{} 0.001) times more likely to search out more information than 
+someone who had not. While most demographic variables do not seem to have a 
+strong effect on whether someone sought out information about the COVID-19 
+vaccine, a few key variables had strong associations.  Respondents who are 
+older are more likely to seek information; The odds are about 3\% higher when 
+age is equal to x + 1 relative to x, possibly indicating a generational effect
+of information-seeking patterns (\emph{p} \textless{} 0.01). Additionally,
+those who were more educated, that is those with an Associate's degree or higher,
+were 1.58 more likely to seek additional information than those without the degree
+(\emph{p} \textless{} 0.05). And finally, there is evidence to suggest that the Black or
 African American sample was more likely to seek out information, specifically:
-Blacks were 3.58 times more likely
-to seek out information over non-Blacks ( \emph{p} \textless{} 0.05). Figure \ref{fig:plot-model-1} illustrates
-the relationship between the coefficients and information seeking.
+Blacks were 3.58 times more likely to seek out information over non-Blacks (\emph{p}
+\textless{} 0.05). Figure \ref{fig:plot-model-1} illustrates the relationship
+between the coefficients and information-seeking.
 
@@
 sought information out intentionally, ``How did you look for information about
-the Covid-19 vaccine?'' Because respondents could select as many responses as
+the COVID-19 vaccine?'' Because respondents could select as many responses as
 applicable, each response is recorded as a dichotomous variable. Table
-\ref{tab:table-1-desc} reveals differences in the prevalence of usage of the
-various information seeking vehicles: Around 40\% of the sample has inquired for
-information from a doctor, a person, or using online search tool (44\%, 42\%, 41\%) while my
+\ref{tab:table-1-ind} reveals differences in the prevalence of usage of the
+various information-seeking vehicles: Around 40\% of the sample has inquired for
+information from a doctor, a person, or using online search tool (44\%, 42\%, 41\%), while my
 respondents used vehicles like online forums (27\%) and social networking sites (18\%)
-to seek out information at significantly lower rates. To investigate how each
+to seek out information at significantly lower rates.
+
+To investigate how each
 Information Search Vehicle are related to each other using the Phi Coefficient
-(\(\\phi\)) of binary association between each Information Search Vehicle pair.
+($\phi$) of binary association between each Information Search Vehicle pair.
 The Phi coefficient can be interpreted like a correlation coefficient, with
-numbers closer to -1 or positive one indicating a very strong relationship
+numbers closer to -1 indicating a very strong negative relationship and those closer to 
+positive 1 indicating a very strong positive relationship
 (Warrens 2008). Table \ref{tab:model-2-phi} shows the results of these
@@
 evidence that the vehicles are distinctly different concepts because most
-coefficients fall under 0.3, the general rule of thumb for correlation
+coefficients fall under 0.3, the general cutoff for correlation
 coefficients to indicate a relationship. There does seem to be a relationship
 between Online Forums and Social Networking Sites, possibly due to an
-individual's propensity to use online networks over in-person networks. These
+individual's latent propensity to use online networks over in-person networks. These
 coefficients indicate a weak relationship between any two vehicles of
@@
 
+I find that indeed the most common vehicles are 
+asking a doctor, asking a friend, and asking a search engine which confirms
+Hypthesis \ref{hyp:drgooglefriend}. However, because the vehicles 95\% confidence intervals 
+in Table \ref{tab:table-1-ind}
+are overlapping, I fail to find evidence for Hypothesis \ref{hyp:online-vs-network},
+that using an online search engine was more commonplace than asking a friend.
+
 \input{tables/paper2/table-model-2}
 
-Results of each logistic regression are displayed in Table \ref{tab:table-model-2}.
+I conduct a separate logistic regression for each search vehicle in Table \ref{tab:table-model-2}. 
 Modeling each response as a separate formula is useful for interpretation, but
@@
 The first model in Table \ref{tab:table-model-2} predicts whether a
-respondent sought information intentionally about Covid-19 vaccinations by
+respondent sought information intentionally about COVID-19 vaccinations by
 asking their doctor or another health professional. First and foremost, I find
-that those who received information about Covid-19 vaccinations were
-6.97 times
-more likely to seek out more information from their doctor than those who had
-not ( \emph{p} \textless{} 0.001). However, receiving information from other vehicles also
+that those who received information about COVID-19 vaccinations were
+6.97 times more likely to seek out more information from their doctor than those who had
+not (\emph{p} \textless{} 0.001). However, receiving information from other vehicles also
 increased the odds of seeking out information from medical professions. Those who
-received information from a person like a friend or a relative were
-2.23 times more likely to ask their doctor ( \emph{p} \textless{} 0.001), while those who received
-information from the news or television were 1.55 times more likely ( \emph{p} \textless{} 0.01).
-I also find that those who received information from an online forum like a subreddit were 51\% more likely to ask their doctors than those who hadn't ( \emph{p} \textless{} 0.05).
-Finally, respondents with an associate's degree or higher were 72\%
-more likely to ask their doctor for information on the Covid-19 vaccinations
-than those who held less education ( \emph{p} \textless{} 0.01).
+received information from a person such as a friend or a relative were
+2.23 times more likely to ask their doctor (\emph{p} \textless{} 0.001), while those who received
+information from the news or television were 1.55 times more likely (\emph{p} \textless{} 0.01). 
+I also find that those who received information from an online forum like a subreddit were 51\% 
+more likely to ask their doctors than those who had not (\emph{p} \textless{} 0.05). 
+Finally, respondents with an Associate's degree or higher were 72\%
+more likely to ask their doctor for information on the COVID-19 vaccinations
+than those who held less education (\emph{p} \textless{} 0.01).
 
 The second model predicts whether a respondent sought information about
-Covid-19 vaccinations by asking a person like friend, neighbor, or family member
+COVID-19 vaccinations by asking a person like friend, neighbor, or family member
 that they know. Only three coefficients in this model were significant and help
@@
 received information from a doctor or other medical professional were 3.08
-times more likely to seek information from a person like a friend ( \emph{p} \textless{} 0.001).
+times more likely to seek information from a person such as a friend (\emph{p} \textless{} 0.001).
 Moreover, it seems that receiving information from your personal social network,
-like a friend or relative, is associated with seeking information from those
+such as a friend or relative, is associated with seeking information from those
 same people; in fact, I find that those who did are 3.32 more
-likely to do so ( \emph{p} \textless{} 0.001). Finally, the respondents who received information
+likely to do so (\emph{p} \textless{} 0.001). Finally, the respondents who received information
 about the vaccine on a social networking site were 55\%
-more likely to seek information from their personal network than those who hadn't
-( \emph{p} \textless{} 0.01). The unexpected result of this model is that very few factors predict
+more likely to seek information from their personal network than those who had not
+(\emph{p} \textless{} 0.01). The unexpected result of this model is that very few factors predict
 personal social network activation, and this model has the lowest McFadden's R\^{}2,
@@
 
-I also wanted to see what was associated with posting in an online discussion
-group, listserve, or other online forum like a Facebook Group or Subreddit about
-Covid-19 vaccinations. This is conceptually different that posting a query on a
+I also wanted to examine what factors were associated with posting in an online discussion
+group, listserv, or other online forum like a Facebook Group or Subreddit about
+COVID-19 vaccinations. This is conceptually different than posting a query on a
 social networking site like Facebook or twitter where identities are involved,
-but is theoretically more {[}costly?{]}{[}friction?{]} than searching on an internet
+but is theoretically more social friction than searching on an internet
 search engine. I found that having received information about the vaccine from
-your personal social network (like a friend or relative), the news, or an online
+your personal social network (such as a friend or relative), the news, or an online
 forum was associated with higher odds of querying an online forum. Specifically,
 receiving information from your personal network is associated with 2.07
-higher odds ( \emph{p} \textless{} 0.001), from news or television media with 1.43 higher odds ( \emph{p} \textless{} 0.05), and receiving information on an online forum associated with 3.55
-higher odds ( \emph{p} \textless{} 0.001). Moreover, I found that those with an associate's
-degree or above were 2.96 times 
-more likely to search for information on an online forum ( \emph{p} \textless{} 0.001). Finally,
-I found a racial-ethnic with Hispanic-Latinos; I found that they were about 70\%
-more likely to query an online forum than non-Hispanics ( \emph{p} \textless{} 0.05). However,
-there were also a few variables that lowered the odds of posting in an online
-discussion group. First, those who had received information from a social networking site were 45\%
-less likely to query a forum than those who hadn't (relative odds ratio =
-\(1 - exp(\beta k)\), \emph{p} \textless{} 0.01). Moreover, I find more ethnoracial effects:
-Respondents who claimed Asian ancestry were 92\%
-less likely to query online forum ( \emph{p} \textless{} 0.01).
+higher odds (\emph{p} \textless{} 0.001), from news or television media with 1.43 
+higher odds (\emph{p} \textless{} 0.05), and receiving information on an online
+forum associated with 3.55 higher odds (\emph{p} \textless{} 0.001). Moreover,
+I found that those with an Associate's degree or above were 2.96 times more
+likely to search for information on an online forum (\emph{p} \textless{} 0.001).
+Finally, I found that Hispanic-Latinos were about 70\% more likely to query 
+an online forum than non-Hispanics (\emph{p} \textless{} 0.05). However, 
+there were also a few variables that lowered the odds of posting in an 
+online discussion group. First, those who had received information from
+a social networking site were 45\% less likely to query a forum than those 
+who had not (odds ratio = \(1 - exp(\beta k)\), \emph{p} \textless{} 0.01).
+Moreover, I found additional ethnoracial effects: Respondents who claimed
+Asian ancestry were 92\% less likely to query online forum (\emph{p} \textless{} 0.01).
 
 The fourth model predicts whether an individual sought information about
-Covid-19 vaccinations through posted queries on a social networking site such
+COVID-19 vaccinations through posted queries on a social networking site such
 as Facebook timeline, Twitter status update, or LinkedIn. Receiving information
-about Covid-19 seems to be quite related to posting on social media. Those who
-received information from their doctor's had 1.72
-higher odds of posting on a social networking site ( \emph{p} \textless{} 0.01), while those
-who received their information from tv/news had 1.67 higher odds ( \emph{p} \textless{} 0.05).
+about COVID-19 seems to be quite related to posting on social media. Those who
+received information from their doctors had 1.72 
+higher odds of posting on a social networking site (\emph{p} \textless{} 0.01), while those
+who received their information from tv/news had 1.67 higher odds (\emph{p} \textless{} 0.05).
 Furthermore, those who received information on social networking sites were more
 likely to post queries on social networking sites (\(\beta\) = 2.08, \emph{p} \textless{} 0.001).
-The respondents in our sample who received information on online forums had 2.65
-higher odds of posting queries on their social networking platforms ( \emph{p} \textless{} 0.001).
+The respondents in our sample who received information from online forums had 2.65
+higher odds of posting queries on their social networking platforms (\emph{p} \textless{} 0.001).
 I found a relationship between education and posting on social networking sites
 as well; specifically, those with an Associate's degree or above were 3.83 times more likely to post vaccination
-queries on social networking sites than those with lower education ( \emph{p} \textless{} 0.001).
+queries on social networking sites than those with lower education (\emph{p} \textless{} 0.001).
 Finally, I find that Hispanic-Latinos were 88\%
 more likely to ask their connections on a social networking site about the
-Covid-19 vaccinations than non-Hispanics ( \emph{p} \textless{} 0.01).
+COVID-19 vaccinations than non-Hispanics (\emph{p} \textless{} 0.01).
 
@@
 friction. Our descriptive statistics showed that not everyone used this vehicle,
-with only 41\% of our sample (See Table \ref{tab:table-1-desc}) having sought
-information about the Covid-19 vaccines using online search engines. My model
+with only 41\% of our sample (See Table \ref{tab:table-1-ind}) having sought
+information about the COVID-19 vaccines using online search engines. My model
 reveals interesting patterns to help explain the variation. As with previous
 models, receiving information of any kind increase the odds of online search,
-though to varying magnitudes (Doctor: 1.54 odds; Person: 1.44 odds; News or Television: 2.98 odds; Social Networking Site: 3.57 odds; Online Forum: 2 odds).
-I also find that older respondents were more likely to search online, with each
-addition year aged to yield 3\%
-higher odds of searching online ( \emph{p} \textless{} 0.001). The most interesting variations
+though to varying magnitudes (Doctor: 1.54 odds; Person: 1.44 odds; News or Television: 2.98 odds; 
+Social Networking Site: 3.57 odds; Online Forum: 2 odds). I also find that older respondents
+were more likely to search online, with each addition year aged to yield 3\%
+higher odds of searching online (\emph{p} \textless{} 0.001). The most interesting variations
 come from what decreases the odds of online search. First, those with an
 Associate's degree or higher were 61\%
-less likely to search online for questions about Covid-19 than those with less
-educational attainment ( \emph{p} \textless{} 0.001). In addition, I find that Hispanic-Latinos
-had 44\% lower odds of searching online than non-Hispanics ( \emph{p} \textless{} 0.05).
+less likely to search online for questions about COVID-19 than those with less
+educational attainment (\emph{p} \textless{} 0.001). In addition, I find that Hispanic-Latinos
+had 44\% lower odds of searching online than non-Hispanics (\emph{p} \textless{} 0.05).
 
 \hypertarget{vaccination-views}{%
-\subsection{Vaccination Views}\label{vaccination-views}}
+\subsection{Choosing to be Vaccinated}\label{vaccination-views}}
 
@@
 Finally, in Table \ref{tab:table-model-3}, I investigate whether there is a
-relationship between information receiving and information seeking behaviors and
-the choice to get vaccinated against Covid-19 through a logistic regression
+relationship between information receiving and information-seeking behaviors and
+the choice to get vaccinated against COVID-19 through a logistic regression
 model predicting Vaccination Outlook. I find that receiving information from a
-doctor or other medical profession is associated with
-2.85 odds of receiving
-a Covid-19 vaccinated ( \emph{p} \textless{} 0.001) and that seeking information from a doctor
-also increases the odds of vaccination by
-4 ( \emph{p} \textless{} 0.001).
+doctor or other medical profession is associated with 2.85 odds of choosing
+to receive a COVID-19 vaccination (\emph{p} \textless{} 0.001) and that seeking 
+information from a doctor also increases the odds of vaccination by 4 (\emph{p} \textless{} 0.001).
 I find that my respondents who received information on a social networking site
 like Facebook or Twitter about the vaccines were 55\%
-\textbf{less likely} to get vaccinated than those who received no information through
-that vehicle ( \emph{p} \textless{} 0.001). However, I did find that those who reached out to
-family or friends with their concerns were
-77\% more likely to become vaccinated ( \emph{p} \textless{} 0.05). Furthermore, my respondents who held an
-Associate's degree or above had 3.6
-higher odds of becoming immunized ( \emph{p} \textless{} 0.001). And finally, I found further
-ethnoracial differences in my sample. I found that Hispanic-Latinos had
-2.83 higher odds of vaccination
-than non-Hispanics ( \emph{p} \textless{} 0.05) and that my Asian sample had
-4.73 higher odds as well over
-non-Asians ( \emph{p} = 0.09). See Figure \ref{fig:plot-model-3} for a visual
+\textbf{less likely} to choose to get vaccinated than those who received no information through
+that vehicle (\emph{p} \textless{} 0.001). However, I did find that those who reached out to
+family or friends with their concerns were 77\% more likely to become vaccinated 
+(\emph{p} \textless{} 0.05). Furthermore, my respondents who held an Associate's degree
+or above had 3.6 higher odds of becoming immunized (\emph{p} \textless{} 0.001).
+And finally, I found further ethnoracial differences in my sample. I found that
+Hispanic-Latinos had 2.83 higher odds of vaccination than non-Hispanics
+(\emph{p} \textless{} 0.05) and that my Asian sample had 4.73 higher odds as well over
+non-Asians (\emph{p}  = 0.09). See Figure \ref{fig:plot-model-3} for a visual
 representation of how these different coefficients are related to vaccination outlook.
-
-% <!-- TODO: watch out about saying vaccinated, this variable is about opinion -->
 
@@
 {\centering \includegraphics[width=0.8\linewidth]{figs/paper2/plot-model-3-1}}
-\caption{Does receiving or searching for information predict vaccination status? Plot of Coefficients}\label{fig:plot-model-3}
+\caption{Does receiving or searching for information predict vaccination outlook? Plot of Coefficients}\label{fig:plot-model-3}
 \end{figure}
@@
 Previous research in Sociology and Infodemiology has greatly failed to
-distinguish between the activation of information seeking behaviors online and
-offline. In this paper, I aim to uncover just how different various methods of
+distinguish between the activation of information-seeking behaviors online and
+offline. In this paper, I sought to uncover just how different various methods of
 information search are and begin a line of research inquiry that investigates
-the factors associated with each different vehicle. Finally, I also aimed to
-uncover how the different fountains of information and information search
-vehicles hold real world consequences through their associations with Covid-19
+the factors associated with each different vehicle. Finally, I also uncovered
+how the different sources of information exposure and information search
+vehicles hold real world consequences through their associations with COVID-19
 vaccination rates and intentions.
 
-I first find that receiving information about Covid-19 vaccinations from any
-outlined source increases the likelihood of searching out more information. I
+I first find that being exposed to information about COVID-19 vaccinations from any 
+source increases the likelihood of searching out more information. I
 also find important demographic differences in the overall propensity to seek
 out information. First, I find that the older a respondent is, the more likely
-they are to seek out information about Covid-19 vaccinations, possibly
+they are to seek out information about COVID-19 vaccinations, possibly
 indicating a larger information need by elderly populations overall, or a more
-pressing need to search for information about the Covid-19 vaccinations because
+pressing need to search for information about the COVID-19 vaccinations because
 of the higher risk of hospitalizations that older populations face
@@
 seeking vehicles queried in this survey are conceptually different and that the
-utilization of different varies by demographic and supply 
-% TODO (information fountain? \textasciitilde{} source of having receiving information). 
-Overall, receiving information about
-Covid-19 vaccination generally is associated with information seeking behaviors,
-though there are key variations. First, if you received information from a
-doctor, you were likely to search from information from a doctor; this may
+utilization of different varies by demographic and information exposure source. 
+Overall, being exposed to information about COVID-19 vaccinations from any 
+source is associated with information-seeking behaviors,
+though there are key variations. First, if one received information from a
+doctor, they were likely to search from information from a doctor; this may
 indicate an already existing trusting relationship between patient and
 healthcare provider but it may also indicate the healthcare provider taking
-initiaive and emphasizing the importance of the vaccine or the survey respondent
+initiative and emphasizing the importance of the vaccine or the survey respondent
 seeking out information from an expert. Another important finding is that if you
@@
 of different methods; for example, Asians seem are less likely to use online
-forums than non-Asians while Hispanics are more likely to use them than
+forums than non-Asians, while Hispanics are more likely to use them than
 non-Hispanics. The internal variations between the different information search
@@
 
-Given the rampant misinformation around Covid-19, her related vaccinations
-\citep{pathakInfodemicsCOVID19Role2020, mottaHowRightLeaningMedia2020, shahsavariConspiracyTimeCorona2020}
+Given the rampant misinformation around COVID-19, its related vaccinations
+\citep{pathakInfodemicsCOVID19Role2020, mottaHowRightLeaningMedia2020, shahsavariConspiracyTimeCorona2020},
 and the slowed rate of vaccinations in the
 United States, it is important to uncover what relationship the different
-fountains of information and information search vehicles for Covid-19 vaccinations
+sources of information exposure and information search vehicles for COVID-19 vaccinations
 are associated with compliance with public health recommendations. Table
-\ref{tab:table-model-3} demonstrated just how these different fountains of
-information and information search vehicles are associated with real world
-consequences through Covid-19 vaccination rates and intentions. The first
+\ref{tab:table-model-3} demonstrated just how these different sources of information 
+exposure and information search vehicles are associated with real world
+consequences through COVID-19 vaccination rates and intentions. The first
 takeaway is that receiving or seeking information from a doctor or other medical
@@
 Site like Facebook timeline or Twitter status update was significantly
-associated with lower vaccination rates. While we don't know what exact
+associated with lower vaccination rates. While we do not know what exact
 information was absorbed on these platforms, the lower odds of vaccination
 indicate that it was not positive. Much has been attempted between 2020 and 2022
-to curb vaccine misinformation on these social networking platforms (see Bowman 2020 for an early example); however, I find evidence that these social
+to curb vaccine misinformation on these social networking platforms 
+\citep[see][for an early example]{bowman20}; however, I find evidence that these social
 networking platforms nevertheless have a measurable negative impact. Finally,
@@
 Hispanic-Latinos and Asians were more likely than non-Hispanics and non-Asians
-to receive or plan to receive a vaccination against Covid-19 (Table
+to receive or plan to receive a vaccination against COVID-19 (Table
 \ref{tab:table-model-3}). Research in this area has mixed results, with some
@@
 many minorities are much more hesitant \citep{momplaisir_etal21, foxworth21}. 
-My finding that college-educated respondents were more likely seek vaccination is largely consistent with the broader literature
-\citep{khairat_etal22}, though again there are many variations depending on the vaccine
+My finding that college-educated respondents were more likely seek vaccination is 
+largely consistent with the broader literature m\citep{khairat_etal22}, though 
+again there are many variations depending on the vaccine
 in question and study context \citep{siddiqui_etal13}.
@@
 Previous research has greatly failed to distinguish between the activation of
-information seeking behaviors online and offline and largely focuses on the
-information that is sent to consumers {[}push{]}, seeing people as passive receivers
+information-seeking behaviors online and offline and largely focuses on the
+information that is sent to consumers [push], seeing people as passive receivers
 of information. In this paper, I instead focus on individuals as active agents
@@
 Given the large swaths of both misinformation and disinformation regarding
-Covid-19 \citep{pathakInfodemicsCOVID19Role2020, mottaHowRightLeaningMedia2020, shahsavariConspiracyTimeCorona2020} and the measurable impacts this misinformation has had on pandemic-related health behaviors
-\citep{loombaMeasuringImpactCOVID192021, greene_murphy21}, Covid-19 provides an ideal study to
+COVID-19 \citep{pathakInfodemicsCOVID19Role2020, mottaHowRightLeaningMedia2020, shahsavariConspiracyTimeCorona2020} 
+and the measurable impacts this misinformation has had on pandemic-related health behaviors
+\citep{loombaMeasuringImpactCOVID192021, greene_murphy21}, COVID-19 provides an ideal study to
 investigate how we choose to search for information that affects both our own
@@
 This paper has provided several key findings that can be used to motivate policy
-interventions for the Covid-19 vaccination campaigns and in the future for other
+interventions for the COVID-19 vaccination campaigns and in the future for other
 information campaigns. However, these findings are not to be taken out of the
-context of their limitations. This paper is built off a small survey sample (
-948) that was hosted online and anonymously through MTurk, a service
-that provides people with micro-jobs. Because of how the website is set up,
-respondents are incentivized to fill out surveys as quick as possible and there
-were many responses that were poor quality and removed from the sample before
-analysis. Because of this, there is no incentive for respondents to be honest in
-these surveys. However, each of these limitations are often pointed to as
-limitations of survey research as a whole. Even given these limitations,
-the finding of this paper are interesting contributions to the literature.
+context of their limitations. This paper is built off a small survey sample (948)
+that was hosted online and anonymously through MTurk, a service
+that provides people with micro-jobs. Because of the structure of the website,
+respondents are incentivized to fill out surveys and other tasks 
+as quick as possible and there is no incentive for respondents to be honest
+in their responses. For the same reason, there were many responses that 
+were poor quality and removed from the sample before analysis.
+However, each of these limitations are common critiques of 
+survey research as a whole. Even given these limitations,
+the finding of this paper are interesting and timely contributions to the literature.
 
@@
 information search impacts the information and quality of information found. By
-looking at how individuals search, I aim to identified pain points and focus areas
-for future interventions (receiving information online; ethnoracial variations) in the misinformation process.
+looking at how individuals search, I aimed to identified pain points and focus areas
+for future interventions (receiving information online; ethnoracial variations) 
+in the misinformation process.

### 2022-03-15 paper3.tex
3 article summaries
finish contributions and future directions
Finish paper 2 revisions

@@
 \hypertarget{paper-3}{%
-\chapter{Social Norms under Uncertain Times: A dynamic study of Stay-At-Home and Vaccination Rates During the Covid-19 Pandemic}\label{paper-3}}
+\chapter{Social Norms under Uncertain Times: A dynamic study of Stay-At-Home and Vaccination Rates During the COVID-19 Pandemic}\label{paper-3}}
 
@@
 This paper examines how social norms are formed under conditions of uncertainty
-using the case studies of stay-at-home and vaccination rates during the Covid-19
+using the case studies of stay-at-home and vaccination rates during the COVID-19
 pandemic. I test fear-based models of behavioral adaption to public health
@@
 mixed effects models. These models show that complex contagion is a valid
-framework for the social contagion of new norms during Covid-19. However, I find
+framework for the social contagion of new norms during COVID-19. However, I find
 important moderating effect of signal discordance, the contextual diversity of
@@
 % need to explain a little bit more what diversity of signals etc means (since this is the first look) 
+% what else needs to be said here to properly convey the importance and impact of this finding?
 
@@
 A second strategy pushed by the CDC, once available, was to receive vaccination
-to prevent the effects of the Covid-19 virus if infected. Vaccinations like
+to prevent the effects of the COVID-19 virus if infected. Vaccinations like
 Pfizer-BioNTech (Comirnaty, tozinameran, BNT162b2), and Janssen/Johnson \&
@@
 or disasters. Though research on the causes of population mobility did expand
-after the onset of the Covid-19 pandemic 
+after the onset of the COVID-19 pandemic 
 \citep{bargainTrustCompliancePublic2020, bourassaStatelevelStayathomeOrders2020, bourassaSocialDistancingHealth2020, grossmanPoliticalPartisanshipInfluences2020, haggerPredictingSocialDistancing2020, hillBloodChristCompels2020, hillNastiestQuestion, hillLoveThyAged2021,huynhDoesCultureMatter2020}, most research focused on unchanging cultural
@@
 This article researches the formation of social norms governing health behaviors
-in cases of extreme uncertainty during the Covid-19 pandemic. Using theories of complex
+in cases of extreme uncertainty during the COVID-19 pandemic. Using theories of complex
 contagion, associative diffusion and the integrated theoretical framework of
@@
 how belief structures are connected to each other is important to test because
-norms around health behaviors became politicized issues during the Covid-19
+norms around health behaviors became politicized issues during the COVID-19
 pandemic. This means that the stay-at-home or vaccination behavior themselves
@@
 diffusing through a population, are not independent of each other \citep{mason_etal07}.
-When we take into account the interdependence between different beliefs that are diffusing, such as Covid-19 is a hoax, social distancing saves
-lives, the Covid-19 vaccine includes a microchip to control your thoughts, and lockdown
+When we take into account the interdependence between different beliefs that are diffusing, such as COVID-19 is a hoax, social distancing saves
+lives, the COVID-19 vaccine includes a microchip to control your thoughts, and lockdown
 is against the rights guaranteed in the US constitution, we can imagine how
@@
 
-\hypertarget{covid-19-case-rates}{%
-\subsubsection{Covid-19 Case Rates}\label{covid-19-case-rates}}
+\hypertarget{COVID-19-case-rates}{%
+\subsubsection{COVID-19 Case Rates}\label{COVID-19-case-rates}}
 
 To estimate the concept of `real threat of infection' for a fear-based model of
-health behaviors, the models use county-level Covid-19 case rates with
+health behaviors, the models use county-level COVID-19 case rates with
 data compiled by The New York Times \citeyearpar{covid_data}. It is widely acknowledged that there are biases in this data due to inconsistencies and availability in testing as well as
@@
 
+% TODO Mention that article-1 says that this can show interest (cite jungherr also) but does not show actions
+
 To operationalize the search for online norms, I use Google search trends \citep{googletrends},
@@
 online in both cases, I use the following search topics: `Social Distancing'
-(2020, stay-at-home case only), `Covid-19 Vaccine' (2021, vaccination uptake case
+(2020, stay-at-home case only), `COVID-19 Vaccine' (2021, vaccination uptake case
 only) and Covid Conspiracy (2020-2021, both cases). Search topics are a more
@@
 `Covid Conspiracy' tend to increase time spent in residence. Interestingly, the
-perceived threat of the virus, measured through Covid-19 case rates, were not
+perceived threat of the virus, measured through COVID-19 case rates, were not
 significantly related to stay-at-home rates in model 1. In other words, for
-every 1 standard deviation increase in Covid-19 case rates, stay-at-home rates
+every 1 standard deviation increase in COVID-19 case rates, stay-at-home rates
 actually decreased by
@@
 \ref{fig:plot-google-h2} illustrates this interaction. In the early days of the
-Covid-19 pandemic, seeing a high rate of time spent in residence by alters led
+COVID-19 pandemic, seeing a high rate of time spent in residence by alters led
 to a high rate of staying-at-home for county egos. However, as the pandemic
@@
 Hypothesis 1 also returns surprising results: every 1 standard deviation
-increase in county Covid-19 case rates is expected to yield a -0.008 decrease in vaccination rates. This may be due to time ordering or reverse
+increase in county COVID-19 case rates is expected to yield a -0.008 decrease in vaccination rates. This may be due to time ordering or reverse
 causality, where individuals in counties who have higher rates of vaccination
-are less likely to take tests to Covid-19 infections because of the higher
+are less likely to take tests to COVID-19 infections because of the higher
 likelihood of asymptomaticity. However, it is important to note that the Case
@@
 using the case studies of stay-at-home rates and vaccination rates during the
-Covid-19 pandemic. I test fear-based models of behavioral adaption to public
+COVID-19 pandemic. I test fear-based models of behavioral adaption to public
 health recommendations as well as patterns of complex social contagion. This
@@
 This article also provides a new adaption of the theory of complex contagion
-using big data from the natural experiment of Covid-19. Because most studies of
+using big data from the natural experiment of COVID-19. Because most studies of
 complex contagion utilize agent-based modeling or studies of social media \citep{aralExerciseContagionGlobal2017,sprague_house17,bond_etal12,latane_etal94}, combining measures of actual behavioral outcomes with data from

### 2022-03-15 tables/paper2/table-1-ind.tex
Finish paper 2 revisions

\begin{table}[!ht]

\caption{\label{tab:table-1-ind}Descriptive Statistics for Independent Variables}
\centering
\begin{tabular}{llrrr}
\toprule
  &    & Mean & SD & 95\% CI\\ \midrule
Sought Info & Overall  &  \num{0.78} & \num{0.41} & \num{0.76} to \num{0.81}\\
Sought Info & Doctor & \num{0.44} & \num{0.50} & \num{0.41} to \num{0.47}\\
Sought Info & Person & \num{0.42} & \num{0.49} & \num{0.39} to \num{0.45}\\
Sought Info & Online Search & \num{0.41} & \num{0.49} & \num{0.38} to \num{0.45}\\
Sought Info & Online Forum & \num{0.27} & \num{0.44} & \num{0.24} to \num{0.30}\\
Sought Info & Social Networking Site & \num{0.18} & \num{0.39} & \num{0.16} to \num{0.21}\\
\bottomrule
\multicolumn{5}{l}{\rule{0pt}{1em}Notes: 948 Surveyed, Conducted December 03 through December 12, 2021.}\\
\end{tabular}
\end{table}

### 2022-03-15 tables/paper2/table-model-2.tex
fix paper 1 tables, finish most of writing
Finish paper 2 revisions

@@
-\begin{table}[!h]
-
+\begin{sidewaystable}
 \caption{\label{tab:table-model-2}What predicts someone intentionally searched for information, by vehicle of information search}
@@
 \resizebox{\linewidth}{!}{
-\begin{tabular}[t]{llllll}
+\begin{tabular}{llllll}
 \toprule
@@
 Age & \num{0.002} & \num{0.001} & \num{-0.007} & \num{-0.003} & \num{0.029}***\\
+\cellcolor{gray!6}{Gender, Male} &\cellcolor{gray!6}{\num{0.100}} & \cellcolor{gray!6}{\num{-0.124}} & \cellcolor{gray!6}{\num{0.070}} & \cellcolor{gray!6}{\num{-0.075}} & \cellcolor{gray!6}{\num{-0.147}}\\
+Gender, Other & \num{-1.078} &\num{-1.307} & \num{-13.953} & \num{-12.740} & \num{-0.954}\\
 \cellcolor{gray!6}{Associate's Deg or above} & \cellcolor{gray!6}{\num{0.542}**} & \cellcolor{gray!6}{\num{0.154}} & \cellcolor{gray!6}{\num{1.086}***} & \cellcolor{gray!6}{\num{1.344}***} & \cellcolor{gray!6}{\num{-0.952}***}\\
@@
 $R_{McFadden}^2$ & \num{0.193} & \num{0.121} & \num{0.145} & \num{0.154} & \num{0.221}\\
-\cellcolor{gray!6}{BIC} & \cellcolor{gray!6}{\num{1152.2}} & \cellcolor{gray!6}{\num{1237.6}} & \cellcolor{gray!6}{\num{1048.0}} & \cellcolor{gray!6}{\num{864.8}} & \cellcolor{gray!6}{\num{1104.6}}\\
-Log.Lik. & \num{-524.709} & \num{-567.376} & \num{-472.576} & \num{-380.971} & \num{-500.907}\\
 \bottomrule
@@
 \end{tabular}}
-\end{table}
+\end{sidewaystable}

### 2022-03-17 paper1.tex
merge in paper 1 critiques and comments

@@
 
-Computational social science and other disciplines are quick to 
+Computational social science and disciplines such as sociology and
+political science are quick to 
 adopt new sources of digital trace data for use in academic research. 
@@
 \section{Introduction}
+
+% TODO define big data sources , are we just talking about digital trace data?
+what is that?
+Define, even if as footnote.
+Are 10K pages of field notes big data?
+Admin data with millions of observations but no text?
+
+% TODO Define digital trace data. I  assume remnants of digital activity archived by corporate or state entities.
+
 New big data sources have led to vast possibilities for social science
@@
 sources and integrating them into our big data toolkits, social scientists must clearly establish
-parameters under which these data sources should be operationalized
+parameters under which these data sources are appropriate, 
+and for which questions they are useful 
 \citep{bailCulturalEnvironmentMeasuring2014, lazerParableGoogleFlu2014}. As
@@
 With the expansion of big data, some computational social science research has
-developed extremely innovative methods that have lead to groundbreaking results using 
+developed extremely innovative methods that have led to groundbreaking results using 
 reliable sources of big data. As an example,\citet{blumenstockPredictingPovertyWealth2015}
@@
 Social scientists have yet to widely utilize Google Search Trends as a source of big data.
-Google Trends is an open data resource provided by Google, a major internet search
+Google Trends is an open data resource
+% TODO Does this just mean free and publicly available?
+
+provided by Google, a major internet search
 engine worldwide, that analyzes the top search queries across different localities, 
@@
 scientists outside of economics have used this resource \citep[see][for examples]{choi2012predicting, jun2018ten,da2011search}.
-Because of this, I set out to provide guidance to social scientists as they introduce
-the data source into their toolboxes on how we can operationalize Google Search Trends
+This paper provides evidence-based guidelines for social scientist who would use these resources in their toolboxes on how we can operationalize
+% TODO: operationalize debated
+Google Search Trends
 as validated indicators and under what circumstances.
@@
 and political indicators from the historical US Presidential Election results \citeyearpar{pres_data}, 
-and the American National Election Survey \citeyearpar{anes_data}. This paper will contribute to the
-creation of methodological norms and standards of how to use Google
-Trends as a big data source for societal research and serve as a
-critical inquiry into the adoption of big data without a critical eye
-for the ecological validity of the sources.
+and the American National Election Survey \citeyearpar{anes_data}. This paper will contribute guidance for creating standards of how to use Google
+Trends for social research, and identify potential pitfalls that can compromise the 
+analysis including 1. a lack of ecological validity, 2: poor 
+% TODO finish this sentence, This is the framework I would use for identifying ‘best practices.’ I would personally just say here is how this can go wrong, here is how you avoid it, and next steps.
+I could see doing a critical spin off for a place like big data and society.
 
@@
 even used Google trends to measure how 'culture' spreads around the globe.
-
+% TODO I’ll just say, while I think there is utility here, it is a very particular aspect of culture in a specific populations.
+I think we are still in the era where the bigness and newness can overshadow truth value.
 \subsection{Google Trends and research on health behaviors}
@@
 Medical Internet Research. While much of this research has focused on
+% TODO I think this may erode your point about increasing legitimacy.
+If you said JAMA or NEJM, that would be a stronger example.
+If not, I’d just point to some specific projects then say new journals have emerged but that does not indicate mainstream acceptance…
 the COVID-19 pandemic \citep{jimenez_etal20, jimenezCOVID19SymptomGoogle2020, limEstimatingInformationSeekingBehaviour2020, mavraganiCOVID19PredictabilityUnited2020, nguyenGoogleTrendsAnalysis2020, todorovaInternetBasedData2021, mingUnderstandingHealthCommunication2021},
@@
 to cover a few examples. For a partial review of other utilizations, see \citet{nutiUseGoogleTrends2014}. According to \citet{jaidkaInformationseekingVsSharing2021}, the majority of studies profess
-a correlation of \> .70, "demonstrating the vast potential of Google
+a correlation of \> .70 between the IV and DV, "demonstrating the vast potential of Google
 Search as a proxy for monitoring population health" (p. 3) based on
@@
 I am not the first author to investigate its validity.
-In contrast to the papers mentioned above, there are researchers who have cautioned against
-the wide usage of Google Search Trends. For instance, \citet{asseoTrackingCOVID19Using2020} 
+Some researchers have cautioned against the wide usage of Google Search Trends. For instance, \citet{asseoTrackingCOVID19Using2020} 
 concludes in their research on COVID-19 case rates and Google searches that the correlation 
@@
 non-negligible issues with the measurement of Google Trends, pointing to 
-errors within the purview of accuracy, completeness, consistency, and validity \citep{KarrDataQuality}. \citet{cebrian_domenech22} point not only to 
+errors within the purview of accuracy, completeness, consistency, and validity
+% TODO I know it is basic stats, but I would provide a footnote explaining each of your terms. Here, these line up with mainline stats but disciplines vary.
+
+\citep{KarrDataQuality}. \citet{cebrian_domenech22} point not only to 
 meta issues like the lack of transparency into the sampling methods 
 and population coverage, but they identify real differences 
-in the data provided by the Google Trends API for the same query, pointing
+in the data provided by the Google Trends API for the same 
+researcher-entered query, pointing 
 to likely internal process used by Google to sample their data to compute the trends.
@@
 further research can determine the cause for the inaccuracies. 
+% TODO Yes, big issue.
+But, it is also seen in machine learning, survey administration, etc.
+I’d assume one solution for dealing with fiddly output is to just sample repetedly and do some sort of average, perhaps with a correction if the direction of the error is non random.
 
@@
 Google Trends as digital trace data do so to indicate
-populations \textit{attention} to a search query. Because
+population's \textit{attention} to a search query. Because
+% TODO I’d also say, the population is examined differently. It is really a population of action remnants being used to get at a population of people, which is presumed to be represented online.
 searches can be done with many different intentions, such as 
-information gathering, ridicule, navigational purposes, etc., it may
+information gathering, navigational purposes, etc., it may
 be hard to declare that an overall level of engagement with a topic
 on Google Search may be indicative of anything more than interest \citep{da2011search}.
+To reference Clifford Geertz's invocation of Ryle, we only know that the search was 
+performed, not whether it indicated a digital wink or twitch \citeyearpar{geertz1973thick}.
+%TODO CITE above, For a soc audience some sort of reference to the dilemma of interpretation would be interesting.
+
 \citet{jungherr_etal17} explore this topic deeply with data from
@@
 it is imperative that we provide a framework for how to use diverse sources
-of digital trace data as a discipline. The aim of this paper is
-to take the first step to build that framework. I will attempt to validate 
-Google Search Trends for use outside of mere interest or attention using the
-methods that follow; specifically, to verify whether
-trends should be used to indicate attitudes, health outcomes, or political support.
+of digital trace data as social scientists. The aim of this paper is
+to take the first step to build that framework. I examine the validity of 
+Google Search Trends to indicate attitudes, health outcomes, or political 
+support using the methods that follow.
 
 \section{Methods}
+
+%TODO There are a lot of validities here. Be precise and explain what you are concretely examining. define which validity here 
 To investigate the construct and criterion validity of the use of Google Trends
@@
 \subsubsection{Google Trends}
-This paper focuses on a validation of Google search trends \citep{googletrends}.
+This paper focuses on a triangulation of Google search trends \citep{googletrends}
+with other sources of credible data.
 Google trends portray the search frequency for specific search terms across
 designated media markets areas (DMAs), a nonoverlapping aggregation of U.S.
-counties to 210 media markets based on similar population clusters \citep{dma_key}.
+counties to 210 media markets based on Nielsen's classification o "similar population clusters" \citep{dma_key}.
 Raw data is on a scale from zero to one hundred, with one hundred being the maximum search
@@
 measurement than a single search term: topics are aggregations of the rates of
-multiple, highly correlated search terms together into a cohesive topic. For
+multiple, highly correlated search terms together into a cohesive topic done
+by Google through it's Knowledge Graph product. For
 example, while 'Beyoncé', 'Beyonce' and 'beyonce knowles' are all separate
@@
 time). To remedy this and build a longitudinal dataset of each search topic 
-to match the longitudinal validated measures, I follow the method proposed in \citet[p. 5]{park_etal}.
-This method involves building a dataset of unscaled cross-sectional values,
+to match the longitudinal validated measures, I follow the method proposed 
+in \citet[][p. 5]{park_etal}\footnote{This method involves building a dataset of unscaled cross-sectional values,
 selecting a DMA to use to establish the rescaling ratio (I use 'Los Angeles
@@
 longitudinal data against multiple samples of time-series data. For a more
-in-depth explanation of this procedure, see \citet[p. 5]{park_etal}. I interpolate 
-missing datapoints in the longitudinal datasets using \texttt{na.approx()} \citep{zoo}.
+in-depth explanation of this procedure, see \citet[p. 5]{park_etal}}. I interpolate 
+missing datapoints in the longitudinal datasets using The Zoo package for R \citep{zoo}.
 
 \subsubsection{Attitudinal}
+
+% TODO create a  table People will want to see a table of variables, their prompts, and ranges.
 
@@
 Another attitudinal indicator I use is the Mask-Wearing Survey Data conducted by
-Dynata for the New York Times from July 2 through 14, 2020 \citep{mask_data}. 250,000
+Dynata, a global online market research firm, for the New York Times from 
+July 2 through 14, 2020 \citep{mask_data}. 250,000
 survey respondents were asked, "How often do you wear a mask in public when you
@@
 consists of 3,148 observations, one for each U.S. County included in the sample. This measure
-represents the percent of adults in the county who never or rarely wear a mask
+is purposed to estimate the percent of adults in the county who never or rarely wear a mask
 (range = 0.10\% to 55.80\%).
@@
 availability in testing as well as different community propensity to test
-\citep{gu22, cdc20a} However, it is the best measure we have of actual case rates.
+% TODO Also blatant political interference in some places, which is probably worth acknowledging.
+\citep{gu22, cdc20a} However, it is the best measure we have of actual case rates
+without extensive adjustments.
 Case Rate is measured as number of cases per 100,000 population. Observations
@@
 December 27, 2021. There are 285,986 cases across 3,136 counties and 101
-dates. Missing data were interpolated using \texttt{na.approx()} \citep{zoo}.
+dates. Missing data were interpolated using The Zoo package for R \citep{zoo}.
 
@@
 
-In addition to specific outcomes of interest, I also gathered various county
-controls to investigate possible variable confounding. The first Seven of these
+In addition to specific measures of interest, I also gathered vadata on potentially
+confounding variables. The first Seven of these
 variables come from the 2010-2019 5-year American Community Surveys
@@
 \citep{pinheiro_etal21} (for longitudinal datasets) to identify the strength of
-relationships across locales. I include city-data like county population size,
-broadband rates, and median income to disentangle potentially
-confounded relationships between Google search Trends and verified
-indicators. Identifying these possible confounded relationships will help to
+relationships across locales.
+%TODO This all sounds fine to me, but I’m less up to date on model specification and nesting, so I’m not the best to ask.
+I would also specify why these models are appropriate in one sentence max because methods people about these things.
+Also,they may have sampling assumptions the data violate so clarifying that that is not an issue may be necessary.
+I include location metadata like county population size,
+broadband rates, and median income to adjust for potentially
+confounded relationships between Google search Trends and credible
+indicators. Identifying these possible confounded relationships may help to
 explain why some articles find relationships between the trends and outcomes
-while others did not. For linear regression models, I normalize independent
+while others did not.
+% TODO Why? To have a standardized net impact? Sociologists usually have a strong negative reaction to this. In contrast, in psych they do this with everything.  
+For linear regression models, I normalize independent
 variables; in other words, variables have been centered and scaled to have a mean of zero and
@@
 ('Coronavirus (Disease)' and vaccine hesitancy). Correlation's under |0.40| are 
-weak according to the common rules of thumb. With only one correlation 
+weak according to the common standards. With only one correlation 
 above that threshold, I conclude that the overall trends are at best weakly
@@
 
+% TODO I find this convincing, but a critic might say the following:
+% 1)	In econometrics they use weaker correlations to substitute variables in a model
+% 2)	If specific point estimates are similar, a lot of this may wash out (a core principle of multiple imputation),
+% 3)	Etc. etc.
+% I Wonder if something like a box plot showing how estimates would vary for a question like—did people say they were against masks--might be useful.
+
 \input{tables/paper1/vacc_hes_analysis}
@@
 Correlation's under |0.20| are negligible according to the
-common rules of thumb. I introduce these trends in multiple linear regression in
+common standards. I introduce these trends in multiple linear regression in
 table \ref{tab:mask_analysis}. Model 1 demonstrates that these five Google
@@
 \section{Discussion and Conclusion}
+%TODO I’d say it is a test or assessment.
+Critique implies the answer is known a priori.
+I would focus on validation, note it it has implication (we need to test more and be more cautious),  and say future research should x,y,z.
+
+% The critique, is really about how and why we overlook being precisely incorrect if we like the aesthetics of an argument. I can think of some egregious examples.
+
+% I would send the first paper to somewhere like soc methods or a stat journal, and the second to big data and society or the like.
+
+% That said, there are things here that die hard stats people may find issues with.
+I also think a direct comparison of what google trends versus traditional survey data would predict would be very strong evidence of literally missing the mark.
+
+% A related thought, is the assumption is the survey is right, since it is the referrant for validation.
+But often, the validation procedures of surveys can also lead to invalid claims.
+Cicourel wrote about this really well in 1982, and there are examples where a measure means totally different things to different respondents.
+E..g Alcohol may be read as ‘spiritis’ but not wine by some groups.
+So, it is possible that google is more accurate, and all these data sources require validation from interactions with humans in their lifeworld.
+That would be my position at least, but I think it is fair to say that the while the surveys have been more thoroughly tested, there are potential errors there as well.
+
 This paper provides a critique of Google Trends for use in Social Science. 
@@
 sort of indicator is clear and fields like the health sciences have freely utilized
-this data source. However, this article shows that there is
-no external validity of Google Trends for these specific uses and social scientists
-will find no replacement for high quality survey data with Google Trends.
+this data source. However, this article shows that Google Trends
+fails to map on to validated survey metrics for attitudes, disease prevalence and political preferences.
+Social scientists should not assume Google Trends data can serve as a replacement
+for high quality survey data, at least for these measures.
 
@@
 of the data that we use so we can be confident in our research findings. As with any
-source of data, we must consider the potential pitfalls, especially in research on big data
-\citep{mcfarlandBigDataDanger2015}. In the case of Google Search Trends, precaution was 
-warranted. While I would like to be able to join \citet{bailCulturalEnvironmentMeasuring2014} 
-in encouraging social scientists to pursue more research with the many new sources of big data, 
-I emphasize that testing out data to verify what it actually corresponds to is an essential step 
-to making impactful research as a discipline going forward.
+source of data, we must consider the potential pitfalls, especially in research on 
+using new methods and data sources \citep{mcfarlandBigDataDanger2015}.
+In the case of Google Search Trends, precaution is warranted.
+
+% While I would like to be able to join \citet{bailCulturalEnvironmentMeasuring2014} 
+% in encouraging social scientists to pursue more research with the many new sources of big data, 
+% I emphasize that testing out data to verify what it actually corresponds to is an essential step 
+% to making impactful research as a discipline going forward.
+
+% TODO I like this, but it is out of place tone-wise.
+It fits better in a critical piece or blog.
+I’d say something like in these cases, GT fails validation tests, and caution future research is warranted.
+Future research should determine its utility using empirical criteria rather than a prior assumptions.
+Triangulation, using various data sources, is necessary.
+
+% A stronger case, if you wanted to go in calling out the big data evangelicals, would be to show that their own work does not replicate or those measures are invalid.
+
+% Some of this is based in logical errors and some is based in the politics, and there are different ways to treat that.

### 2022-03-23 abstract.tex
Final committee edits

--- 2022-03-02 abstract.tex
@@
-The online world presents new avenues for the spread of information in addition to the traditional word of mouth effects of social networks.
-It also provides new big data sources for social science research because they are bigger, cheaper, and already available.
-In my dissertation, I combine these two areas of inquiry by examining the differences between the social network contagion of ideas (push) and information seeking (pull) and their relation to the creation of social norms.
-My first article tests the construct validity of the Google Search Trends source of big data as an indicator of three different cases, namely cultural attitudes, disease prevalence and voting behavior, using pairwise correlations .
-My second article establishes how individuals perform information search, whether through interpersonal networks or online, using my original survey data of 900 Adults in the United States.
-My final article builds on these by investigating how new health-behavior social norms form in the face of assortative signals through associative cognitive diffusion.
-This research will be a contribution to methodology of computational social science as it tests the reliability of a big data source, questions what behavioral processes lead to macro-level outcomes recorded in big data sources, and uses novel combinations of data sources and methodology to investigate questions of sociological interest.
-This research will also contribute to the sociology study of information technologies in the digital age, medical sociology, and social networks.
+% at least 150 words, generally no more than 500 words
+
+This dissertation focuses on how people search for information and how people
+rely on this information to inform their health behaviors and develop social
+norms. Information can be shared and promoted by others
+through information campaigns and consumed by an individual, called information
+push, or information can be intentionally sought out by individuals, 
+called information pull, and how the information then relates to the
+creation of social norms. In academia and policy, the focus in research on 
+information has most often focused on the information that is sent to 
+consumers, seeing people as passive receivers of information.
+My dissertation instead focuses on individuals as active agents 
+in their search for information.
+
+The first article tests the construct validity of the Google Search Trends source,
+an online indicator of computer-mediated information search. I attempt to
+validate Google Search Trends for use as indicators of attitudes, disease prevalence
+and political preferences using five different validated data sources. 
+I fail to find correlation among any of the Google Trends tested and their
+validated indicators. I demonstrate that there is no criterion validity of
+Google Trends for the selected cases and social scientists will find no replacement for
+high quality survey data with Google Trends. Instead, we must only use 
+Google Trends to demonstrate interest or attention.
+
+Knowing that Google Trends data only encompasses a small portion of the
+information-seeking done by modern humans, my second article 
+is motivated by the research question: How do computer-mediated or interpersonal 
+information-seeking strategies vary across populations? Using original survey data
+of 948 Americans, I investigate their experiences seeking out information about 
+the COVID-19 vaccines among the following information seeking modalities: 
+personal connection, doctor, social networking site, online forum, and online search engine. 
+I find little evidence that online search is more utilized than
+seeking social support from personal network connections or health professionals
+as I had hypothesized based on uses and gratifications theory, 
+that media users are not passive consumers but instead actively chose
+the media sources based on the satisfaction of their individual needs.
+I find that different exposure points, the ways people first are exposed to 
+information without searching for it, and information search modalities, the 
+ways people intentionally search for information, hold real world consequences
+through their associations with COVID-19 vaccination rates and intentions.
+For example, receiving or seeking out information from a doctor increases 
+ COVID-19 vaccination uptake while receiving information from a social 
+ networking site like Facebook or Twitter was associated with lower odds of vaccination.
+
+My final article takes a deeper dive into the formation of social norms
+governing health behaviors in cases of extreme uncertainty, specifically using the cases of
+ stay-at-home rates and vaccination rates as responses to public health
+recommendations to mitigate the COVID-19 pandemic. Using theories like associative diffusion
+and the integrated theoretical framework of norms, I test models of behavioral adaption
+to public health recommendations and patterns of complex contagion (the need for
+repeated exposures to a something novel for it to diffuse) using linear
+mixed effects models. My results show that complex contagion is a valid 
+framework for the social contagion of new norms during COVID-19. 
+However, I find an important novel moderating effect of signal discordance; 
+if there is diversity in the information received by an ego, 
+contagion is less likely to occur. This paper shows that
+the contagion process is not fully understood without looking at the context
+of each exposure to a contagion within the range of contagions one experiences.
+
+The introductory chapter provides a summary of the research and an explanation of how this
+research contributes to the sociology, social science, and society. Namely, 
+this paper provides important perspectives on search as an agentic process
+and how the micro-level information seeking process of an individual can
+lead to macro-level social norms. I show that information diffusion
+is disrupted when conflicting information and behaviors are simultaneously
+diffusing and therein contribute to research on diffusion, social networks,
+and social norms.

### 2022-03-23 ch1.tex
merge in paper 1 critiques and comments
Final committee edits

@@
-\hypertarget{intro}{%
-\chapter{Introduction}\label{intro}}
-
-% TODO entire dissertation Covid vs COVID vs Coronavirus
+\hypertarget{intro}
+{\chapter{Introduction}\label{intro}}
 
 This dissertation focuses on how people search for information and how people
-rely on this information to inform their health-behaviors and develop social
+rely on this information to inform their health behaviors and develop social
 norms. Information permeates every facet of human society, from the hordes of
@@
 in the recent and ongoing COVID-19 pandemic. While the vaccines against the
-COVID-19 virus prevent severe illness, hospitalization, and death, only 60\% of
-Arizonans over 12 years old are fully vaccinated against the virus. We know that
+COVID-19 virus are effective in preventing severe illness, hospitalization, 
+and death, only 60\% of Arizonans over 12 years old \citep{owid}
+are fully vaccinated against the virus. We know that
 people exposed to misinformation are much less likely to receive vaccinations
@@
 timely social implications for Arizona and the United States. I
-uncovers how norms are created during periods of norm uncertainty and builds the
+uncover how norms are created during periods of norm uncertainty and builds the
 foundation to theorize and test interventions that promote positive norms in
 times of disasters and uncertainty. Specifically, I investigate how local
-diffusion leads to social norms through information search which will have
+diffusion leads to social norms through information search, which will have
 strong implications for the prevention of global polarization and the spread of
-misinformation.
+misinformation, as I now explain.
 
@@
 active agents in their search for information. By looking at how individuals 
-search, I aim to identify pain points and focus areas for future interventions
-in the misinformation process.
+search, I aim to identify focus areas for future interventions
+to counter the misinformation process.
 
-The information that spread to communities in Arizona led to the health
+The information that spread to communities in Arizona contributed to the health
 behaviors exhibited today by Arizonans. While the information spread in various
-ways, like through diffusion and polarization, it contributed to our newly
+ways, including by means of diffusion and polarization, it contributed to our newly
 established norms in the Spring of 2020 and since. By uncovering how norms were
@@
 masses dramatically increased. And for a while, behavioral scientists 
-adopted really simplistic models of persuasion like the hypodermic needle model
-\citep{bineham1988historical}. This simplistic perception of human behavior 
-thought that the media basically injects messages into passive consumers
-who wholly accept the message and are affected by its contents \citep{lasswellpropaganda}.
+adopted really simplistic models of persuasion like the assumption
+that the media influences behavior in a direct, unmediated, and 
+all-powerful way (termed the hypodermic needle model in
+\citet{bineham1988historical}) \citep{lasswellpropaganda}.
 
 A critical turning point in the study of the flow of information was put forth by
-renowned Sociologist Paul Lazarsfeld \citeyearpar{lazarsfeldPeopleChoice1944}.
-Lazarsfeld and others theorized that the media did not directly influence the
+renowned sociologist Paul Lazarsfeld and colleagues Verelson and Gaudet \citeyearpar{lazarsfeldPeopleChoice1944}.
+They theorized that the media did not directly influence the
 masses, but that a "Two-Step Flow" was occurring where "opinion leaders"
@@
 transmitted through personal ties" \citep[p. 1374]{granovetterStrengthWeakTies1973}. 
-Lazarsfeld \citeyearpar{lazarsfeldPeopleChoice1944}'s first study focused on
-politics but follow up studies from \citep{katzPersonalInfluencePart1955} showed
+Lazarsfeld et al's \citeyearpar{lazarsfeldPeopleChoice1944} first study focused on
+politics, but follow up studies by \citet{katzPersonalInfluencePart1955} showed
 that this model matched information flows beyond the political realm. In
@@
 The spread of information has been thoroughly studied from the perspective
-of social networks. Individuals engage with each other and their distributive
+of social networks. Individuals engage with each other and their distributed
 ties to create community contexts where norms, beliefs, and values circulate.
@@
 directed searching by individuals to obtain information.
-\citep{pejtersenDesignComputeraidedUsersystem1984}, a scholar of library and
+\citet{pejtersenDesignComputeraidedUsersystem1984}, a scholar of library and
 information science, theorized that there are 5 strategies for searching for
@@
 channels of mass personal communication facilitating perceptions of interactions
-among users, deriving value primarily from user-generated content.” \citep[][p.
+among users, deriving value primarily from user-generated content” \citep[][p.
 50]{carr2015social}. While an email between colleagues is computer-mediated
@@
 revolutionized the speed and ease at which we can find information. Early web
-search engines allowed information seekers to browse web directories and early
+search engines allowed information seekers to browse web directories, and early
 engines like Yahoo! and Altavista found success using keyword-based search,
@@
 from sources like NetMarketShare, Statista, DuckDuckGo, Yahoo Finance, Google,
-and Pew Research they found that about Around 93\% of all web traffic is
+and Pew Research they found that about 93\% of all web traffic is
 via a search engine and that 78.39\% of all internet searches performed are done
-so using Google. Because computer-mediated information search is instantaneous 
+using Google. Because computer-mediated information search is instantaneous 
 and only requires mobile data or WiFi, there is virtually no cost to seeking
@@
 interchangeably with the term social networks and social integration
-\citep{houseStructuresProcessesSocial1988}, are the emotional, informational,
-and instrumental assistance functions performed between social ties and have
-strong and measurable association with health outcomes
+\citep{houseStructuresProcessesSocial1988}, consisted of the emotional, informational,
+and instrumental assistance functions performed by social ties. Social 
+support has strong and measurable association with health outcomes
 \citep{houseMeasuresConceptsSocial1985, thoitsMechanismsLinkingSocial2011}.
@@
 There has been some research into how different platforms allow for different user 
-experiences or "affordances" \citep{boyd2010social}. For example, \citet{bossetta18} first show
+experiences or "affordances" \citep{boyd2010social}. For example, 
+\citet{bossetta18} first show
 that all social media platforms must provide "tools that are easy to use and 
@@
 informational support will be activated from network ties when the informational
-need is related to forming and deepening social ties
-\citep{baumeister,grieve2013face} but search will be conducted outside of network
-activation when information is needed but an individual does not have an additional cognitive
-need to fill through social interaction. Alternative goals such as identity
-management or relational maintenance
+need is accompanied by or related to a need to form or maintain social ties
+\citep{baumeister,grieve2013face}. For instance, Dani, a young college student, 
+could search on Google to find how to turn iron their dress shirt properly, 
+but instead Dani choses to call their parent(s) and ask the best strategy so their parent(s)
+feels respected and valued and their relationship is strengthened. 
+Conversely, I theorize that search will be conducted outside of network
+activation when information is needed but an individual does not have 
+an additional cognitive need to fill through social interaction. 
+For example, Taylor could ask their neighbor who is a medical professional about 
+the newfound headaches they've been experiencing, but every time they talk to their
+neighbor they ask for help cleaning their gutters, which is too much work; Taylor
+instead may choose to ask the Facebook group they're a part of to gain information.
+Alternative goals such as identity management or relational maintenance
 \citep{brashersInformationSeekingAvoiding2002} need to be balanced and may also
@@
 search for information. However, in situations of rapidly changing norms,
-uncertainty is prevalent. This dissertation will also focus on developing
+uncertainty is prevalent. This dissertation also focuses on the development of
 new social norms in situations of uncertainty about how to behave. 
@@
 behavior of others to set their own norms for behavior \citep{alvarez2018,
-horneNormsIntegratedFramework2020}. This project will investigate how search
+horneNormsIntegratedFramework2020}. This project investigates how search
 contributes to the development of said spontaneous norms.
@@
 \citep{horneNormsIntegratedFramework2020}. One of the main critiques of the
-consequentialist argument is that it relies on the same interpretation of the perceived action
+consequentialist argument is that it relies on the same interpretation 
+of the perceived action
 by all parties of what is harmful and beneficial. The Relational argument 
@@
 theorize that individuals strategically look towards other high-status
-individuals, institutions, and perform regimented searches to establish for
+individuals and institutions, and perform regimented searches to establish for
 themselves the behavior that is compatible with other cognitive associations
@@
 new norms in health behaviors form, I first provide an outline of the 
-information push and pull process in figure \ref{fig:concept-map}. After 
+information push and pull process in Figure \ref{fig:concept-map}. After 
 being exposed to new information, an actor can choose to further investigate
@@
 This dissertation uses three articles to investigate different parts of
-the theoretical framework (figure \ref{fig:concept-map}).
+the theoretical framework (Figure \ref{fig:concept-map}).
 The dissertation is divided into three parts, with Article 1 focusing 
@@
 
-Computational social science and other disciplines are quick to adopt new
+Computational social science and social science disciplines are quick to adopt new
 sources of digital trace data for use in academic research. In this article, I
-examine the validity of one of these new sources, Google Search Trends. I
+examine the criterion validity of one of these new sources, Google Search Trends. I
 validate how Google Trends can be used to demonstrate three different cases,
-namely attitudes, disease prevalence and political preferences using eight %TODO double check number
+namely attitudes, disease prevalence and political preferences using five
 different validated data sources. This paper asks, "How can we operationalize
@@
 and the total model interpretability remained low, even when controlling for
-demographic variables. This article shows that there is no external validity of
-Google Trends for these uses and social scientists will find no replacement for
+demographic variables. This article shows that there is no external or 
+criterion validity of Google Trends for these uses and social scientists will find no replacement for
 high quality survey data with Google Trends. Instead, we must only use 
@@
 support and uses and gratifications theory, I investigate the factors associated
-with each information seeking vehicle: personal connection,
+with each information seeking modality: personal connection,
 doctor, social networking site, online forum, and online search engine. I use
@@
 across populations?
-  \item How does the information search vehicle utilized affect COVID-19 Vaccination uptake? 
+  \item How does the information search modality utilized affect COVID-19 Vaccination uptake? 
 \end{itemize}
@@
 as I hypothesize based on uses and gratifications theory. I find evidence that
-the categorizations of vehicles queried in this survey are indeed conceptually
-different from each other and that the utilization of different vehicles varies
+the categorizations of modalities queried in this survey are indeed conceptually
+different from each other and that the utilization of different modalities varies
 by demography and information exposure points. Finally, I find that different
-exposure points and information search vehicles hold real world consequences
+exposure points and information search modalities hold real world consequences
 through their associations with COVID-19 vaccination rates and intentions, as
 information from a doctor increases the COVID-19 vaccination uptake while
-receiving information from a Social Networking Site like Facebook or Twitter was
+receiving information from a social networking site like Facebook or Twitter was
 associated with lower odds of vaccination.
@@
 governing health behaviors in cases of extreme uncertainty using the cases of
-both stay-at-home rates and vaccination rates as responses to public health recommendations to mitigate the COVID-19 pandemic. Using theories of associative diffusion and the integrated
-theoretical framework of norms, I test models of behavioral adaption to public health
-recommendations as well as patterns of complex social contagion using linear
+both stay-at-home rates and vaccination rates as responses to public health recommendations to mitigate the COVID-19 pandemic. Using theories like associative diffusion
+and the integrated theoretical framework of norms, I test models of behavioral adaption
+to public health recommendations and patterns of complex contagion (the need for
+repeated exposures to a something novel for it to diffuse) using linear
 mixed effects models.
@@
 a novel moderating effect of signal discordance, the contextual diversity of
-signals received by an ego. This paper shows that the contagion process is not
-fully understood without looking at the context of each exposure point within the
-range of exposures one experiences.
+signals received by an ego. If there is diversity in the information received
+by an ego, contagion is less likely to occur. This paper shows that the contagion 
+process cannot be not fully understood without looking at the context of each
+exposure to a contagion within  within the range of contagions one experiences.
 
@@
 % search as an agentic process
-This research will make contributions to multiple subfields and literatures. 
+This research makes contributions to multiple subfields and literatures. 
 First and foremost, these articles contribute to the sociological literature.
@@
 diffusion when combined with cognitive perspectives like that of
-Goldberg and Stein (2018). How people search for information determines
+\citet{goldbergSocialContagionAssociative2018}. How people
+search for information is a strong determinant of 
 the information that they find. The information they uncover is filtered
@@
 through social network ties theoretically will uncover potentially
-different information than that would be uncovered through online web
+different information than would be uncovered through online web
 search and will change how people are organized and how people behave.
-\hyperlink{paper-2}{Article 2} importantly shows that 
-the vehicles used to search for information have a significant impact on the choice to get vaccinated against COVID-19, a real-world consequence to the minutiae of individual information search.
+\hyperlink{paper-2}{Article 2} Article 2, for instance, demonstrates that 
+the choice to receive a COVID-19 vaccine is impacted by how
+individuals search for information on the vaccine. 
+This is a real-world consequence to the variation in the individual information
+search process.
 
@@
 lead to macro-level outcomes?" With the exponentially growing size of digital-trace data
-that is available, it is important to not only uncover the external validity of 
+that is available, it is important to not only uncover the external and criterion validity of 
 the data and correspondence to real world behaviors (see \hyperlink{paper-1}{Article 1})
-but also important to understand the social forces that leads to the big data. 
-One of the contributions of \hyperlink{paper-2}{Article 2} dives deep
+but also important to understand the social forces that lead to the big data. 
+One of the contributions of \hyperlink{paper-2}{Article 2} is to dive deep
 into this question, uncovering why some people choose to use web search engines over other
-information-vehicles. These papers are a first step in validating and establishing
+information search modalities. These papers are a first step in validating and establishing
 a deeper understanding of who the users are that contribute to macro-level aggregate trends.
@@
 % social networks / diffusion
-This dissertation will also have implications for the study of social
+This dissertation also has implications for the study of social
 networks and diffusion. \citet{centolaComplexContagionsWeakness2007}

### 2022-03-23 paper1.tex
Final committee edits

@@
 \chapter{Digital Trace Data as Indicators of the Social World: Validating Google Trends for use in Scientific Research}\label{paper-1}}
-
-% TODO: should I add in some figures to outline these relationships?
 
@@
 Computational social science and disciplines such as sociology and
-political science are quick to 
-adopt new sources of digital trace data for use in academic research. 
+political science are often quick to adopt new sources of digital 
+trace data for use in academic research. 
 In this article, I examine the validity of Google Search Trends 
 as potential indicators of three different cases, namely attitudes, 
-disease prevalence and political preferences using eight %TODO double check number
+disease prevalence and political preferences using five
 different validated data sources. I use Pearson and Repeated Measures Correlations 
@@
 
-% TODO define big data sources , are we just talking about digital trace data?
-what is that?
-Define, even if as footnote.
-Are 10K pages of field notes big data?
-Admin data with millions of observations but no text?
-
-% TODO Define digital trace data. I  assume remnants of digital activity archived by corporate or state entities.
-
-New big data sources have led to vast possibilities for social science
+New sources of digital trace data have led to vast possibilities for social science
 research because they are bigger, cheaper, and already available 
 \citep{kingEnsuringDataRichFuture2011,lazerComputationalSocialScience2009,salganikBitBitSocial2017}.
+Digital trace data are the expansive volumes of information that are now available with the
+introduction and widespread adoption of the internet and include sources such as  
+social media sites, search data, blogs, adminstrative data on websites, the internet 
+archives, etc. In short, digital trace data are the crumbs that are left as a person
+peruses and interacts in digital spaces. Scholars have noted that these data provide
+many new research avenues for social scientists because they are always on, non-reactive to
+a researcher's observation, and very often captual social interactions and relationships,
+but warn they can be Inaccessible, Non-Representative, and be prone to drifting due to
+algorithmic confounding \citep{salganikBitBitSocial2017}.
 Before overenthusiastically embracing these
@@
 rare and costly. However, \citet{blumenstockPredictingPovertyWealth2015} go to
-great lengths to demonstrate that their operationalization of the cell
+great lengths to demonstrate that their use of the cell
 phone data creates a reliable and valid construct; few social science
@@
 Social scientists have yet to widely utilize Google Search Trends as a source of big data.
-Google Trends is an open data resource
-% TODO Does this just mean free and publicly available?
-
+Google Trends is a free and publicly accessible data resource
 provided by Google, a major internet search
@@
 scientists outside of economics have used this resource \citep[see][for examples]{choi2012predicting, jun2018ten,da2011search}.
-This paper provides evidence-based guidelines for social scientist who would use these resources in their toolboxes on how we can operationalize
-% TODO: operationalize debated
-Google Search Trends
+This paper provides evidence-based guidelines for social scientist who would use these resources in their toolboxes on how we can triangulate Google Search Trends
 as validated indicators and under what circumstances.
@@
 US cases rates of COVID-19 from The New York Times \citeyearpar{covid_data},  
-and political indicators from the historical US Presidential Election results \citeyearpar{pres_data}, 
-and the American National Election Survey \citeyearpar{anes_data}. This paper will contribute guidance for creating standards of how to use Google
+and political indicators from the historical US Presidential Election results \citeyearpar{pres_data}.
+% , and the American National Election Survey \citeyearpar{anes_data}.
+This paper will contribute guidance for creating standards of how to use Google
 Trends for social research, and identify potential pitfalls that can compromise the 
-analysis including 1. a lack of ecological validity, 2: poor 
-% TODO finish this sentence, This is the framework I would use for identifying ‘best practices.’ I would personally just say here is how this can go wrong, here is how you avoid it, and next steps.
-I could see doing a critical spin off for a place like big data and society.
+analysis including the focus of this paper, which shows that Google Trends has a
+lack of ecological validity.
 
@@
 I will use three categorizations of ways I propose Google Trends could
-be operationalized for social scientific usage. First, I test Google
-Trends as an operationalization of attitudinal indicators. 
+be utilized for social scientific usage. First, I test Google
+Trends as an indicator of attitudinal indicators. 
 After \citet{bailCulturalEnvironmentMeasuring2014}'s call for
@@
 Extending into social networks and culture, \citet{bailPrestigeProximityPrejudice2019}
-even used Google trends to measure how 'culture' spreads around the globe.
-% TODO I’ll just say, while I think there is utility here, it is a very particular aspect of culture in a specific populations.
-I think we are still in the era where the bigness and newness can overshadow truth value.
+even used Google trends to measure how they saw 'culture' spreads around the globe
+through the proliferation of search terms.
+
 \subsection{Google Trends and research on health behaviors}
@@
 Google Search Trends have been utilized to estimate disease prevalence
-and population health in journals like the Journal of
-Medical Internet Research. While much of this research has focused on
-% TODO I think this may erode your point about increasing legitimacy.
-If you said JAMA or NEJM, that would be a stronger example.
-If not, I’d just point to some specific projects then say new journals have emerged but that does not indicate mainstream acceptance…
+and population throughout the health sciences. While much of this research has focused on
 the COVID-19 pandemic \citep{jimenez_etal20, jimenezCOVID19SymptomGoogle2020, limEstimatingInformationSeekingBehaviour2020, mavraganiCOVID19PredictabilityUnited2020, nguyenGoogleTrendsAnalysis2020, todorovaInternetBasedData2021, mingUnderstandingHealthCommunication2021},
@@
 Elections relate to attention measured by search traffic.
-\citet{prado-romanGoogleTrendsPredictor2020} demonstrate how Google Search trends
+\citet{pradoromanGoogleTrendsPredictor2020} demonstrate how Google Search trends
 successfully predicts presidential election results in both the United
@@
 how Google data can help elucidate governments' approval in Latin
-America \citep{montoyaUsingGoogleData2020}. 
-% TODO what are the results of these papers? do they show promise?
+America \citep{montoyaUsingGoogleData2020}. Overall, the papers 
+cited here find favorable relationships between Google Trends and
+voting outcomes and claim that it is also a valid measure of public attention.
 
@@
 non-negligible issues with the measurement of Google Trends, pointing to 
-errors within the purview of accuracy, completeness, consistency, and validity
-% TODO I know it is basic stats, but I would provide a footnote explaining each of your terms. Here, these line up with mainline stats but disciplines vary.
-
-\citep{KarrDataQuality}. \citet{cebrian_domenech22} point not only to 
+errors within the purview of accuracy, completeness, consistency, and validity,
+as outlined in \citet{KarrDataQuality}.  
+% I know it is basic stats, but I would provide a footnote explaining each of your terms. Here, these line up with mainline stats but disciplines vary.
+ \citet{cebrian_domenech22} point not only to 
 meta issues like the lack of transparency into the sampling methods 
@@
 in the data provided by the Google Trends API for the same 
-researcher-entered query, pointing 
-to likely internal process used by Google to sample their data to compute the trends.
+researcher-entered query, pointing to likely internal process 
+used by Google to sample their data to compute the trends.
 These authors show that the variability of the results over time for the same query
-can alter the results of analysis and forecasting significantly; they propose
-caution in the use of the digital trace data for other researchers until
-further research can determine the cause for the inaccuracies. 
-% TODO Yes, big issue.
-But, it is also seen in machine learning, survey administration, etc.
-I’d assume one solution for dealing with fiddly output is to just sample repetedly and do some sort of average, perhaps with a correction if the direction of the error is non random.
+can alter the results of analysis and forecasting significantly. While the 
+issue of unreliability isn't unique to the Google Trends API, 
+\citet{cebrian_domenech22} propose 
+caution in the use of this digital trace data for other researchers until
+further research can determine the root cause for the inaccuracies.
+% Yes, big issue. But, it is also seen in machine learning, survey 
+% administration, etc. I’d assume one solution for dealing with fiddly 
+% output is to just sample repetedly and do some sort of average, 
+% perhaps with a correction if the direction of the error is non random.
 
@@
 population's \textit{attention} to a search query. Because
-% TODO I’d also say, the population is examined differently. It is really a population of action remnants being used to get at a population of people, which is presumed to be represented online.
+% I’d also say, the population is examined differently. It is really a population of action remnants being used to get at a population of people, which is presumed to be represented online.
 searches can be done with many different intentions, such as 
@@
 performed, not whether it indicated a digital wink or twitch \citeyearpar{geertz1973thick}.
-%TODO CITE above, For a soc audience some sort of reference to the dilemma of interpretation would be interesting.
+% For a soc audience some sort of reference to the dilemma of interpretation would be interesting.
 
@@
 
-%TODO There are a lot of validities here. Be precise and explain what you are concretely examining. define which validity here 
-To investigate the construct and criterion validity of the use of Google Trends
-in these three areas, I gathered geo-located social science data across multiple
+To test how well Google Trends can be used to indicate other measures, 
+I use various tests to validate the criterion validity of the trends. 
+Criterion validity measures how well one measure, an operationalization of a 
+specific construct, is able to predict a theoretical representation 
+of the construct — the criterion. For this article, I employ 
+concurrent criterion validity which looks at how Google Trends can
+predict various criterions in the same time scale. 
+I gathered geo-located social science data across multiple
 sources to address the three areas of inquiry for this paper.  Table
@@
 
-% TODO create a  table People will want to see a table of variables, their prompts, and ranges.
+%  create a  Table People will want to see a Table of variables, their prompts, and ranges.
 
@@
 availability in testing as well as different community propensity to test
-% TODO Also blatant political interference in some places, which is probably worth acknowledging.
+%  Also blatant political interference in some places, which is probably worth acknowledging.
 \citep{gu22, cdc20a} However, it is the best measure we have of actual case rates
@@
 
-Finally, I evaluate Google Trends as an operationalization of political
+Finally, I evaluate Google Trends as an indicator of political
 attitudes by first looking at actual voting outcomes in historical US
@@
 
-In addition, I use data on political opinions from the American National
-Election Survey 2020 Time-Series Study \citep{anes_data}. This data is paired with
-restricted data provided by ICPSR, the Inter-university Consortium for Political
-and Social Research, which contains the geo-ids of the 5,441
-survey respondents. The study interviewed respondents in a pre-election survey
-that was conducted between August 18, 2020, and the day of the US Presidential
-election, November 3, 2020.  %TODO
-I will write about actual variables when my data extract request is approved.
+% In addition, I use data on political opinions from the American National
+% Election Survey 2020 Time-Series Study \citep{anes_data}. This data is paired with
+% restricted data provided by ICPSR, the Inter-university Consortium for Political
+% and Social Research, which contains the geo-ids of the 5,441
+% survey respondents. The study interviewed respondents in a pre-election survey
+% that was conducted between August 18, 2020, and the day of the US Presidential
+% election, November 3, 2020.  %TODO
+% I will write about actual variables when my data extract request is approved.
 
-% TODO: WHICH VARIABLES
-% TODO: VARIABLE SCALE
+% % TODO: WHICH VARIABLES
+% % TODO: VARIABLE SCALE
 
@@
 
-In addition to specific measures of interest, I also gathered vadata on potentially
+In addition to specific measures of interest, I also gathered data on potentially
 confounding variables. The first Seven of these
@@
 association for paired measures across time and counties. Results of these 
-correlations are in table \ref{tab:corr-results}.
+correlations are in Table \ref{tab:corr-results}.
 
@@
 I employ multiple linear regression
-(for cross-sectional datasets) and random intercept hierarchical linear models
+(for cross-sectional datasets) and fixed effect hierarchical linear models
 \citep{pinheiro_etal21} (for longitudinal datasets) to identify the strength of
-relationships across locales.
-%TODO This all sounds fine to me, but I’m less up to date on model specification and nesting, so I’m not the best to ask.
-I would also specify why these models are appropriate in one sentence max because methods people about these things.
-Also,they may have sampling assumptions the data violate so clarifying that that is not an issue may be necessary.
-I include location metadata like county population size,
+relationships across locales. Multiple linear regression is appropriate because 
+the cross-sectional data are non-nested which a continous outcome. Hierarchical
+linear models are necessary to control for the between-subject variation 
+in the longitudinal models. Fixed models are appropriate because 
+they extract the between group-differences from the model to allow the reader to 
+focus on the overall effects of each variable. 
+In these models, include location metadata like county population size,
 broadband rates, and median income to adjust for potentially
@@
 while others did not.
-% TODO Why? To have a standardized net impact? Sociologists usually have a strong negative reaction to this. In contrast, in psych they do this with everything.  
 For linear regression models, I normalize independent
-variables; in other words, variables have been centered and scaled to have a mean of zero and
-standard deviation of one. Results of these models are in tables \ref{tab:vacc_hes_analysis} through \ref{tab:pres_2020_analysis}.
+variables so that each variable across each model is on the same scale and can be compared. 
+In other words, variables have been centered and scaled to have a mean of zero and
+standard deviation of one. Results of these models are in Tables \ref{tab:vacc_hes_analysis} through \ref{tab:pres_2020_analysis}.
 
@@
 correlated with these attitudes. When running these
-correlations in multiple linear regression (see the results in table
+correlations in multiple linear regression (see the results in Table
 \ref{tab:vacc_hes_analysis}), I see an $r^2$ of 0.233 (Model 1),
@@
 \input{tables/paper1/vacc_hes_analysis}
+\begin{figure}[h]
+{\centering \includegraphics[width=0.8\linewidth]{figs/paper1/vacc_hes_plot-1.pdf}}
+\caption{Vaccine hesitancy by each Google Trend with a fitted linear regression line}\label{fig:vacc_hes_plot}
+\end{figure}
 
@@
 \input{tables/paper1/mask_analysis}
+\begin{figure}[h]
+{\centering \includegraphics[width=0.8\linewidth]{figs/paper1/mask_plot-1.pdf}}
+\caption{Rare mask usage by each Google Trend with a fitted linear regression line}\label{fig:mask_plot-1}
+\end{figure}
 
@@
 include the three trends in random intercept hierarchical linear models. Model 1
-of table \ref{tab:covid_analysis} indicates that the trends themselves are able
+of Table \ref{tab:covid_analysis} indicates that the trends themselves are able
 to explain about 20\% of the variation in COVID-19 rates ($r^2$ = 0.201). Few
@@
 \input{tables/paper1/covid_analysis}
+\begin{figure}[h]
+{\centering \includegraphics[width=0.8\linewidth]{figs/paper1/covid_plot-1.pdf}}
+\caption{Covid case rate for 09-14-2020 by each Google Trend with a fitted linear regression line}\label{fig:covid_plot-1}
+\end{figure}
 
@@
 negligible. I introduce these trends into a random intercept model to control
-for inter-group variation over time in table \ref{tab:suicide_analysis}. While
+for inter-group variation over time in Table \ref{tab:suicide_analysis}. While
 table \ref{tab:suicide_analysis} model 1 reveals a statistically significant relationship
@@
 \input{tables/paper1/suicide_analysis}
+\begin{figure}[h]
+{\centering \includegraphics[width=0.8\linewidth]{figs/paper1/suicide_plot-1.pdf}}
+\caption{Suicide death rate for 2019 by each Google Trend with a fitted linear regression line}\label{fig:suicide_plot-1}
+\end{figure}
 
@@
 
-In table \ref{tab:pres_2016_analysis}, I outline the results for the model
+In Table \ref{tab:pres_2016_analysis}, I outline the results for the model
 predicting the county percentage of votes for Hillary Clinton. Model 1
@@
 2020 election and predicts the percentage of votes for Joe Biden. While this
-model is analogous to those in table \ref{tab:pres_2016_analysis}, this
+model is analogous to those in Table \ref{tab:pres_2016_analysis}, this
 model 1 demonstrates how unrelated Google Trends can be from actual outcomes. In
@@
 political support.
+
+\begin{figure}[h]
+{\centering \includegraphics[width=0.8\linewidth]{figs/paper1/pres_plot-1.pdf}}
+\caption{Presidential voting outcomes for 2016 and 2020 by each Google Trend with a fitted linear regression line}\label{fig:pres_plot-1}
+\end{figure}
 
@@
 
-This paper provides a critique of Google Trends for use in Social Science. 
+This paper provides a test of the criterion validity of Google Trends for use in Social Science. 
 I failed to find correlation between the Google Trends and their 
@@
 In the case of Google Search Trends, precaution is warranted.
-
-% While I would like to be able to join \citet{bailCulturalEnvironmentMeasuring2014} 
-% in encouraging social scientists to pursue more research with the many new sources of big data, 
-% I emphasize that testing out data to verify what it actually corresponds to is an essential step 
-% to making impactful research as a discipline going forward.
-
-% TODO I like this, but it is out of place tone-wise.
-It fits better in a critical piece or blog.
-I’d say something like in these cases, GT fails validation tests, and caution future research is warranted.
-Future research should determine its utility using empirical criteria rather than a prior assumptions.
-Triangulation, using various data sources, is necessary.
-
-% A stronger case, if you wanted to go in calling out the big data evangelicals, would be to show that their own work does not replicate or those measures are invalid.
-
-% Some of this is based in logical errors and some is based in the politics, and there are different ways to treat that.

### 2022-03-23 paper2.tex
merge in paper 1 critiques and comments
Final committee edits

@@
 support and 2) uses and gratifications theory I investigate the factors associated
-with each vehicle type when on information-seeking vehicle: personal connection,
+with each modality type when on information-seeking modality: personal connection,
 doctor, social networking site, online forum, and online search engine. Using
@@
 search is more utilized than seeking social support from personal network
-connections or health professionals. I find evidence that the vehicles queried
+connections or health professionals. I find evidence that the modalities queried
 in this survey are conceptually different and that the utilization of different
-vehicles varies by demography and information sources. Finally, I find that
-different sources of information exposure and information search vehicles hold real
+modalities varies by demography and information sources. Finally, I find that
+different sources of information exposure and information search modalities hold real
 world consequences through their associations with COVID-19 vaccination rates
 and intentions, as information from a doctor increased the COVID-19 vaccination
-uptake while receiving information from a Social Networking Site like Facebook
+uptake while receiving information from a social networking site like Facebook
 or Twitter was associated with lower odds of vaccination.
@@
 \hypertarget{intro-1}{%
-\section{Intro}\label{intro-1}}
+\section{Introduction}\label{intro-1}}
 
@@
 \citep{johnsonOnlineCompetitionPro2020, broniatowski_etal20}.
-% TODO cite something else here
 
-The lack of research in which vehicles are likely to be chosen when an
+The lack of research in which modalities are likely to be chosen when an
 individual faces a need for information makes it difficult for policy makers to
@@
 I use the case of information around COVID-19 vaccinations to explore the
-variation of usage of information search vehicles. In doing so, I seek to answer
+variation of usage of information search modalities. In doing so, I seek to answer
 how computer-mediated or interpersonal information-seeking strategies vary
@@
 answers two research questions: (1) How do computer-mediated or interpersonal information-seeking
-strategies vary across populations? (2) How does the information search vehicle utilized 
+strategies vary across populations? (2) How does the information search modality utilized 
 affect COVID-19 Vaccination uptake?
@@
 modern human life, it makes sense that performing online search has become one
-of the most convenient vehicles for information search. Small
+of the most convenient modalities for information search. Small
 \citet{smallSomeoneTalk2017} showed that Graduate students often
@@
 
-There are three computer-mediated vehicles I consider for this analysis: online
+There are three computer-mediated modalities I consider for this analysis: online
 search engines like Google or Bing, posting questions on online forums like
@@
 help us to theorize that the psychosocial needs like identity management or relational
-maintenance of an individual may influence their chosen information search vehicle: 
+maintenance of an individual may influence their chosen information search modality: 
 when the informational need is related to forming and deepening social ties search 
@@
 are non-nested, cross-sectional data with binary independent variables. In Table \ref{tab:table-model-1}
-\footnote{All tables in this paper were created with the modelsummary package in \texttt{r} 
+\footnote{All Tables in this paper were created with the modelsummary package in \texttt{r} 
 \citep{modelsummary}},I fit a logistic regression model predicting
@@
   Coefficient, I utilize the Psych \texttt{r} package \citep{psych}} I then investigate the
-associations between my predictors and the five information search vehicles by
+associations between my predictors and the five information search modalities by
 modelling a series of logistic regressions in Table \ref{tab:table-model-2}.
@@
 {\centering \includegraphics[width=0.8\linewidth]{figs/paper2/plot-model-1-1}}
-\caption{What predicts someone intentionally searched for information, Plot of Coefficients?}\label{fig:plot-model-1}
+\caption{What predicts someone intentionally searched for information? Plot of Coefficients}\label{fig:plot-model-1}
 \end{figure}
@@
 analysis predicting whether someone sought information about COVID-19. These
-initial results suggest similar results for each vehicle of information
+initial results suggest similar results for each modality of information
 delivery: each mode of receiving information whether from a doctor, a person,
@@
 
-\hypertarget{information-search-vehicles}{%
-\subsection{Information Search Vehicles}\label{information-search-vehicles}}
+\hypertarget{information-search-modalities}{%
+\subsection{Information Search Modalities}\label{information-search-modalities}}
 
@@
 \ref{tab:table-1-ind} reveals differences in the prevalence of usage of the
-various information-seeking vehicles: Around 40\% of the sample has inquired for
+various information-seeking modalities: Around 40\% of the sample has inquired for
 information from a doctor, a person, or using online search tool (44\%, 42\%, 41\%), while my
-respondents used vehicles like online forums (27\%) and social networking sites (18\%)
+respondents used modalities like online forums (27\%) and social networking sites (18\%)
 to seek out information at significantly lower rates.
@@
 To investigate how each
-Information Search Vehicle are related to each other using the Phi Coefficient
-($\phi$) of binary association between each Information Search Vehicle pair.
+Information Search modality are related to each other using the Phi Coefficient
+($\phi$) of binary association between each Information Search modality pair.
 The Phi coefficient can be interpreted like a correlation coefficient, with
@@
 (Warrens 2008). Table \ref{tab:model-2-phi} shows the results of these
-coefficients. Out of the five information search vehicles investigated, there is
-evidence that the vehicles are distinctly different concepts because most
+coefficients. Out of the five information search modalities investigated, there is
+evidence that the modalities are distinctly different concepts because most
 coefficients fall under 0.3, the general cutoff for correlation
 coefficients to indicate a relationship. There does seem to be a relationship
-between Online Forums and Social Networking Sites, possibly due to an
+between Online Forums and social networking sites, possibly due to an
 individual's latent propensity to use online networks over in-person networks. These
-coefficients indicate a weak relationship between any two vehicles of
+coefficients indicate a weak relationship between any two modalities of
 information search and that respondents in my sample utilize each of these a
@@
 
-I find that indeed the most common vehicles are 
+I find that indeed the most common modalities are 
 asking a doctor, asking a friend, and asking a search engine which confirms
-Hypthesis \ref{hyp:drgooglefriend}. However, because the vehicles 95\% confidence intervals 
+Hypthesis \ref{hyp:drgooglefriend}. However, because the modalities 95\% confidence intervals 
 in Table \ref{tab:table-1-ind}
@@
 
-I conduct a separate logistic regression for each search vehicle in Table \ref{tab:table-model-2}. 
+I conduct a separate logistic regression for each search modality in Table \ref{tab:table-model-2}. 
 Modeling each response as a separate formula is useful for interpretation, but
@@
 can, however, use the direction and significance of the coefficients to draw
-conclusions about these different forms of information search vehicles.
+conclusions about these different forms of information search modalities.
 
@@
 6.97 times more likely to seek out more information from their doctor than those who had
-not (\emph{p} \textless{} 0.001). However, receiving information from other vehicles also
+not (\emph{p} \textless{} 0.001). However, receiving information from other modalities also
 increased the odds of seeking out information from medical professions. Those who
@@
 Searching for information using an online search engine such as Google or Bing
-is theoretically the search vehicle with the least amount of social or cognitive
-friction. Our descriptive statistics showed that not everyone used this vehicle,
+is theoretically the search modality with the least amount of social or cognitive
+friction. Our descriptive statistics showed that not everyone used this modality,
 with only 41\% of our sample (See Table \ref{tab:table-1-ind}) having sought
@@
 though to varying magnitudes (Doctor: 1.54 odds; Person: 1.44 odds; News or Television: 2.98 odds; 
-Social Networking Site: 3.57 odds; Online Forum: 2 odds). I also find that older respondents
+social networking site: 3.57 odds; Online Forum: 2 odds). I also find that older respondents
 were more likely to search online, with each addition year aged to yield 3\%
@@
 \textbf{less likely} to choose to get vaccinated than those who received no information through
-that vehicle (\emph{p} \textless{} 0.001). However, I did find that those who reached out to
+that modality (\emph{p} \textless{} 0.001). However, I did find that those who reached out to
 family or friends with their concerns were 77\% more likely to become vaccinated 
@@
 information search are and begin a line of research inquiry that investigates
-the factors associated with each different vehicle. Finally, I also uncovered
+the factors associated with each different modality. Finally, I also uncovered
 how the different sources of information exposure and information search
-vehicles hold real world consequences through their associations with COVID-19
+modalities hold real world consequences through their associations with COVID-19
 vaccination rates and intentions.
@@
 how individuals seek information. First, I find that the different information
-seeking vehicles queried in this survey are conceptually different and that the
+seeking modalities queried in this survey are conceptually different and that the
 utilization of different varies by demographic and information exposure source. 
@@
 seeking out information from an expert. Another important finding is that if you
-received information from a Social Networking Site like Facebook or Twitter, you
+received information from a social networking site like Facebook or Twitter, you
 were less likely to query Online Forums like Reddit or Facebook Groups; this may
@@
 substitute sources of information and those who were satisfied with the
-information they received on a Social Networking Site didn't have the need to
+information they received on a social networking site didn't have the need to
 seek out more information. Finally, the ethnoracial variations exhibited in
@@
 non-Hispanics. The internal variations between the different information search
-vehicles hint at different user profiles and may have major repercussions on the
+modalities hint at different user profiles and may have major repercussions on the
 quality of information they find and who is exposed to poor quality information.
@@
 United States, it is important to uncover what relationship the different
-sources of information exposure and information search vehicles for COVID-19 vaccinations
+sources of information exposure and information search modalities for COVID-19 vaccinations
 are associated with compliance with public health recommendations. Table
 \ref{tab:table-model-3} demonstrated just how these different sources of information 
-exposure and information search vehicles are associated with real world
+exposure and information search modalities are associated with real world
 consequences through COVID-19 vaccination rates and intentions. The first
@@
 
-Overall, this research project is important because the vehicles used in
+Overall, this research project is important because the modalities used in
 information search impacts the information and quality of information found. By

### 2022-03-23 paper3.tex
Final committee edits

@@
 mixed effects models. These models show that complex contagion is a valid
-framework for the social contagion of new norms during COVID-19. However, I find
-important moderating effect of signal discordance, the contextual diversity of
-signals received by an ego.
-
-% need to explain a little bit more what diversity of signals etc means (since this is the first look) 
-% what else needs to be said here to properly convey the importance and impact of this finding?
+framework for the social contagion of new norms during COVID-19. Importantly, I
+find a novel moderating effect of signal discordance, the contextual diversity
+of signals received by an ego. In other words, if there is diversity in the
+information received by an ego, contagion is less likely to occur. This article
+is an important contribution to literature on diffusion and social networks, as
+it shows that the contagion process cannot be not fully understood without
+looking at the context of each exposure to a contagion within  within the range
+of contagions one experiences.
 
 Keywords: Social Networks, Social Norms, Health Behavior, Diffusion, Contagion
-
-% TODO
-\citep{mirbabaie_etal20, ternullo22}
 
@@
 disease or to learn simple bits of information.
-Centola and Macy \citeyearpar{centolaComplexContagionsWeakness2007}'s large contribution was the theorizing
-of complex contagions, those that require ``independent affirmation or
+Centola and Macy \citeyearpar{centolaComplexContagionsWeakness2007}'s large contribution
+was the theorizing of complex contagions, those that require ``independent affirmation or
 reinforcement from multiple sources'' (p. 703) and is not based on the number of
@@
 of another county-ego if the county-ego receives highly discordant signals, as
-seen in figure \ref{fig:dag}.
+seen in Figure \ref{fig:dag}.
 
@@
 distancing or vaccination uptake \emph{meant} were spreading between populations of
-individuals. Moreover, as \citet{houghton20} outlines, diffusants - the things that are
+individuals. Moreover, as \citet{houghton20} outlines, diffusants, the things that are
 diffusing through a population, are not independent of each other \citep{mason_etal07}. 
-When we take into account the interdependence between different beliefs that are diffusing, such as COVID-19 is a hoax, social distancing saves
+When we take into account the interdependence between different beliefs that are 
+diffusing, such as COVID-19 is a hoax, social distancing saves
 lives, the COVID-19 vaccine includes a microchip to control your thoughts, and lockdown
@@
 these various diffusants become associated together into structures of belief
-through schemas of perception \citep{houghton20}.
-While this cognitive theory of cultural variation is difficult to test, the theory it supplies provides a solid framework for how behavioral norms formed during the pandemic.
+through schemas of perception \citep{houghton20}. While this cognitive theory of
+cultural variation is difficult to test, the theory it supplies provides a solid
+framework for how behavioral norms formed during the pandemic.
 
-The figure above illustrates how I interpret associative diffusion will impact
-stay-at-home and vaccination rates in times of unsettled norms. An
-individual enters this framework when they realize they don't have a normative
+Individuals look to norms to regulate behavior, avoid
+deviance, and to maintain order \citep{horneNormsIntegratedFramework2020, shepherdStructurePerceptionHow2017}. When they realize they don't have a normative
 set of responses in their cultural toolkit to respond to an unfamiliar situation
-they are presented with. Individuals look to norms to regulate behavior, avoid
-deviance, and to maintain order \citep{horneNormsIntegratedFramework2020, shepherdStructurePerceptionHow2017}; when they don't have a normative behavior
-to follow (or rebel against), individuals look to the other sources in their
+they are presented with, individuals look to the other sources in their
 ``community'' to mimic behavior, such as high-status individuals, institutions,
 and members of their social network. I theorize that individuals look towards
-their physical community, to their social network, popular media (which may
-include government and science recommendations), established norms that they may
-find online through search, and to the real threat of infection (what would
-happen if I do nothing about this norm). Following both the Integrated
-Theoretical Framework of Norms \citep{horneNormsIntegratedFramework2020} and
-associative diffusion \citep{dellapostaWhyLiberalsDrink2015, goldbergSocialContagionAssociative2018}, I theorize that individuals interpret
+their physical community, to their social network, popular media, established
+norms that they may find online through search, and to the real threat of 
+infection (what would happen if I do nothing about this norm). 
+Following both the Integrated Theoretical Framework of Norms 
+\citep{horneNormsIntegratedFramework2020} and
+associative diffusion \citep{dellapostaWhyLiberalsDrink2015, goldbergSocialContagionAssociative2018},
+I theorize that individuals interpret
 signals from their ``community'' through their cognitive biases and behavioral
@@
 recommendations against religious ideologies.
-Furthermore, as COVID-19 has become a politically polarizing issue, conservative
-ideology and a general mistrust of ``big government'' \citep{frank2007, gauchat2008} are likely to lead to resistance to the
-government and scientific guidance.
+Furthermore, as COVID-19 has become a politically polarizing issue \citep{ternullo22},
+conservative ideology and a general mistrust of ``big government'' \citep{frank2007, gauchat2008} 
+are likely to lead to resistance to the government and scientific guidance.
 
@@
 {\centering \includegraphics[width=0.7\linewidth]{figs/paper3/assortativity-vacc-1}}
-\caption{How Signal Mean and Signal Assortativity are Measured}\label{fig:assortativity-vacc}
+\caption{How Network Signal and Discordance are Calculated, Sampled Regions}\label{fig:assortativity-vacc}
 \end{figure}
@@
 \begin{figure}
-\begin{center}\includegraphics[width=0.5\linewidth,]{figs/paper3/discordancenetwork-1} 
+\begin{center}\includegraphics[width=0.5\linewidth,]{figs/paper3/discordancenetwork-1.pdf} 
   \begin{equation}
@@
     x = \begin{bmatrix}29.9\\20.4\\27.7\\24.6\\24.3\end{bmatrix} \longrightarrow
-    \begin{matrix} \bar{x}, signal = 25.083\\ s, discordance = 1.41 \end{matrix} 
+    \begin{matrix} \bar{x}*, signal = 25.083\\ s*, discordance = 1.41 \end{matrix} 
   \end{equation}
-  \caption{Visualization of how Network Signal and Discordance are Calculated}
+  \caption{How Network Signal and Discordance are Calculated, Mathematical Example}
   \label{fig:discordancenetwork}
@@
 
-\hypertarget{online-norms}{%
-\subsubsection{Online Norms}\label{online-norms}}
+\hypertarget{online-norms}{\subsubsection{Online Norms}\label{online-norms}}
 
-% TODO Mention that article-1 says that this can show interest (cite jungherr also) but does not show actions
-
-To operationalize the search for online norms, I use Google search trends \citep{googletrends},
-over the study period across individual designated media markets areas (DMAs), a
-nonoverlapping aggregation of U.S. counties to 210 media markets based on
-similar population clusters \citep{dma_key}. To investigate the rate of \emph{searching} for norms
+To operationalize the search for online norms, I use Google search trends
+\citep{googletrends}. In \hyperlink{paper-1}{\subsection{Article 1}}, I show
+that Google Search Trends can only be used to indicate interest due to their low
+criterion validity \citep{jungherr_etal17}. I use Google Trends over the study
+period across individual designated media markets areas (DMAs), a nonoverlapping
+aggregation of U.S. counties to 210 media markets based on similar population
+clusters \citep{dma_key}. To investigate the rate of \emph{searching} for norms
 online in both cases, I use the following search topics: `Social Distancing'
-(2020, stay-at-home case only), `COVID-19 Vaccine' (2021, vaccination uptake case
-only) and Covid Conspiracy (2020-2021, both cases). Search topics are a more
-robust measurement than a single search term: topics are aggregations of the
-rates of multiple, highly correlated search terms together into a cohesive
+(2020, stay-at-home case only), `COVID-19 Vaccine' (2021, vaccination uptake
+case only) and Covid Conspiracy (2020-2021, both cases). Search topics are a
+more robust measurement than a single search term: topics are aggregations of
+the rates of multiple, highly correlated search terms together into a cohesive
 topic. For example, while `Beyoncé,' `Beyonce' and `beyonce knowles' are all
 separate search terms, `Beyoncé Knowles' encompasses all of these into a single
-search topic. While the data is originally on a scale of 0 to 100, with
-100 being the maximum search popularity out of all DMAs, Google Search Trend are
-now only available cross-sectionally (a single time period across a geography)
-or time-series (a single geo-location across time). To remedy this and build a
-longitudinal dataset of each search topic, I follow the method proposed in \citet[p. 5]{park_etal}.
-This method involves building a dataset of unscaled
+search topic. While the data is originally on a scale of 0 to 100, with 100
+being the maximum search popularity out of all DMAs, Google Search Trend are now
+only available cross-sectionally (a single time period across a geography) or
+time-series (a single geo-location across time). To remedy this and build a
+longitudinal dataset of each search topic, I follow the method proposed in
+\citet[p. 5]{park_etal}. This method involves building a dataset of unscaled
 cross-sectional values, selecting a DMA to use to establish the rescaling ratio
@@
 counties, I set a random effect for signal nested by county. A visual
-representation of this interaction can be seen in figures
+representation of this interaction can be seen in Figures
 \ref{fig:plot-google-h2} and \ref{fig:plot-vacc-h2}. Model 3 further
@@
 Hypothesis 1 also returns surprising results: every 1 standard deviation
-increase in county COVID-19 case rates is expected to yield a -0.008 decrease in vaccination rates. This may be due to time ordering or reverse
-causality, where individuals in counties who have higher rates of vaccination
-are less likely to take tests to COVID-19 infections because of the higher
-likelihood of asymptomaticity. However, it is important to note that the Case
-Rate variable actually becomes distorted with the addition of Vaccination Signal
-and Vaccination Discordance in models 2 and 3. Distortion occurs when the
-direction of a focal relationship reverses sign once a third (distorter)
-variable is controlled, in this case, those related to signal. Therefore, the
-results of hypothesis 1 are quite inconclusive.
+increase in county COVID-19 case rates is expected to yield a -0.008 decrease in
+vaccination rates. This may be due to time ordering or reverse causality, where
+individuals in counties who have higher rates of vaccination are less likely to
+take tests to COVID-19 infections because of the higher likelihood of
+asymptomaticity. However, it is important to note that the Case Rate variable
+actually becomes distorted with the addition of Vaccination Signal and
+Vaccination Discordance in models 2 and 3. Distortion occurs when the direction
+of a focal relationship reverses sign once a third (distorter) variable is
+controlled, in this case, those related to signal. Therefore, the results of
+hypothesis 1 are quite inconclusive.
 

### 2022-03-23 tables/paper1/data-sources-table.tex
3 article summaries
Final committee edits

@@
 
-\begin{table}[!h]
+\begin{table}[!ht]
 \caption{\label{tab:data-sources-table}Data Sources}
@@
 Mask-Wearing Survey Data \citep{mask_data} & Cross-Sectional & July 2 - 14, 2020 & Search Topics: 'Coronavirus (Disease)', 'Coronavirus (Virus)', 'Cloth   Face Mask', 'Mask', 'Civil and Political Rights' \\
-American National Election Survey \citep{anes_data}& Cross-Sectional & 2020 & NA \\
+% American National Election Survey \citep{anes_data}& Cross-Sectional & 2020 & NA \\
 % \rowcolor{lightblue}
@@
 \multicolumn{4}{l}{\textbf{Political}} \\\hline
-American National Election Survey \citep{anes_data}& Cross-Sectional & 2020 & NA \\
+% American National Election Survey \citep{anes_data}& Cross-Sectional & 2020 & NA \\
 Presidential Election Results \citep{pres_data}& Cross Sectional & 2016 \& 2020 & Search Topics: 'Hilary Clinton', 'Donald Trump', 'Joe Biden' \\ \bottomrule

### 2022-03-24 abstract.tex
review of ch 1

@@
 rely on this information to inform their health behaviors and develop social
-norms. Information can be shared and promoted by others
-through information campaigns and consumed by an individual, called information
-push, or information can be intentionally sought out by individuals, 
-called information pull, and how the information then relates to the
-creation of social norms. In academia and policy, the focus in research on 
+norms. In academia and policy, the focus in research on 
 information has most often focused on the information that is sent to 
-consumers, seeing people as passive receivers of information.
-My dissertation instead focuses on individuals as active agents 
-in their search for information.
+consumers, seeing people as passive receivers of information. This
+is otherwise known as a focus on the information 'push'. But, 
+information is also intentionally sought out by individuals;
+called information pull. My dissertation focuses on individuals as active agents 
+in their search for information and how the information discovered through
+these push and pull processes relates to the creation of social norms.
 
-The first article tests the construct validity of the Google Search Trends source,
-an online indicator of computer-mediated information search. I attempt to
+My first article tests the criterion validity of Google Search Trends as
+an indicator of computer-mediated information search. I attempt to
 validate Google Search Trends for use as indicators of attitudes, disease prevalence
 and political preferences using five different validated data sources. 
-I fail to find correlation among any of the Google Trends tested and their
+My analysis revealed no correlation among any of the Google Trends tested and their
 validated indicators. I demonstrate that there is no criterion validity of
@@
 of 948 Americans, I investigate their experiences seeking out information about 
-the COVID-19 vaccines among the following information seeking modalities: 
+the COVID-19 vaccines. I investigate five distinct information seeking modalities, or methods of searching for information: 
 personal connection, doctor, social networking site, online forum, and online search engine. 
-I find little evidence that online search is more utilized than
-seeking social support from personal network connections or health professionals
-as I had hypothesized based on uses and gratifications theory, 
-that media users are not passive consumers but instead actively chose
-the media sources based on the satisfaction of their individual needs.
+% I find little evidence that online search is more utilized than
+% seeking social support from personal network connections or health professionals
+% as I had hypothesized based on uses and gratifications theory, 
+% that media users are not passive consumers but instead actively choose
+% media sources based on the satisfaction of their individual needs.
 I find that different exposure points, the ways people first are exposed to 
@@
 ways people intentionally search for information, hold real world consequences
-through their associations with COVID-19 vaccination rates and intentions.
+through their associations with COVID-19 vaccination intentions and rates.
 For example, receiving or seeking out information from a doctor increases 
  COVID-19 vaccination uptake while receiving information from a social 
- networking site like Facebook or Twitter was associated with lower odds of vaccination.
+ networking site was associated with lower odds of vaccination.
 
@@
  stay-at-home rates and vaccination rates as responses to public health
-recommendations to mitigate the COVID-19 pandemic. Using theories like associative diffusion
+recommendations to mitigate the COVID-19 pandemic. Using the theories of associative diffusion
 and the integrated theoretical framework of norms, I test models of behavioral adaption
@@
 The introductory chapter provides a summary of the research and an explanation of how this
-research contributes to the sociology, social science, and society. Namely, 
+research contributes to sociology, social science, and society. Namely, 
 this paper provides important perspectives on search as an agentic process

### 2022-03-24 ch1.tex
review of ch 1

@@
 ways, including by means of diffusion and polarization, it contributed to our newly
-established norms in the Spring of 2020 and since. By uncovering how norms were
+established norms since the Spring of 2020. By uncovering how norms were
 created during this time of norm uncertainty, my research will contribute to the
@@
 level of uncertainty on a subject and desired level of uncertainty.
+% connect better to social support if possible
 
@@
 \citep{baumeister,grieve2013face}. For instance, Dani, a young college student, 
-could search on Google to find how to turn iron their dress shirt properly, 
+could search on Google to find how to iron their dress shirt properly, 
 but instead Dani choses to call their parent(s) and ask the best strategy so their parent(s)
@@
 an additional cognitive need to fill through social interaction. 
-For example, Taylor could ask their neighbor who is a medical professional about 
+For example, Taylor could ask their neighbor, who is a medical professional about 
 the newfound headaches they've been experiencing, but every time they talk to their
@@
 Social norms form the building blocks of social organization and have been a
-focus of sociology since the beginning. In a recent Annual Review of Sociology
+focus of sociology since the beginning. In a 2020 Annual Review of Sociology
 piece focused on social norms, Horne and Mollborn define norms as "group-level
@@
 being exposed to new information, an actor can choose to further investigate
-the information online or offline and, in turn, further share the 
-information they were exposed to.
+the information if their level of uncertainty on the subject surpasses
+the desired level of uncertainty \citep{brashersCommunicationUncertaintyManagement2001}. 
+Search can then be performed online or offline and be pushed further to the actor's 
+networks.
 
@@
 
-I fail to find correlation among any of the Google Trends tested and their
+I find no correlation among any of the Google Trends tested and their
 validated indicators. While some Google Trends tested were significantly
@@
 governing health behaviors in cases of extreme uncertainty using the cases of
-both stay-at-home rates and vaccination rates as responses to public health recommendations to mitigate the COVID-19 pandemic. Using theories like associative diffusion
+both stay-at-home rates and vaccination rates as responses to public health 
+recommendations to mitigate the COVID-19 pandemic. Using theories like associative diffusion
 and the integrated theoretical framework of norms, I test models of behavioral adaption
@@
 process cannot be not fully understood without looking at the context of each
-exposure to a contagion within  within the range of contagions one experiences.
+exposure to a contagion within the range of contagions one experiences.
 
@@
 through social network ties theoretically will uncover potentially
-different information than would be uncovered through online web
+different information than would be found through online web
 search and will change how people are organized and how people behave.
-\hyperlink{paper-2}{Article 2} Article 2, for instance, demonstrates that 
+\hyperlink{paper-2}{Article 2}, for instance, demonstrates that 
 the choice to receive a COVID-19 vaccine is impacted by how
@@
 This dissertation also contributes to computational social science \&
-critical big data studies. I base much of my dissertation around Google
-Search Trends, which are relatively underutilized in the social sciences
+critical big data studies. In two articles, I employ Google Search Trends 
+which are relatively underutilized in the social sciences
 compared to health sciences and business. Because \hyperlink{paper-1}{Article 1} 
@@
 pitfalls that any source of big data face \citep{mcfarlandBigDataDanger2015} and explicitly
-test just how well Google Trends can be used as an indicator for different concepts. 
-Importantly, I find that there is no replacement for high quality survey data with Google Trends. 
+test just how well Google Trends can be used as an indicator for different concepts through
+criterion validity. Importantly, I find that Google Trends cannot replace
+high quality survey data. 
 This is a large contribution to the field of critical big data studies but also provides
@@
 versus injunctive, prescriptive versus proscriptive).  
-The focus on the formation of new social norms during times of upheaval 
+The focus on the formation of new social norms during times of uncertainty
 has implications for interventions in social behavioral outcomes, 
@@
 I also make important contributions to social epidemiology through this
-research. Each of the three papers in this dissertation use health case
-studies for questions of sociological interest. Because of this, I 
+research with the use of health case studies for questions of sociological interest
+across my three articles. Because of this, I 
 contribute to the social epidemiological conversation on vaccine hesitancy,

### 2022-03-24 paper2.tex
review of ch 1

@@
 \hypertarget{paper-2}{%
-\chapter{Information-Seeking Behaviors for Information on COVID-19 Vaccinations}\label{paper-2}}
+\chapter{information seeking Behaviors for Information on COVID-19 Vaccinations}\label{paper-2}}
 
@@
 Previous research has greatly failed to distinguish between the activation of
-information-seeking behaviors online and offline. Using theories of 1) social
+information seeking behaviors online and offline. Using theories of 1) social
 support and 2) uses and gratifications theory I investigate the factors associated
-with each modality type when on information-seeking modality: personal connection,
+with each modality type when on information seeking modality: personal connection,
 doctor, social networking site, online forum, and online search engine. Using
@@
 
-\textbf{Keywords}: Information-Seeking Behavior, COVID-19, Vaccine Hesitancy, Social Networks, Social Support, Information \& Communication Technologies
+\textbf{Keywords}: information seeking Behavior, COVID-19, Vaccine Hesitancy, Social Networks, Social Support, Information \& Communication Technologies
 
@@
 variation of usage of information search modalities. In doing so, I seek to answer
-how computer-mediated or interpersonal information-seeking strategies vary
+how computer-mediated or interpersonal information seeking strategies vary
 across populations in their search for information about COVID-19 vaccinations
 and investigate how these strategies affect vaccination uptake. Specifically, this article 
-answers two research questions: (1) How do computer-mediated or interpersonal information-seeking
+answers two research questions: (1) How do computer-mediated or interpersonal information seeking
 strategies vary across populations? (2) How does the information search modality utilized 
@@
 Before addressing the results to these research questions, I offer an overview of the
-current state of social science literature in regards to information-seeking
+current state of social science literature in regards to information seeking
 strategies and providing a description of the research methodology and
@@
 
-There are important factors that can influence information-seeking strategies
+There are important factors that can influence information seeking strategies
 besides the strength of social capital or ease of search. For instance, we can
@@
 \end{hyp}
+
+% this actually makes more sense not from UGT but as a transactional cost perspective (maybe like disposable ties), that you have to use social capital to activate your social network, but online search is free.
 
@@
 The second part of the survey focuses on network resource activation and 
-information-seeking behaviors of individuals regarding COVID-19 vaccinations
+information seeking behaviors of individuals regarding COVID-19 vaccinations
 for this paper.
@@
 age, education level and race. Figure \ref{fig:plot-model-1} then illustrates
-the relationship between the coefficients and information-seeking.\footnote{Figures 
+the relationship between the coefficients and information seeking.\footnote{Figures 
 in this paper were all created using the \texttt{r} packages jtools \citep{jtools}
 and ggplot2 \citep{wickham_etal, wickham11}}.
-In Table \ref{tab:model-2-phi}, I disaggregate information-seeking behaviors by
+In Table \ref{tab:model-2-phi}, I disaggregate information seeking behaviors by
 investigating the difference in proportions of each of the 5 different avenues
@@
 Finally, in Table \ref{tab:table-model-3}, I investigate whether there is a
-relationship between information exposure sources, information-seeking behaviors and
+relationship between information exposure sources, information seeking behaviors and
 the choice to get vaccinated against COVID-19 through a logistic regression
@@
 
-\hypertarget{information-seeking}{%
-\subsection{information-seeking}\label{information-seeking}}
+\hypertarget{information seeking}{%
+\subsection{Information Seeking}\label{information seeking}}
 
@@
 age is equal to x + 1 relative to x, possibly indicating a generational effect
-of information-seeking patterns (\emph{p} \textless{} 0.01). Additionally,
+of information seeking patterns (\emph{p} \textless{} 0.01). Additionally,
 those who were more educated, that is those with an Associate's degree or higher,
@@
 \textless{} 0.05). Figure \ref{fig:plot-model-1} illustrates the relationship
-between the coefficients and information-seeking.
+between the coefficients and information seeking.
 
@@
 \ref{tab:table-1-ind} reveals differences in the prevalence of usage of the
-various information-seeking modalities: Around 40\% of the sample has inquired for
+various information seeking modalities: Around 40\% of the sample has inquired for
 information from a doctor, a person, or using online search tool (44\%, 42\%, 41\%), while my
@@
 models, receiving information of any kind increase the odds of online search,
-though to varying magnitudes (Doctor: 1.54 odds; Person: 1.44 odds; News or Television: 2.98 odds; 
+though to varying magnitudes (Doctor: 1.54 odds; Person: 1.44 odds; 
+News or Television: 2.98 odds; 
 social networking site: 3.57 odds; Online Forum: 2 odds). I also find that older respondents
@@
 Finally, in Table \ref{tab:table-model-3}, I investigate whether there is a
-relationship between information receiving and information-seeking behaviors and
+relationship between information receiving and information seeking behaviors and
 the choice to get vaccinated against COVID-19 through a logistic regression
@@
 \hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
+\section{Discussion and Conclusion}\label{discussion}}
 
 Previous research in Sociology and Infodemiology has greatly failed to
-distinguish between the activation of information-seeking behaviors online and
+distinguish between the activation of information seeking behaviors online and
 offline. In this paper, I sought to uncover just how different various methods of
@@
 vaccination rates and intentions.
+
+% TODO explain finding about online search being less prominent than social networks, though opposite to the theory.
+relate this to Rains work and how it may be the search for personalized or experiential information making the difference.
 
@@
 Overall, being exposed to information about COVID-19 vaccinations from any 
-source is associated with information-seeking behaviors,
+source is associated with information seeking behaviors,
 though there are key variations. First, if one received information from a
@@
 
-\hypertarget{conclusion}{%
-\section{Conclusion}\label{conclusion}}
-
 Previous research has greatly failed to distinguish between the activation of
-information-seeking behaviors online and offline and largely focuses on the
+information seeking behaviors online and offline and largely focuses on the
 information that is sent to consumers [push], seeing people as passive receivers

### 2022-03-24 paper3.tex
review of ch 1

@@
 To operationalize the search for online norms, I use Google search trends
-\citep{googletrends}. In \hyperlink{paper-1}{\subsection{Article 1}}, I show
+\citep{googletrends}. In \hyperlink{paper-1}{Article 1}, I show
 that Google Search Trends can only be used to indicate interest due to their low

### 2022-03-25 abstract.tex
Final Draft before defense

@@
 rely on this information to inform their health behaviors and develop social
-norms. In academia and policy, the focus in research on 
-information has most often focused on the information that is sent to 
-consumers, seeing people as passive receivers of information. This
-is otherwise known as a focus on the information 'push'. But, 
-information is also intentionally sought out by individuals;
-called information pull. My dissertation focuses on individuals as active agents 
-in their search for information and how the information discovered through
-these push and pull processes relates to the creation of social norms.
+norms. In academia and policy, the focus in research on information has most
+often studied the information that is sent to consumers, seeing people as
+passive receivers of information. This is otherwise known as information 'push'.
+But, information is also intentionally sought out by individuals; called
+information pull. My dissertation focuses on individuals as active agents in
+their search for information and how the information discovered through these
+push and pull processes relates to the creation of social norms.
 
-My first article tests the criterion validity of Google Search Trends as
-an indicator of computer-mediated information search. I attempt to
-validate Google Search Trends for use as indicators of attitudes, disease prevalence
-and political preferences using five different validated data sources. 
-My analysis revealed no correlation among any of the Google Trends tested and their
-validated indicators. I demonstrate that there is no criterion validity of
-Google Trends for the selected cases and social scientists will find no replacement for
-high quality survey data with Google Trends. Instead, we must only use 
-Google Trends to demonstrate interest or attention.
+My first article tests the criterion validity of Google Search Trends as an
+indicator of computer-mediated information search. I attempt to validate Google
+Search Trends for use as indicators of attitudes, disease prevalence and
+political preferences using five different data sources. My analysis revealed no
+correlation among any of the Google Trends tested and their validated
+indicators. I demonstrate that there is no criterion validity of Google Trends
+for the selected cases and social scientists will find no replacement for high
+quality survey data with Google Trends. Instead, we must only use Google Trends
+to demonstrate interest or attention.
 
 Knowing that Google Trends data only encompasses a small portion of the
-information-seeking done by modern humans, my second article 
-is motivated by the research question: How do computer-mediated or interpersonal 
-information-seeking strategies vary across populations? Using original survey data
-of 948 Americans, I investigate their experiences seeking out information about 
-the COVID-19 vaccines. I investigate five distinct information seeking modalities, or methods of searching for information: 
-personal connection, doctor, social networking site, online forum, and online search engine. 
-% I find little evidence that online search is more utilized than
-% seeking social support from personal network connections or health professionals
-% as I had hypothesized based on uses and gratifications theory, 
-% that media users are not passive consumers but instead actively choose
-% media sources based on the satisfaction of their individual needs.
-I find that different exposure points, the ways people first are exposed to 
-information without searching for it, and information search modalities, the 
-ways people intentionally search for information, hold real world consequences
-through their associations with COVID-19 vaccination intentions and rates.
-For example, receiving or seeking out information from a doctor increases 
- COVID-19 vaccination uptake while receiving information from a social 
- networking site was associated with lower odds of vaccination.
+information-seeking done by modern humans, my second article is motivated by the
+research question: How do computer-mediated or interpersonal information-seeking
+strategies vary across populations? Using original survey data of 948 Americans,
+I investigate their experiences seeking out information about COVID-19 vaccines.
+I investigate five distinct information seeking modalities, or methods of
+searching for information: personal connection, doctor, social networking site,
+online forum, and online search engine. 
+%I find little evidence that online search is more utilized than % seeking social support from personal network connections or health professionals % as I had hypothesized based on uses and gratifications theory, % that media users are not passive consumers but instead actively choose % media sources based on the satisfaction of their individual needs.
+I find that different exposure points, the ways people first are exposed
+to information without searching for it, and information search modalities hold
+real world consequences through their associations with COVID-19 vaccination
+intentions and rates. For example, I find that receiving or seeking out
+information from a doctor increases COVID-19 vaccination uptake while receiving
+information from a social networking site is associated with lower odds of
+vaccination.
 
 My final article takes a deeper dive into the formation of social norms
-governing health behaviors in cases of extreme uncertainty, specifically using the cases of
- stay-at-home rates and vaccination rates as responses to public health
-recommendations to mitigate the COVID-19 pandemic. Using the theories of associative diffusion
-and the integrated theoretical framework of norms, I test models of behavioral adaption
-to public health recommendations and patterns of complex contagion (the need for
-repeated exposures to a something novel for it to diffuse) using linear
-mixed effects models. My results show that complex contagion is a valid 
-framework for the social contagion of new norms during COVID-19. 
-However, I find an important novel moderating effect of signal discordance; 
-if there is diversity in the information received by an ego, 
-contagion is less likely to occur. This paper shows that
-the contagion process is not fully understood without looking at the context
-of each exposure to a contagion within the range of contagions one experiences.
+governing health behaviors in cases of extreme uncertainty. I specifically use
+the cases of stay-at-home rates and vaccination rates as responses to public
+health recommendations to mitigate the COVID-19 pandemic. Using the theories of
+associative diffusion and the integrated theoretical framework of norms, I test
+models of behavioral adaption to public health recommendations and patterns of
+complex contagion (the need for repeated exposures to a something novel for it
+to diffuse) using linear mixed effects models. My results show that complex
+contagion is a valid framework for the social contagion of new norms during
+COVID-19. However, I find an important novel moderating effect of signal
+discordance; if there is diversity in the information received by an ego,
+contagion is less likely to occur. This paper shows that the contagion process
+is not fully understood without looking at the context of each exposure to a
+contagion within the range of contagions one experiences.
 
-The introductory chapter provides a summary of the research and an explanation of how this
-research contributes to sociology, social science, and society. Namely, 
-this paper provides important perspectives on search as an agentic process
-and how the micro-level information seeking process of an individual can
-lead to macro-level social norms. I show that information diffusion
-is disrupted when conflicting information and behaviors are simultaneously
-diffusing and therein contribute to research on diffusion, social networks,
-and social norms.
+The introductory chapter provides a summary of the research and an explanation
+of how this research contributes to sociology, social science, and society.
+Namely, this paper provides important perspectives on search as an agentic
+process and how the micro-level information seeking process of an individual can
+lead to macro-level social norms. I show that information diffusion is disrupted
+when conflicting information and behaviors are simultaneously diffusing and
+therein contribute to research on diffusion, social networks, and social norms.

### 2022-03-25 ch1.tex
Final Draft before defense

@@
 through information campaigns and consumed by an individual, called information
-push, or information can be intentionally sought out by individuals, 
-called information pull \citep{cybenkoFoundationsInformationPush1999}.
+push, or information can be intentionally sought out by individuals, called
+information pull \citep{cybenkoFoundationsInformationPush1999}.
 
-We must understand the information individuals receive and seek out 
-to develop a well-functioning society. The information that
-one consumes consolidates to create the entire worldview of every individual,
-leading to how they understand the world and behave civilly therein. New and
-emerging social norms must align with one's worldview to anticipate any sort of 
-behavioral change, for better or for worse.
+We must understand the information individuals receive and seek out to develop a
+well-functioning society. The information that one consumes consolidates to
+create the entire worldview of every individual, leading to how they understand
+the world and behave civilly therein. New and emerging social norms must align
+with one's worldview to anticipate any sort of behavioral change, for better or
+for worse.
 
-The importance of reputable information and misinformation was clear
-in the recent and ongoing COVID-19 pandemic. While the vaccines against the
-COVID-19 virus are effective in preventing severe illness, hospitalization, 
-and death, only 60\% of Arizonans over 12 years old \citep{owid}
-are fully vaccinated against the virus. We know that
-people exposed to misinformation are much less likely to receive vaccinations
-against the virus \citep{loombaMeasuringImpactCOVID192021}. It is not an
-exaggeration to claim that misinformation has been deadly for Arizona
+The importance of reputable information and misinformation was clear in the
+recent and ongoing COVID-19 pandemic. While the vaccines against the COVID-19
+virus are effective in preventing severe illness, hospitalization, and death,
+only 60\% of Arizonans over 12 years old \citep{owid} are fully vaccinated
+against the virus. We know that people exposed to misinformation are much less
+likely to receive vaccinations against the virus
+\citep{loombaMeasuringImpactCOVID192021}. It is not an exaggeration to claim
+that misinformation has been deadly for Arizona
 \citep{pathakInfodemicsCOVID19Role2020, greene_murphy21}.
@@
 This dissertation on information search and norm development provides clear and
-timely social implications for Arizona and the United States. I
-uncover how norms are created during periods of norm uncertainty and builds the
-foundation to theorize and test interventions that promote positive norms in
-times of disasters and uncertainty. Specifically, I investigate how local
-diffusion leads to social norms through information search, which will have
-strong implications for the prevention of global polarization and the spread of
-misinformation, as I now explain.
+timely social implications for Arizona and the United States. I uncover how
+norms are created during periods of norm uncertainty and builds the foundation
+to theorize and test interventions that promote positive norms in times of
+disasters and uncertainty. Specifically, I investigate how local diffusion leads
+to social norms through information search, which will have strong implications
+for the prevention of global polarization and the spread of misinformation, as I
+now explain.
 
-In academia and policy, the focus in research on information has always
-been the information that is sent to consumers, seeing people as passive
-receivers of information. My dissertation instead focuses on individuals as
-active agents in their search for information. By looking at how individuals 
-search, I aim to identify focus areas for future interventions
-to counter the misinformation process.
+In academia and policy, the focus in research on information has always been the
+information that is sent to consumers, seeing people as passive receivers of
+information. My dissertation instead focuses on individuals as active agents in
+their search for information. By looking at how individuals search, I aim to
+identify focus areas for future interventions to counter the misinformation
+process.
 
@@
 behaviors exhibited today by Arizonans. While the information spread in various
-ways, including by means of diffusion and polarization, it contributed to our newly
-established norms since the Spring of 2020. By uncovering how norms were
+ways, including by means of diffusion and polarization, it contributed to our
+newly established norms since the Spring of 2020. By uncovering how norms were
 created during this time of norm uncertainty, my research will contribute to the
@@
 \subsection{Information Flow}
-Humans have long been interested in how to persuade the masses. With the 
-rise of democracy, the need of the powerful to persuade and appease the
-masses dramatically increased. And for a while, behavioral scientists 
-adopted really simplistic models of persuasion like the assumption
-that the media influences behavior in a direct, unmediated, and 
-all-powerful way (termed the hypodermic needle model in
-\citet{bineham1988historical}) \citep{lasswellpropaganda}.
 
-A critical turning point in the study of the flow of information was put forth by
-renowned sociologist Paul Lazarsfeld and colleagues Verelson and Gaudet \citeyearpar{lazarsfeldPeopleChoice1944}.
-They theorized that the media did not directly influence the
-masses, but that a "Two-Step Flow" was occurring where "opinion leaders"
-interpreted messages from mass media and then, in turn, promoted their opinions
-to the masses \citep{katzPersonalInfluencePart1955}. The opinion leaders
-interpret, explain, and diffuse contents to "opinion followers". From a networks
-perspective, "people rarely act on mass-media information unless it is also
-transmitted through personal ties" \citep[p. 1374]{granovetterStrengthWeakTies1973}. 
-Lazarsfeld et al's \citeyearpar{lazarsfeldPeopleChoice1944} first study focused on
-politics, but follow up studies by \citet{katzPersonalInfluencePart1955} showed
-that this model matched information flows beyond the political realm. In
-contrast to the one-step flow, where media directly influences the masses,
-Lazarsfeld's theory remains in prominence today. While many scholars assumed
-that modern micro-targeted marketing strategies would provide evidence for a
-one-step flow perspective \citep{bennettOneStepFlowCommunication2006}, many
-scholars find that "opinion leaders" (often influencers and celebrities) still
-create a two-step flow of information transmission \citep{choi15,
-hilbertOneStepTwo2017}.
+Humans have long been interested in how to persuade the masses. With the rise of
+democracy, the need of the powerful to persuade and appease the masses
+dramatically increased. And for a while, behavioral scientists adopted really
+simplistic models of persuasion like the assumption that the media influences
+behavior in a direct, unmediated, and all-powerful way (termed the hypodermic
+needle model in \citet{bineham1988historical}) \citep{lasswellpropaganda}.
 
-The spread of information has been thoroughly studied from the perspective
-of social networks. Individuals engage with each other and their distributed
-ties to create community contexts where norms, beliefs, and values circulate.
+A critical turning point in the study of the flow of information was put forth
+by renowned sociologist Paul Lazarsfeld and colleagues Verelson and Gaudet
+\citeyearpar{lazarsfeldPeopleChoice1944}. They theorized that the media did not
+directly influence the masses, but that a "Two-Step Flow" was occurring where
+"opinion leaders" interpreted messages from mass media and then, in turn,
+promoted their opinions to the masses \citep{katzPersonalInfluencePart1955}. The
+opinion leaders interpret, explain, and diffuse contents to "opinion followers".
+From a networks perspective, "people rarely act on mass-media information unless
+it is also transmitted through personal ties" \citep[p.
+1374]{granovetterStrengthWeakTies1973}. Lazarsfeld et al's
+\citeyearpar{lazarsfeldPeopleChoice1944} first study focused on politics, but
+follow up studies by \citet{katzPersonalInfluencePart1955} showed that this
+model matched information flows beyond the political realm. In contrast to the
+one-step flow, where media directly influences the masses, Lazarsfeld's theory
+remains in prominence today. While many scholars assumed that modern
+micro-targeted marketing strategies would provide evidence for a one-step flow
+perspective \citep{bennettOneStepFlowCommunication2006}, many scholars find that
+"opinion leaders" (often influencers and celebrities) still create a two-step
+flow of information transmission \citep{choi15, hilbertOneStepTwo2017}.
+
+The spread of information has been thoroughly studied from the perspective of
+social networks. Individuals engage with each other and their distributed ties
+to create community contexts where norms, beliefs, and values circulate.
 Information diffuses through communities and social networks
@@
 \subsection{Information Search}
-I have only discussed the way that information is passively
-consumed through push efforts by opinion leaders and social networks. However,
-sociological literature is sparse on the opposite behavior: active
-directed searching by individuals to obtain information.
+I have only discussed the way that information
+is passively consumed through push efforts by opinion leaders and social
+networks. However, sociological literature is sparse on the opposite behavior:
+active directed searching by individuals to obtain information.
 \citet{pejtersenDesignComputeraidedUsersystem1984}, a scholar of library and
@@
 information. The most common strategy is browsing, where people follow leads
-based on associations without planning. Another strategy is analytical,
-which includes an explicit consideration of all facets of the question to guide
-a search. The empirical method guides the search based on tactics that were
+based on associations without planning. Another strategy is analytical, which
+includes an explicit consideration of all facets of the question to guide a
+search. The empirical method guides the search based on tactics that were
 successful in past research. The known site strategy is to go to the direct
@@
 The constant connectedness facilitates communication, but also presents people
-with overchoice, or the difficulty in deciding because simply every
-network connection you may want to activate is permanently connected and easy to
-reach. In other words, constant connection may be debilitating to many who are
-seeking information. \citet{smallSomeoneTalk2017} provides many examples of this
-when he demonstrates that often, graduate students who needed
-support simply asked "miscellaneous classmates encountered down the hall" (p.
-176) rather than their trusted, long-term confidants. It seems that network
-activation may rely on more than just trust; namely: convenience.
+with overchoice, or the difficulty in deciding because simply every network
+connection you may want to activate is permanently connected and easy to reach.
+In other words, constant connection may be debilitating to many who are seeking
+information. \citet{smallSomeoneTalk2017} provides many examples of this when he
+demonstrates that often, graduate students who needed support simply asked
+"miscellaneous classmates encountered down the hall" (p. 176) rather than their
+trusted, long-term confidants. It seems that network activation may rely on more
+than just trust; namely: convenience.
 
-The digital age did not only revolutionize communication. It also
-revolutionized information search \citep{ramirez2002information}. Just as prior
-to the digital age you could open an encyclopedia or peruse the library to find
-the information you seek, much of the computer-mediated information search
-surely occurs outside of social network activation contexts. While searching in
-an encyclopedia is far less common today, internet search engines have
-revolutionized the speed and ease at which we can find information. Early web
-search engines allowed information seekers to browse web directories, and early
-engines like Yahoo! and Altavista found success using keyword-based search,
-though the early algorithms were limited in what they could find and relied
-heavily on the wording of the queries. Google, the major web search engine used
-today, introduced the disruptive PageRank algorithm in the early 2000s, securing
-its place as the information hegemon of the 21st century
-\citep{brin1998anatomy}. Not only has computer-mediated information search
-revolutionized the ease of obtaining information, but it has also changed our
-brains. \citet{sparrow2011google} show that the digital age has led to worse
-memory and higher reliance on technology to keep track of information for us.
-These search engines have also shaped our cultures by controlling, whether
-through algorithm or intentionally, the information the engine provides. For
-example, Google will not show results for various neo-Nazi websites in countries
-where holocaust denial is illegal, like France and Germany. This is illustrative
-of the control engines have over information and how this control may introduce
-various political, economic, and social biases in the information they provide
-\citep{segev2010google}. When 99Firms \citeyearpar{99firms22} compiled the data
-from sources like NetMarketShare, Statista, DuckDuckGo, Yahoo Finance, Google,
-and Pew Research they found that about 93\% of all web traffic is
-via a search engine and that 78.39\% of all internet searches performed are done
-using Google. Because computer-mediated information search is instantaneous 
-and only requires mobile data or WiFi, there is virtually no cost to seeking
-information on one of these mediums.
+The digital age did not only revolutionize communication. It also revolutionized
+information search \citep{ramirez2002information}. Just as prior to the digital
+age you could open an encyclopedia or peruse the library to find the information
+you seek, much of the computer-mediated information search surely occurs outside
+of social network activation contexts. While searching in an encyclopedia is far
+less common today, internet search engines have revolutionized the speed and
+ease at which we can find information. Early web search engines allowed
+information seekers to browse web directories, and early engines like Yahoo! and
+Altavista found success using keyword-based search, though the early algorithms
+were limited in what they could find and relied heavily on the wording of the
+queries. Google, the major web search engine used today, introduced the
+disruptive PageRank algorithm in the early 2000s, securing its place as the
+information hegemon of the 21st century \citep{brin1998anatomy}. Not only has
+computer-mediated information search revolutionized the ease of obtaining
+information, but it has also changed our brains. \citet{sparrow2011google} show
+that the digital age has led to worse memory and higher reliance on technology
+to keep track of information for us. These search engines have also shaped our
+cultures by controlling, whether through algorithm or intentionally, the
+information the engine provides. For example, Google will not show results for
+various neo-Nazi websites in countries where holocaust denial is illegal, like
+France and Germany. This is illustrative of the control engines have over
+information and how this control may introduce various political, economic, and
+social biases in the information they provide \citep{segev2010google}. When
+99Firms \citeyearpar{99firms22} compiled the data from sources like
+NetMarketShare, Statista, DuckDuckGo, Yahoo Finance, Google, and Pew Research
+they found that about 93\% of all web traffic is via a search engine and that
+78.39\% of all internet searches performed are done using Google. Because
+computer-mediated information search is instantaneous and only requires mobile
+data or WiFi, there is virtually no cost to seeking information on one of these
+mediums.
 
@@
 interchangeably with the term social networks and social integration
-\citep{houseStructuresProcessesSocial1988}, consisted of the emotional, informational,
-and instrumental assistance functions performed by social ties. Social 
-support has strong and measurable association with health outcomes
+\citep{houseStructuresProcessesSocial1988}, consisted of the emotional,
+informational, and instrumental assistance functions performed by social ties.
+Social support has strong and measurable association with health outcomes
 \citep{houseMeasuresConceptsSocial1985, thoitsMechanismsLinkingSocial2011}.
@@
 network" \citeyearpar[p. 260]{brashersInformationSeekingAvoiding2002}. Both
-definitions provide important lenses for my question of how
-computer-mediated or interpersonal information-seeking strategies vary. 
-Some research has revealed that Facebook users who utilize the platform to 
-find information and to maintain relationships have high levels of bridging
-social capital \citep{liu2016meta}. However, this leaves the question 
-of who activates their social networks for information using social networking 
-sites like Facebook instead of activating these networks in face-to-face
-interactions.
+definitions provide important lenses for my question of how computer-mediated or
+interpersonal information-seeking strategies vary. Some research has revealed
+that Facebook users who utilize the platform to find information and to maintain
+relationships have high levels of bridging social capital \citep{liu2016meta}.
+However, this leaves the question of who activates their social networks for
+information using social networking sites like Facebook instead of activating
+these networks in face-to-face interactions.
 
@@
 \citep{blumlerUsesMassCommunications1974, tanMassCommunicationTheories1985} may
-lend itself to theorizing why information-seeking strategies vary among different
-platforms and activation types. UGT posits that users are not passive
+lend itself to theorizing why information-seeking strategies vary among
+different platforms and activation types. UGT posits that users are not passive
 consumers of media and that people have an active role in choosing different
@@
 
-There has been some research into how different platforms allow for different user 
-experiences or "affordances" \citep{boyd2010social}. For example, 
-\citet{bossetta18} first show
-that all social media platforms must provide "tools that are easy to use and 
-functional to the demands of varying user demographics" (p. 473). They also
-explain how each digital architecture enables, constrains and shapes how users
-behave on their platform and in virtual space, leading to many different experiences 
-along the dimensions of searchability, connectivity, and privacy.
+There has been some research into how different platforms allow for different
+user experiences or "affordances" \citep{boyd2010social}. For example,
+\citet{bossetta18} first show that all social media platforms must provide
+"tools that are easy to use and functional to the demands of varying user
+demographics" (p. 473). They also explain how each digital architecture enables,
+constrains and shapes how users behave on their platform and in virtual space,
+leading to many different experiences along the dimensions of searchability,
+connectivity, and privacy.
 
-Adapting UGT to my own purposes, I theorize that
-informational support will be activated from network ties when the informational
-need is accompanied by or related to a need to form or maintain social ties
+Adapting UGT to my own purposes, I theorize that informational support will be
+activated from network ties when the informational need is accompanied by or
+related to a need to form or maintain social ties
 \citep{baumeister,grieve2013face}. For instance, Dani, a young college student,
-could search on Google to find how to iron their dress shirt properly, 
-but instead Dani choses to call their parent(s) and ask the best strategy so their parent(s)
-feels respected and valued and their relationship is strengthened. 
+could search on Google to find how to iron their dress shirt properly, but
+instead Dani choses to call their parent(s) and ask the best strategy so their
+parent(s) feels respected and valued and their relationship is strengthened.
 Conversely, I theorize that search will be conducted outside of network
-activation when information is needed but an individual does not have 
-an additional cognitive need to fill through social interaction. 
-For example, Taylor could ask their neighbor, who is a medical professional about 
-the newfound headaches they've been experiencing, but every time they talk to their
-neighbor they ask for help cleaning their gutters, which is too much work; Taylor
-instead may choose to ask the Facebook group they're a part of to gain information.
-Alternative goals such as identity management or relational maintenance
-\citep{brashersInformationSeekingAvoiding2002} need to be balanced and may also
-influence where search is conducted.
+activation when information is needed but an individual does not have an
+additional cognitive need to fill through social interaction. For example,
+Taylor could ask their neighbor, who is a medical professional about the
+newfound headaches they've been experiencing, but every time they talk to their
+neighbor they ask for help cleaning their gutters, which is too much work;
+Taylor instead may choose to ask the Facebook group they're a part of to gain
+information. Alternative goals such as identity management or relational
+maintenance \citep{brashersInformationSeekingAvoiding2002} need to be balanced
+and may also influence where search is conducted.
 
 \subsection{Social Norms}
-I showed that the levels of uncertainty may direct how and when people
-search for information. However, in situations of rapidly changing norms,
-uncertainty is prevalent. This dissertation also focuses on the development of
-new social norms in situations of uncertainty about how to behave. 
-Minimal research exists in quickly emerging
-norms in times of emergency but shows that people are likely to rely on the
-behavior of others to set their own norms for behavior \citep{alvarez2018,
-horneNormsIntegratedFramework2020}. This project investigates how search
-contributes to the development of said spontaneous norms.
+I showed that the levels of uncertainty may direct how and when people search
+for information. However, in situations of rapidly changing norms, uncertainty
+is prevalent. This dissertation also focuses on the development of new social
+norms in situations of uncertainty about how to behave. Minimal research exists
+in quickly emerging norms in times of emergency but shows that people are likely
+to rely on the behavior of others to set their own norms for behavior
+\citep{alvarez2018, horneNormsIntegratedFramework2020}. This project
+investigates how search contributes to the development of said spontaneous
+norms.
 
@@
 beliefs, and values as parts of collective consciousness that provide for
-societal integration \citeyearpar{durkheimSuicide1897, durkheimDivisionLaborSociety1933}.
-For Durkheim, norms were therefore the glue that held society together in cohesion.
+societal integration \citeyearpar{durkheimSuicide1897,
+durkheimDivisionLaborSociety1933}. For Durkheim, norms were therefore the glue
+that held society together in cohesion.
 
@@
 
-The causes and logics of social norms are debated. The consequentialist
-argument for norms focuses merely on the consequence a behavior has on
-group members and that norms will be promoted if the behavior benefits
-others and denounced if it negatively affects others \citep{ullmannmargalitEmergenceNorms1977}.
- While this theory has been tested and performs well in the lab,
-researchers have raised questions regarding its ecological validity
+The causes and logics of social norms are debated. The consequentialist argument
+for norms focuses merely on the consequence a behavior has on group members and
+that norms will be promoted if the behavior benefits others and denounced if it
+negatively affects others \citep{ullmannmargalitEmergenceNorms1977}. While this
+theory has been tested and performs well in the lab, researchers have raised
+questions regarding its ecological validity
 \citep{horneNormsIntegratedFramework2020}. One of the main critiques of the
-consequentialist argument is that it relies on the same interpretation 
-of the perceived action
-by all parties of what is harmful and beneficial. The Relational argument 
-for norms is based on the value people place on their relationships and
-the assumption that people will behave in ways that will garner them
-positive social reactions. This argument relies on individuals assuming
-what their peers will approve and disapprove of. In turn, norms are
+consequentialist argument is that it relies on the same interpretation of the
+perceived action by all parties of what is harmful and beneficial. The
+Relational argument for norms is based on the value people place on their
+relationships and the assumption that people will behave in ways that will
+garner them positive social reactions. This argument relies on individuals
+assuming what their peers will approve and disapprove of. In turn, norms are
 developed when individuals make inferences from their social worlds
-\citep{fryeCulturalMeaningsAggregation2017}. Importantly,
-people look to others performing an action and often
-interpret that performance as an indication that an action is approved,
-paying particular attention to high-status individuals and institutions
-\citep{robalinoPeerEffectsAdolescent2018, tankardEffectSupremeCourt2017}.
+\citep{fryeCulturalMeaningsAggregation2017}. Importantly, people look to others
+performing an action and often interpret that performance as an indication that
+an action is approved, paying particular attention to high-status individuals
+and institutions \citep{robalinoPeerEffectsAdolescent2018,
+tankardEffectSupremeCourt2017}.
 
@@
 
-Norms are formed inside of social networks; "Networks operate in a larger cultural
-context that can facilitate or inhibit acceptance of general cultural norms and
-beliefs" \citep[][p. 44]{pescosolidoDurkheimSuicideReligion1989}. 
-Because of this, people tend to resemble
-their network as a form of network autocorrelation and homophily
-\citep{dellapostaWhyLiberalsDrink2015}. While "birds of a feather flock
-together" in homophily \citep{mcphersonBirdsFeatherHomophily2001}, attitudes and
-behaviors are shaped by peers, creating filter bubbles of social influence
+Norms are formed inside of social networks; "Networks operate in a larger
+cultural context that can facilitate or inhibit acceptance of general cultural
+norms and beliefs" \citep[][p. 44]{pescosolidoDurkheimSuicideReligion1989}.
+Because of this, people tend to resemble their network as a form of network
+autocorrelation and homophily \citep{dellapostaWhyLiberalsDrink2015}. While
+"birds of a feather flock together" in homophily
+\citep{mcphersonBirdsFeatherHomophily2001}, attitudes and behaviors are shaped
+by peers, creating filter bubbles of social influence
 \citep{dellapostaWhyLiberalsDrink2015}.
@@
 perceptions about which beliefs or behaviors are compatible with one another,
-what they call "associative diffusion". 
-This relates back to the theory of relational norms, where individuals assume
-what their peers will approve and disapprove of. For these assumptions 
-to take place, they must understand which behaviors and beliefs
-are possessed by whom in their network and how new associations may influence
-or disrupt the expected actions. In times of behavioral uncertainty, I
-theorize that individuals strategically look towards other high-status
-individuals and institutions, and perform regimented searches to establish for
-themselves the behavior that is compatible with other cognitive associations
-and biases they hold.
+what they call "associative diffusion". This relates back to the theory of
+relational norms, where individuals assume what their peers will approve and
+disapprove of. For these assumptions to take place, they must understand which
+behaviors and beliefs are possessed by whom in their network and how new
+associations may influence or disrupt the expected actions. In times of
+behavioral uncertainty, I theorize that individuals strategically look towards
+other high-status individuals and institutions, and perform regimented searches
+to establish for themselves the behavior that is compatible with other cognitive
+associations and biases they hold.
 
@@
 
-To investigate information-seeking behaviors, online search tools, and how
-new norms in health behaviors form, I first provide an outline of the 
-information push and pull process in Figure \ref{fig:concept-map}. After 
-being exposed to new information, an actor can choose to further investigate
-the information if their level of uncertainty on the subject surpasses
-the desired level of uncertainty \citep{brashersCommunicationUncertaintyManagement2001}. 
-Search can then be performed online or offline and be pushed further to the actor's 
+To investigate information-seeking behaviors, online search tools, and how new
+norms in health behaviors form, I first provide an outline of the information
+push and pull process in Figure \ref{fig:concept-map}. After being exposed to
+new information, an actor can choose to further investigate the information if
+their level of uncertainty on the subject surpasses the desired level of
+uncertainty \citep{brashersCommunicationUncertaintyManagement2001}. Search can
+then be performed online or offline and be pushed further to the actor's
 networks.
@@
 
-This dissertation uses three articles to investigate different parts of
-the theoretical framework (Figure \ref{fig:concept-map}).
-The dissertation is divided into three parts, with Article 1 focusing 
-on online information search, Article 2 focusing on online and offline
-information search, and Article 3 investigating the entire information
-push and pull process in the context of establishing new norms.
+This dissertation uses three articles to investigate different parts of the
+theoretical framework (Figure \ref{fig:concept-map}). The dissertation is
+divided into three parts, with Article 1 focusing on online information search,
+Article 2 focusing on online and offline information search, and Article 3
+investigating the entire information push and pull process in the context of
+establishing new norms.
 
@@
 
-Computational social science and social science disciplines are quick to adopt new
-sources of digital trace data for use in academic research. In this article, I
-examine the criterion validity of one of these new sources, Google Search Trends. I
-validate how Google Trends can be used to demonstrate three different cases,
-namely attitudes, disease prevalence and political preferences using five
+Computational social science and social science disciplines are quick to adopt
+new sources of digital trace data for use in academic research. In this article,
+I examine the criterion validity of one of these new sources, Google Search
+Trends. I validate how Google Trends can be used to demonstrate three different
+cases, namely attitudes, disease prevalence and political preferences using five
 different validated data sources. This paper asks, "How can we operationalize
@@
 the validated indicators as well as multiple linear regression (for
-cross-sectional datasets) and random intercept hierarchical linear models (for
+cross-sectional datasets) and fixed effect hierarchical linear models (for
 longitudinal datasets) as additional tests of the data.
 
-I find no correlation among any of the Google Trends tested and their
-validated indicators. While some Google Trends tested were significantly
-associated with the outcome in the regression models, effects tended to be small
-and the total model interpretability remained low, even when controlling for
-demographic variables. This article shows that there is no external or 
-criterion validity of Google Trends for these uses and social scientists will find no replacement for
-high quality survey data with Google Trends. Instead, we must only use 
-Google Trends to demonstrate interest or attention.
+I find no correlation among any of the Google Trends tested and their validated
+indicators. While some Google Trends tested were significantly associated with
+the outcome in the regression models, effects tended to be small and the total
+model interpretability remained low, even when controlling for demographic
+variables. This article shows that there is no external or criterion validity of
+Google Trends for these uses and social scientists will find no replacement for
+high quality survey data with Google Trends. Instead, we must only use Google
+Trends to demonstrate interest or attention.
 
@@
 Knowing that Google trends data only encompasses a small portion of the
-information-seeking done by modern humans, it is important to
-investigate what leads individuals to search for a question online using
-a search engine versus more
-traditional means of information gathering, such as network activation
-(asking someone in their social network for informational support). 
-Previous research has greatly failed to distinguish between the activation of
-information seeking behaviors online and offline. Using theories of social
-support and uses and gratifications theory, I investigate the factors associated
-with each information seeking modality: personal connection,
-doctor, social networking site, online forum, and online search engine. I use
-original survey data of 948 Americans to investigate their experiences seeking out
-information about the COVID-19 vaccines.
+information-seeking done by modern humans, it is important to investigate what
+leads individuals to search for a question online using a search engine versus
+more traditional means of information gathering, such as network activation
+(asking someone in their social network for informational support). Previous
+research has greatly failed to distinguish between the activation of information
+seeking behaviors online and offline. Using theories of social support and uses
+and gratifications theory, I investigate the factors associated with each
+information seeking modality: personal connection, doctor, social networking
+site, online forum, and online search engine. I use original survey data of 948
+Americans to investigate their experiences seeking out information about the
+COVID-19 vaccines.
 
@@
 the categorizations of modalities queried in this survey are indeed conceptually
-different from each other and that the utilization of different modalities varies
-by demography and information exposure points. Finally, I find that different
-exposure points and information search modalities hold real world consequences
-through their associations with COVID-19 vaccination rates and intentions, as
-information from a doctor increases the COVID-19 vaccination uptake while
-receiving information from a social networking site like Facebook or Twitter was
-associated with lower odds of vaccination.
+different from each other and that the utilization of different modalities
+varies by demography and information exposure points. Finally, I find that
+different exposure points and information search modalities hold real world
+consequences through their associations with COVID-19 vaccination rates and
+intentions, as information from a doctor increases the COVID-19 vaccination
+uptake while receiving information from a social networking site like Facebook
+or Twitter was associated with lower odds of vaccination.
 
@@
 both stay-at-home rates and vaccination rates as responses to public health
-recommendations to mitigate the COVID-19 pandemic. Using theories like associative diffusion
-and the integrated theoretical framework of norms, I test models of behavioral adaption
-to public health recommendations and patterns of complex contagion (the need for
-repeated exposures to a something novel for it to diffuse) using linear
-mixed effects models.
+recommendations to mitigate the COVID-19 pandemic. Using theories like
+associative diffusion and the integrated theoretical framework of norms, I test
+models of behavioral adaption to public health recommendations and patterns of
+complex contagion (the need for repeated exposures to a something novel for it
+to diffuse) using linear mixed effects models.
 
-These models show that complex contagion is a valid 
-framework for the social contagion of new norms during COVID-19. Importantly, I find
-a novel moderating effect of signal discordance, the contextual diversity of
-signals received by an ego. If there is diversity in the information received
-by an ego, contagion is less likely to occur. This paper shows that the contagion 
-process cannot be not fully understood without looking at the context of each
-exposure to a contagion within the range of contagions one experiences.
+These models show that complex contagion is a valid framework for the social
+contagion of new norms during COVID-19. Importantly, I find a novel moderating
+effect of signal discordance, the contextual diversity of signals received by an
+ego. If there is diversity in the information received by an ego, contagion is
+less likely to occur. This paper shows that the contagion process cannot be not
+fully understood without looking at the context of each exposure to a contagion
+within the range of contagions one experiences.
 
@@
 % search as an agentic process
-This research makes contributions to multiple subfields and literatures. 
-First and foremost, these articles contribute to the sociological literature.
-The spread of information has long been investigated in the discipline (diffusion, mass
-communication, social influence). However, it is almost always researched from a structural
-perspective which disregards individual agency and choice in the
-acquisition of new information. This dissertation adopts the second perspective,
-centering people as active agents in their search for information aligned
-with their own preferences and gratifications instead of just
-passive receivers of information signals.
-Taking this agentic perspective is critical in the study of information
-diffusion when combined with cognitive perspectives like that of
-\citet{goldbergSocialContagionAssociative2018}. How people
-search for information is a strong determinant of 
-the information that they find. The information they uncover is filtered
-through cognitive biases and predispositions to how they interpret and
-act upon the newfound information. Searching for informational support
-through social network ties theoretically will uncover potentially
-different information than would be found through online web
-search and will change how people are organized and how people behave.
-\hyperlink{paper-2}{Article 2}, for instance, demonstrates that 
-the choice to receive a COVID-19 vaccine is impacted by how
-individuals search for information on the vaccine. 
-This is a real-world consequence to the variation in the individual information
-search process.
+This research makes contributions to multiple subfields and literatures. First
+and foremost, these articles contribute to the sociological literature. The
+spread of information has long been investigated in the discipline (diffusion,
+mass communication, social influence). However, it is almost always researched
+from a structural perspective which disregards individual agency and choice in
+the acquisition of new information. This dissertation adopts the second
+perspective, centering people as active agents in their search for information
+aligned with their own preferences and gratifications instead of just passive
+receivers of information signals. Taking this agentic perspective is critical in
+the study of information diffusion when combined with cognitive perspectives
+like that of \citet{goldbergSocialContagionAssociative2018}. How people search
+for information is a strong determinant of the information that they find. The
+information they uncover is filtered through cognitive biases and
+predispositions to how they interpret and act upon the newfound information.
+Searching for informational support through social network ties theoretically
+will uncover potentially different information than would be found through
+online web search and will change how people are organized and how people
+behave. \hyperlink{paper-2}{Article 2}, for instance, demonstrates that the
+choice to receive a COVID-19 vaccine is impacted by how individuals search for
+information on the vaccine. This is a real-world consequence to the variation in
+the individual information search process.
 
 % CSS & big data
-This dissertation also contributes to computational social science \&
-critical big data studies. In two articles, I employ Google Search Trends 
-which are relatively underutilized in the social sciences
-compared to health sciences and business. Because \hyperlink{paper-1}{Article 1} 
-takes a critical big data studies approach, I consider the potential
-pitfalls that any source of big data face \citep{mcfarlandBigDataDanger2015} and explicitly
-test just how well Google Trends can be used as an indicator for different concepts through
-criterion validity. Importantly, I find that Google Trends cannot replace
-high quality survey data. 
-This is a large contribution to the field of critical big data studies but also provides
-the groundwork for future tests of external validity for big data for future computational
-social scientists.
+This dissertation also contributes to computational social science \& critical
+big data studies. In two articles, I employ Google Search Trends which are
+relatively underutilized in the social sciences compared to health sciences and
+business. Because \hyperlink{paper-1}{Article 1} takes a critical big data
+studies approach, I consider the potential pitfalls that any source of big data
+face \citep{mcfarlandBigDataDanger2015} and explicitly test just how well Google
+Trends can be used as an indicator for different concepts through criterion
+validity. Importantly, I find that Google Trends cannot replace high quality
+survey data. This is a large contribution to the field of critical big data
+studies but also provides the groundwork for future tests of external validity
+for big data for future computational social scientists.
 
 % micro behaviors to macro processes
-Bridging the contribution of search as an agentic process 
-and critical big data studies, this dissertation contributes to the question posed by 
-\citet{breigerScaling2015}, "what are the behavioral processes that 
-lead to macro-level outcomes?" With the exponentially growing size of digital-trace data
-that is available, it is important to not only uncover the external and criterion validity of 
-the data and correspondence to real world behaviors (see \hyperlink{paper-1}{Article 1})
-but also important to understand the social forces that lead to the big data. 
-One of the contributions of \hyperlink{paper-2}{Article 2} is to dive deep
-into this question, uncovering why some people choose to use web search engines over other
-information search modalities. These papers are a first step in validating and establishing
-a deeper understanding of who the users are that contribute to macro-level aggregate trends.
+Bridging the contribution of search as an agentic process and critical big data
+studies, this dissertation contributes to the question posed by
+\citet{breigerScaling2015}, "what are the behavioral processes that lead to
+macro-level outcomes?" With the exponentially growing size of digital-trace data
+that is available, it is important to not only uncover the external and
+criterion validity of the data and correspondence to real world behaviors (see
+\hyperlink{paper-1}{Article 1}) but also important to understand the social
+forces that lead to the big data. One of the contributions of
+\hyperlink{paper-2}{Article 2} is to dive deep into this question, uncovering
+why some people choose to use web search engines over other information search
+modalities. These papers are a first step in validating and establishing a
+deeper understanding of who the users are that contribute to macro-level
+aggregate trends.
 
 % social norms
-Additionally, this dissertation investigates how social norms are
-formed in situations of uncertainty, an area that is far less developed in
-sociology. While sociologists have studied social norms since the
-formation of the discipline, norms are most often studied under the lens
-of the emergence of norms and transmission of norms between groups, 
-deviance and social control, the interaction of norms as "mental 
-representations of appropriate behavior" \citep{aarts2003silence}, 
-and research categorizing different types of norms (e.g., descriptive 
-versus injunctive, prescriptive versus proscriptive).  
-The focus on the formation of new social norms during times of uncertainty
-has implications for interventions in social behavioral outcomes, 
-research on cultural change, and the spread of cognitive associations. 
-Moreover, \hyperlink{paper-3}{Article 3} focuses on how conflicting
-behaviors become settled into cognitive associations, providing
-a relevant framework for research on unrest and disasters.
+Additionally, this dissertation investigates how social norms are formed in
+situations of uncertainty, an area that is far less developed in sociology.
+While sociologists have studied social norms since the formation of the
+discipline, norms are most often studied under the lens of the emergence of
+norms and transmission of norms between groups, deviance and social control, the
+interaction of norms as "mental representations of appropriate behavior"
+\citep{aarts2003silence}, and research categorizing different types of norms
+(e.g., descriptive versus injunctive, prescriptive versus proscriptive). The
+focus on the formation of new social norms during times of uncertainty has
+implications for interventions in social behavioral outcomes, research on
+cultural change, and the spread of cognitive associations. Moreover,
+\hyperlink{paper-3}{Article 3} focuses on how conflicting behaviors become
+settled into cognitive associations, providing a relevant framework for research
+on unrest and disasters.
 
 % social networks / diffusion
-This dissertation also has implications for the study of social
-networks and diffusion. \citet{centolaComplexContagionsWeakness2007}
-introduced a pivotal disruption to the diffusion literature when
-they developed complex contagion, the need for reinforcement through multiple
-exposures.  \hyperlink{paper-3}{Article 3} in this dissertation
-takes this disruption one step further to demonstrate that the concordance
-of the exposure affects the contagion process; in other words, being exposed to a 
-diversity of diffusants (discordance) can prevent the diffusant from spreading. 
-This critical finding provides many new areas of exploration for scholars 
-to further investigate the interdependence between different beliefs that
-are diffusing and under what contexts the discordance matters.
+This dissertation also has implications for the study of social networks and
+diffusion. \citet{centolaComplexContagionsWeakness2007} introduced a pivotal
+disruption to the diffusion literature when they developed complex contagion,
+the need for reinforcement through multiple exposures.
+\hyperlink{paper-3}{Article 3} in this dissertation takes this disruption one
+step further to demonstrate that the concordance of the exposure affects the
+contagion process; in other words, being exposed to a diversity of diffusants
+(discordance) can prevent the diffusant from spreading. This critical finding
+provides many new areas of exploration for scholars to further investigate the
+interdependence between different beliefs that are diffusing and under what
+contexts the discordance matters.
 
 % social epidemiology
-I also make important contributions to social epidemiology through this
-research with the use of health case studies for questions of sociological interest
-across my three articles. Because of this, I 
-contribute to the social epidemiological conversation on vaccine hesitancy,
-health communication, and diffusion of high-risk health behaviors. While
-all these areas are important to social epidemiology, there hold
-potential important health implications for these contributions on
-outside of the academy, covered in the first paragraphs of this chapter.
+I also make important contributions to social epidemiology through this research
+with the use of health case studies for questions of sociological interest
+across my three articles. Because of this, I contribute to the social
+epidemiological conversation on vaccine hesitancy, health communication, and
+diffusion of high-risk health behaviors. While all these areas are important to
+social epidemiology, they hold potential important health implications for these
+contributions on outside of the academy, covered in the first paragraphs of this
+chapter.
 

### 2022-03-25 paper1.tex
Final Draft before defense

@@
 
-Computational social science and disciplines such as sociology and
-political science are often quick to adopt new sources of digital 
-trace data for use in academic research. 
-In this article, I examine the validity of Google Search Trends 
-as potential indicators of three different cases, namely attitudes, 
-disease prevalence and political preferences using five
-different validated data sources. I use Pearson and Repeated Measures Correlations 
-between the Google Trends and the validated indicators as well as multiple linear regression
-(for cross-sectional datasets) and random intercept hierarchical linear models
-(for longitudinal datasets) as additional tests of the data. 
-I fail to find correlation among any of the Google 
-Trends tested and their validated indicators. While some Google Trends 
-tested were significantly associated with the outcome in the regression models,
-effects tended to be small and the total model interpretability remained low,
-even when controlling for demographic variables. This article shows that there is no 
-external validity of Google Trends for these uses and social scientists
-will find no replacement for high quality survey data with Google Trends.
+Computational social science and disciplines such as sociology and political
+science are often quick to adopt new sources of digital trace data for use in
+academic research. In this article, I examine the criterion validity of Google
+Search Trends as potential indicators of three different cases, namely
+attitudes, disease prevalence and political preferences using five different
+validated data sources. I use Pearson and Repeated Measures Correlations between
+the Google Trends and the validated indicators as well as multiple linear
+regression (for cross-sectional datasets) and fixed effect hierarchical linear
+models (for longitudinal datasets) as additional tests of the data. I find no
+correlation among any of the Google Trends tested and their validated
+indicators. While some Google Trends tested were significantly associated with
+the outcome in the regression models, effects tended to be small and the total
+model interpretability remained low, even when controlling for demographic
+variables. This article shows that there is no criterion validity of Google
+Trends for these uses and social scientists are not able to use Google Trends as
+a stand-in for high quality survey data.
 
@@
 
-New sources of digital trace data have led to vast possibilities for social science
-research because they are bigger, cheaper, and already available 
+New sources of digital trace data have led to vast possibilities for social
+science research because they are bigger, cheaper, and already available
 \citep{kingEnsuringDataRichFuture2011,lazerComputationalSocialScience2009,salganikBitBitSocial2017}.
-Digital trace data are the expansive volumes of information that are now available with the
-introduction and widespread adoption of the internet and include sources such as  
-social media sites, search data, blogs, adminstrative data on websites, the internet 
-archives, etc. In short, digital trace data are the crumbs that are left as a person
-peruses and interacts in digital spaces. Scholars have noted that these data provide
-many new research avenues for social scientists because they are always on, non-reactive to
-a researcher's observation, and very often captual social interactions and relationships,
-but warn they can be Inaccessible, Non-Representative, and be prone to drifting due to
-algorithmic confounding \citep{salganikBitBitSocial2017}.
-Before overenthusiastically embracing these
-sources and integrating them into our big data toolkits, social scientists must clearly establish
-parameters under which these data sources are appropriate, 
-and for which questions they are useful 
+Digital trace data are the expansive volumes of information that are now
+available with the introduction and widespread adoption of the internet and
+include sources such as social media sites, search data, blogs, administrative
+data on websites, the internet archives, etc. In short, digital trace data are
+the crumbs that are left as a person peruses and interacts in digital spaces.
+Scholars have noted that these data provide many new research avenues for social
+scientists because they are always on, non-reactive to a researcher's
+observation, and very often capture social interactions and relationships, but
+warn they can be inaccessible, non-representative, and be prone to drifting due
+to algorithmic confounding\citep{salganikBitBitSocial2017}. Before
+overenthusiastically embracing these sources and integrating them into our big
+data toolkits, social scientists must clearly establish parameters under which
+these data sources are appropriate, and for which questions they are useful
 \citep{bailCulturalEnvironmentMeasuring2014, lazerParableGoogleFlu2014}. As
-prior research outlined, the "quantity of data does not mean that one
-can ignore foundational issues of measurement and construct validity and
-reliability and dependencies among data" 
-\citep[p. 1203]{lazerParableGoogleFlu2014}.
+prior research outlined, the "quantity of data does not mean that one can ignore
+foundational issues of measurement and construct validity and reliability and
+dependencies among data" \citep[p. 1203]{lazerParableGoogleFlu2014}.
 
 With the expansion of big data, some computational social science research has
-developed extremely innovative methods that have led to groundbreaking results using 
-reliable sources of big data. As an example,\citet{blumenstockPredictingPovertyWealth2015}
-use county-level cell-phone records to construct the distribution of poverty
-and wealth in Rwanda, a country where national surveys and censuses are
-rare and costly. However, \citet{blumenstockPredictingPovertyWealth2015} go to
-great lengths to demonstrate that their use of the cell
-phone data creates a reliable and valid construct; few social science
-papers utilizing big data dig into the construct validity of their
-metrics to this extent and even fewer publications focus on
-methodological guidelines of how to use sources of big data
-\citep[For exceptions, see ][]{asseoTrackingCOVID19Using2020, stilesAssessingCriterionValidity2018}.
-However, research has shown the small adjustments to an algorithm or
-metric may void any research insight we can pull from such data
-\citep{lazerParableGoogleFlu2014}.
+developed extremely innovative methods that have led to groundbreaking results
+using reliable sources of big data. As an
+example,\citet{blumenstockPredictingPovertyWealth2015} use county-level
+cell-phone records to construct the distribution of poverty and wealth in
+Rwanda, a country where national surveys and censuses are rare and costly.
+However, \citet{blumenstockPredictingPovertyWealth2015} go to great lengths to
+demonstrate that their use of the cell phone data creates a reliable and valid
+construct; few social science papers utilizing big data dig into the construct
+validity of their metrics to this extent and even fewer publications focus on
+methodological guidelines of how to use sources of big data \citep[For
+exceptions, see ][]{asseoTrackingCOVID19Using2020,
+stilesAssessingCriterionValidity2018}. However, research has shown the small
+adjustments to an algorithm or metric may void any research insight we can pull
+from such data \citep{lazerParableGoogleFlu2014}.
 
@@
 
-Social scientists have yet to widely utilize Google Search Trends as a source of big data.
-Google Trends is a free and publicly accessible data resource
-provided by Google, a major internet search
-engine worldwide, that analyzes the top search queries across different localities, 
-languages, and time. While Google Trends is freely available and holds a breadth of 
-online activities that could potentially be of use in social science, few social 
-scientists outside of economics have used this resource \citep[see][for examples]{choi2012predicting, jun2018ten,da2011search}.
-This paper provides evidence-based guidelines for social scientist who would use these resources in their toolboxes on how we can triangulate Google Search Trends
-as validated indicators and under what circumstances.
+Social scientists have yet to widely utilize Google Search Trends as a source of
+big data. Google Trends is a free and publicly accessible data resource provided
+by Google, a major internet search engine worldwide, that analyzes the top
+search queries across different localities, languages, and time. While Google
+Trends is freely available and holds a breadth of online activities that could
+potentially be of use in social science, few social scientists outside of
+economics have used this resource \citep[see][for examples]{choi2012predicting,
+jun2018ten,da2011search}. This paper provides evidence-based guidelines for
+social scientist who would use these resources in their toolboxes on how we can
+triangulate Google Search Trends as validated indicators and under what
+circumstances.
 
-Building on prior research outlining the various issues with different sources of big data
-\citep{boydCriticalQuestionsBig2012,lazerIssuesConstructValidity2015},
-this paper evaluates the construct validity of Google Search Trends as an indicator of three different
-cases, namely attitudes, disease prevalence and political preferences.
-These three cases will be tested using attitudinal indicators from the %NORC General Social Survey, 
-CDC \citeyearpar{vaches_data} and New York Times \citeyearpar{mask_data}, 
-health indicators from the CDC \citeyearpar{suic_data}, 
-US cases rates of COVID-19 from The New York Times \citeyearpar{covid_data},  
-and political indicators from the historical US Presidential Election results \citeyearpar{pres_data}.
-% , and the American National Election Survey \citeyearpar{anes_data}.
-This paper will contribute guidance for creating standards of how to use Google
-Trends for social research, and identify potential pitfalls that can compromise the 
-analysis including the focus of this paper, which shows that Google Trends has a
-lack of ecological validity.
+Building on prior research outlining the various issues with different sources
+of big data
+\citep{boydCriticalQuestionsBig2012,lazerIssuesConstructValidity2015}, this
+paper evaluates the construct validity of Google Search Trends as an indicator
+of three different cases, namely attitudes, disease prevalence and political
+preferences. These three cases will be tested using attitudinal indicators from
+the %NORC General Social Survey, CDC \citeyearpar{vaches_data} and New York
+Times \citeyearpar{mask_data}, health indicators from the CDC
+\citeyearpar{suic_data}, US cases rates of COVID-19 from The New York Times
+\citeyearpar{covid_data}, and political indicators from the historical US
+Presidential Election results \citeyearpar{pres_data}. % , and the American
+National Election Survey \citeyearpar{anes_data}. This paper will contribute
+guidance for creating standards of how to use Google Trends for social research,
+and identify potential pitfalls that can compromise the analysis including the
+focus of this paper, which shows that Google Trends has a lack of ecological
+validity.
 
@@
 
-I will use three categorizations of ways I propose Google Trends could
-be utilized for social scientific usage. First, I test Google
-Trends as an indicator of attitudinal indicators. 
-After \citet{bailCulturalEnvironmentMeasuring2014}'s call for
-cultural sociologists to utilize the ever-expanding world of big data,
-Google trends began slowly appearing as a data source in sociological and
-social science research. From research on mass shootings and firearms \citep{brownsteinInternetSearchPatterns2020, semenzaInformationseekingWakeTragedy2020}, 
-protest and anti-Muslim sentiment \citep{bailUsingInternetSearch2018,barrieSearchingRacismGeorge2020,grossThereFergusonEffect2017},
+I will use three categorizations of ways I propose Google Trends could be
+utilized for social scientific usage. First, I test Google Trends as an
+indicator of attitudinal indicators. After
+\citet{bailCulturalEnvironmentMeasuring2014}'s call for cultural sociologists to
+utilize the ever-expanding world of big data, Google trends began slowly
+appearing as a data source in sociological and social science research. From
+research on mass shootings and firearms
+\citep{brownsteinInternetSearchPatterns2020, semenzaInformationseekingWakeTragedy2020},
+protest and anti-Muslim sentiment
+\citep{bailUsingInternetSearch2018,barrieSearchingRacismGeorge2020,grossThereFergusonEffect2017},
 to analyzing country-level changes in social perception \citep{reyes_etal18},
 Google search trends are a new and innovative indicator of cultural interest.
-Extending into social networks and culture, \citet{bailPrestigeProximityPrejudice2019}
-even used Google trends to measure how they saw 'culture' spreads around the globe
-through the proliferation of search terms.
+Extending into social networks and culture,
+\citet{bailPrestigeProximityPrejudice2019} even used Google trends to measure
+how they saw 'culture' spreads around the globe through the proliferation of
+search terms.
 
@@
 
-Google Search Trends have been utilized to estimate disease prevalence
-and population throughout the health sciences. While much of this research has focused on
-the COVID-19 pandemic \citep{jimenez_etal20, jimenezCOVID19SymptomGoogle2020, limEstimatingInformationSeekingBehaviour2020, mavraganiCOVID19PredictabilityUnited2020, nguyenGoogleTrendsAnalysis2020, todorovaInternetBasedData2021, mingUnderstandingHealthCommunication2021},
-other research has investigated Google Trends as indicators of wellbeing
-\citep{brodeurCOVID19LockdownsWellbeing2021, carpiTwitterSubjectiveWellBeing2020, duCOVID19IncreasesOnline2020},
-suicidality \citep{burnettTimeTrendsPublic2020}, 
-vaccination uptake \citep{dalumhansenEnsembleLearnedVaccination2016}, 
-obesity \citep{sarigulNowcastingObesityUsing2014}, 
-and even insomnia \citep{zittingGoogleTrendsReveal2020},
-to cover a few examples. For a partial review of other utilizations, see \citet{nutiUseGoogleTrends2014}. According to \citet{jaidkaInformationseekingVsSharing2021}, the majority of studies profess
-a correlation of \> .70 between the IV and DV, "demonstrating the vast potential of Google
-Search as a proxy for monitoring population health" (p. 3) based on
-assumptions that individuals search because of self-diagnosis and to
-identify possible courses of treatment \citep{dechoudhurySeekingSharingHealth2014}.
+Google Search Trends have been utilized to estimate disease prevalence and
+population throughout the health sciences. While much of this research has
+focused on the COVID-19 pandemic \citep{jimenez_etal20,
+jimenezCOVID19SymptomGoogle2020, limEstimatingInformationSeekingBehaviour2020,
+mavraganiCOVID19PredictabilityUnited2020, nguyenGoogleTrendsAnalysis2020,
+todorovaInternetBasedData2021, mingUnderstandingHealthCommunication2021}, other
+research has investigated Google Trends as indicators of wellbeing
+\citep{brodeurCOVID19LockdownsWellbeing2021,
+carpiTwitterSubjectiveWellBeing2020, duCOVID19IncreasesOnline2020}, suicidality
+\citep{burnettTimeTrendsPublic2020}, vaccination uptake
+\citep{dalumhansenEnsembleLearnedVaccination2016}, obesity
+\citep{sarigulNowcastingObesityUsing2014}, and even insomnia
+\citep{zittingGoogleTrendsReveal2020}, to cover a few examples. For a partial
+review of other utilizations, see \citet{nutiUseGoogleTrends2014}. According to
+\citet{jaidkaInformationseekingVsSharing2021}, the majority of studies profess a
+correlation of \> .70 between the IV and DV, "demonstrating the vast potential
+of Google Search as a proxy for monitoring population health" (p. 3) based on
+assumptions that individuals search because of self-diagnosis and to identify
+possible courses of treatment \citep{dechoudhurySeekingSharingHealth2014}.
 
@@
 
-Various sources have also used Google Trends to forecast
-political elections and political attitudes
-\citep{wolfTrendingRightDirection2018}. For instance,
-\citet{swearingenGoogleInsightsSenate2014} investigate how U.S. Senate
-Elections relate to attention measured by search traffic.
+Various sources have also used Google Trends to forecast political elections and
+political attitudes \citep{wolfTrendingRightDirection2018}. For instance,
+\citet{swearingenGoogleInsightsSenate2014} investigate how U.S. Senate Elections
+relate to attention measured by search traffic.
 \citet{pradoromanGoogleTrendsPredictor2020} demonstrate how Google Search trends
-successfully predicts presidential election results in both the United
-States and Canada. Finally, the OECD Development Centre is investigating
-how Google data can help elucidate governments' approval in Latin
-America \citep{montoyaUsingGoogleData2020}. Overall, the papers 
-cited here find favorable relationships between Google Trends and
-voting outcomes and claim that it is also a valid measure of public attention.
+successfully predicts presidential election results in both the United States
+and Canada. Finally, the OECD Development Centre is investigating how Google
+data can help elucidate governments' approval in Latin America
+\citep{montoyaUsingGoogleData2020}. Overall, the papers cited here find
+favorable relationships between Google Trends and voting outcomes and claim that
+it is also a valid measure of public attention.
 
@@
 While Google Trends has not been widely used or validated by social scientists,
-I am not the first author to investigate its validity.
-Some researchers have cautioned against the wide usage of Google Search Trends. For instance, \citet{asseoTrackingCOVID19Using2020} 
-concludes in their research on COVID-19 case rates and Google searches that the correlation 
-is often spurious and due to confounding. They even explain that "searches would
-result not only from self-symptoms, but also from interest elicited by
-media coverage" \citep[][p.1]{asseoTrackingCOVID19Using2020}.
+I am not the first author to investigate its validity. Some researchers have
+cautioned against the wide usage of Google Search Trends. For instance,
+\citet{asseoTrackingCOVID19Using2020} concludes in their research on COVID-19
+case rates and Google searches that the correlation is often spurious and due to
+confounding. They even explain that "searches would result not only from
+self-symptoms, but also from interest elicited by media coverage"
+\citep[][p.1]{asseoTrackingCOVID19Using2020}.
 
-\citet{rovetta21} also investigates the reliability of COVID-19 searches to infer 
-the quality of the data; the author finds that there are various issues with missing data in 
-smaller regions and significant variation in correlations between the sampled regions throughout
-the study period. Rovetta indicates that this is a cause for concern and is undoubtedly due to more 
-serious causes than behavioral changes among the population or changes in the underlying product algorithm.
+\citet{rovetta21} also investigates the reliability of COVID-19 searches to
+infer the quality of the data; the author finds that there are various issues
+with missing data in smaller regions and significant variation in correlations
+between the sampled regions throughout the study period. Rovetta indicates that
+this is a cause for concern and is undoubtedly due to more serious causes than
+behavioral changes among the population or changes in the underlying product
+algorithm.
 
 \citet{cebrian_domenech22} emphasize in their research that there are some
-non-negligible issues with the measurement of Google Trends, pointing to 
-errors within the purview of accuracy, completeness, consistency, and validity,
-as outlined in \citet{KarrDataQuality}.  
-% I know it is basic stats, but I would provide a footnote explaining each of your terms. Here, these line up with mainline stats but disciplines vary.
- \citet{cebrian_domenech22} point not only to 
-meta issues like the lack of transparency into the sampling methods 
-and population coverage, but they identify real differences 
-in the data provided by the Google Trends API for the same 
-researcher-entered query, pointing to likely internal process 
-used by Google to sample their data to compute the trends.
-These authors show that the variability of the results over time for the same query
-can alter the results of analysis and forecasting significantly. While the 
+non-negligible issues with the measurement of Google Trends, pointing to errors
+within the purview of accuracy, completeness, consistency, and validity, as
+outlined in \citet{KarrDataQuality}. % I know it is basic stats, but I would
+provide a footnote explaining each of your terms. Here, these line up with
+mainline stats but disciplines vary. \citet{cebrian_domenech22} point not only
+to meta issues like the lack of transparency into the sampling methods and
+population coverage, but they identify real differences in the data provided by
+the Google Trends API for the same researcher-entered query, pointing to likely
+internal process used by Google to sample their data to compute the trends.
+These authors show that the variability of the results over time for the same
+query can alter the results of analysis and forecasting significantly. While the
 issue of unreliability isn't unique to the Google Trends API,
-\citet{cebrian_domenech22} propose 
-caution in the use of this digital trace data for other researchers until
-further research can determine the root cause for the inaccuracies.
+\citet{cebrian_domenech22} propose caution in the use of this digital trace data
+for other researchers until further research can determine the root cause for
+the inaccuracies.
 % Yes, big issue. But, it is also seen in machine learning, survey 
 % administration, etc. I’d assume one solution for dealing with fiddly 
-% output is to just sample repetedly and do some sort of average, 
+% output is to just sample repeatedly and do some sort of average, 
 % perhaps with a correction if the direction of the error is non random.
 
-Finally, it is important to note that most of the research using 
-Google Trends as digital trace data do so to indicate
-population's \textit{attention} to a search query. Because
-% I’d also say, the population is examined differently. It is really a population of action remnants being used to get at a population of people, which is presumed to be represented online.
-searches can be done with many different intentions, such as 
-information gathering, navigational purposes, etc., it may
-be hard to declare that an overall level of engagement with a topic
-on Google Search may be indicative of anything more than interest \citep{da2011search}.
-To reference Clifford Geertz's invocation of Ryle, we only know that the search was 
-performed, not whether it indicated a digital wink or twitch \citeyearpar{geertz1973thick}.
+Finally, it is important to note that most of the research using Google Trends
+as digital trace data do so to indicate population's \textit{attention} to a
+search query. Because % I’d also say, the population is examined differently. It
+is really a population of action remnants being used to get at a population of
+people, which is presumed to be represented online. searches can be done with
+many different intentions, such as information gathering, navigational purposes,
+etc., it may be hard to declare that an overall level of engagement with a topic
+on Google Search may be indicative of anything more than interest
+\citep{da2011search}. To reference Clifford Geertz's invocation of Ryle, we only
+know that the search was performed, not whether it indicated a digital wink or
+twitch \citeyearpar{geertz1973thick}.
 % For a soc audience some sort of reference to the dilemma of interpretation would be interesting.
@@
 
-Building on this previous research in the reliability and accuracy of the trends, 
-it is imperative that we provide a framework for how to use diverse sources
-of digital trace data as social scientists. The aim of this paper is
-to take the first step to build that framework. I examine the validity of 
-Google Search Trends to indicate attitudes, health outcomes, or political 
-support using the methods that follow.
+Building on this previous research in the reliability and accuracy of the
+trends, it is imperative that we provide a framework for how to use diverse
+sources of digital trace data as social scientists. The aim of this paper is to
+take the first step to build that framework. I examine the validity of Google
+Search Trends to indicate attitudes, health outcomes, or political support using
+the methods that follow.
 
@@
 
-To test how well Google Trends can be used to indicate other measures, 
-I use various tests to validate the criterion validity of the trends. 
-Criterion validity measures how well one measure, an operationalization of a 
-specific construct, is able to predict a theoretical representation 
-of the construct — the criterion. For this article, I employ 
-concurrent criterion validity which looks at how Google Trends can
-predict various criterions in the same time scale. 
-I gathered geo-located social science data across multiple
-sources to address the three areas of inquiry for this paper.  Table
-\ref{tab:data-sources-table} outlines which data sources I use in this
-project and which trends are matched to each source.
+To test how well Google Trends can be used to indicate other measures, I use
+various tests to validate the criterion validity of the trends. Criterion
+validity measures how well one measure, an operationalization of a specific
+construct, is able to predict a theoretical representation of the construct —
+the criterion. For this article, I employ concurrent criterion validity which
+looks at how Google Trends can predict various criterions in the same time
+scale. I gathered geolocated social science data across multiple sources to
+address the three areas of inquiry for this paper.  Table
+\ref{tab:data-sources-table} outlines which data sources I use in this project
+and which trends are matched to each source.
 
@@
 \subsubsection{Google Trends}
-This paper focuses on a triangulation of Google search trends \citep{googletrends}
-with other sources of credible data.
-Google trends portray the search frequency for specific search terms across
-designated media markets areas (DMAs), a nonoverlapping aggregation of U.S.
-counties to 210 media markets based on Nielsen's classification o "similar population clusters" \citep{dma_key}.
-Raw data is on a scale from zero to one hundred, with one hundred being the maximum search
-popularity out of all DMAs. When available, I use Google search topics to
-measure trends as opposed to search terms. Search topics are a more robust
-measurement than a single search term: topics are aggregations of the rates of
-multiple, highly correlated search terms together into a cohesive topic done
-by Google through it's Knowledge Graph product. For
+This paper focuses on a triangulation of Google search trends
+\citep{googletrends} with other sources of credible data. Google trends portray
+the search frequency for specific search terms across designated media markets
+areas (DMAs), a nonoverlapping aggregation of U.S. counties to 210 media markets
+based on Nielsen's classification o "similar population clusters"
+\citep{dma_key}. Raw data is on a scale from zero to one hundred, with one
+hundred being the maximum search popularity out of all DMAs. When available, I
+use Google search topics to measure trends as opposed to search terms. Search
+topics are a more robust measurement than a single search term: topics are
+aggregations of the rates of multiple, highly correlated search terms together
+into a cohesive topic done by Google through it's Knowledge Graph product. For
 example, while 'Beyoncé', 'Beyonce' and 'beyonce knowles' are all separate
@@
 period across a geography) or as time-series (a single geo-location across
-time). To remedy this and build a longitudinal dataset of each search topic 
-to match the longitudinal validated measures, I follow the method proposed 
-in \citet[][p. 5]{park_etal}\footnote{This method involves building a dataset of unscaled cross-sectional values,
-selecting a DMA to use to establish the rescaling ratio (I use 'Los Angeles
-CA'), and then finding the time-series values for the one DMA. To find the
-rescaling ratio for each week in the time-series, you divide the time-series
-value for each week by the cross-sectional value for each week, resulting in a
-rescaling vector to be used for all weeks in the dataset across geographies. To
-rescale each longitudinal value, multiply the respective week's rescaling ratio
-by the cross-sectional value. To validate this method, I compared the rescaled
-longitudinal data against multiple samples of time-series data. For a more
-in-depth explanation of this procedure, see \citet[p. 5]{park_etal}}. I interpolate 
-missing datapoints in the longitudinal datasets using The Zoo package for R \citep{zoo}.
+time). To remedy this and build a longitudinal dataset of each search topic to
+match the longitudinal validated measures, I follow the method proposed in
+\citet[][p. 5]{park_etal}\footnote{This method involves building a dataset of
+unscaled cross-sectional values, selecting a DMA to use to establish the
+rescaling ratio (I use 'Los Angeles CA'), and then finding the time-series
+values for the one DMA. To find the rescaling ratio for each week in the
+time-series, you divide the time-series value for each week by the
+cross-sectional value for each week, resulting in a rescaling vector to be used
+for all weeks in the dataset across geographies. To rescale each longitudinal
+value, multiply the respective week's rescaling ratio by the cross-sectional
+value. To validate this method, I compared the rescaled longitudinal data
+against multiple samples of time-series data. For a more in-depth explanation of
+this procedure, see \citet[p. 5]{park_etal}}. I interpolate missing data points
+in the longitudinal datasets using The Zoo package for R \citep{zoo}.
 
@@
 One measure of attitudinal indicators is the Vaccine Hesitancy for COVID-19
-\citep{vaches_data}. The CDC uses the U.S. Census Bureau’s Household Pulse Survey
-(HPS) and the 2019 American Community Survey (ACS) 1-year Public Use Microdata
-Sample (PUMS) to measure U.S. residents’ intentions to receive the COVID-19
-vaccine if available during May 26, 2021 – June 7, 2021. This dataset consists
-of 3,148 observations, one for each U.S. County. The variable
-measures the percent of adults in the county who describe themselves as
-“unsure”, “probably not”, or “definitely not” going to get a COVID-19 vaccine
-once one is available to them. The variable ranges from 4.99\% to 32.33\%.
+\citep{vaches_data}. The CDC uses the U.S. Census Bureau’s Household Pulse
+Survey (HPS) and the 2019 American Community Survey (ACS) 1-year Public Use
+Microdata Sample (PUMS) to measure U.S. residents’ intentions to receive the
+COVID-19 vaccine if available during May 26, 2021 – June 7, 2021. This dataset
+consists of 3,148 observations, one for each U.S. County. The variable measures
+the percent of adults in the county who describe themselves as “unsure”,
+“probably not”, or “definitely not” going to get a COVID-19 vaccine once one is
+available to them. The variable ranges from 4.99\% to 32.33\%.
 
 Another attitudinal indicator I use is the Mask-Wearing Survey Data conducted by
-Dynata, a global online market research firm, for the New York Times from 
-July 2 through 14, 2020 \citep{mask_data}. 250,000
-survey respondents were asked, "How often do you wear a mask in public when you
-expect to be within six feet of another person?". The NYT weighted each response
-to create a county level measure of what percent of the county never, rarely,
-sometimes, frequently, and always wore a mask when in public. This dataset
-consists of 3,148 observations, one for each U.S. County included in the sample. This measure
-is purposed to estimate the percent of adults in the county who never or rarely wear a mask
+Dynata, a global online market research firm, for the New York Times from July 2
+through 14, 2020 \citep{mask_data}. 250,000 survey respondents were asked, "How
+often do you wear a mask in public when you expect to be within six feet of
+another person?". The NYT weighted each response to create a county level
+measure of what percent of the county never, rarely, sometimes, frequently, and
+always wore a mask when in public. This dataset consists of 3,148 observations,
+one for each U.S. County included in the sample. This measure is purposed to
+estimate the percent of adults in the county who never or rarely wear a mask
 (range = 0.10\% to 55.80\%).
@@
 I also use U.S. COVID-19 rates to validate health and disease related topics. I
-retrieve U.S. county-level COVID-19 rates from \citet{covid_data}, who compile this
-data based on reports from state and local health agencies. It is widely
+retrieve U.S. county-level COVID-19 rates from \citet{covid_data}, who compile
+this data based on reports from state and local health agencies. It is widely
 acknowledged that there are biases in this data due to inconsistencies and
-availability in testing as well as different community propensity to test
-%  Also blatant political interference in some places, which is probably worth acknowledging.
-\citep{gu22, cdc20a} However, it is the best measure we have of actual case rates
-without extensive adjustments.
-Case Rate is measured as number of cases per 100,000 population. Observations
-vary from a minimum of zero to a maximum of 1460.46 for each Monday from January 27, 2020, through
-December 27, 2021. There are 285,986 cases across 3,136 counties and 101
-dates. Missing data were interpolated using The Zoo package for R \citep{zoo}.
+availability in testing as well as different community propensity to test %
+Also blatant political interference in some places, which is probably worth
+acknowledging. \citep{gu22, cdc20a} However, it is the best measure we have of
+actual case rates without extensive adjustments. Case Rate is measured as number
+of cases per 100,000 population. Observations vary from a minimum of zero to a
+maximum of 1460.46 for each Monday from January 27, 2020, through December 27,
+2021. There are 285,986 cases across 3,136 counties and 101 dates. Missing data
+were interpolated using The Zoo package for R \citep{zoo}.
 
 I also use county-level suicide rates from the US Centers for Disease Control
-and Prevention \citeyearpar{suic_data}. Data is grouped by year from 2010-2020. Raw death
-rates are scaled by population size for each year and can be interpreted as the
-death rate by suicide for every one thousand people. There are 34,683 total
-cases, resulting from 10 observations of 3,147 counties. Missing data were interpolated using
-\texttt{na.approx()} \citep{zoo}. Measures range from 0.034 to 53.254.
+and Prevention \citeyearpar{suic_data}. Data is grouped by year from 2010-2020.
+Raw death rates are scaled by population size for each year and can be
+interpreted as the death rate by suicide for every one thousand people. There
+are 34,683 total cases, resulting from 10 observations of 3,147 counties.
+Missing data were interpolated using \citet{zoo}. Measures range from 0.034 to
+53.254.
 
@@
 
-Finally, I evaluate Google Trends as an indicator of political
-attitudes by first looking at actual voting outcomes in historical US
-Presidential Election results. This data comes from  \citet{pres_data}, who scraped the
-results from Townhall.com, Fox News, Politico, and the New York Times. Data on 
-presidential outcomes were available for 3,147 counties in 2016 and
-3,118 counties in 2020. Each variable measures the percent of votes
-for the candidate, with the lowest percent at 3.09\% and the highest at 92.15\%.
+Finally, I evaluate Google Trends as an indicator of political attitudes by
+first looking at actual voting outcomes in historical US Presidential Election
+results. This data comes from  \citet{pres_data}, who scraped the results from
+Townhall.com, Fox News, Politico, and the New York Times. Data on presidential
+outcomes were available for 3,147 counties in 2016 and 3,118 counties in 2020.
+Each variable measures the percent of votes for the candidate, with the lowest
+percent at 3.09\% and the highest at 92.15\%.
 
@@
 
-In addition to specific measures of interest, I also gathered data on potentially
-confounding variables. The first Seven of these
-variables come from the 2010-2019 5-year American Community Surveys
-\citep{acs2019, acs2018, acs2017, acs2016, acs2015, acs2014, acs2013, acs2012, acs2011, acs2010}. 
-These data include total population, population density,
-unemployment rate for those sixteen years old and over, median county income, average commute
-time, percent of households living under the poverty line, and percent above 65
-years old. In addition, some models employ the U.S. Current Population Survey \&
-American Community Survey Geographic Estimates of Internet Use, 1997-2018
-\citep{internet_use} to estimate households with broadband internet subscriptions.
-This final variable is an attempt to capture the latent propensity to use the
-internet for information search.
+In addition to specific measures of interest, I also gathered data on
+potentially confounding variables. The first Seven of these variables come from
+the 2010-2019 5-year American Community Surveys \citep{acs2019, acs2018,
+acs2017, acs2016, acs2015, acs2014, acs2013, acs2012, acs2011, acs2010}. These
+data include total population, population density, unemployment rate for those
+sixteen years old and over, median county income, average commute time, percent
+of households living under the poverty line, and percent above 65 years old. In
+addition, some models employ the U.S. Current Population Survey \& American
+Community Survey Geographic Estimates of Internet Use, 1997-2018
+\citep{internet_use} to estimate households with broadband internet
+subscriptions. This final variable is an attempt to capture the latent
+propensity to use the internet for information search.
 
@@
 Google Search Trends data and additional demographic data were merged with each
-individual indicator based on County FIPS Codes and date using \texttt{dplyr} in \texttt{r},
-version 4.1.2 \citep{tidyverse}. After creating these different datasets, I use the 
-Pearson correlation formula (\eqref{eq:pearsoncorr}) for cross-sectional 
-numeric data to calculate the strength of the relationship between each Google
-Trend and the respective data source.
+individual indicator based on County FIPS Codes and date using \texttt{dplyr} in
+\texttt{r}, version 4.1.2 \citep{tidyverse}. After creating these different
+datasets, I use the Pearson correlation formula (\eqref{eq:pearsoncorr}) for
+cross-sectional numeric data to calculate the strength of the relationship
+between each Google Trend and the respective data source.
 
@@
 
-As an additional criteria to evaluate the strength of the relationships, 
-I employ multiple linear regression
-(for cross-sectional datasets) and fixed effect hierarchical linear models
-\citep{pinheiro_etal21} (for longitudinal datasets) to identify the strength of
-relationships across locales. Multiple linear regression is appropriate because 
-the cross-sectional data are non-nested which a continous outcome. Hierarchical
-linear models are necessary to control for the between-subject variation 
-in the longitudinal models. Fixed models are appropriate because 
-they extract the between group-differences from the model to allow the reader to 
-focus on the overall effects of each variable. 
-In these models, include location metadata like county population size,
-broadband rates, and median income to adjust for potentially
-confounded relationships between Google search Trends and credible
-indicators. Identifying these possible confounded relationships may help to
-explain why some articles find relationships between the trends and outcomes
-while others did not.
-For linear regression models, I normalize independent
-variables so that each variable across each model is on the same scale and can be compared. 
-In other words, variables have been centered and scaled to have a mean of zero and
-standard deviation of one. Results of these models are in Tables \ref{tab:vacc_hes_analysis} through \ref{tab:pres_2020_analysis}.
+As an additional criteria to evaluate the strength of the relationships, I
+employ multiple linear regression (for cross-sectional datasets) and fixed
+effect hierarchical linear models \citep{pinheiro_etal21} (for longitudinal
+datasets) to identify the strength of relationships across locales. Multiple
+linear regression is appropriate because the cross-sectional data are non-nested
+which a continuous outcome. Hierarchical linear models are necessary to control
+for the between-subject variation in the longitudinal models. Fixed models are
+appropriate because they extract the between group-differences from the model to
+allow the reader to focus on the overall effects of each variable. In these
+models, include location metadata like county population size, broadband rates,
+and median income to adjust for potentially confounded relationships between
+Google search Trends and credible indicators. Identifying these possible
+confounded relationships may help to explain why some articles find
+relationships between the trends and outcomes while others did not. For linear
+regression models, I normalize independent variables so that each variable
+across each model is on the same scale and can be compared. In other words,
+variables have been centered and scaled to have a mean of zero and standard
+deviation of one. Results of these models are in Tables
+\ref{tab:vacc_hes_analysis} through \ref{tab:pres_2020_analysis}.
 
@@
 ('Coronavirus (Disease)' and vaccine hesitancy). Correlation's under |0.40| are
-weak according to the common standards. With only one correlation 
-above that threshold, I conclude that the overall trends are at best weakly
-correlated with these attitudes. When running these
-correlations in multiple linear regression (see the results in Table
-\ref{tab:vacc_hes_analysis}), I see an $r^2$ of 0.233 (Model 1),
-indicating that the Google Trends explains about 23\% of
-the variation in Vaccine Hesitancy alone. Demographic characteristics like the
+weak according to the common standards. With only one correlation above that
+threshold, I conclude that the overall trends are at best weakly correlated with
+these attitudes. When running these correlations in multiple linear regression
+(see the results in Table \ref{tab:vacc_hes_analysis}), I see an $r^2$ of 0.233
+(Model 1), indicating that the Google Trends explains about 23\% of the
+variation in Vaccine Hesitancy alone. Demographic characteristics like the
 percentage of households with broadband internet and the population density are
@@
 models. The Trend coefficients for the trends themselves, however, are
-significant and remain significant when controlling for demographics.
-This reinforces the finding from the Pearson Correlation that there is a significant but weak relationship between the Google Trends and Vaccine Hesitancy.
+significant and remain significant when controlling for demographics. This
+reinforces the finding from the Pearson Correlation that there is a significant
+but weak relationship between the Google Trends and Vaccine Hesitancy.
 
@@
 correlations, reveals similarly weak results with a maximum correlation of 0.32
-between 'smell loss' and rates of COVID-19. To further investigate the relationship, I
-include the three trends in random intercept hierarchical linear models. Model 1
-of Table \ref{tab:covid_analysis} indicates that the trends themselves are able
-to explain about 20\% of the variation in COVID-19 rates ($r^2$ = 0.201). Few
-of the demographic variables influence COVID-19 rates in models 2 or 3,
-though there is some suppression for median income, unemployment rates,
-and population density. Model 3 has an $r^2$ of 0.200. I conclude that the
-Google Trends are slightly related to COVID-19 rates, but that this relationship
-is weak, and we should not attempt to use Google Trends as an indicator of actual
-health outcomes.
+between 'smell loss' and rates of COVID-19. To further investigate the
+relationship, I include the three trends in fixed effect hierarchical linear
+models. Model 1 of Table \ref{tab:covid_analysis} indicates that the trends
+themselves are able to explain about 20\% of the variation in COVID-19 rates
+($r^2$ = 0.201). Few of the demographic variables influence COVID-19 rates in
+models 2 or 3, though there is some suppression for median income, unemployment
+rates, and population density. Model 3 has an $r^2$ of 0.200. I conclude that
+the Google Trends are slightly related to COVID-19 rates, but that this
+relationship is weak, and we should not attempt to use Google Trends as an
+indicator of actual health outcomes.
 
@@
 correlation coefficient we see a maximum of 0.142 correlation, remaining
-negligible. I introduce these trends into a random intercept model to control
-for inter-group variation over time in Table \ref{tab:suicide_analysis}. While
-table \ref{tab:suicide_analysis} model 1 reveals a statistically significant relationship
-between suicide hotline trends and suicide rates, the effect is small, and the
-entire model only has an $r^2$ of 0.058. Adding in demographic features in model
-2 improves the $r^2$ to 0.56. In model 3, the inclusion of Google Trends
-decreases the overall amount of suicide rate variance explained
+negligible. I introduce these trends into a fixed effect model to control for
+inter-group variation over time in Table \ref{tab:suicide_analysis}. While table
+\ref{tab:suicide_analysis} model 1 reveals a statistically significant
+relationship between suicide hotline trends and suicide rates, the effect is
+small, and the entire model only has an $r^2$ of 0.058. Adding in demographic
+features in model 2 improves the $r^2$ to 0.56. In model 3, the inclusion of
+Google Trends decreases the overall amount of suicide rate variance explained
 compared to model 2. These analyses lead me to conclude that Google Search
-Trends should not be used by researchers as indicators of suicide rates or intentions.
+Trends should not be used by researchers as indicators of suicide rates or
+intentions.
 
@@
 predicting the county percentage of votes for Hillary Clinton. Model 1
-demonstrates how well Google Trends predict the votes; while the
-trend for 'Hillary Clinton' is significantly associated with votes, the model's
-$r^2$ ($r^2$ = 0.027) shows that it does little to help explain the model
-variance. On the other hand, adding in demographic features improves the model
-fit quite well, bringing the $r^2$ up to 0.313 in model 2 and $r^2$ 0.327 in
-model 3. Table \ref{tab:pres_2020_analysis} shows this same analysis for the
-2020 election and predicts the percentage of votes for Joe Biden. While this
-model is analogous to those in Table \ref{tab:pres_2016_analysis}, this
-model 1 demonstrates how unrelated Google Trends can be from actual outcomes. In
+demonstrates how well Google Trends predict the votes; while the trend for
+'Hillary Clinton' is significantly associated with votes, the model's $r^2$
+($r^2$ = 0.027) shows that it does little to help explain the model variance. On
+the other hand, adding in demographic features improves the model fit quite
+well, bringing the $r^2$ up to 0.313 in model 2 and $r^2$ 0.327 in model 3.
+Table \ref{tab:pres_2020_analysis} shows this same analysis for the 2020
+election and predicts the percentage of votes for Joe Biden. While this model is
+analogous to those in Table \ref{tab:pres_2016_analysis}, this model 1
+demonstrates how unrelated Google Trends can be from actual outcomes. In
 conclusion, I find that Google Trends are an unreliable and invalid indicator of
@@
 
-This paper provides a test of the criterion validity of Google Trends for use in Social Science. 
-I failed to find correlation between the Google Trends and their 
+This paper provides a test of the criterion validity of Google Trends for use in
+Social Science. I failed to find correlation between the Google Trends and their
 validated indicators. While some Google Trends tested were significantly
-associated with the outcome in the linear regression model, effects tended
-to be small and the total model interpretability remained low, even when 
+associated with the outcome in the linear regression model, effects tended to be
+small and the total model interpretability remained low, even when
 controlling for demographic variables.
 
-Some previous research has shown strong innovation in the computational social sciences
-to gather sociodemographic data when survey or other research methods are too costly
-\citep{blumenstockPredictingPovertyWealth2015}. Google Trends, in theory, sounds like 
-a promising data source to 'nowcast' attitudinal, health, and political indicators.
-Not only would the data be easily and freely accessible, but it would also provide 
-indicators for areas where conducting research may be too costly. The demand for this 
-sort of indicator is clear and fields like the health sciences have freely utilized
-this data source. However, this article shows that Google Trends
-fails to map on to validated survey metrics for attitudes, disease prevalence and political preferences.
-Social scientists should not assume Google Trends data can serve as a replacement
-for high quality survey data, at least for these measures.
+Some previous research has shown strong innovation in the computational social
+sciences to gather sociodemographic data when survey or other research methods
+are too costly \citep{blumenstockPredictingPovertyWealth2015}. Google Trends, in
+theory, sounds like a promising data source to 'nowcast' attitudinal, health,
+and political indicators. Not only would the data be easily and freely
+accessible, but it would also provide indicators for areas where conducting
+research may be too costly. The demand for this sort of indicator is clear and
+fields like the health sciences have freely utilized this data source. However,
+this article shows that Google Trends fails to map on to validated survey
+metrics for attitudes, disease prevalence and political preferences. Social
+scientists should not assume Google Trends data can serve as a replacement for
+high quality survey data, at least for these measures.
 
 As social scientists it is our responsibility to deeply investigate the validity
-of the data that we use so we can be confident in our research findings. As with any
-source of data, we must consider the potential pitfalls, especially in research on 
-using new methods and data sources \citep{mcfarlandBigDataDanger2015}.
-In the case of Google Search Trends, precaution is warranted.
+of the data that we use so we can be confident in our research findings. As with
+any source of data, we must consider the potential pitfalls, especially in
+research on using new methods and data sources
+\citep{mcfarlandBigDataDanger2015}. In the case of Google Search Trends,
+precaution is warranted.

### 2022-03-25 paper2.tex
Final Draft before defense

@@
 information seeking behaviors online and offline. Using theories of 1) social
-support and 2) uses and gratifications theory I investigate the factors associated
-with each modality type when on information seeking modality: personal connection,
-doctor, social networking site, online forum, and online search engine. Using
-novel survey data of 948 Americans and their experience seeking out
-information about the COVID-19 vaccines, I find little evidence that online
-search is more utilized than seeking social support from personal network
+support and 2) uses and gratifications theory I investigate the factors
+associated with each type of information search: 
+personal connection, doctor, social networking site, online forum, and online
+search engine. Using novel survey data of 948 Americans and their experience
+seeking out information about the COVID-19 vaccines, I find little evidence that
+online search is more utilized than seeking social support from personal network
 connections or health professionals. I find evidence that the modalities queried
 in this survey are conceptually different and that the utilization of different
-modalities varies by demography and information sources. Finally, I find that
-different sources of information exposure and information search modalities hold real
-world consequences through their associations with COVID-19 vaccination rates
-and intentions, as information from a doctor increased the COVID-19 vaccination
-uptake while receiving information from a social networking site like Facebook
-or Twitter was associated with lower odds of vaccination.
+modalities varies by demography and information exposure points, where
+individuals are provided with information without seeking it. Finally, I find that
+different sources of information exposure and information search modalities hold
+real world consequences through their associations with COVID-19 vaccination
+intentions and rates, as information from a doctor increases COVID-19
+vaccination uptake while receiving information from a social networking site
+is associated with lower odds of vaccination.
 
@@
 misinformation, disinformation, and mistrust in traditional institutions
-\citep{starbird19, kata10}. While no belief in false information can be thought of as
-harmless \citep{douglas21} some discredited theories such as 'vaccines cause autism'
-have major ramifications for both the individual and public health.
-For example, a newfound public resistance to vaccination
-against Measles by so-called 'anti-vaxxers' caused a 17\% increase in rates
-worldwide in 2019. This increase killed  142,000 people, most of whom were
-children under the age of five \citep{givetash19}. However, even in the ever-evolving
-research agenda of misinformation and infodemiology \citep{eysenbach02}, much of the
-research focuses on the 'push' or 'supply' side of information, like spaces where
+\citep{starbird19, kata10}. While no belief in false information can be thought
+of as harmless \citep{douglas21} some discredited theories such as 'vaccines
+cause autism' have major ramifications for both the individual and public
+health. For example, a newfound public resistance to vaccination against Measles
+by so-called 'anti-vaxxers' caused a 17\% increase in rates worldwide in 2019.
+This increase killed  142,000 people, most of whom were children under the age
+of five \citep{givetash19}. However, even in the ever-evolving research agenda
+of misinformation and infodemiology \citep{eysenbach02}, much of the research
+focuses on the 'push' or 'supply' side of information, like spaces where
 individuals first encounter with conspiracy theories or other information
@@
 individual faces a need for information makes it difficult for policy makers to
-propose effective information campaigns that promote the health and wellbeing of
-individuals in our society. Even outside of the misinformation literature, much
-of the research conducted in social networks and communication focus on senders,
-influencers, and persuasion strategies 
-\citep{mertonManifestLatentFunctions1968, katzPersonalInfluencePart1955, lazarsfeldPeopleChoice1944},
-rather than on “the receiver as an active information seeker and processor." 
-\citep{johnsonComprehensiveModelCancerRelated1993}
-\citep[for an exception, see]{eysenbach09}.
+propose effective information campaigns that promote the health and well-being
+of individuals in our society. Even outside of the misinformation literature,
+much of the research conducted in social networks and communication focus on
+senders, influencers, and persuasion strategies
+\citep{mertonManifestLatentFunctions1968, katzPersonalInfluencePart1955,
+lazarsfeldPeopleChoice1944}, rather than on “the receiver as an active
+information seeker and processor."
+\citep{johnsonComprehensiveModelCancerRelated1993} \citep[for an exception,
+see]{eysenbach09}.
 
 I use the case of information around COVID-19 vaccinations to explore the
-variation of usage of information search modalities. In doing so, I seek to answer
-how computer-mediated or interpersonal information seeking strategies vary
-across populations in their search for information about COVID-19 vaccinations
-and investigate how these strategies affect vaccination uptake. Specifically, this article 
-answers two research questions: (1) How do computer-mediated or interpersonal information seeking
-strategies vary across populations? (2) How does the information search modality utilized 
-affect COVID-19 Vaccination uptake?
+variation of usage of information search modalities. In doing so, I seek to
+answer how computer-mediated or interpersonal information seeking strategies
+vary across populations in their search for information about COVID-19
+vaccinations and investigate how these strategies affect vaccination uptake.
+Specifically, this article answers two research questions: (1) How do
+computer-mediated or interpersonal information seeking strategies vary across
+populations? (2) How does the information search modality utilized affect
+COVID-19 Vaccination uptake?
 
-Before addressing the results to these research questions, I offer an overview of the
-current state of social science literature in regards to information seeking
-strategies and providing a description of the research methodology and
+Before addressing the results to these research questions, I offer an overview
+of the current state of social science literature in regards to information
+seeking strategies and providing a description of the research methodology and
 analytic sample. I then discuss the implications of these findings for the
@@
 
-\hypertarget{information-search}{%
-\subsection{Information Search}\label{information-search}}
+\hypertarget{information-search}{\subsection{Information Search}\label{information-search}}
 
 Active, directed searching by individuals to obtain information is sparsely
-discussed in the sociological literature. Pejtersen \citet{pejtersenDesignComputeraidedUsersystem1984}, a scholar
-of library and information science, theorized that there are five strategies for
-searching for information: browsing, analytical, empirical, known site, and similarity. 
-The most common strategy is browsing, where people
-follow leads based on associations without premeditation. Another strategy is
-analytical, which includes an explicit consideration of all facets of the
-question to guide a search. The empirical method guides the search based on
-tactics that were successful in past research. The known site strategy is to go
-to the direct source of the information if known. And finally, the similarity
-method is to find information based on another similar question that already has
-an answer. These five strategies vary in their demands for prior knowledge,
-cognitive processing, memory, and time spent. While this theory is aimed at
-finding information in a library setting, scholars have extended the theory to
-other fields and validated the framework
-\citep{fidelHumanInformationInteraction2012}; the frame is a useful beginning point
-for my theories of information search through network activation or through
-computer-mediated communication.
+discussed in the sociological literature.
+\citet{pejtersenDesignComputeraidedUsersystem1984}, a scholar of library and
+information science, theorized that there are five strategies for searching for
+information: browsing, analytical, empirical, known site, and similarity. The
+most common strategy is browsing, where people follow leads based on
+associations without premeditation. Another strategy is analytical, which
+includes an explicit consideration of all facets of the question to guide a
+search. The empirical method guides the search based on tactics that were
+successful in past research. The known site strategy is to go to the direct
+source of the information if known. And finally, the similarity method is to
+find information based on another similar question that already has an answer.
+These five strategies vary in their demands for prior knowledge, cognitive
+processing, memory, and time spent. While this theory is aimed at finding
+information in a library setting, scholars have extended the theory to other
+fields and validated the framework \citep{fidelHumanInformationInteraction2012};
+the frame is a useful beginning point for my theories of information search
+through network activation or through computer-mediated communication.
 
@@
 first place. The Theory of Uncertainty Management
-\citep{brashersCommunicationUncertaintyManagement2001} professes that people search
-for information when their uncertainty around the subject leads to anxiety or
-other cognitive harms. The Theory of Motivated Information Management
+\citep{brashersCommunicationUncertaintyManagement2001} professes that people
+search for information when their uncertainty around the subject leads to
+anxiety or other cognitive harms. The Theory of Motivated Information Management
 \citep{afifiTheoryMotivatedInformation2004, afifiSeekingInformationSexual2006}
@@
 interchangeably with the terms social networks and social integration
-\citep{houseStructuresProcessesSocial1988}, are the emotional, informational, and
-instrumental assistance functions performed between social ties and have strong
-and measurable association with health outcomes
+\citep{houseStructuresProcessesSocial1988}, are the emotional, informational,
+and instrumental assistance functions performed between social ties and have
+strong and measurable association with health outcomes
 \citep{houseMeasuresConceptsSocial1985, thoitsMechanismsLinkingSocial2011}.
@@
 coping with life stresses… that may be exchanged among members of a support
-network” \citet[][p. 260]{brashersInformationSeekingAvoiding2002}.These definitions
-help to differentiate between seeking information through social ties or through
-something anonymous like online search; a need for coping or deeper
-understanding of important matters is thought to sway that decision.
+network” \citet[][p. 260]{brashersInformationSeekingAvoiding2002}.These
+definitions help to differentiate between seeking information through social
+ties or through something anonymous like online search; a need for coping or
+deeper understanding of important matters is thought to sway that decision.
 
 Social support has long been theorized to stem from core discussion networks and
-much of the historical social support surveys only examined these core
-networks. The underlying assumption is that individuals reach out to a handful
-of strong ties when in need of support, which could be elicited in surveys using
-name generators \citep{marsdenCoreDiscussionNetworks1987}. This approach has yielded
-important insights, but largely overlooks crucial
-processes of resource activation \citep{hurlbertCoreNetworksTie2000,
-perrySocialNetworkActivation2015, smithDonPutMy2005}. For instance, Small
-\citet{smallSomeoneTalk2017} shows that the core discussion network does not capture
-how people activate social support in practice and indicates that people draw on
-much broader social connections for support, reminiscent of the weak ties
-research by Granovetter \citet{granovetterStrengthWeakTies1973}. There is ongoing
-research investigating how weak-tie support holds for different support types
-based on the architecture put forward by 
-\citet{houseStructuresProcessesSocial1988} of instrumental, emotional, and
-informational support.
+much of the historical social support surveys only examined these core networks.
+The underlying assumption is that individuals reach out to a handful of strong
+ties when in need of support, which could be elicited in surveys using name
+generators \citep{marsdenCoreDiscussionNetworks1987}. This approach has yielded
+important insights, but largely overlooks crucial processes of resource
+activation \citep{hurlbertCoreNetworksTie2000, perrySocialNetworkActivation2015,
+smithDonPutMy2005}. For instance, Small \citet{smallSomeoneTalk2017} shows that
+the core discussion network does not capture how people activate social support
+in practice and indicates that people draw on much broader social connections
+for support, reminiscent of the weak ties research by Granovetter
+\citet{granovetterStrengthWeakTies1973}. There is ongoing research investigating
+how weak-tie support holds for different support types based on the architecture
+put forward by \citet{houseStructuresProcessesSocial1988} of instrumental,
+emotional, and informational support.
 
@@
 context, namely via computer-mediated information search tools such as the
-process of “Googling”, or the utilization of internet search engines. 
-As the online environment began penetrating all facets of
-modern human life, it makes sense that performing online search has become one
-of the most convenient modalities for information search. Small
-\citet{smallSomeoneTalk2017} showed that Graduate students often
-confided in a "miscellaneous classmates encountered down the hall" (p.
-176) instead of established and trusted confidants because they
-simply were there at the right time. I theorize that online search engines
-may be the most frictionless and costless mode of support. 
-No social capital or relationship is necessary when choosing to utilize a search engine.
+process of “Googling”, or the utilization of internet search engines. As the
+online environment began penetrating all facets of modern human life, it makes
+sense that performing online search has become one of the most convenient
+modalities for information search. Small \citet{smallSomeoneTalk2017} showed
+that Graduate students often confided in a "miscellaneous classmates encountered
+down the hall" (p. 176) instead of established and trusted confidants because
+they simply were there at the right time. I theorize that online search engines
+may be the most frictionless and costless mode of support. No social capital or
+relationship is necessary when choosing to utilize a search engine.
 
@@
 borrow uses and gratifications theory (UGT) from studies of mass communication
-\citep{blumlerUsesMassCommunications1974, tanMassCommunicationTheories1985}. 
-UGT posits that users are not passive consumers of media and that people have an
+\citep{blumlerUsesMassCommunications1974, tanMassCommunicationTheories1985}. UGT
+posits that users are not passive consumers of media and that people have an
 active role in choosing different sources of media based on their satisfaction
 of specific needs on an individual basis. UGT is based on Maslow’s
-\citeyear{maslowTheoryHumanMotivation1943} hierarchy of needs and is compatible with
-Lazarsfeld and Katz’s theory of two-step flow \cite{katzPersonalInfluencePart1955}
-because people can choose their media and the opinion leaders they follow.
-Modern-day theorists have extended UGT theory and classified the uses and
-gratifications of the internet and of social media. 
+\citeyear{maslowTheoryHumanMotivation1943} hierarchy of needs and is compatible
+with Lazarsfeld and Katz’s theory of two-step flow
+\cite{katzPersonalInfluencePart1955} because people can choose their media and
+the opinion leaders they follow. Modern-day theorists have extended UGT theory
+and classified the uses and gratifications of the internet and of social media.
 \citet{staffordDeterminingUsesGratifications2004} theorize that the internet
@@
 potential avoidance of embarrassment and other negative social interactions,
-especially in the case on search engines. \citet{rainsCopingIllnessDigitally2018}
-finds that patients tend to search for
+especially in the case on search engines.
+\citet{rainsCopingIllnessDigitally2018} finds that patients tend to search for
 technical information about an illness online but they then turn to their social
 network for experiential information from others facing similar circumstances in
-the case of cancer. The type of information sought is therefore important.
-If specific expertise on a specific topic is desired by a searcher, they may
-reach out to personal connections that they see as expert such as a doctor, or
-if an individual distrusts the medical establishment, they may be more likely to
+the case of cancer. The type of information sought is therefore important. If
+specific expertise on a specific topic is desired by a searcher, they may reach
+out to personal connections that they see as expert such as a doctor, or if an
+individual distrusts the medical establishment, they may be more likely to
 activate informational support among their social network or turn to online
-groups that validate their worldview \citep{bogersHowSocialAre2014}. Finally, UGT and
-Brasher's definition of social support \citeyearpar{brashersInformationSeekingAvoiding2002}
-help us to theorize that the psychosocial needs like identity management or relational
-maintenance of an individual may influence their chosen information search modality: 
-when the informational need is related to forming and deepening social ties search 
-is likely to be done from network ties.
+groups that validate their worldview \citep{bogersHowSocialAre2014}. Finally,
+UGT and Brasher's definition of social support
+\citeyearpar{brashersInformationSeekingAvoiding2002} help us to theorize that
+the psychosocial needs like identity management or relational maintenance of an
+individual may influence the chosen information search modality: when the
+informational need is related to forming and deepening social ties search is
+likely to be done from network ties.
 
@@
 
-\hypertarget{research-methodology}{%
-\section{Research Methodology}\label{research-methodology}}
+\hypertarget{research-methodology}{\section{Research Methodology}\label{research-methodology}}
 
 The data used for this research project are based on original survey data
-collected between December 03, 2021 through December 12, 2021.
-This survey was hosted on Qualtrics and participants were paid and 
-recruited using Amazon Turk (MTurk). Potential MTurkers were invited
-to participate if they were located in the United States, had a task
-rate approval of over 95 percent, had completed 50 tasks, and had not 
-completed this survey in previous sessions. The total valid 
+collected between December 03, 2021 through December 12, 2021. This survey was
+hosted on Qualtrics and participants were paid and recruited using Amazon Turk
+(MTurk). Potential MTurkers were invited to participate if they were located in
+the United States, had a task rate approval of over 95 percent, had completed 50
+tasks, and had not completed this survey in previous sessions. The total valid
 survey responses (\emph{n} = 948) were selected from a total of 1,066
@@
 responses), poor quality typed responses (e.g., social network alters
-consistently named random nouns), or taking the survey more than once. The sample
-is slightly gender unbalanced, skewing towards male respondents. For the
-respondents who provided their zip code (p = 0.98), the sample is quite balanced with
-a slight skew towards MTurkers in the South (p = 0.41).
+consistently named random nouns), or taking the survey more than once. The
+sample is slightly gender unbalanced, skewing towards male respondents. For the
+respondents who provided their zip code (p = 0.98), the sample is quite balanced
+with a slight skew towards MTurkers in the South (p = 0.41).
 
-The survey took an average of 24.48 minutes with a standard deviation of 13.23 minutes.
-The shortest valid survey took 3.75 minutes and the longest took 111.08 minutes.
-Participants received \$6.00 in compensation for their participation in the survey
-\footnote{All funding for this survey was provided by a Grant awarded to Kelsey E. 
-Gonzalez and Nicolas Legewie by the Summer Institute in Computational Social Science
-and the Russell Sage Foundation.}. The survey consisted of two main parts. The
-first portion of the survey is a replication of they survey conducted by 
+The survey took an average of 24.48 minutes with a standard deviation of 13.23
+minutes. The shortest valid survey took 3.75 minutes and the longest took 111.08
+minutes. Participants received \$6.00 in compensation for their participation in
+the survey \footnote{All funding for this survey was provided by a Grant from
+the Summer Institute in Computational Social Science and the Russell Sage
+Foundation.}. The survey consisted of two main parts. The first portion of the
+survey is a replication of they survey conducted by
 \citet{smallSomeoneTalk2017}. In this section, we expand Small's research on
 support activation by segregating weak-tie social support into instrumental,
-emotional, and informational categories \citep[see][]{houseStructuresProcessesSocial1988}.
-The second part of the survey focuses on network resource activation and 
-information seeking behaviors of individuals regarding COVID-19 vaccinations
-for this paper.
+emotional, and informational categories
+\citep[see][]{houseStructuresProcessesSocial1988}. The second part of the survey
+focuses on network resource activation and information seeking behaviors of
+individuals regarding COVID-19 vaccinations for this paper.
 
@@
 Further dependent variables segment the above question into multiple options;
-``How did you look for information about the COVID-19 vaccine?'' Respondents were
-posed with 5 responses and `other,' of which they could select multiple. The
-largest proportion, 44\%, asked their `doctor or another health professional'.
-About 42\% said they asked, `a person like friend, neighbor, or family member 
-that [they] know'. An additional 41\% searched `for [their] question
-using an online search engine such as Google or Bing'. About a quarter of the
-sample, 27\%, `posted queries in an online discussion group, listserv, or 
-other online forum like a Facebook Group or Subreddit'. And finally, 18\% of 
-the sample `posted queries on a social networking site such as Facebook timeline, 
-Twitter status update, or LinkedIn'.
-Much of the question wording and the specific categories of search were inspired
-by ICPSR project 37220 \citep{scanlon19}.
+``How did you look for information about the COVID-19 vaccine?'' Respondents
+were posed with 5 responses and `other,' of which they could select multiple.
+The largest proportion, 44\%, asked their `doctor or another health
+professional'. About 42\% said they asked, `a person like friend, neighbor, or
+family member that [they] know'. An additional 41\% searched `for [their]
+question using an online search engine such as Google or Bing'. About a quarter
+of the sample, 27\%, `posted queries in an online discussion group, listserv, or
+other online forum like a Facebook Group or Subreddit'. And finally, 18\% of the
+sample `posted queries on a social networking site such as Facebook timeline,
+Twitter status update, or LinkedIn'. Much of the question wording and the
+specific categories of search were inspired by ICPSR project 37220
+\citep{scanlon19}.
 
-\hypertarget{vaccination-outlook}{%
-\subsubsection{Vaccination Outlook}\label{vaccination-outlook}}
+\hypertarget{vaccination-outlook}{\subsubsection{Vaccination Outlook}\label{vaccination-outlook}}
 
@@
 Another Dependent variable for this analysis is a dichotomous variable
-indicating whether the respondent has received or plans to receive a vaccination against
-COVID-19. For this survey, the number of doses or timeline of receipt were less
-relevant to the research question. This variable instead focuses on intent or
-opinion about the vaccine. About 87\% have a
-positive view about the vaccine. This construct is made through the combination
-of two survey items. The first item is actual vaccination status, obtained through
-the question `Did you receive a COVID-19 vaccine?'
-84\% of the sample said that
-they had indeed received a vaccination (95\% Confidence Interval = \{82\%, 87\%\}).
-As the national vaccination rate is closer to 75\% \citep{cdc20}, this indicates 
-some bias in our sample that must be
-acknowledged: either MTurkers are more likely to be vaccinated that the normal
-population (sampling bias) or there is some conformity bias in the responses
-causing survey takers to provide false answers. The second survey item that
-contributes to `Vaccination Outlook' was only given to those who had not
-responded `yes' to the to their vaccination status. These respondents were asked 
-`Do you plan to receive a vaccine for the prevention of the COVID-19 virus?' Of those
-who were asked this question (n = 147), 9\% said they were `definitely yes' getting the vaccine;
-9\% said they were `probably yes' going to receive vaccine. The rest of the sample was
-more unsure: 15\% said they `Might or might not,' 26\% said `Probably not,' and finally
-41\% said they would `definitely not' receive the vaccine. The variable `Vaccination 
-Outlook' indicates that either the respondent received a COVID-19 vaccine or
-either probably or definitely will in the future.
+indicating whether the respondent has received or plans to receive a vaccination
+against COVID-19. For this survey, the number of doses or timeline of receipt
+were less relevant to the research question. This variable instead focuses on
+intent or opinion about the vaccine. About 87\% have a positive view about the
+vaccine. This construct is made through the combination of two survey items. The
+first item is actual vaccination status, obtained through the question `Did you
+receive a COVID-19 vaccine?' 84\% of the sample said that they had indeed
+received a vaccination (95\% Confidence Interval = \{82\%, 87\%\}). As the
+national vaccination rate is closer to 75\% \citep{cdc20}, this indicates some
+bias in our sample that must be acknowledged: either MTurkers are more likely to
+be vaccinated that the normal population (sampling bias) or there is some
+conformity bias in the responses causing survey takers to provide false answers.
+The second survey item that contributes to `Vaccination Outlook' was only given
+to those who had not responded `yes' to the to their vaccination status. These
+respondents were asked `Do you plan to receive a vaccine for the prevention of
+the COVID-19 virus?' Of those who were asked this question (n = 147), 9\% said
+they were `definitely yes' getting the vaccine; 9\% said they were `probably
+yes' going to receive vaccine. The rest of the sample was more unsure: 15\% said
+they `Might or might not,' 26\% said `Probably not,' and finally 41\% said they
+would `definitely not' receive the vaccine. The variable `Vaccination Outlook'
+indicates that either the respondent received a COVID-19 vaccine or either
+probably or definitely will in the future.
 
@@
 `In the past 12 months, without searching for it, did you receive information
-about the COVID-19 vaccine from \ldots{} (check all sources you received information
-from).' This differs from the `How did you look for information' question above
-because this is based on passive reception of information. The largest proportion
-of respondents had received information from "a person like friend, neighbor, or
-family member that [they] know" (\(\widehat{p}\) = 67\%). Respondents
-also commonly received information from a television news channel
-or a newspaper, about 65\% of the sample.
-47\% of the sample had received information from
-their doctor or other health professional, while 40\%
-received information from a social networking site such as Facebook timeline,
-Twitter status update, or LinkedIn. Finally, the lowest proportion of the sample
-had received information from an online discussion group, listserv, or other
-online forum like a Facebook group or subreddit
-(\(\widehat{p}\) = 35\%).
+about the COVID-19 vaccine from \ldots{} (check all sources you received
+information from).' This differs from the `How did you look for information'
+question above because this is based on passive reception of information. The
+largest proportion of respondents had received information from "a person like
+friend, neighbor, or family member that [they] know" (\(\widehat{p}\) = 67\%).
+Respondents also commonly received information from a television news channel or
+a newspaper, about 65\% of the sample. 47\% of the sample had received
+information from their doctor or other health professional, while 40\% received
+information from a social networking site such as Facebook timeline, Twitter
+status update, or LinkedIn. Finally, the lowest proportion of the sample had
+received information from an online discussion group, listserv, or other online
+forum like a Facebook group or subreddit (\(\widehat{p}\) = 35\%).
 
-We also asked various demographic questions to describe our sample. The
-average age of our sample was 37.76. 44\% of our sample self-identified as female, 
-while 55\% self-identified as male. The sample is diverse racially though some ethnic
-groups are underrepresented compared to national averages. Race was evaluated using the
-question, `What is your race? If you are ``mixed race,'' select all that apply.'
-Because of the multi-selection question, each variable is dichotomous and
-proportions are shown. 88\% of the sample claimed
-they were `White,' 8\% claimed to be `Black or
-African American,' 3\% chose `American Indian or
-Alaskan Native,' 4\% selected `Asian,' and finally
-when asked, `Are you Hispanic, Latino/a/x, or Latin American Origin?'
-15\% selected `Yes.' Respondents were also asked to
-select the highest level of education that you have completed. Based on the
-breakdown between `Less than high school,' `High school graduate,' `Some college,'
-`Associate's or Technical degree,' `Bachelor's degree,' and `Graduate or
-professional degree,' 74\% of the sample were classified
-to have a college-level education (Associate's degree or above).
+We also asked various demographic questions to describe our sample. The average
+age of our sample was 37.76. 44\% of our sample self-identified as female, while
+55\% self-identified as male. The sample is diverse racially though some ethnic
+groups are underrepresented compared to national averages. Race was evaluated
+using the question, `What is your race? If you are ``mixed race,'' select all
+that apply.' Because of the multi-selection question, each variable is
+dichotomous and proportions are shown. 88\% of the sample claimed they were
+`White,' 8\% claimed to be `Black or African American,' 3\% chose `American
+Indian or Alaskan Native,' 4\% selected `Asian,' and finally when asked, `Are
+you Hispanic, Latino/a/x, or Latin American Origin?' 15\% selected `Yes.'
+Respondents were also asked to select the highest level of education that you
+have completed. Based on the breakdown between `Less than high school,' `High
+school graduate,' `Some college,' `Associate's or Technical degree,' `Bachelor's
+degree,' and `Graduate or professional degree,' 74\% of the sample were
+classified to have a college-level education (Associate's degree or above).
 
@@
 
-My analytic strategy proceeds in four steps. In Tables \ref{tab:table-1-ind}
-\& \ref{tab:table-2-dep}, I present descriptive statistics for all study
-variables, including variable ranges, means, and standard deviations. For this
-paper, I rely heavily on logistic regression, modeled in \texttt{r}; specifically, I
-fit a series of binomial generalized linear models with a logit link \citep{venables2002a},
-otherwise known as logistic regression model \citep{hothorn2006handbook}.
-This approach is appropriate because the data
-are non-nested, cross-sectional data with binary independent variables. In Table \ref{tab:table-model-1}
-\footnote{All Tables in this paper were created with the modelsummary package in \texttt{r} 
-\citep{modelsummary}},I fit a logistic regression model predicting
-whether someone sought information about COVID-19 using their sources of
-information (`Received info') as well as various demographic variables such as
-age, education level and race. Figure \ref{fig:plot-model-1} then illustrates
-the relationship between the coefficients and information seeking.\footnote{Figures 
-in this paper were all created using the \texttt{r} packages jtools \citep{jtools}
-and ggplot2 \citep{wickham_etal, wickham11}}.
-In Table \ref{tab:model-2-phi}, I disaggregate information seeking behaviors by
-investigating the difference in proportions of each of the 5 different avenues
-of seeking information about COVID-19: from another person, from a doctor, on an
-online forum, on a social networking site, or using an online search tool. I
-investigate these differences through a phi coefficient \citep{warrens08}, otherwise
-known as a mean square contingency coefficient, which is used to investigate the
-degree of association between two binary variables.\footnote{To calculate the Phi
-  Coefficient, I utilize the Psych \texttt{r} package \citep{psych}} I then investigate the
-associations between my predictors and the five information search modalities by
-modelling a series of logistic regressions in Table \ref{tab:table-model-2}.
-Finally, in Table \ref{tab:table-model-3}, I investigate whether there is a
-relationship between information exposure sources, information seeking behaviors and
-the choice to get vaccinated against COVID-19 through a logistic regression
-model predicting Vaccination Outlook. Figure \ref{fig:plot-model-3} then
-illustrates the relationship between the coefficients and vaccination outlook.
+My analytic strategy proceeds in four steps. In Tables \ref{tab:table-1-ind} \&
+\ref{tab:table-2-dep}, I present descriptive statistics for all study variables,
+including variable ranges, means, and standard deviations. For this paper, I
+rely heavily on logistic regression, modeled in \texttt{r}; specifically, I fit
+a series of binomial generalized linear models with a logit link
+\citep{venables2002a}, otherwise known as logistic regression model
+\citep{hothorn2006handbook}. This approach is appropriate because the data are
+non-nested, cross-sectional data with binary independent variables. In Table
+\ref{tab:table-model-1} \footnote{All Tables in this paper were created with the
+modelsummary package in \texttt{r} \citep{modelsummary}},I fit a logistic
+regression model predicting whether someone sought information about COVID-19
+using their sources of information (`Received info') as well as various
+demographic variables such as age, education level and race. Figure
+\ref{fig:plot-model-1} then illustrates the relationship between the
+coefficients and information seeking.\footnote{Figures in this paper were all
+created using the \texttt{r} packages jtools \citep{jtools} and ggplot2
+\citep{wickham_etal, wickham11}}. In Table \ref{tab:model-2-phi}, I disaggregate
+information seeking behaviors by investigating the difference in proportions of
+each of the 5 different avenues of seeking information about COVID-19: from
+another person, from a doctor, on an online forum, on a social networking site,
+or using an online search tool. I investigate these differences through a phi
+coefficient \citep{warrens08}, otherwise known as a mean square contingency
+coefficient, which is used to investigate the degree of association between two
+binary variables.\footnote{To calculate the Phi Coefficient, I utilize the Psych
+\texttt{r} package \citep{psych}} I then investigate the associations between my
+predictors and the five information search modalities by modelling a series of
+logistic regressions in Table \ref{tab:table-model-2}. Finally, in Table
+\ref{tab:table-model-3}, I investigate whether there is a relationship between
+information exposure sources, information seeking behaviors and the choice to
+get vaccinated against COVID-19 through a logistic regression model predicting
+Vaccination Outlook. Figure \ref{fig:plot-model-3} then illustrates the
+relationship between the coefficients and vaccination outlook.
 
@@
 seeking out information. For example, respondents who had received information
-from a doctor or other medical professional were 2.82 (odds ratio = \(exp(\beta k)\),
-\emph{p} \textless{} 0.001) times more likely to seek out information over someone
-who had not. Similarly, respondents who had received information from `a
+from a doctor or other medical professional were 2.82 (odds ratio = \(exp(\beta
+k)\), \emph{p} \textless{} 0.001) times more likely to seek out information over
+someone who had not. Similarly, respondents who had received information from `a
 person like friend, neighbor, or family member that [they] know' were 1.87
@@
 someone who had not received information from a person like that. Interesting,
-those who had received information from an online discussion group, listserv,
-or other online forum including a Facebook group or subreddit were 2.39 (\emph{p}
-\textless{} 0.001) times more likely to search out more information than 
-someone who had not. While most demographic variables do not seem to have a 
-strong effect on whether someone sought out information about the COVID-19 
-vaccine, a few key variables had strong associations.  Respondents who are 
-older are more likely to seek information; The odds are about 3\% higher when 
-age is equal to x + 1 relative to x, possibly indicating a generational effect
-of information seeking patterns (\emph{p} \textless{} 0.01). Additionally,
-those who were more educated, that is those with an Associate's degree or higher,
-were 1.58 more likely to seek additional information than those without the degree
-(\emph{p} \textless{} 0.05). And finally, there is evidence to suggest that the Black or
+those who had received information from an online discussion group, listserv, or
+other online forum including a Facebook group or subreddit were 2.39 (\emph{p}
+\textless{} 0.001) times more likely to search out more information than someone
+who had not. While most demographic variables do not seem to have a strong
+effect on whether someone sought out information about the COVID-19 vaccine, a
+few key variables had strong associations.  Respondents who are older are more
+likely to seek information; The odds are about 3\% higher when age is equal to x
++ 1 relative to x, possibly indicating a generational effect of information
+seeking patterns (\emph{p} \textless{} 0.01). Additionally, those who were more
+educated, that is those with an Associate's degree or higher, were 1.58 more
+likely to seek additional information than those without the degree (\emph{p}
+\textless{} 0.05). And finally, there is evidence to suggest that the Black or
 African American sample was more likely to seek out information, specifically:
-Blacks were 3.58 times more likely to seek out information over non-Blacks (\emph{p}
-\textless{} 0.05). Figure \ref{fig:plot-model-1} illustrates the relationship
-between the coefficients and information seeking.
+Blacks were 3.58 times more likely to seek out information over non-Blacks
+(\emph{p} \textless{} 0.05). Figure \ref{fig:plot-model-1} illustrates the
+relationship between the coefficients and information seeking.
 
@@
 \ref{tab:table-1-ind} reveals differences in the prevalence of usage of the
-various information seeking modalities: Around 40\% of the sample has inquired for
-information from a doctor, a person, or using online search tool (44\%, 42\%, 41\%), while my
-respondents used modalities like online forums (27\%) and social networking sites (18\%)
-to seek out information at significantly lower rates.
+various information seeking modalities: Around 40\% of the sample has inquired
+for information from a doctor, a person, or using online search tool (44\%,
+42\%, 41\%), while my respondents used modalities like online forums (27\%) and
+social networking sites (18\%) to seek out information at significantly lower
+rates.
 
-To investigate how each
-Information Search modality are related to each other using the Phi Coefficient
-($\phi$) of binary association between each Information Search modality pair.
-The Phi coefficient can be interpreted like a correlation coefficient, with
-numbers closer to -1 indicating a very strong negative relationship and those closer to 
-positive 1 indicating a very strong positive relationship
-(Warrens 2008). Table \ref{tab:model-2-phi} shows the results of these
-coefficients. Out of the five information search modalities investigated, there is
-evidence that the modalities are distinctly different concepts because most
-coefficients fall under 0.3, the general cutoff for correlation
-coefficients to indicate a relationship. There does seem to be a relationship
-between Online Forums and social networking sites, possibly due to an
-individual's latent propensity to use online networks over in-person networks. These
-coefficients indicate a weak relationship between any two modalities of
-information search and that respondents in my sample utilize each of these a
-little bit differently.
+To investigate how each Information Search modality are related to each other
+using the Phi Coefficient ($\phi$) of binary association between each
+Information Search modality pair. The Phi coefficient can be interpreted like a
+correlation coefficient, with numbers closer to -1 indicating a very strong
+negative relationship and those closer to positive 1 indicating a very strong
+positive relationship (Warrens 2008). Table \ref{tab:model-2-phi} shows the
+results of these coefficients. Out of the five information search modalities
+investigated, there is evidence that the modalities are distinctly different
+concepts because most coefficients fall under 0.3, the general cutoff for
+correlation coefficients to indicate a relationship. There does seem to be a
+relationship between Online Forums and social networking sites, possibly due to
+an individual's latent propensity to use online networks over in-person
+networks. These coefficients indicate a weak relationship between any two
+modalities of information search and that respondents in my sample utilize each
+of these a little bit differently.
 
-I find that indeed the most common modalities are 
-asking a doctor, asking a friend, and asking a search engine which confirms
-Hypthesis \ref{hyp:drgooglefriend}. However, because the modalities 95\% confidence intervals 
-in Table \ref{tab:table-1-ind}
-are overlapping, I fail to find evidence for Hypothesis \ref{hyp:online-vs-network},
-that using an online search engine was more commonplace than asking a friend.
+I find that indeed the most common modalities are asking a doctor, asking a
+friend, and asking a search engine which confirms Hypothesis
+\ref{hyp:drgooglefriend}. However, because the modalities 95\% confidence
+intervals in Table \ref{tab:table-1-ind} are overlapping, I fail to find
+evidence for Hypothesis \ref{hyp:online-vs-network}, that using an online search
+engine was more commonplace than asking a friend.
 
@@
 
-I conduct a separate logistic regression for each search modality in Table \ref{tab:table-model-2}. 
-Modeling each response as a separate formula is useful for interpretation, but
-there are important caveats: because each logistic regression is on a different
-scale, one must not compare the magnitude of coefficients between models. We
-can, however, use the direction and significance of the coefficients to draw
-conclusions about these different forms of information search modalities.
+I conduct a separate logistic regression for each search modality in Table
+\ref{tab:table-model-2}. Modeling each response as a separate formula is useful
+for interpretation, but there are important caveats: because each logistic
+regression is on a different scale, one must not compare the magnitude of
+coefficients between models. We can, however, use the direction and significance
+of the coefficients to draw conclusions about these different forms of
+information search modalities.
 
-The first model in Table \ref{tab:table-model-2} predicts whether a
-respondent sought information intentionally about COVID-19 vaccinations by
-asking their doctor or another health professional. First and foremost, I find
-that those who received information about COVID-19 vaccinations were
-6.97 times more likely to seek out more information from their doctor than those who had
-not (\emph{p} \textless{} 0.001). However, receiving information from other modalities also
-increased the odds of seeking out information from medical professions. Those who
-received information from a person such as a friend or a relative were
-2.23 times more likely to ask their doctor (\emph{p} \textless{} 0.001), while those who received
-information from the news or television were 1.55 times more likely (\emph{p} \textless{} 0.01). 
-I also find that those who received information from an online forum like a subreddit were 51\%
-more likely to ask their doctors than those who had not (\emph{p} \textless{} 0.05). 
-Finally, respondents with an Associate's degree or higher were 72\%
-more likely to ask their doctor for information on the COVID-19 vaccinations
-than those who held less education (\emph{p} \textless{} 0.01).
+The first model in Table \ref{tab:table-model-2} predicts whether a respondent
+sought information intentionally about COVID-19 vaccinations by asking their
+doctor or another health professional. First and foremost, I find that those who
+received information about COVID-19 vaccinations were 6.97 times more likely to
+seek out more information from their doctor than those who had not (\emph{p}
+\textless{} 0.001). However, receiving information from other modalities also
+increased the odds of seeking out information from medical professions. Those
+who received information from a person such as a friend or a relative were 2.23
+times more likely to ask their doctor (\emph{p} \textless{} 0.001), while those
+who received information from the news or television were 1.55 times more likely
+(\emph{p} \textless{} 0.01). I also find that those who received information
+from an online forum like a subreddit were 51\% more likely to ask their doctors
+than those who had not (\emph{p} \textless{} 0.05). Finally, respondents with an
+Associate's degree or higher were 72\% more likely to ask their doctor for
+information on the COVID-19 vaccinations than those who held less education
+(\emph{p} \textless{} 0.01).
 
-The second model predicts whether a respondent sought information about
-COVID-19 vaccinations by asking a person like friend, neighbor, or family member
-that they know. Only three coefficients in this model were significant and help
-us draw any conclusions on who is most likely to activate their personal social
+The second model predicts whether a respondent sought information about COVID-19
+vaccinations by asking a person like friend, neighbor, or family member that
+they know. Only three coefficients in this model were significant and help us
+draw any conclusions on who is most likely to activate their personal social
 network for informational support. In this study, I find that receiving
@@
 networking site is associated with seeking out more information. Those who
-received information from a doctor or other medical professional were 3.08
-times more likely to seek information from a person such as a friend (\emph{p} \textless{} 0.001).
-Moreover, it seems that receiving information from your personal social network,
-such as a friend or relative, is associated with seeking information from those
-same people; in fact, I find that those who did are 3.32 more
-likely to do so (\emph{p} \textless{} 0.001). Finally, the respondents who received information
-about the vaccine on a social networking site were 55\%
-more likely to seek information from their personal network than those who had not
-(\emph{p} \textless{} 0.01). The unexpected result of this model is that very few factors predict
-personal social network activation, and this model has the lowest McFadden's R\^{}2,
-indicating possible omitted variables.
+received information from a doctor or other medical professional were 3.08 times
+more likely to seek information from a person such as a friend (\emph{p}
+\textless{} 0.001). Moreover, it seems that receiving information from your
+personal social network, such as a friend or relative, is associated with
+seeking information from those same people; in fact, I find that those who did
+are 3.32 more likely to do so (\emph{p} \textless{} 0.001). Finally, the
+respondents who received information about the vaccine on a social networking
+site were 55\% more likely to seek information from their personal network than
+those who had not (\emph{p} \textless{} 0.01). The unexpected result of this
+model is that very few factors predict personal social network activation, and
+this model has the lowest McFadden's R\^{}2, indicating possible omitted
+variables.
 
-I also wanted to examine what factors were associated with posting in an online discussion
-group, listserv, or other online forum like a Facebook Group or Subreddit about
-COVID-19 vaccinations. This is conceptually different than posting a query on a
-social networking site like Facebook or twitter where identities are involved,
-but is theoretically more social friction than searching on an internet
-search engine. I found that having received information about the vaccine from
-your personal social network (such as a friend or relative), the news, or an online
-forum was associated with higher odds of querying an online forum. Specifically,
-receiving information from your personal network is associated with 2.07
-higher odds (\emph{p} \textless{} 0.001), from news or television media with 1.43 
-higher odds (\emph{p} \textless{} 0.05), and receiving information on an online
-forum associated with 3.55 higher odds (\emph{p} \textless{} 0.001). Moreover,
-I found that those with an Associate's degree or above were 2.96 times more
-likely to search for information on an online forum (\emph{p} \textless{} 0.001).
-Finally, I found that Hispanic-Latinos were about 70\% more likely to query 
-an online forum than non-Hispanics (\emph{p} \textless{} 0.05). However, 
-there were also a few variables that lowered the odds of posting in an 
-online discussion group. First, those who had received information from
-a social networking site were 45\% less likely to query a forum than those 
-who had not (odds ratio = \(1 - exp(\beta k)\), \emph{p} \textless{} 0.01).
-Moreover, I found additional ethnoracial effects: Respondents who claimed
-Asian ancestry were 92\% less likely to query online forum (\emph{p} \textless{} 0.01).
+I also wanted to examine what factors were associated with posting in an online
+discussion group, listserv, or other online forum like a Facebook Group or
+Subreddit about COVID-19 vaccinations. This is conceptually different than
+posting a query on a social networking site like Facebook or twitter where
+identities are involved, but is theoretically more social friction than
+searching on an internet search engine. I found that having received information
+about the vaccine from your personal social network (such as a friend or
+relative), the news, or an online forum was associated with higher odds of
+querying an online forum. Specifically, receiving information from your personal
+network is associated with 2.07 higher odds (\emph{p} \textless{} 0.001), from
+news or television media with 1.43 higher odds (\emph{p} \textless{} 0.05), and
+receiving information on an online forum associated with 3.55 higher odds
+(\emph{p} \textless{} 0.001). Moreover, I found that those with an Associate's
+degree or above were 2.96 times more likely to search for information on an
+online forum (\emph{p} \textless{} 0.001). Finally, I found that
+Hispanic-Latinos were about 70\% more likely to query an online forum than
+non-Hispanics (\emph{p} \textless{} 0.05). However, there were also a few
+variables that lowered the odds of posting in an online discussion group. First,
+those who had received information from a social networking site were 45\% less
+likely to query a forum than those who had not (odds ratio = \(1 - exp(\beta
+k)\), \emph{p} \textless{} 0.01). Moreover, I found additional ethnoracial
+effects: Respondents who claimed Asian ancestry were 92\% less likely to query
+online forum (\emph{p} \textless{} 0.01).
 
 The fourth model predicts whether an individual sought information about
-COVID-19 vaccinations through posted queries on a social networking site such
-as Facebook timeline, Twitter status update, or LinkedIn. Receiving information
+COVID-19 vaccinations through posted queries on a social networking site such as
+Facebook timeline, Twitter status update, or LinkedIn. Receiving information
 about COVID-19 seems to be quite related to posting on social media. Those who
-received information from their doctors had 1.72 
-higher odds of posting on a social networking site (\emph{p} \textless{} 0.01), while those
-who received their information from tv/news had 1.67 higher odds (\emph{p} \textless{} 0.05).
+received information from their doctors had 1.72 higher odds of posting on a
+social networking site (\emph{p} \textless{} 0.01), while those who received
+their information from tv/news had 1.67 higher odds (\emph{p} \textless{} 0.05).
 Furthermore, those who received information on social networking sites were more
-likely to post queries on social networking sites (\(\beta\) = 2.08, \emph{p} \textless{} 0.001).
-The respondents in our sample who received information from online forums had 2.65
-higher odds of posting queries on their social networking platforms (\emph{p} \textless{} 0.001).
-I found a relationship between education and posting on social networking sites
-as well; specifically, those with an Associate's degree or above were 3.83 times more likely to post vaccination
-queries on social networking sites than those with lower education (\emph{p} \textless{} 0.001).
-Finally, I find that Hispanic-Latinos were 88\%
-more likely to ask their connections on a social networking site about the
-COVID-19 vaccinations than non-Hispanics (\emph{p} \textless{} 0.01).
+likely to post queries on social networking sites (\(\beta\) = 2.08, \emph{p}
+\textless{} 0.001). The respondents in our sample who received information from
+online forums had 2.65 higher odds of posting queries on their social networking
+platforms (\emph{p} \textless{} 0.001). I found a relationship between education
+and posting on social networking sites as well; specifically, those with an
+Associate's degree or above were 3.83 times more likely to post vaccination
+queries on social networking sites than those with lower education (\emph{p}
+\textless{} 0.001). Finally, I find that Hispanic-Latinos were 88\% more likely
+to ask their connections on a social networking site about the COVID-19
+vaccinations than non-Hispanics (\emph{p} \textless{} 0.01).
 
 Searching for information using an online search engine such as Google or Bing
-is theoretically the search modality with the least amount of social or cognitive
-friction. Our descriptive statistics showed that not everyone used this modality,
-with only 41\% of our sample (See Table \ref{tab:table-1-ind}) having sought
-information about the COVID-19 vaccines using online search engines. My model
-reveals interesting patterns to help explain the variation. As with previous
-models, receiving information of any kind increase the odds of online search,
-though to varying magnitudes (Doctor: 1.54 odds; Person: 1.44 odds; 
-News or Television: 2.98 odds; 
-social networking site: 3.57 odds; Online Forum: 2 odds). I also find that older respondents
-were more likely to search online, with each addition year aged to yield 3\%
-higher odds of searching online (\emph{p} \textless{} 0.001). The most interesting variations
-come from what decreases the odds of online search. First, those with an
-Associate's degree or higher were 61\%
-less likely to search online for questions about COVID-19 than those with less
-educational attainment (\emph{p} \textless{} 0.001). In addition, I find that Hispanic-Latinos
-had 44\% lower odds of searching online than non-Hispanics (\emph{p} \textless{} 0.05).
+is theoretically the search modality with the least amount of social or
+cognitive friction. Our descriptive statistics showed that not everyone used
+this modality, with only 41\% of our sample (See Table \ref{tab:table-1-ind})
+having sought information about the COVID-19 vaccines using online search
+engines. My model reveals interesting patterns to help explain the variation. As
+with previous models, receiving information of any kind increase the odds of
+online search, though to varying magnitudes (Doctor: 1.54 odds; Person: 1.44
+odds; News or Television: 2.98 odds; social networking site: 3.57 odds; Online
+Forum: 2 odds). I also find that older respondents were more likely to search
+online, with each addition year aged to yield 3\% higher odds of searching
+online (\emph{p} \textless{} 0.001). The most interesting variations come from
+what decreases the odds of online search. First, those with an Associate's
+degree or higher were 61\% less likely to search online for questions about
+COVID-19 than those with less educational attainment (\emph{p} \textless{}
+0.001). In addition, I find that Hispanic-Latinos had 44\% lower odds of
+searching online than non-Hispanics (\emph{p} \textless{} 0.05).
 
@@
 model predicting Vaccination Outlook. I find that receiving information from a
-doctor or other medical profession is associated with 2.85 odds of choosing
-to receive a COVID-19 vaccination (\emph{p} \textless{} 0.001) and that seeking 
-information from a doctor also increases the odds of vaccination by 4 (\emph{p} \textless{} 0.001).
-I find that my respondents who received information on a social networking site
-like Facebook or Twitter about the vaccines were 55\%
-\textbf{less likely} to choose to get vaccinated than those who received no information through
-that modality (\emph{p} \textless{} 0.001). However, I did find that those who reached out to
-family or friends with their concerns were 77\% more likely to become vaccinated 
-(\emph{p} \textless{} 0.05). Furthermore, my respondents who held an Associate's degree
-or above had 3.6 higher odds of becoming immunized (\emph{p} \textless{} 0.001).
-And finally, I found further ethnoracial differences in my sample. I found that
-Hispanic-Latinos had 2.83 higher odds of vaccination than non-Hispanics
-(\emph{p} \textless{} 0.05) and that my Asian sample had 4.73 higher odds as well over
-non-Asians (\emph{p}  = 0.09). See Figure \ref{fig:plot-model-3} for a visual
-representation of how these different coefficients are related to vaccination outlook.
+doctor or other medical profession is associated with 2.85 odds of choosing to
+receive a COVID-19 vaccination (\emph{p} \textless{} 0.001) and that seeking
+information from a doctor also increases the odds of vaccination by 4 (\emph{p}
+\textless{} 0.001). I find that my respondents who received information on a
+social networking site like Facebook or Twitter about the vaccines were 55\%
+\textbf{less likely} to choose to get vaccinated than those who received no
+information through that modality (\emph{p} \textless{} 0.001). However, I did
+find that those who reached out to family or friends with their concerns were
+77\% more likely to become vaccinated (\emph{p} \textless{} 0.05). Furthermore,
+my respondents who held an Associate's degree or above had 3.6 higher odds of
+becoming immunized (\emph{p} \textless{} 0.001). And finally, I found further
+ethnoracial differences in my sample. I found that Hispanic-Latinos had 2.83
+higher odds of vaccination than non-Hispanics (\emph{p} \textless{} 0.05) and
+that my Asian sample had 4.73 higher odds as well over non-Asians (\emph{p}  =
+0.09). See Figure \ref{fig:plot-model-3} for a visual representation of how
+these different coefficients are related to vaccination outlook.
 
@@
 distinguish between the activation of information seeking behaviors online and
-offline. In this paper, I sought to uncover just how different various methods of
-information search are and begin a line of research inquiry that investigates
+offline. In this paper, I sought to uncover just how different various methods
+of information search are and begin a line of research inquiry that investigates
 the factors associated with each different modality. Finally, I also uncovered
@@
 
-I first find that being exposed to information about COVID-19 vaccinations from any 
-source increases the likelihood of searching out more information. I
-also find important demographic differences in the overall propensity to seek
-out information. First, I find that the older a respondent is, the more likely
-they are to seek out information about COVID-19 vaccinations, possibly
-indicating a larger information need by elderly populations overall, or a more
-pressing need to search for information about the COVID-19 vaccinations because
-of the higher risk of hospitalizations that older populations face
-\citep{turner_etal18}. Furthermore, I find that those who are college educated were
-more likely to seek out information; for the most part this trend can be
-observed in Table \ref{tab:table-model-2} as well. Human Capital Theory
-\citep{mirowsky_ross98} may help to explain this finding; this theory claims that
-higher education can provides the skills to gain health-related knowledge and
-use this knowledge to be proactive in their own lives. Finally, I find that my
-respondents who identified as Black were more likely to seek out further
-information; this may be explained by the maltreatment that African Americans
-have endured in the US healthcare system \citep{baileyStructuralRacismHealth2017}
-which has led to major distrust of the medical establishment among the
-population \citep{center2019, murray15, bronson2014don}.
+I first find that being exposed to information about COVID-19 vaccinations from
+any source increases the likelihood of searching out more information. I also
+find important demographic differences in the overall propensity to seek out
+information. First, I find that the older a respondent is, the more likely they
+are to seek out information about COVID-19 vaccinations, possibly indicating a
+larger information need by elderly populations overall, or a more pressing need
+to search for information about the COVID-19 vaccinations because of the higher
+risk of hospitalizations that older populations face \citep{turner_etal18}.
+Furthermore, I find that those who are college educated were more likely to seek
+out information; for the most part this trend can be observed in Table
+\ref{tab:table-model-2} as well. Human Capital Theory \citep{mirowsky_ross98}
+may help to explain this finding; this theory claims that higher education can
+provides the skills to gain health-related knowledge and use this knowledge to
+be proactive in their own lives. Finally, I find that my respondents who
+identified as Black were more likely to seek out further information; this may
+be explained by the maltreatment that African Americans have endured in the US
+healthcare system \citep{baileyStructuralRacismHealth2017} which has led to
+major distrust of the medical establishment among the population
+\citep{center2019, murray15, bronson2014don}.
 
-Table \ref{tab:table-model-2} further demonstrated important takeaways about
-how individuals seek information. First, I find that the different information
-seeking modalities queried in this survey are conceptually different and that the
-utilization of different varies by demographic and information exposure source. 
-Overall, being exposed to information about COVID-19 vaccinations from any 
-source is associated with information seeking behaviors,
-though there are key variations. First, if one received information from a
-doctor, they were likely to search from information from a doctor; this may
-indicate an already existing trusting relationship between patient and
-healthcare provider but it may also indicate the healthcare provider taking
-initiative and emphasizing the importance of the vaccine or the survey respondent
-seeking out information from an expert. Another important finding is that if you
-received information from a social networking site like Facebook or Twitter, you
-were less likely to query Online Forums like Reddit or Facebook Groups; this may
-be an example of Uses and Gratification Theory
-\citep{blumlerUsesMassCommunications1974}, where the two online platforms may act as
-substitute sources of information and those who were satisfied with the
-information they received on a social networking site didn't have the need to
-seek out more information. Finally, the ethnoracial variations exhibited in
-Table \ref{tab:table-model-2} likely demonstrate how cultural attitudes around
-the trustworthiness of different sources of information affect the utilization
-of different methods; for example, Asians seem are less likely to use online
-forums than non-Asians, while Hispanics are more likely to use them than
-non-Hispanics. The internal variations between the different information search
-modalities hint at different user profiles and may have major repercussions on the
-quality of information they find and who is exposed to poor quality information.
+Table \ref{tab:table-model-2} further demonstrated important takeaways about how
+individuals seek information. First, I find that the different information
+seeking modalities queried in this survey are conceptually different and that
+the utilization of different varies by demographic and information exposure
+source. Overall, being exposed to information about COVID-19 vaccinations from
+any source is associated with information seeking behaviors, though there are
+key variations. First, if one received information from a doctor, they were
+likely to search from information from a doctor; this may indicate an already
+existing trusting relationship between patient and healthcare provider but it
+may also indicate the healthcare provider taking initiative and emphasizing the
+importance of the vaccine or the survey respondent seeking out information from
+an expert. Another important finding is that if you received information from a
+social networking site like Facebook or Twitter, you were less likely to query
+Online Forums like Reddit or Facebook Groups; this may be an example of Uses and
+Gratification Theory \citep{blumlerUsesMassCommunications1974}, where the two
+online platforms may act as substitute sources of information and those who were
+satisfied with the information they received on a social networking site didn't
+have the need to seek out more information. Finally, the ethnoracial variations
+exhibited in Table \ref{tab:table-model-2} likely demonstrate how cultural
+attitudes around the trustworthiness of different sources of information affect
+the utilization of different methods; for example, Asians seem are less likely
+to use online forums than non-Asians, while Hispanics are more likely to use
+them than non-Hispanics. The internal variations between the different
+information search modalities hint at different user profiles and may have major
+repercussions on the quality of information they find and who is exposed to poor
+quality information.
 
 Given the rampant misinformation around COVID-19, its related vaccinations
-\citep{pathakInfodemicsCOVID19Role2020, mottaHowRightLeaningMedia2020, shahsavariConspiracyTimeCorona2020},
-and the slowed rate of vaccinations in the
+\citep{pathakInfodemicsCOVID19Role2020, mottaHowRightLeaningMedia2020,
+shahsavariConspiracyTimeCorona2020}, and the slowed rate of vaccinations in the
 United States, it is important to uncover what relationship the different
-sources of information exposure and information search modalities for COVID-19 vaccinations
-are associated with compliance with public health recommendations. Table
-\ref{tab:table-model-3} demonstrated just how these different sources of information 
-exposure and information search modalities are associated with real world
-consequences through COVID-19 vaccination rates and intentions. The first
+sources of information exposure and information search modalities for COVID-19
+vaccinations are associated with compliance with public health recommendations.
+Table \ref{tab:table-model-3} demonstrated just how these different sources of
+information exposure and information search modalities are associated with real
+world consequences through COVID-19 vaccination rates and intentions. The first
 takeaway is that receiving or seeking information from a doctor or other medical
-profession was associated with higher likelihood of completed or planned vaccinations.
-While blanket advice like ``Healthcare Providers should recommend the vaccine to
-their patients'' would be ineffective because of the declining number of
-Americans with a primary care doctor \citep{levine_etal20}, increasing trust in the
-institution of medicine seems to remain a strong predictor of vaccinations.
-A second major takeaway is that receiving information from a Social Networking
-Site like Facebook timeline or Twitter status update was significantly
-associated with lower vaccination rates. While we do not know what exact
-information was absorbed on these platforms, the lower odds of vaccination
+profession was associated with higher likelihood of completed or planned
+vaccinations. While blanket advice like ``Healthcare Providers should recommend
+the vaccine to their patients'' would be ineffective because of the declining
+number of Americans with a primary care doctor \citep{levine_etal20}, increasing
+trust in the institution of medicine seems to remain a strong predictor of
+vaccinations. A second major takeaway is that receiving information from a
+Social Networking Site like Facebook timeline or Twitter status update was
+significantly associated with lower vaccination rates. While we do not know what
+exact information was absorbed on these platforms, the lower odds of vaccination
 indicate that it was not positive. Much has been attempted between 2020 and 2022
 to curb vaccine misinformation on these social networking platforms
-\citep[see][for an early example]{bowman20}; however, I find evidence that these social
-networking platforms nevertheless have a measurable negative impact. Finally,
-this study also contributes to the conversation on ethnoracial and
+\citep[see][for an early example]{bowman20}; however, I find evidence that these
+social networking platforms nevertheless have a measurable negative impact.
+Finally, this study also contributes to the conversation on ethnoracial and
 educational differences in vaccine hesitancy. I find in my sample that
@@
 \ref{tab:table-model-3}). Research in this area has mixed results, with some
-studies showcasing consistent findings to these \citep{bagasra_etal21,king_etal21},
-while others show that Whites have the lowest levels of vaccine hesitancy and
-many minorities are much more hesitant \citep{momplaisir_etal21, foxworth21}. 
-My finding that college-educated respondents were more likely seek vaccination is 
-largely consistent with the broader literature m\citep{khairat_etal22}, though 
-again there are many variations depending on the vaccine
-in question and study context \citep{siddiqui_etal13}.
+studies showcasing consistent findings to these
+\citep{bagasra_etal21,king_etal21}, while others show that Whites have the
+lowest levels of vaccine hesitancy and many minorities are much more hesitant
+\citep{momplaisir_etal21, foxworth21}. My finding that college-educated
+respondents were more likely seek vaccination is largely consistent with the
+broader literature m\citep{khairat_etal22}, though again there are many
+variations depending on the vaccine in question and study context
+\citep{siddiqui_etal13}.
 
@@
 Given the large swaths of both misinformation and disinformation regarding
-COVID-19 \citep{pathakInfodemicsCOVID19Role2020, mottaHowRightLeaningMedia2020, shahsavariConspiracyTimeCorona2020} 
-and the measurable impacts this misinformation has had on pandemic-related health behaviors
-\citep{loombaMeasuringImpactCOVID192021, greene_murphy21}, COVID-19 provides an ideal study to
-investigate how we choose to search for information that affects both our own
-lives and the lives of others.
+COVID-19 \citep{pathakInfodemicsCOVID19Role2020, mottaHowRightLeaningMedia2020,
+shahsavariConspiracyTimeCorona2020} and the measurable impacts this
+misinformation has had on pandemic-related health behaviors
+\citep{loombaMeasuringImpactCOVID192021, greene_murphy21}, COVID-19 provides an
+ideal study to investigate how we choose to search for information that affects
+both our own lives and the lives of others.
 
@@
 information campaigns. However, these findings are not to be taken out of the
-context of their limitations. This paper is built off a small survey sample (948)
-that was hosted online and anonymously through MTurk, a service
-that provides people with micro-jobs. Because of the structure of the website,
-respondents are incentivized to fill out surveys and other tasks 
-as quick as possible and there is no incentive for respondents to be honest
-in their responses. For the same reason, there were many responses that 
-were poor quality and removed from the sample before analysis.
-However, each of these limitations are common critiques of 
-survey research as a whole. Even given these limitations,
-the finding of this paper are interesting and timely contributions to the literature.
+context of their limitations. This paper is built off a small survey sample
+(948) that was hosted online and anonymously through MTurk, a service that
+provides people with micro-jobs. Because of the structure of the website,
+respondents are incentivized to fill out surveys and other tasks as quick as
+possible and there is no incentive for respondents to be honest in their
+responses. For the same reason, there were many responses that were poor quality
+and removed from the sample before analysis. However, each of these limitations
+are common critiques of survey research as a whole. Even given these
+limitations, the finding of this paper are interesting and timely contributions
+to the literature.
 

### 2022-03-25 paper3.tex
Final Draft before defense

@@
 
-This paper examines how social norms are formed under conditions of uncertainty
-using the case studies of stay-at-home and vaccination rates during the COVID-19
-pandemic. I test fear-based models of behavioral adaption to public health
-recommendations as well as patterns of complex social contagion using linear
-mixed effects models. These models show that complex contagion is a valid
-framework for the social contagion of new norms during COVID-19. Importantly, I
-find a novel moderating effect of signal discordance, the contextual diversity
-of signals received by an ego. In other words, if there is diversity in the
-information received by an ego, contagion is less likely to occur. This article
-is an important contribution to literature on diffusion and social networks, as
-it shows that the contagion process cannot be not fully understood without
-looking at the context of each exposure to a contagion within  within the range
-of contagions one experiences.
+My final article takes a deeper dive into the formation of social norms
+governing health behaviors in cases of extreme uncertainty using the cases of
+both stay-at-home rates and vaccination rates as responses to public health
+recommendations to mitigate the COVID-19 pandemic. Using theories like
+associative diffusion and the integrated theoretical framework of norms, I test
+models of behavioral adaption to public health recommendations and patterns of
+complex contagion (the need for repeated exposures to a something novel for it
+to diffuse) using linear mixed effects models. These models show that complex
+contagion is a valid framework for the social contagion of new norms during
+COVID-19. Importantly, I find a novel moderating effect of signal discordance,
+the contextual diversity of signals received by an ego. If there is diversity in
+the information received by an ego, contagion is less likely to occur. This
+paper shows that the contagion process cannot be not fully understood without
+looking at the context of each exposure to a contagion within the range of
+contagions one experiences.
 
-Keywords: Social Networks, Social Norms, Health Behavior, Diffusion, Contagion
+Keywords: Social Networks, Complex Contagion, Social Norms, Health Behavior, Diffusion
 
-\hypertarget{background}{%
-\section{Background}\label{background}}
+\hypertarget{background}{\section{Background}\label{background}}
 
@@
 (COVID-19) became a leading cause of death in the United States. Although the
-Centers for Disease Control and Prevention (CDC) \citeyearpar{centersfordiseasecontrolandpreventionHowProtectYourself2020} proposed several potential mitigation strategies, the method of mitigation that received the most national
-attention is the call to stay-at-home and social distance for non-essential
-workers. CDC officials and frontline health care professionals advise that the
-best way to prevent exposure to the virus is to stay at home and avoid close
-contact with people.
+Centers for Disease Control and Prevention (CDC)
+\citeyearpar{centersfordiseasecontrolandpreventionHowProtectYourself2020}
+proposed several potential mitigation strategies, the method of mitigation that
+received the most national attention is the call to stay-at-home and social
+distance for non-essential workers. CDC officials and front line health care
+professionals advise that the best way to prevent exposure to the virus is to
+stay-at-home and avoid close contact with people.
 
@@
 variation in how individuals came to understand the threats of the disease
-\citep{akpanAssociationWhatPeople2021, bailey_etal20}, but also due to habitus: the
-ingrained habits, skills and dispositions of individuals and groups
+\citep{akpanAssociationWhatPeople2021, bailey_etal20}, but also due to habitus:
+the ingrained habits, skills and dispositions of individuals and groups
 \citep{bourdieu77}. Habitus shapes how individuals perceive different social
 interactions and norms and shape how they adopt different policies, leading to
-different social outcomes and a divergence of attitudes \citep{scottarthur_etal21, williams95, madeira_etal18}.
+different social outcomes and a divergence of attitudes
+\citep{scottarthur_etal21, williams95, madeira_etal18}.
 
@@
 after the onset of the COVID-19 pandemic
-\citep{bargainTrustCompliancePublic2020, bourassaStatelevelStayathomeOrders2020, bourassaSocialDistancingHealth2020, grossmanPoliticalPartisanshipInfluences2020, haggerPredictingSocialDistancing2020, hillBloodChristCompels2020, hillNastiestQuestion, hillLoveThyAged2021,huynhDoesCultureMatter2020}, most research focused on unchanging cultural
-determinants of the reduction in stay-at-home rates. For instance, \citet{gibbons_etal21}
- finds that social capital had spatially inconsistent effects on
-stay-at-home rates. Instead of focusing on cultural relationships with
-stay-at-home rates, this paper will instead focus on the dynamic nature of
-population mobility across population networks.
+\citep{bargainTrustCompliancePublic2020, bourassaStatelevelStayathomeOrders2020,
+bourassaSocialDistancingHealth2020, grossmanPoliticalPartisanshipInfluences2020,
+haggerPredictingSocialDistancing2020, hillBloodChristCompels2020,
+hillNastiestQuestion, hillLoveThyAged2021,huynhDoesCultureMatter2020}, most
+research focused on unchanging cultural determinants of the reduction in
+stay-at-home rates. For instance, \citet{gibbons_etal21} finds that social
+capital had spatially inconsistent effects on stay-at-home rates. Instead of
+focusing on cultural relationships with stay-at-home rates, this paper will
+instead focus on the dynamic nature of population mobility across population
+networks.
 
-There is more research on vaccine uptake \citep{schmidBarriersInfluenzaVaccination2017}
- because of increased hesitancy and
-anti-vaccination movements over previous decades \citep{baumgaertnerInfluencePoliticalIdeology2018, hornseyDonaldTrumpVaccination2020, johnsonOnlineCompetitionPro2020, whiteheadHowCultureWars2020}.
-While some studies use social network analysis to
-study the discussions for an against vaccinations online \citep{milaniVisualVaccineDebate2020}, vaccination rates are a great way to
+There is more research on vaccine uptake
+\citep{schmidBarriersInfluenzaVaccination2017} because of increased hesitancy
+and anti-vaccination movements over previous decades
+\citep{baumgaertnerInfluencePoliticalIdeology2018,
+hornseyDonaldTrumpVaccination2020, johnsonOnlineCompetitionPro2020,
+whiteheadHowCultureWars2020}. While some studies use social network analysis to
+study the discussions for an against vaccinations online
+\citep{milaniVisualVaccineDebate2020}, vaccination rates are a great way to
 investigate the establishment of new social norms. First, vaccination uptake is
-measurable with stable information tracking infrastructure and vaccination
-rates are varied across locations and time. Secondly, because vaccines have 
-become politicized \citep{mottaRepublicansNotDemocrats2021, mottaIdentifyingPrevalenceCorrelates2021}, the social contagion effects can be
+measurable with stable information tracking infrastructure and vaccination rates
+are varied across locations and time. Secondly, because vaccines have become
+politicized \citep{mottaRepublicansNotDemocrats2021,
+mottaIdentifyingPrevalenceCorrelates2021}, the social contagion effects can be
 studied.
@@
 This article researches the formation of social norms governing health behaviors
-in cases of extreme uncertainty during the COVID-19 pandemic. Using theories of complex
-contagion, associative diffusion and the integrated theoretical framework of
-norms, I test how these health behaviors are outcomes of contagion and
-discordance of signals, as well as other factors affecting associations like
-religious and political conservatism, attention to television media sources,
-and online norms as measured by information-search behaviors. Before outlining
-my central hypotheses, I offer an overview of the current state of the social
+in cases of extreme uncertainty during the COVID-19 pandemic. Using theories of
+complex contagion, associative diffusion and the integrated theoretical
+framework of norms, I test how these health behaviors are outcomes of contagion
+and discordance of signals, as well as other factors affecting associations like
+religious and political conservatism, attention to television media sources, and
+online norms as measured by information-search behaviors. Before outlining my
+central hypotheses, I offer an overview of the current state of the social
 contagion literature. After that, I will outline how I compiled this unique
@@
 define and calculate signal and discordance, two key independent variables for
-this paper. To model stay-at-home and vaccination rates, I use linear mixed effects
-models with random effects as a longitudinal model of contagion. After
+this paper. To model stay-at-home and vaccination rates, I use linear mixed
+effects models with random effects as a longitudinal model of contagion. After
 interpreting the results of the models, I discuss the implications of these
@@
 
-\hypertarget{the-social-contagion-model}{%
-\subsection{The Social Contagion Model}\label{the-social-contagion-model}}
+\hypertarget{the-social-contagion-model}{\subsection{The Social Contagion Model}\label{the-social-contagion-model}}
 
@@
 strongest locally, leading to the emergence of clusters of people sharing
-similar behavior'' \citep{kitts_shi18}. This community
-interaction ultimately leads to converged communities of belief structures with
-variations in how much they diverge from the norm \citep{cullumCulturalEvolutionInterpersonal2007, lataneExperimentalEvidenceDynamic1996, okadaStructureCulturalRejection2017}.
+similar behavior'' \citep{kitts_shi18}. This community interaction ultimately
+leads to converged communities of belief structures with variations in how much
+they diverge from the norm \citep{cullumCulturalEvolutionInterpersonal2007,
+lataneExperimentalEvidenceDynamic1996, okadaStructureCulturalRejection2017}.
 
 ``Culture'' diffuses through communities and social networks. Information and
-opinions spread \citep{bond_etal12, fowler2010cooperative,klarEffectNetworkStructure2017}, behaviors are adopted \citep{aralExerciseContagionGlobal2017, centolaSpreadBehaviorOnline2010, centolaExperimentalStudyHomophily2011,christakis2008collective,rosenquist2010spread}, and there are patterns of health contagion \citep{cacioppo2009alone,christakisSpreadObesityLarge2007}.
-However,
-``different things spread in different ways and to different extents''
-\citep[p. 563]{christakisSocialContagionTheory2013} and when modeling diffusion and
+opinions spread \citep{bond_etal12,
+fowler2010cooperative,klarEffectNetworkStructure2017}, behaviors are adopted
+\citep{aralExerciseContagionGlobal2017, centolaSpreadBehaviorOnline2010,
+centolaExperimentalStudyHomophily2011,christakis2008collective,rosenquist2010spread},
+and there are patterns of health contagion
+\citep{cacioppo2009alone,christakisSpreadObesityLarge2007}. However, ``different
+things spread in different ways and to different extents'' \citep[p.
+563]{christakisSocialContagionTheory2013} and when modeling diffusion and
 contagion, we must be very specific about our scope conditions as they are
@@
 Most of the diffusion literature does not focus on establishment of new norms
-but the adoption of culture and specific deviant behaviors 
-\citep[see][for an exception]{centolaSpontaneousEmergenceConventions2015}. 
-\citet{dellapostaWhyLiberalsDrink2015} outline how the spread of culture
-and behavior is tied to network autocorrelation, or ``the tendency for people to
-resemble their network neighbors.'' They show that the distance between to agents
-in sociocultural space can determine the likelihood of the adoption of a new
-behavior. Like \citet{axelrodDisseminationCultureModel1997}, this outlines
-how the local convergence of close network actors becomes amplified and can
-lead to global polarization between groups.
+but the adoption of culture and specific deviant behaviors \citep[see][for an
+exception]{centolaSpontaneousEmergenceConventions2015}.
+\citet{dellapostaWhyLiberalsDrink2015} outline how the spread of culture and
+behavior is tied to network autocorrelation, or ``the tendency for people to
+resemble their network neighbors.'' They show that the distance between to
+agents in sociocultural space can determine the likelihood of the adoption of a
+new behavior. Like \citet{axelrodDisseminationCultureModel1997}, this outlines
+how the local convergence of close network actors becomes amplified and can lead
+to global polarization between groups.
 
@@
 about the risks of behaviors will lead to changes in behaviors to mitigate those
-said risks \citep[e.g.][]{flay_etal80}. However, while this model can be valid in specific
-cases, more research has shown how the risks themselves do little to motivate
-behavioral change \citep{witte_allen00,wolburg06}. Often, an appeal to fear is
-found to be a major driver of the adoption of information campaigns and some
-research has shown that ``social network exposure to COVID-19 cases shapes
-individuals'' beliefs and behaviors concerning the coronavirus'' \citep{bailey_etal20}. Because of this, it is logical that higher local incidences of
-infection would inspire fear and increase adherence to public health measures
-according to this older model.
+said risks \citep[e.g.][]{flay_etal80}. However, while this model can be valid
+in specific cases, more research has shown how the risks themselves do little to
+motivate behavioral change \citep{witte_allen00,wolburg06}. Often, an appeal to
+fear is found to be a major driver of the adoption of information campaigns and
+some research has shown that ``social network exposure to COVID-19 cases shapes
+individuals'' beliefs and behaviors concerning the coronavirus''
+\citep{bailey_etal20}. Because of this, it is logical that higher local
+incidences of infection would inspire fear and increase adherence to public
+health measures according to this older model.
 
-\begin{enumerate}
-\def\labelenumi{(\arabic{enumi})}
-\tightlist
-\item
-  \emph{Hypothesis 1} Relatively higher local rates of infection will lead to increased time spent in residence and increase vaccination uptake
-\end{enumerate}
+\begin{hyp2}[H\ref{hyp:infection}] \label{hyp:infection}
+ Relatively higher local rates of infection will lead to increased time spent in residence and increase vaccination uptake
+\end{hyp2}
 
-\hypertarget{complex-contagion-and-discordance}{%
-\subsection{Complex Contagion and Discordance}\label{complex-contagion-and-discordance}}
+\hypertarget{complex-contagion-and-discordance}{\subsection{Complex Contagion and Discordance}\label{complex-contagion-and-discordance}}
 
-\citep{centolaComplexContagionsWeakness2007} theorize that simple contagions are not
-enough to spread behavioral change. Simple contagions are those in which only
-one point of contact is needed to receive contagion, like with infectious
-disease or to learn simple bits of information.
-Centola and Macy \citeyearpar{centolaComplexContagionsWeakness2007}'s large contribution
-was the theorizing of complex contagions, those that require ``independent affirmation or
-reinforcement from multiple sources'' (p. 703) and is not based on the number of
-exposures but the number of sources of exposure. In the case of behavioral
+\citep{centolaComplexContagionsWeakness2007} theorize that simple contagions are
+not enough to spread behavioral change. Simple contagions are those in which
+only one point of contact is needed to receive contagion, like with infectious
+disease or to learn simple bits of information. Centola and Macy
+\citeyearpar{centolaComplexContagionsWeakness2007}'s large contribution was the
+theorizing of complex contagions, those that require ``independent affirmation
+or reinforcement from multiple sources'' (p. 703) and is not based on the number
+of exposures but the number of sources of exposure. In the case of behavioral
 contagion, this means that the behavior must be reinforced through witnessing
@@
 
-\begin{enumerate}
-\def\labelenumi{(\arabic{enumi})}
-\setcounter{enumi}{1}
-\tightlist
-\item
-  \emph{Hypothesis 2} increased average time spent in residence (signal direction) from alters will have a positive effect on stay-at-home rates the ego-county; increased vaccine uptake by alters will have a positive effect on vaccine uptake for the ego-county
-\end{enumerate}
+\begin{hyp2}[H\ref{hyp:direction}] \label{hyp:direction}
+Increased average time spent in residence (signal direction) from alters will have a positive effect on stay-at-home rates the ego-county; increased vaccine uptake by alters will have a positive effect on vaccine uptake for the ego-county
+\end{hyp2}
 
@@
 
-\begin{enumerate}
-\def\labelenumi{(\arabic{enumi})}
-\setcounter{enumi}{2}
-\tightlist
-\item
-  \emph{Hypothesis 3} the effect of signal direction on time spent in residence and vaccine uptake will be moderated by diversity in signals (discordance)
-\end{enumerate}
+\begin{hyp2}[H\ref{hyp:discordance}] \label{hyp:discordance}
+The effect of signal direction on time spent in residence and vaccine uptake will be moderated by diversity in signals (discordance)
+\end{hyp2}
 
@@
 on structural boundaries and homophily as causes of how diffusion occurs,
-\citet{goldbergSocialContagionAssociative2018} propose a
-disrupting alternative mechanism. They argue that what actually diffuses during
-social contagion are the perceptions about which beliefs or behaviors are
-compatible with one another, what they call ``associative diffusion.'' This
-argument that culture does not spread like a virus but instead is dependent on
-how belief structures are connected to each other is important to test because
-norms around health behaviors became politicized issues during the COVID-19
-pandemic. This means that the stay-at-home or vaccination behavior themselves
-were not contagious, but the cognitive association of precisely what social
-distancing or vaccination uptake \emph{meant} were spreading between populations of
-individuals. Moreover, as \citet{houghton20} outlines, diffusants, the things that are
-diffusing through a population, are not independent of each other \citep{mason_etal07}. 
+\citet{goldbergSocialContagionAssociative2018} propose a disrupting alternative
+mechanism. They argue that what actually diffuses during social contagion are
+the perceptions about which beliefs or behaviors are compatible with one
+another, what they call ``associative diffusion.'' This argument that culture
+does not spread like a virus but instead is dependent on how belief structures
+are connected to each other is important to test because norms around health
+behaviors became politicized issues during the COVID-19 pandemic. This means
+that the stay-at-home or vaccination behavior themselves were not contagious,
+but the cognitive association of precisely what social distancing or vaccination
+uptake \emph{meant} were spreading between populations of individuals. Moreover,
+as \citet{houghton20} outlines, diffusants, the things that are diffusing
+through a population, are not independent of each other \citep{mason_etal07}.
 When we take into account the interdependence between different beliefs that are
-diffusing, such as COVID-19 is a hoax, social distancing saves
-lives, the COVID-19 vaccine includes a microchip to control your thoughts, and lockdown
-is against the rights guaranteed in the US constitution, we can imagine how
-these various diffusants become associated together into structures of belief
-through schemas of perception \citep{houghton20}. While this cognitive theory of
+diffusing, such as COVID-19 is a hoax, social distancing saves lives, the
+COVID-19 vaccine includes a microchip to control your thoughts, and lockdown is
+against the rights guaranteed in the US constitution, we can imagine how these
+various diffusants become associated together into structures of belief through
+schemas of perception \citep{houghton20}. While this cognitive theory of
 cultural variation is difficult to test, the theory it supplies provides a solid
@@
 
-Individuals look to norms to regulate behavior, avoid
-deviance, and to maintain order \citep{horneNormsIntegratedFramework2020, shepherdStructurePerceptionHow2017}. When they realize they don't have a normative
-set of responses in their cultural toolkit to respond to an unfamiliar situation
-they are presented with, individuals look to the other sources in their
-``community'' to mimic behavior, such as high-status individuals, institutions,
-and members of their social network. I theorize that individuals look towards
-their physical community, to their social network, popular media, established
-norms that they may find online through search, and to the real threat of 
-infection (what would happen if I do nothing about this norm). 
+Individuals look to norms to regulate behavior, avoid deviance, and to maintain
+order \citep{horneNormsIntegratedFramework2020,
+shepherdStructurePerceptionHow2017}. When they realize they don't have a
+normative set of responses in their cultural toolkit to respond to an unfamiliar
+situation they are presented with, individuals look to the other sources in
+their ``community'' to mimic behavior, such as high-status individuals,
+institutions, and members of their social network. I theorize that individuals
+look towards their physical community, to their social network, popular media,
+established norms that they may find online through search, and to the real
+threat of infection (what would happen if I do nothing about this norm).
 Following both the Integrated Theoretical Framework of Norms
-\citep{horneNormsIntegratedFramework2020} and
-associative diffusion \citep{dellapostaWhyLiberalsDrink2015, goldbergSocialContagionAssociative2018},
-I theorize that individuals interpret
-signals from their ``community'' through their cognitive biases and behavioral
-predispositions to determine their formation of new behavioral norms.
+\citep{horneNormsIntegratedFramework2020} and associative diffusion
+\citep{dellapostaWhyLiberalsDrink2015, goldbergSocialContagionAssociative2018},
+I theorize that individuals interpret signals from their ``community'' through
+their cognitive biases and behavioral predispositions to determine their
+formation of new behavioral norms.
 
 There is some evidence I can draw upon to support the associative diffusion
-fraemwork. For instance, there is a central conflict between religious and
+framework. For instance, there is a central conflict between religious and
 scientific ideologies which I theorize leads more religious counties to reject
-the stay-at-home order and vaccines \citep{evansReligionScienceEpistemological2008}
-because the associative diffusion of these behaviors pits public health
-recommendations against religious ideologies.
-Furthermore, as COVID-19 has become a politically polarizing issue \citep{ternullo22},
-conservative ideology and a general mistrust of ``big government'' \citep{frank2007, gauchat2008} 
-are likely to lead to resistance to the government and scientific guidance.
+the stay-at-home order and vaccines
+\citep{evansReligionScienceEpistemological2008} because the associative
+diffusion of these behaviors pits public health recommendations against
+religious ideologies. Furthermore, as COVID-19 has become a politically
+polarizing issue \citep{ternullo22}, conservative ideology and a general
+mistrust of ``big government'' \citep{frank2007, gauchat2008} are likely to lead
+to resistance to the government and scientific guidance.
 
-\hypertarget{data-and-methods}{%
-\section{Data and Methods}\label{data-and-methods}}
+\hypertarget{data-and-methods}{\section{Data and Methods}\label{data-and-methods}}
 
@@
 
-\hypertarget{stay-at-home-rates}{%
-\subsection{Stay at Home Rates}\label{stay-at-home-rates}}
+\hypertarget{stay-at-home-rates}{\subsection{Stay-at-Home Rates}\label{stay-at-home-rates}}
 
@@
 {\centering \includegraphics[width=0.8\linewidth]{figs/paper3/plot-google-1}}
-\caption{Stay at Home Rates over Time}\label{fig:plot-google}
+\caption{Stay-at-Home Rates over Time}\label{fig:plot-google}
 \end{figure}
@@
 COVID-19 Community Mobility Reports include multiple measures of mobility based
-on location and activity information, the change in time spent in residence
-most closely aligns to an operationalization of an obedience to CDC and governor
+on location and activity information, the change in time spent in residence most
+closely aligns to an operationalization of an obedience to CDC and governor
 orders, a new and emerging norm in 2020. The change in time spent in residence
@@
 counties if they did not have sufficient statistically significant levels of
-data, my final county sample is \emph{n} = 1375
-(compared to the total population of 3,107 US counties). Particular areas that
-are excluded in this analysis include all counties in Alaska and DC, and over
-half of the counties in North Dakota, South Dakota. A full list of excluded
-counties available upon request. These data are longitudinal measures calculated
-by creating a moving average of stay-at-home rates for each county (rolling
-window width = 7 days) and then sampling every
-Monday in the sample for 44 measures from March 02, 2020 through December 28,
-2020.
+data, my final county sample is \emph{n} = 1375 (compared to the total
+population of 3,107 US counties). Particular areas that are excluded in this
+analysis include all counties in Alaska and DC, and over half of the counties in
+North Dakota, South Dakota. A full list of excluded counties available upon
+request. These data are longitudinal measures calculated by creating a moving
+average of stay-at-home rates for each county (rolling window width = 7 days)
+and then sampling every Monday in the sample for 44 measures from March 02, 2020
+through December 28, 2020.
 
@@
 vaccination rate information in the United States from January 2021 through
-August 30 2021 \citep{cdcCOVID19Vaccination2021}. Data represents all vaccine partners including
-jurisdictional partner clinics, retail pharmacies, long-term care facilities,
-dialysis centers, Federal Emergency Management Agency and Health Resources and
-Services Administration partner sites, and federal entity facilities.
-Vaccination data is available for all US counties with the exception of parts of
-California and Massachusetts, Hawaii, and Texas. In Texas and Hawaii, no county
-level information is available, and California does not report the county of
-residence for vaccinations when the county of residence has a population less
-than 20,000 people. Finally, Massachusetts does not provide vaccination data for
-Barnstable, Dukes, and Nantucket counties because of their small populations.
-Therefore, my final county sample for vaccination rates is \emph{n} = 2819
-(compared to the total population of 3,107 US counties). A list of included FIPS
-are available upon request. Vaccination rates are scaled with a rolling mean
-with a rolling window width of seven days to smooth out intra-week noise. I
-sample every Monday between January 2021 through August 30, 2021 for 35 total
-observations for each county.
+August 30 2021 \citep{cdcCOVID19Vaccination2021}. Data represents all vaccine
+partners including jurisdictional partner clinics, retail pharmacies, long-term
+care facilities, dialysis centers, Federal Emergency Management Agency and
+Health Resources and Services Administration partner sites, and federal entity
+facilities. Vaccination data is available for all US counties with the exception
+of parts of California and Massachusetts, Hawaii, and Texas. In Texas and
+Hawaii, no county level information is available, and California does not report
+the county of residence for vaccinations when the county of residence has a
+population less than 20,000 people. Finally, Massachusetts does not provide
+vaccination data for Barnstable, Dukes, and Nantucket counties because of their
+small populations. Therefore, my final county sample for vaccination rates is
+\emph{n} = 2819 (compared to the total population of 3,107 US counties). A list
+of included FIPS are available upon request. Vaccination rates are scaled with a
+rolling mean with a rolling window width of seven days to smooth out intra-week
+noise. I sample every Monday between January 2021 through August 30, 2021 for 35
+total observations for each county.
 
@@
 
-I utilize the likelihood of a friendship connection between counties
-to create a county-level social network weighted by the probability of a tie.
-Using this network and the two independent variables above, I examine how the
-vaccination and stay-at-home rates of peer counties is contagious to the
-ego-county. To do this, I first take the weighted average of each ego's network
-signals using equation \eqref{eq:networksignal} where \texttt{x} denotes the
-vaccination and stay-at-home rates of each alter county and \texttt{w} represents the
-likelihood of a friendship connection between the ego county and each of their
-alters, lagged by one week. This `signal' of norms gives us insight into the
-coevolving contagion patterns of the new social norm being established. The
-likelihood of friendship connection comes from the ``Social Connectedness Index''
-\citep{Bailey2018, facebook20} which indexes the social links between geographies by
-the likelihood of Facebook friends. It is an aggregated measure of Facebook
-friendship connections between counties. It corresponds to ``the (relative)
-probability that two arbitrary Facebook users across two geographies are friends
-with each other.'' The data is available at various geographic aggregation
-levels, such as U.S. zip codes or entire countries. However, data is only
-available at one time point because Facebook has found that although there are
-individual changes in friendship connections over time, the aggregate
+I utilize the likelihood of a friendship connection between counties to create a
+county-level social network weighted by the probability of a tie. Using this
+network and the two independent variables above, I examine how the vaccination
+and stay-at-home rates of peer counties is contagious to the ego-county. To do
+this, I first take the weighted average of each ego's network signals using
+equation \eqref{eq:networksignal} where \texttt{x} denotes the vaccination and
+stay-at-home rates of each alter county and \texttt{w} represents the likelihood
+of a friendship connection between the ego county and each of their alters,
+lagged by one week. This `signal' of norms gives us insight into the co-evolving
+contagion patterns of the new social norm being established. The likelihood of
+friendship connection comes from the ``Social Connectedness Index''
+\citep{Bailey2018, facebook20} which indexes the social links between
+geographies by the likelihood of Facebook friends. It is an aggregated measure
+of Facebook friendship connections between counties. It corresponds to ``the
+(relative) probability that two arbitrary Facebook users across two geographies
+are friends with each other.'' The data is available at various geographic
+aggregation levels, such as U.S. zip codes or entire countries. However, data is
+only available at one time point because Facebook has found that although there
+are individual changes in friendship connections over time, the aggregate
 statistical probabilities of friendship remain stable. This measure is based on
@@
 population and Facebook friendship links largely represent real-world
-friendships \citep{bailey_etal18, jones_etal13}. The data has been tested to show
-how initial COVID-19 hotspots are related to subsequent virus spread to
-non-hotspots, even after controlling for population density and geographic
+friendships \citep{bailey_etal18, jones_etal13}. The data has been tested to
+show how initial COVID-19 hot spots are related to subsequent virus spread to
+non-hot-spots, even after controlling for population density and geographic
 distance \citep{Kuchler2020}.
@@
 
-The second independent variable, \emph{Signal Discordance}, builds on the network
-signal but looks specifically at the extent to which a given ego-network
-receives diverse contagion signals. Based on the hypothesis that when the
-majority of alters is in concordance with each other, the signal to the ego is
-reinforced and more impactful on the ego, a high discordance coefficient is
-indicative of diverse signals which may prevent any clear interpretation of a
-norm developing, whereas a low discordance coefficient would indicate reinforced
-signaling. I use the formula to calculate weighted standard deviations, (see equation
-\eqref{eq:signaldiscordance}) to provide a metric of a diversity of signals. In
-this formula, \texttt{x} denotes the vaccination and stay-at-home rates of each alter
-county and \texttt{w} represents the likelihood of a friendship connection between the
-ego county and each of their alters, lagged by one week. Furthermore, \(\bar{x}^*\)
-represents the weighted mean.
+The second independent variable, \emph{Signal Discordance}, builds on the
+network signal but looks specifically at the extent to which a given ego-network
+receives diverse contagion signals. Based on Hypothesis \ref{hyp:discordance},
+that when the majority of alters is in concordance with each other, the signal
+to the ego is reinforced and more potent on the ego, a high discordance
+coefficient is indicative of diverse signals which may prevent any clear
+interpretation of a norm developing, whereas a low discordance coefficient would
+indicate reinforced signaling. I use the formula to calculate weighted standard
+deviations, (see equation \eqref{eq:signaldiscordance}) to provide a metric of a
+diversity of signals. In this formula, \texttt{x} denotes the vaccination and
+stay-at-home rates of each alter county and \texttt{w} represents the likelihood
+of a friendship connection between the ego county and each of their alters,
+lagged by one week. Furthermore, \(\bar{x}^*\) represents the weighted mean.
 
@@
 
-Figures \ref{fig:assortativity-vacc} and \ref{fig:discordancenetwork} provide
-a visualization of both network signal and signal discordance for April 26, 2021
-for 7 selected counties.\footnote{Figures in this paper were all created using ggplot2
-\citep{wickham_etal, wickham11}, patchwork \citep{pedersen20}, and ggridges \citep{ggridges}}
-While a county like Lake County, Ohio has low discordance meaning the signal of
-vaccination rate is reinforced, Navajo County, Arizona receives very diverse
-signals from their county-alters, negating any contagion effects. Figure
-\ref{fig:discordancenetwork} explicitly outline how the weights and signals are
-calculated for an ego with only 5 alters.
+Figures \ref{fig:assortativity-vacc} and \ref{fig:discordancenetwork} provide a
+visualization of both network signal and signal discordance for April 26, 2021
+for 7 selected counties.\footnote{Figures in this paper were all created using
+ggplot2 \citep{wickham_etal, wickham11}, patchwork \citep{pedersen20}, and
+ggridges \citep{ggridges}} While a county like Lake County, Ohio has low
+discordance meaning the signal of vaccination rate is reinforced, Navajo County,
+Arizona receives very diverse signals from their county-alters, negating any
+contagion effects. Figure \ref{fig:discordancenetwork} explicitly outline how
+the weights and signals are calculated for an ego with only 5 alters.
 
@@
 To estimate the concept of `real threat of infection' for a fear-based model of
-health behaviors, the models use county-level COVID-19 case rates with
-data compiled by The New York Times \citeyearpar{covid_data}. It is widely acknowledged that there are biases in this data due to inconsistencies and availability in testing as well as
-different community propensity to test \citep{gu22, cdc20a}. However, it is the best
-measure we have of actual case rates. County data are scaled with a rolling mean
-with a rolling window width of seven days to smooth out intra-week noise. Case
-Rate is measured as number of cases per 100,000 population. Observations vary
-from a minimum of 0 to a maximum of 1,565 across the two datasets.
+health behaviors, the models use county-level COVID-19 case rates with data
+compiled by The New York Times \citeyearpar{covid_data}. It is widely
+acknowledged that there are biases in this data due to inconsistencies and
+availability in testing as well as different community propensity to test
+\citep{gu22, cdc20a}. However, it is the best measure we have of actual case
+rates. County data are scaled with a rolling mean with a rolling window width of
+seven days to smooth out intra-week noise. Case Rate is measured as number of
+cases per 100,000 population. Observations vary from a minimum of 0 to a maximum
+of 1,565 across the two datasets.
 
@@
 Research has shown that stay-at-home rates and other pandemic health behaviors
-are related to various `pillars of conservatism' \citep{gonzalez_etal21,hillBloodChristCompels2020,hillLoveThyAged2021, hillNastiestQuestion}. Namely, research shows that politically conservative
+are related to various `pillars of conservatism'
+\citep{gonzalez_etal21,hillBloodChristCompels2020,hillLoveThyAged2021,
+hillNastiestQuestion}. Namely, research shows that politically conservative
 indicators, such as Republican political leadership, conservative Protestantism
@@
 Christians. These county-level data were collected through the 2010 U.S.
-Religion Census: Religious Congregations and Membership Study \citep{grammich_etal18}. Finally, right-wing media consumption is assessed using
-Google Search Trends to capture ``Fox News'' searches over the study period across
-individual designated media markets areas (DMAs). I use this measure to indicate
-active interest in and attention toward Fox News. Google Search Trends have been
-validated for use in a range of research contexts and for use with survey data,
-voting data, and ecological data \citep{bailPrestigeProximityPrejudice2019, reyesUsingInternetSearch2018, scheitleGoogleInsightsSearch2011, stephensdavidowitzCostRacialAnimus2014, swearingenGoogleInsightsSenate2014}.
+Religion Census: Religious Congregations and Membership Study
+\citep{grammich_etal18}. Finally, right-wing media consumption is assessed using
+Google Search Trends to capture ``Fox News'' searches over the study period
+across individual designated media markets areas (DMAs). I use this measure to
+indicate active interest in and attention toward Fox News. Google Search Trends
+have been validated for use in a range of research contexts and for use with
+survey data, voting data, and ecological data
+\citep{bailPrestigeProximityPrejudice2019, reyesUsingInternetSearch2018,
+scheitleGoogleInsightsSearch2011, stephensdavidowitzCostRacialAnimus2014,
+swearingenGoogleInsightsSenate2014}.
 
@@
 degree, (4) median income, and (5) monthly county unemployment rate. Measures 1
-through 4 are obtained from the 2018 American Community Survey: 5-Year Estimates \citep{uscensusbureauAmericanCommunitySurvey2018}; unemployment rates are gathered
-from the U.S. Bureau of Labor Statistics \citep{labor2020a}.
+through 4 are obtained from the 2018 American Community Survey: 5-Year Estimates
+\citep{uscensusbureauAmericanCommunitySurvey2018}; unemployment rates are
+gathered from the U.S. Bureau of Labor Statistics \citep{labor2020a}.
 
@@
 three linear mixed effects regression models using the nlme package in R
-\citep{pinheiro_etal21, pinheiro_bates00} for our two cases, Stay-at-Home rates and
-Vaccination rates. Linear mixed effects models are a form of hierarchical linear
-models that contain both random and fixed effects. These models treat the
+\citep{pinheiro_etal21, pinheiro_bates00} for our two cases, Stay-at-Home rates
+and Vaccination rates. Linear mixed effects models are a form of hierarchical
+linear models that contain both random and fixed effects. These models treat the
 dependent variables as continuous. The following strategies I will outline are
-identical for both case studies. Models 1 through 3 address hypotheses 1 through
-3 respectively. Each model utilizes normalized independent variables, i.e.
-variables that have been centered and scaled to have a mean of 0 and standard
-deviation 1. The first model is a baseline linear mixed effects model that
-employs all basic controls to predict the dependent variable, allowing both
-time-varying and county-level variables to predict the outcome. All variables
-have fixed effects, meaning that the county-level exogenous effects are
-controlled for when estimating the coefficient. In addition, models are
-specified with a random intercept per county. The lme models are set with a
-autoregressive correlation structure (\texttt{correlation\ =\ corAR1()}) to control for
-temporally autocorrelated error structures; models are also optimized using
-Nelder--Mead, quasi-Newton and conjugate-gradient algorithms for box-constrained
-optimization and simulated annealing (\texttt{control\ =\ lmeControl(opt\ =\ "optim")}).
-This first model will address Hypothesis 1. To test hypothesis 2, I estimate
-model 2 which builds on model 1 by first introducing vaccination signal. Because
-the signal varies by week, I estimate this model with an interaction between
-week and signal. And finally, because signal may have divergent effects across
-counties, I set a random effect for signal nested by county. A visual
-representation of this interaction can be seen in Figures
-\ref{fig:plot-google-h2} and \ref{fig:plot-vacc-h2}. Model 3 further
+identical for both case studies. Models 1 through 3 address hypotheses
+\ref{hyp:infection} through \ref{hyp:discordance} respectively. Each model
+utilizes normalized independent variables, i.e. variables that have been
+centered and scaled to have a mean of 0 and standard deviation 1. The first
+model is a baseline linear mixed effects model that employs all basic controls
+to predict the dependent variable, allowing both time-varying and county-level
+variables to predict the outcome. All variables have fixed effects, meaning that
+the county-level exogenous effects are controlled for when estimating the
+coefficient. In addition, models are specified with a random intercept per
+county. The lme models are set with a autoregressive correlation structure
+(\texttt{correlation\ =\ corAR1()}) to control for temporally autocorrelated
+error structures; models are also optimized using Nelder--Mead, quasi-Newton and
+conjugate-gradient algorithms for box-constrained optimization and simulated
+annealing (\texttt{control\ =\ lmeControl(opt\ =\ "optim")}). This first model
+will address Hypothesis \ref{hyp:infection}. To test Hypothesis
+\ref{hyp:direction}, I estimate model 2 which builds on model 1 by first
+introducing vaccination signal. Because the signal varies by week, I estimate
+this model with an interaction between week and signal. And finally, because
+signal may have divergent effects across counties, I set a random effect for
+signal nested by county. A visual representation of this interaction can be seen
+in Figures \ref{fig:plot-google-h2} and \ref{fig:plot-vacc-h2}. Model 3 further
 elaborates on the previous model by introducing both a fixed effect for signal
@@
 predict stay-at-home rates, or, time spent in residence. Model 1 addresses
-hypothesis 1, that relatively higher local rates of infection will lead to
-increased time spent in residence. This model's phi paramter is 0.933, which is
-a good indicator that adjacent time points for each county are related and the
-model is specified correctly (Finch, Bolin, and Kelley 2014). In this first model, many controls
-have an impact on the outcome. For instance, when controlling for everything
-else, the percent of GOP votes in 2016, the percentage of residents who identify
-racially as White, and higher rates of unemployment increased the stay-at-home
-rate while Searches for norms online seems to
-have an effect on the outcome: searches for `Fox News' are associated with
-decreased stay-at-home rates, while searching for both `Social Distancing' and
-`Covid Conspiracy' tend to increase time spent in residence. Interestingly, the
-perceived threat of the virus, measured through COVID-19 case rates, were not
-significantly related to stay-at-home rates in model 1. In other words, for
+Hypothesis \ref{hyp:infection}, that relatively higher local rates of infection
+will lead to increased time spent in residence. This model's phi parameter is
+0.933, which is a good indicator that adjacent time points for each county are
+related and the model is specified correctly (Finch, Bolin, and Kelley 2014). In
+this first model, many controls have an impact on the outcome. For instance,
+when controlling for everything else, the percent of GOP votes in 2016, the
+percentage of residents who identify racially as White, and higher rates of
+unemployment increased the stay-at-home rate while Searches for norms online
+seems to have an effect on the outcome: searches for `Fox News' are associated
+with decreased stay-at-home rates, while searching for both `Social Distancing'
+and `Covid Conspiracy' tend to increase time spent in residence. Interestingly,
+the perceived threat of the virus, measured through COVID-19 case rates, were
+not significantly related to stay-at-home rates in model 1. In other words, for
 every 1 standard deviation increase in COVID-19 case rates, stay-at-home rates
-actually decreased by
-0.0003 (\emph{p} = 0.936),
-a very small and insignificant effect. In this case, I fail to reject the null
-hypothesis that relatively higher local rates of infection will lead to
-increased time spent in residence.
+actually decreased by 0.0003 (\emph{p} = 0.936), a very small and insignificant
+effect. In this case, I fail to reject the null hypothesis that relatively
+higher local rates of infection will lead to increased time spent in residence.
 
-Table \ref{tab:google-tab} Model 2 investigates Hypothesis 2, that increased
-average time spent in residence (signal direction) from alters will have a
-positive effect on stay-at-home rates for the ego-county. This model builds on
-model 1 by adding in the variable for Movement Signal (see \protect\hyperlink{network-signal}{Network
-Signal} for specifications). For every one standard deviation
-increase in the average time spent in residence of the county alters, an ego tends to also increase its' own stay-at-home rate by
-0.473
-(\emph{p} \textless{} 0.001). I am therefore able to reject my null hypothesis for hypothesis
-2, that an increased average time spent in residence (signal direction) from
-alters will have a positive effect on time spent in residence for the
-ego-county.
+Table \ref{tab:google-tab} Model 2 investigates Hypothesis \ref{hyp:direction},
+that increased average time spent in residence (signal direction) from alters
+will have a positive effect on stay-at-home rates for the ego-county. This model
+builds on model 1 by adding in the variable for Movement Signal (see
+\protect\hyperlink{network-signal}{Network Signal} for specifications). For
+every one standard deviation increase in the average time spent in residence of
+the county alters, an ego tends to also increase its' own stay-at-home rate by
+0.473 (\emph{p} \textless{} 0.001). I am therefore able to reject my null
+hypothesis for Hypothesis \ref{hyp:direction}, that an increased average time
+spent in residence (signal direction) from alters will have a positive effect on
+time spent in residence for the ego-county.
 
@@
 {\centering \includegraphics[width=0.8\linewidth]{figs/paper3/plot-google-h2-1}}
-\caption{Predicted Values of Stay at Home Rate by Movement Signal}\label{fig:plot-google-h2}
+\caption{Predicted Values of Stay-at-Home Rate by Movement Signal, Model 2}\label{fig:plot-google-h2}
 \end{figure}
@@
 with strong public health norms and felt safe and justified their own deviance.
-However, if an ego county received signals that
-others were failing to social distance, they were more likely to stay-at-home.
-In this case, the threat of the virus may have been more evident for
-individuals.
+However, if an ego county received signals that others were failing to social
+distance, they were more likely to stay-at-home. In this case, the threat of the
+virus may have been more evident for individuals.
 
@@
 {\centering \includegraphics[width=0.8\linewidth]{figs/paper3/plot-google-h3-1}}
-\caption{Predicted Values of Stay at Home Rate Moderated}\label{fig:plot-google-h3}
+\caption{Predicted Values of Stay-at-Home Rate Moderated by Discordance, Model 3}\label{fig:plot-google-h3}
 \end{figure}
 
-Model 3 then adds the concept of Signal Discordance to investigate Hypothesis 3,
-that the effect of signal direction on stay-at-home rates will be moderated by a
-diversity in signals (\emph{discordance}). Many of the controls remain consistent
-throughout the models, with the exception of `Social Distancing' Trend whose
-effect has been completely mediated by the inclusion of signal discordance.
-Importantly, signal discordance has a negative effect on stay-at-home rates,
-where every one standard deviation increase in discordance lowers stay-at-home rates by
--0.101
-(\emph{p} \textless{} 0.001). The interaction between signal and signal discordance have a
-coefficient of a similar magnitude, with every one standard deviation increase
-in discordance and signal resulting in
--0.092
-lower rates of time spent in residence, indicating moderation. Figure
-\ref{fig:plot-google-h3} illustrates the moderating effect that signal
-discordance has on signal. Under high discordance, the social influence effect
-is almost completely moderated because there is no clear story or norm forming.
-However, under low discordance, the signal is condensed, allowing for social
-influence to have an effect. Explicitly, if a county is receiving a wide array
-of low and high signals, their stay at home rates won't be affected by social
-contagion. When a signal is concentrated or in agreement, the theoretical effect
-of movement signaling on the ego are the strongest. With this, I am able to
-reject the null hypothesis of no relationship for hypothesis 3 and find that the
-effect of signal direction on time spent in residence is moderated by diversity
-in signals.
+Model 3 then adds the concept of Signal Discordance to investigate Hypothesis
+\ref{hyp:discordance}, that the effect of signal direction on stay-at-home rates
+will be moderated by a diversity in signals (\emph{discordance}). Many of the
+controls remain consistent throughout the models, with the exception of `Social
+Distancing' Trend whose effect has been completely mediated by the inclusion of
+signal discordance. Importantly, signal discordance has a negative effect on
+stay-at-home rates, where every one standard deviation increase in discordance
+lowers stay-at-home rates by -0.101 (\emph{p} \textless{} 0.001). The
+interaction between signal and signal discordance have a coefficient of a
+similar magnitude, with every one standard deviation increase in discordance and
+signal resulting in -0.092 lower rates of time spent in residence, indicating
+moderation. Figure \ref{fig:plot-google-h3} illustrates the moderating effect
+that signal discordance has on signal. Under high discordance, the social
+influence effect is almost completely moderated because there is no clear story
+or norm forming. However, under low discordance, the signal is condensed,
+allowing for social influence to have an effect. Explicitly, if a county is
+receiving a wide array of low and high signals, their stay-at-home rates won't
+be affected by social contagion. When a signal is concentrated or in agreement,
+the theoretical effect of movement signaling on the ego are the strongest. With
+this, I am able to reject the null hypothesis of no relationship for Hypothesis
+\ref{hyp:discordance} and find that the effect of signal direction on time spent
+in residence is moderated by diversity in signals.
 
@@
 is an appropriate modeling technique for the data \citep{finch_etal14}. Table
-\ref{tab:vacc-tab} Model 1 addresses hypothesis 1, that relatively higher local
-rates of infection will lead to increased vaccination uptake. In this first
-model, we see various controls impacting vaccination rates. For instance, when
-controlling for everything else, higher income areas lead to higher vaccination
-uptake. On the other hand, counties with higher unemployment and higher votes
-for Donald J. Trump in the 2020 election are associated with lower vaccination
-rates. Interestingly, counties that search for Fox News are more likely to have
-higher vaccination rates while those performing Google searches for information
-about the vaccine are likely to have lower rates of vaccination. The test of
-Hypothesis 1 also returns surprising results: every 1 standard deviation
-increase in county COVID-19 case rates is expected to yield a -0.008 decrease in
-vaccination rates. This may be due to time ordering or reverse causality, where
-individuals in counties who have higher rates of vaccination are less likely to
-take tests to COVID-19 infections because of the higher likelihood of
-asymptomaticity. However, it is important to note that the Case Rate variable
-actually becomes distorted with the addition of Vaccination Signal and
-Vaccination Discordance in models 2 and 3. Distortion occurs when the direction
-of a focal relationship reverses sign once a third (distorter) variable is
-controlled, in this case, those related to signal. Therefore, the results of
-hypothesis 1 are quite inconclusive.
+\ref{tab:vacc-tab} Model 1 addresses Hypothesis \ref{hyp:infection}, that
+relatively higher local rates of infection will lead to increased vaccination
+uptake. In this first model, we see various controls impacting vaccination
+rates. For instance, when controlling for everything else, higher income areas
+lead to higher vaccination uptake. On the other hand, counties with higher
+unemployment and higher votes for Donald J. Trump in the 2020 election are
+associated with lower vaccination rates. Interestingly, counties that search for
+Fox News are more likely to have higher vaccination rates while those performing
+Google searches for information about the vaccine are likely to have lower rates
+of vaccination. The test of Hypothesis \ref{hyp:infection} also returns
+surprising results: every 1 standard deviation increase in county COVID-19 case
+rates is expected to yield a -0.008 decrease in vaccination rates. This may be
+due to time ordering or reverse causality, where individuals in counties who
+have higher rates of vaccination are less likely to take tests to COVID-19
+infections because of the higher likelihood of asymptomaticity. However, it is
+important to note that the Case Rate variable actually becomes distorted with
+the addition of Vaccination Signal and Vaccination Discordance in models 2 and
+3. Distortion occurs when the direction of a focal relationship reverses sign
+once a third (distorter) variable is controlled, in this case, those related to
+signal. Therefore, the results of Hypothesis \ref{hyp:infection} are quite
+inconclusive.
 
@@
 {\centering \includegraphics[width=0.8\linewidth]{figs/paper3/plot-vacc-h2-1}}
-\caption{Predicted Values of Vaccination Rate}\label{fig:plot-vacc-h2}
+\caption{Predicted Values of Vaccination Rate by Vaccination Signal, Model 2}\label{fig:plot-vacc-h2}
 \end{figure}
 
-Table \ref{tab:vacc-tab} model 2 tests the hypothesis 2 that increase vaccine
-uptake by alters will have a positive effect on vaccine uptake for the
-ego-county. The results are incredibly clear: seeing alter counties receiving
-vaccines is associated with higher vaccination rates. Specifically, a 1 standard
-deviation increase in vaccine signal, the average rate of vaccination of a
-county's alters, is associated with a
-0.854
-percent increase of vaccination rates for the ego county. The strength of this
-result leads me to reject the null hypothesis for hypothesis 2 and find that
-increased average time spent in residence (signal direction) from alters will
-have a positive effect on time spent in residence for the ego-county. The
-interaction of vaccine signal can be seen in Figure \ref{fig:plot-vacc-h2}.
-While the interaction is not as extreme as the results for Hypothesis 2 for
-Stay-at-Home rates, there is still a distinction between high and low
+Table \ref{tab:vacc-tab} model 2 tests the Hypothesis \ref{hyp:direction} that
+increase vaccine uptake by alters will have a positive effect on vaccine uptake
+for the ego-county. The results are incredibly clear: seeing alter counties
+receiving vaccines is associated with higher vaccination rates. Specifically, a
+1 standard deviation increase in vaccine signal, the average rate of vaccination
+of a county's alters, is associated with a 0.854 percent increase of vaccination
+rates for the ego county. The strength of this result leads me to reject the
+null hypothesis for Hypothesis \ref{hyp:direction} and find that increased
+average time spent in residence (signal direction) from alters will have a
+positive effect on time spent in residence for the ego-county. The interaction
+of vaccine signal can be seen in Figure \ref{fig:plot-vacc-h2}. While the
+interaction is not as extreme as the results for Hypothesis \ref{hyp:direction}
+for Stay-at-Home rates, there is still a distinction between high and low
 vaccination signals over time. The slope for Higher Vaccination Signal is less
@@
 {\centering \includegraphics[width=0.8\linewidth]{figs/paper3/plot-vacc-h3-1}}
-\caption{Predicted Values of Vaccination Rate}\label{fig:plot-vacc-h3}
+\caption{Predicted Values of Vaccination Rate Moderated by Discordance, Model 3}\label{fig:plot-vacc-h3}
 \end{figure}
@@
 Table \ref{tab:vacc-tab} Model 3 then models the moderation of signal direction
-for vaccine uptake by diversity in signals (\emph{Discordance}). This is a second
-test of Hypothesis 3, that the effect of signal direction on vaccine uptake will
-be moderated by diversity in signals. The coefficients in model 3 are largely
-consistent with model 2 and there is very little change in the magnitude
-or significance of the coefficients. Vaccination signal maintains to have a positive
-effect on the alter's vaccination rates, while vaccination discordance has a negative effect on vaccination rates, where every one standard deviation increase in discordance lowers rates by -0.072 (\emph{p} \textless{} 0.001).
-The interaction between signal and signal discordance have a coefficient of a similar magnitude, with every one standard deviation increase
-in discordance \emph{and} signal resulting in 
-lower rates of vaccination. Figure \ref{fig:plot-vacc-h3} illustrates this
-relationship, where there is slight moderation of the effect on vaccine signal
-on vaccination rates. If a county receives consistently high signals, they are
-more likely to have more residents vaccinated. If a county receives high but
-inconsistent signals, they are still decently likely to raise vaccination rates
-but to a lesser extent. While not as strong of moderation the the findings for
-Stay-at-Home Rates for hypothesis 3, I also reject the null hypothesis and find
-a moderation of the relationship between signal direction and vaccine uptake by
-discordance.
+for vaccine uptake by diversity in signals (\emph{Discordance}). This is a
+second test of Hypothesis \ref{hyp:discordance}, that the effect of signal
+direction on vaccine uptake will be moderated by diversity in signals. The
+coefficients in model 3 are largely consistent with model 2 and there is very
+little change in the magnitude or significance of the coefficients. Vaccination
+signal maintains to have a positive effect on the alter's vaccination rates,
+while vaccination discordance has a negative effect on vaccination rates, where
+every one standard deviation increase in discordance lowers rates by -0.072
+(\emph{p} \textless{} 0.001). The interaction between signal and signal
+discordance have a coefficient of a similar magnitude, with every one standard
+deviation increase in discordance \emph{and} signal resulting in lower rates of
+vaccination. Figure \ref{fig:plot-vacc-h3} illustrates this relationship, where
+there is slight moderation of the effect on vaccine signal on vaccination rates.
+If a county receives consistently high signals, they are more likely to have
+more residents vaccinated. If a county receives high but inconsistent signals,
+they are still decently likely to raise vaccination rates but to a lesser
+extent. While not as strong of moderation the the findings for Stay-at-Home
+Rates for Hypothesis \ref{hyp:discordance}, I also reject the null hypothesis
+and find a moderation of the relationship between signal direction and vaccine
+uptake by discordance.
 
@@
 This study is sensitive to aggregation error and sampling error derived from the
-multiple big-data sources \citep{facebook20, google2020}. The aggregation errors are
-potentially linked to the assumption that the average stay-at-home behavior of a
-county is a good representation of the diversity in behaviors within that
+multiple big-data sources \citep{facebook20, google2020}. The aggregation errors
+are potentially linked to the assumption that the average stay-at-home behavior
+of a county is a good representation of the diversity in behaviors within that
 county. If stay-at-home rates are normally distributed, this is a correct
@@
 using big data from the natural experiment of COVID-19. Because most studies of
-complex contagion utilize agent-based modeling or studies of social media \citep{aralExerciseContagionGlobal2017,sprague_house17,bond_etal12,latane_etal94}, combining measures of actual behavioral outcomes with data from
-social media websites provides a further test of ecological and external
-validity for the theory.
+complex contagion utilize agent-based modeling or studies of social media
+\citep{aralExerciseContagionGlobal2017,sprague_house17,bond_etal12,latane_etal94},
+combining measures of actual behavioral outcomes with data from social media
+websites provides a further test of ecological and external validity for the
+theory.
 
@@
 reinforcing actors, while other theories focus on how different diffusants
-interact with each other \citep{houghton20,goldbergSocialContagionAssociative2018,mason_etal07}.
-Discordance, on the other hand, looks specifically at the context of the reinforcing actors among the other signals.
-This study finds that indeed the context of the signals matters for diffusion.
+interact with each other
+\citep{houghton20,goldbergSocialContagionAssociative2018,mason_etal07}.
+Discordance, on the other hand, looks specifically at the context of the
+reinforcing actors among the other signals. This study finds that indeed the
+context of the signals matters for diffusion.

### 2022-04-14 abstract.tex
copyedits, add desc stat table

@@
 models of behavioral adaption to public health recommendations and patterns of
-complex contagion (the need for repeated exposures to a something novel for it
+complex contagion (the need for repeated exposures to something novel for it
 to diffuse) using linear mixed effects models. My results show that complex

### 2022-04-14 ch1.tex
copyedits, add desc stat table

@@
 \citeyearpar{lazarsfeldPeopleChoice1944}. They theorized that the media did not
-directly influence the masses, but that a "Two-Step Flow" was occurring where
-"opinion leaders" interpreted messages from mass media and then, in turn,
+directly influence the masses, but that a ``Two-Step Flow'' was occurring where
+``opinion leaders'' interpreted messages from mass media and then, in turn,
 promoted their opinions to the masses \citep{katzPersonalInfluencePart1955}. The
-opinion leaders interpret, explain, and diffuse contents to "opinion followers".
-From a networks perspective, "people rarely act on mass-media information unless
-it is also transmitted through personal ties" \citep[p.
+opinion leaders interpret, explain, and diffuse contents to ``opinion followers''.
+From a networks perspective, ``people rarely act on mass-media information unless
+it is also transmitted through personal ties'' \citep[p.
 1374]{granovetterStrengthWeakTies1973}. Lazarsfeld et al's
@@
 perspective \citep{bennettOneStepFlowCommunication2006}, many scholars find that
-"opinion leaders" (often influencers and celebrities) still create a two-step
+``opinion leaders'' (often influencers and celebrities) still create a two-step
 flow of information transmission \citep{choi15, hilbertOneStepTwo2017}.
@@
 \citep{fowler2010cooperative, bond_etal12, klarEffectNetworkStructure2017}.
-However, "different things spread in different ways and to different extents"
+However, ``different things spread in different ways and to different extents''
 \citep[p. 563]{christakisSocialContagionTheory2013} and information can spread
@@
 one-to-one, one-to-many, or many-to-many exchanges. Social media, on the other
-hand, are more specific, and are "Internet-based, disentrained, and persistent
+hand, are more specific, and are ``Internet-based, disentrained, and persistent
 channels of mass personal communication facilitating perceptions of interactions
-among users, deriving value primarily from user-generated content” \citep[][p.
+among users, deriving value primarily from user-generated content'' \citep[][p.
 50]{carr2015social}. While an email between colleagues is computer-mediated
@@
 behaviors of individuals in the 21st century? Not only is it quicker to perform
-network activation and seek support, but people are "permanently online,
-permanently connected" making activation easy \citep{vorderer2017permanently}.
+network activation and seek support, but people are ``permanently online,
+permanently connected'' making activation easy \citep{vorderer2017permanently}.
 The constant connectedness facilitates communication, but also presents people
@@
 demonstrates that often, graduate students who needed support simply asked
-"miscellaneous classmates encountered down the hall" (p. 176) rather than their
+``miscellaneous classmates encountered down the hall'' (p. 176) rather than their
 trusted, long-term confidants. It seems that network activation may rely on more
@@
 \citep{houseMeasuresConceptsSocial1985, thoitsMechanismsLinkingSocial2011}.
-Informational support is the process of seeking "help in defining,
+Informational support is the process of seeking ``help in defining,
 understanding, and coping with problematic events and include education, advice,
-or referral to another source of support" \citep[p. 640]{winemiller_etal93}.
+or referral to another source of support'' \citep[p. 640]{winemiller_etal93}.
 Brashers, a health communications researcher, defines informational support
-slightly differently, focusing on the exchange of information that "facilitates
+slightly differently, focusing on the exchange of information that ``facilitates
 coping with life stresses... that may be exchanged among members of a support
-network" \citeyearpar[p. 260]{brashersInformationSeekingAvoiding2002}. Both
+network'' \citeyearpar[p. 260]{brashersInformationSeekingAvoiding2002}. Both
 definitions provide important lenses for my question of how computer-mediated or
@@
 There has been some research into how different platforms allow for different
-user experiences or "affordances" \citep{boyd2010social}. For example,
+user experiences or ``affordances'' \citep{boyd2010social}. For example,
 \citet{bossetta18} first show that all social media platforms must provide
-"tools that are easy to use and functional to the demands of varying user
-demographics" (p. 473). They also explain how each digital architecture enables,
+``tools that are easy to use and functional to the demands of varying user
+demographics'' (p. 473). They also explain how each digital architecture enables,
 constrains and shapes how users behave on their platform and in virtual space,
@@
 focus of sociology since the beginning. In a 2020 Annual Review of Sociology
-piece focused on social norms, Horne and Mollborn define norms as "group-level
+piece focused on social norms, Horne and Mollborn define norms as ``group-level
 evaluations of behavior ... [or] when people have expectations about how others
-evaluate behaviors" \citeyearpar[p. 468-69]{horneNormsIntegratedFramework2020}.
+evaluate behaviors'' \citeyearpar[p. 468-69]{horneNormsIntegratedFramework2020}.
 One of the principal architects of sociology, \'{E}mile Durkheim, saw that
@@
 
-Norms are formed inside of social networks; "Networks operate in a larger
+Norms are formed inside of social networks; ``Networks operate in a larger
 cultural context that can facilitate or inhibit acceptance of general cultural
-norms and beliefs" \citep[][p. 44]{pescosolidoDurkheimSuicideReligion1989}.
+norms and beliefs'' \citep[][p. 44]{pescosolidoDurkheimSuicideReligion1989}.
 Because of this, people tend to resemble their network as a form of network
 autocorrelation and homophily \citep{dellapostaWhyLiberalsDrink2015}. While
-"birds of a feather flock together" in homophily
+``birds of a feather flock together'' in homophily
 \citep{mcphersonBirdsFeatherHomophily2001}, attitudes and behaviors are shaped
@@
 perceptions about which beliefs or behaviors are compatible with one another,
-what they call "associative diffusion". This relates back to the theory of
+what they call ``associative diffusion''. This relates back to the theory of
 relational norms, where individuals assume what their peers will approve and
@@
 cases, namely attitudes, disease prevalence and political preferences using five
-different validated data sources. This paper asks, "How can we operationalize
-Google Search Trends as a valid indicator for uses in social science research?"
+different validated data sources. This paper asks, ``How can we operationalize
+Google Search Trends as a valid indicator for uses in social science research?''
 I use Pearson and Repeated Measures Correlations between the Google Trends and
@@
 models of behavioral adaption to public health recommendations and patterns of
-complex contagion (the need for repeated exposures to a something novel for it
+complex contagion (the need for repeated exposures to something novel for it
 to diffuse) using linear mixed effects models.
@@
 ego. If there is diversity in the information received by an ego, contagion is
-less likely to occur. This paper shows that the contagion process cannot be not
+less likely to occur. This paper shows that the contagion process cannot be
 fully understood without looking at the context of each exposure to a contagion
@@
 studies, this dissertation contributes to the question posed by
-\citet{breigerScaling2015}, "what are the behavioral processes that lead to
-macro-level outcomes?" With the exponentially growing size of digital-trace data
+\citet{breigerScaling2015}, ``what are the behavioral processes that lead to
+macro-level outcomes?'' With the exponentially growing size of digital-trace data
 that is available, it is important to not only uncover the external and
@@
 norms and transmission of norms between groups, deviance and social control, the
-interaction of norms as "mental representations of appropriate behavior"
+interaction of norms as ``mental representations of appropriate behavior''
 \citep{aarts2003silence}, and research categorizing different types of norms
-(e.g., descriptive versus injunctive, prescriptive versus proscriptive). The
+(e.g.\, descriptive versus injunctive, prescriptive versus proscriptive). The
 focus on the formation of new social norms during times of uncertainty has

### 2022-04-14 paper1.tex
copyedits, add desc stat table

@@
 \citep{bailCulturalEnvironmentMeasuring2014, lazerParableGoogleFlu2014}. As
-prior research outlined, the "quantity of data does not mean that one can ignore
+prior research outlined, the ``quantity of data does not mean that one can ignore
 foundational issues of measurement and construct validity and reliability and
-dependencies among data" \citep[p. 1203]{lazerParableGoogleFlu2014}.
+dependencies among data'' \citep[p. 1203]{lazerParableGoogleFlu2014}.
 
@@
 Building on prior research outlining the various issues with different sources
-of big data
-\citep{boydCriticalQuestionsBig2012,lazerIssuesConstructValidity2015}, this
+of big data \citep{boydCriticalQuestionsBig2012,lazerIssuesConstructValidity2015}, this
 paper evaluates the construct validity of Google Search Trends as an indicator
@@
 preferences. These three cases will be tested using attitudinal indicators from
-the %NORC General Social Survey, CDC \citeyearpar{vaches_data} and New York
-Times \citeyearpar{mask_data}, health indicators from the CDC
+the CDC \citeyearpar{vaches_data} and New York Times \citeyearpar{mask_data}, 
+health indicators from the CDC
 \citeyearpar{suic_data}, US cases rates of COVID-19 from The New York Times
 \citeyearpar{covid_data}, and political indicators from the historical US
-Presidential Election results \citeyearpar{pres_data}. % , and the American
-National Election Survey \citeyearpar{anes_data}. This paper will contribute
+Presidential Election results \citeyearpar{pres_data}. 
+% , and the American National Election Survey \citeyearpar{anes_data}.
+This paper will contribute
 guidance for creating standards of how to use Google Trends for social research,
@@
 \citet{bailCulturalEnvironmentMeasuring2014}'s call for cultural sociologists to
-utilize the ever-expanding world of big data, Google trends began slowly
+utilize the ever-expanding world of big data, Google Trends began slowly
 appearing as a data source in sociological and social science research. From
@@
 \citet{jaidkaInformationseekingVsSharing2021}, the majority of studies profess a
-correlation of \> .70 between the IV and DV, "demonstrating the vast potential
-of Google Search as a proxy for monitoring population health" (p. 3) based on
+correlation of \> .70 between the IV and DV, ``demonstrating the vast potential
+of Google Search as a proxy for monitoring population health'' (p. 3) based on
 assumptions that individuals search because of self-diagnosis and to identify
@@
 political attitudes \citep{wolfTrendingRightDirection2018}. For instance,
-\citet{swearingenGoogleInsightsSenate2014} investigate how U.S. Senate Elections
+\citet{swearingenGoogleInsightsSenate2014} investigate how U.S. Senate elections
 relate to attention measured by search traffic.
@@
 case rates and Google searches that the correlation is often spurious and due to
-confounding. They even explain that "searches would result not only from
-self-symptoms, but also from interest elicited by media coverage"
+confounding. They even explain that ``searches would result not only from
+self-symptoms, but also from interest elicited by media coverage''
 \citep[][p.1]{asseoTrackingCOVID19Using2020}.
@@
 within the purview of accuracy, completeness, consistency, and validity, as
-outlined in \citet{KarrDataQuality}. % I know it is basic stats, but I would
-provide a footnote explaining each of your terms. Here, these line up with
-mainline stats but disciplines vary. \citet{cebrian_domenech22} point not only
+outlined in \citet{KarrDataQuality}. 
+% I know it is basic stats, but I would provide a footnote explaining each of your terms. 
+% Here, these line up with mainline stats but disciplines vary.
+\citet{cebrian_domenech22} point not only
 to meta issues like the lack of transparency into the sampling methods and
@@
 as digital trace data do so to indicate population's \textit{attention} to a
-search query. Because % I’d also say, the population is examined differently. It
-is really a population of action remnants being used to get at a population of
-people, which is presumed to be represented online. searches can be done with
+search query. Because searches can be done with
+% I’d also say, the population is examined differently. It is really a population of action remnants being used to get at a population of people, which is presumed to be represented online. 
 many different intentions, such as information gathering, navigational purposes,
@@
 various tests to validate the criterion validity of the trends. Criterion
-validity measures how well one measure, an operationalization of a specific
-construct, is able to predict a theoretical representation of the construct —
+validity measures how well an \textit{operationalization} of a specific
+construct is able to predict a \textit{theoretical representation} of the construct —
 the criterion. For this article, I employ concurrent criterion validity which
@@
 \ref{tab:data-sources-table} outlines which data sources I use in this project
-and which trends are matched to each source.
+and which trends are matched to each source. In addition, descriptive statistics
+for all variables used in these analyses are included in Table \ref{tab:a1_desc_stats}.
 
 \input{tables/paper1/data-sources-table}
+\input{tables/paper1/desc_stats}
 
@@
 areas (DMAs), a nonoverlapping aggregation of U.S. counties to 210 media markets
-based on Nielsen's classification o "similar population clusters"
+based on Nielsen's classification of ``similar population clusters''
 \citep{dma_key}. Raw data is on a scale from zero to one hundred, with one
@@
 consists of 3,148 observations, one for each U.S. County. The variable measures
-the percent of adults in the county who describe themselves as “unsure”,
-“probably not”, or “definitely not” going to get a COVID-19 vaccine once one is
+the percent of adults in the county who describe themselves as ``unsure'',
+``probably not'', or ``definitely not'' going to get a COVID-19 vaccine once one is
 available to them. The variable ranges from 4.99\% to 32.33\%.
@@
 Dynata, a global online market research firm, for the New York Times from July 2
-through 14, 2020 \citep{mask_data}. 250,000 survey respondents were asked, "How
+through 14, 2020 \citep{mask_data}. 250,000 survey respondents were asked, ``How
 often do you wear a mask in public when you expect to be within six feet of
-another person?". The NYT weighted each response to create a county level
+another person?''. The NYT weighted each response to create a county level
 measure of what percent of the county never, rarely, sometimes, frequently, and
@@
 acknowledged that there are biases in this data due to inconsistencies and
-availability in testing as well as different community propensity to test %
-Also blatant political interference in some places, which is probably worth
-acknowledging. \citep{gu22, cdc20a} However, it is the best measure we have of
+availability in testing as well as different community propensity to test \citep{gu22, cdc20a}.
+However, it is the best measure we have of
 actual case rates without extensive adjustments. Case Rate is measured as number
@@
 In addition to specific measures of interest, I also gathered data on
-potentially confounding variables. The first Seven of these variables come from
+potentially confounding variables. The first seven of these variables come from
 the 2010-2019 5-year American Community Surveys \citep{acs2019, acs2018,
@@
 linear regression is appropriate because the cross-sectional data are non-nested
-which a continuous outcome. Hierarchical linear models are necessary to control
+with a continuous outcome. Hierarchical linear models are necessary to control
 for the between-subject variation in the longitudinal models. Fixed models are
@@
 and median income to adjust for potentially confounded relationships between
-Google search Trends and credible indicators. Identifying these possible
+Google search Trends and credible indicators. 'County level fips mean' is included
+in each model to control for within-group variation of the outcome, a standard practice
+in mixed effects modeling. Identifying these possible
 confounded relationships may help to explain why some articles find
@@
 \ref{tab:vacc_hes_analysis} through \ref{tab:pres_2020_analysis}. 
+In addition to coefficients, each table include the marginal $R^2$ and sometimes 
+a conditional $R^2$, the first describes the proportion of variance explained by the fixed factor alone and the latter the fixed and random factors.
 
@@
 
+% # TODO All variables have been standardized, right?
+So when you say an effect is ``small,'' could you give an illustration?
+E.g., translate it back into metric coefficients?
+For example, ''for every 100 additional calls to a suicide hotline, the suicide rate increases by x per 1,000 residents, according to the model,'' or something like that?
+The main thing is to have an intuitive description of what the effect size is, not just to look at a standardized coefficient of .002.
+
 \input{tables/paper1/suicide_analysis}
@@
 and U.S. Presidential Election results in 2016 and 2020. In 2016, Pearson
-correlations for Both Hilary Clinton and Donald Trump do not exceed a |0.17|
-correlation with the actual percentage of votes for either candidate. In 2020,
+correlations of search trends with actual percentage of votes for Both Hilary
+Clinton and Donald Trump do not exceed a |0.17| correlation for either candidate. In 2020,
 results are even less related, with searches for neither Joe Biden nor Donald
@@
 
+% The sign in Model 1 is interesting.
+The more likely a voter is to vote against Clinton, the more they search for her?
+(Obsessive?) Is that right?
+Also, I may be not seeing this correctly, but again I think I'd be interested in an interpretation in the original metrics of variables: ''According to Model 1, for every 1,000 searches for Clinton, she received X% less of the total actual vote,'' or something like that.
 In Table \ref{tab:pres_2016_analysis}, I outline the results for the model
@@
 precaution is warranted.
+
+%  TODO What might be some limitations of your analysis? Are there some issues raised here that should be further explored in subsequent research?

### 2022-04-14 paper2.tex
copyedits, add desc stat table

@@
-\hypertarget{paper-2}{%
-\chapter{information seeking Behaviors for Information on COVID-19 Vaccinations}\label{paper-2}}
+\hypertarget{paper-2}{\chapter{Information seeking Behaviors for Information on COVID-19 Vaccinations}\label{paper-2}}
 
-\hypertarget{abstract}{%
-\section{Abstract}\label{abstract}}
+\hypertarget{abstract}{\section{Abstract}\label{abstract}}
 
@@
 
-\hypertarget{intro-1}{%
-\section{Introduction}\label{intro-1}}
+\hypertarget{intro-1}{\section{Introduction}\label{intro-1}}
 
@@
 focuses on the 'push' or 'supply' side of information, like spaces where
-individuals first encounter with conspiracy theories or other information
+individuals first encounter conspiracy theories or other information
 \citep{johnsonOnlineCompetitionPro2020, broniatowski_etal20}.
@@
 \citep{mertonManifestLatentFunctions1968, katzPersonalInfluencePart1955,
-lazarsfeldPeopleChoice1944}, rather than on “the receiver as an active
-information seeker and processor."
-\citep{johnsonComprehensiveModelCancerRelated1993} \citep[for an exception,
-see]{eysenbach09}.
+lazarsfeldPeopleChoice1944}, rather than on ``the receiver as an active
+information seeker and processor''
+\citep[][p. 344]{johnsonComprehensiveModelCancerRelated1993} \citep[for an exception,
+see][]{eysenbach09}.
 
@@
 answer how computer-mediated or interpersonal information seeking strategies
-vary across populations in their search for information about COVID-19
-vaccinations and investigate how these strategies affect vaccination uptake.
+vary across populations as people search for information about COVID-19
+vaccinations, and I investigate how these strategies affect vaccination uptake.
 Specifically, this article answers two research questions: (1) How do
@@
 of the current state of social science literature in regards to information
-seeking strategies and providing a description of the research methodology and
+seeking strategies and provide a description of the research methodology and
 analytic sample. I then discuss the implications of these findings for the
@@
 \citep{houseMeasuresConceptsSocial1985, thoitsMechanismsLinkingSocial2011}.
-Informational support is the process of seeking “help in defining,
+Informational support is the process of seeking ``help in defining,
 understanding, and coping with problematic events and include education, advice,
-or referral to another source of support” \citep[][p. 640]{winemiller_etal93}.
+or referral to another source of support'' \citep[][p. 640]{winemiller_etal93}.
 Brashers, a health communications researcher, defines informational support
-slightly differently, focusing on the exchange of information that “facilitates
+slightly differently, focusing on the exchange of information that ``facilitates
 coping with life stresses… that may be exchanged among members of a support
-network” \citet[][p. 260]{brashersInformationSeekingAvoiding2002}.These
+network'' \citet[][p. 260]{brashersInformationSeekingAvoiding2002}. These
 definitions help to differentiate between seeking information through social
@@
 activation \citep{hurlbertCoreNetworksTie2000, perrySocialNetworkActivation2015,
-smithDonPutMy2005}. For instance, Small \citet{smallSomeoneTalk2017} shows that
+smithDonPutMy2005}. For instance, \citet{smallSomeoneTalk2017} shows that
 the core discussion network does not capture how people activate social support
 in practice and indicates that people draw on much broader social connections
-for support, reminiscent of the weak ties research by Granovetter
-\citet{granovetterStrengthWeakTies1973}. There is ongoing research investigating
+for support, reminiscent of the weak ties research by \citet{granovetterStrengthWeakTies1973}.
+There is ongoing research investigating
 how weak-tie support holds for different support types based on the architecture
@@
 context, namely via computer-mediated information search tools such as the
-process of “Googling”, or the utilization of internet search engines. As the
+process of ``Googling'', or the utilization of internet search engines. As the
 online environment began penetrating all facets of modern human life, it makes
 sense that performing online search has become one of the most convenient
-modalities for information search. Small \citet{smallSomeoneTalk2017} showed
-that Graduate students often confided in a "miscellaneous classmates encountered
-down the hall" (p. 176) instead of established and trusted confidants because
-they simply were there at the right time. I theorize that online search engines
+modalities for information search. \citet{smallSomeoneTalk2017} showed
+that graduate students often confided in ``miscellaneous classmates encountered
+down the hall'' (p. 176) instead of established and trusted confidants because
+they simply were there at the right time.
+% Ron: Is it that simple? I think you have a lot in common with ``misc classmates down the hall'' in comparison with, let's say, a random sample of same-aged Tucsonans.
+I theorize that online search engines
 may be the most frictionless and costless mode of support. No social capital or
@@
 with Lazarsfeld and Katz’s theory of two-step flow
-\cite{katzPersonalInfluencePart1955} because people can choose their media and
+\citep{katzPersonalInfluencePart1955} because people can choose their media and
 the opinion leaders they follow. Modern-day theorists have extended UGT theory
@@
 Seeking information from experts, search engines, and other people
-will be the most common modes of information search. 
+will be the most common modes of information search in comparison
+to online forums and social networking sites. 
 \end{hyp}
@@
 detected usage of a VPN, random answer clicking (determined by illogical
-responses), poor quality typed responses (e.g., social network alters
+responses), poor quality typed responses (e.g.\, social network alters
 consistently named random nouns), or taking the survey more than once. The
@@
 survey is a replication of they survey conducted by
-\citet{smallSomeoneTalk2017}. In this section, we expand Small's research on
+\citet{smallSomeoneTalk2017}. In this section, I expand Small's research on
 support activation by segregating weak-tie social support into instrumental,
@@
 
-\input{tables/paper2/table-1-ind}
+\input{tables/paper2/table-1-dep}
 
-\hypertarget{measures}{%
-\subsection{Measures}\label{measures}}
+\hypertarget{measures}{\subsection{Measures}\label{measures}}
 
-\hypertarget{sought-information}{%
-\subsubsection{Sought Information}\label{sought-information}}
+\hypertarget{sought-information}{\subsubsection{Sought Information}\label{sought-information}}
 
@@
 specific categories of search were inspired by ICPSR project 37220
-\citep{scanlon19}.
+\citep{scanlon19}. While each survey is not a direct comparison to the other, \citet{scanlon19}'s 
+research focused on patient activation and health care utilization 
+and therefore provided relevant, already validated survey questions for this survey.
 
@@
 
-\input{tables/paper2/table-2-dep}
-
-Another Dependent variable for this analysis is a dichotomous variable
+Another dependent variable for this analysis is a dichotomous variable
 indicating whether the respondent has received or plans to receive a vaccination
@@
 bias in our sample that must be acknowledged: either MTurkers are more likely to
-be vaccinated that the normal population (sampling bias) or there is some
+be vaccinated than the normal population (sampling bias) or there is some
 conformity bias in the responses causing survey takers to provide false answers.
 The second survey item that contributes to `Vaccination Outlook' was only given
-to those who had not responded `yes' to the to their vaccination status. These
+to those who had not responded `yes' to their vaccination status. These
 respondents were asked `Do you plan to receive a vaccine for the prevention of
@@
 
-\hypertarget{independent-variables}{%
-\subsubsection{Independent Variables}\label{independent-variables}}
+\input{tables/paper2/table-2-ind}
+
+\hypertarget{independent-variables}{\subsubsection{Independent Variables}\label{independent-variables}}
 
@@
 question above because this is based on passive reception of information. The
-largest proportion of respondents had received information from "a person like
-friend, neighbor, or family member that [they] know" (\(\widehat{p}\) = 67\%).
+largest proportion of respondents had received information from ``a person like
+friend, neighbor, or family member that [they] know'' (\(\widehat{p}\) = 67\%).
 Respondents also commonly received information from a television news channel or
@@
 
-\hypertarget{analysis}{%
-\section{Analysis}\label{analysis}}
+\hypertarget{analysis}{\section{Analysis}\label{analysis}}
 
@@
 non-nested, cross-sectional data with binary independent variables. In Table
-\ref{tab:table-model-1} \footnote{All Tables in this paper were created with the
-modelsummary package in \texttt{r} \citep{modelsummary}},I fit a logistic
+\ref{tab:table-model-1}\footnote{All Tables in this paper were created with the
+modelsummary package in \texttt{r} \citep{modelsummary}}, I fit a logistic
 regression model predicting whether someone sought information about COVID-19
@@
 
-\hypertarget{results}{%
-\section{Results}\label{results}}
+\hypertarget{results}{\section{Results}\label{results}}
 
-\hypertarget{information seeking}{%
-\subsection{Information Seeking}\label{information seeking}}
+\hypertarget{information seeking}{\subsection{Information Seeking}\label{information seeking}}
 
@@
 
-\hypertarget{information-search-modalities}{%
-\subsection{Information Search Modalities}\label{information-search-modalities}}
+\hypertarget{information-search-modalities}{\subsection{Information Search Modalities}\label{information-search-modalities}}
 
@@
 
-To investigate how each Information Search modality are related to each other
+To investigate how each information search modality is related to each other
 using the Phi Coefficient ($\phi$) of binary association between each
@@
 I find that indeed the most common modalities are asking a doctor, asking a
-friend, and asking a search engine which confirms Hypothesis
+friend, and asking a search engine which provides evidence to reject the null
+hypothesis for Hypothesis
 \ref{hyp:drgooglefriend}. However, because the modalities 95\% confidence
-intervals in Table \ref{tab:table-1-ind} are overlapping, I fail to find
-evidence for Hypothesis \ref{hyp:online-vs-network}, that using an online search
+intervals in Table \ref{tab:table-1-ind} are overlapping, I fail to reject 
+the null Hypothesis \ref{hyp:online-vs-network}, that using an online search
 engine was more commonplace than asking a friend.
@@
 seeking information from those same people; in fact, I find that those who did
-are 3.32 more likely to do so (\emph{p} \textless{} 0.001). Finally, the
+are 3.32 more likely to do so (\emph{p} \textless{} 0.001, see Table
+\ref{tab:table-model-2}, ``Person'' model). Finally, the
 respondents who received information about the vaccine on a social networking
@@
 model is that very few factors predict personal social network activation, and
-this model has the lowest McFadden's R\^{}2, indicating possible omitted
+this model has the lowest McFadden's R\^{2}, indicating possible omitted
 variables.
@@
 
-\hypertarget{vaccination-views}{%
-\subsection{Choosing to be Vaccinated}\label{vaccination-views}}
+\hypertarget{vaccination-views}{\subsection{Choosing to be Vaccinated}\label{vaccination-views}}
 
@@
 0.09). See Figure \ref{fig:plot-model-3} for a visual representation of how
-these different coefficients are related to vaccination outlook.
+these different coefficients are related to vaccination outlook. 'Gender, Other'
+is likely an outlier with an inflated effect here due to only 6 participants
+being coded as 'Other' for their gender.
 
@@
 
-\hypertarget{discussion}{%
-\section{Discussion and Conclusion}\label{discussion}}
+\hypertarget{discussion}{\section{Discussion and Conclusion}\label{discussion}}
 
@@
 \citep{center2019, murray15, bronson2014don}.
+% TODO This is interesting speculation. Is there some way (in future studies) to further investigate this?
 
@@
 key variations. First, if one received information from a doctor, they were
-likely to search from information from a doctor; this may indicate an already
+likely to search for information from a doctor; this may indicate an already
 existing trusting relationship between patient and healthcare provider but it
@@
 attitudes around the trustworthiness of different sources of information affect
-the utilization of different methods; for example, Asians seem are less likely
+the utilization of different methods; for example, Asians seem to be less likely
 to use online forums than non-Asians, while Hispanics are more likely to use
@@
 vaccinations. While blanket advice like ``Healthcare Providers should recommend
-the vaccine to their patients'' would be ineffective because of the declining
+the vaccine to their patients'' would be less than totally effective because of the declining
 number of Americans with a primary care doctor \citep{levine_etal20}, increasing

### 2022-04-14 paper3.tex
copyedits, add desc stat table

@@
-\hypertarget{paper-3}{%
-\chapter{Social Norms under Uncertain Times: A dynamic study of Stay-At-Home and Vaccination Rates During the COVID-19 Pandemic}\label{paper-3}}
+\hypertarget{paper-3}{\chapter{Social Norms under Uncertain Times: A dynamic study of Stay-At-Home and Vaccination Rates During the COVID-19 Pandemic}\label{paper-3}}
 
-\hypertarget{abstract-1}{%
-\section{Abstract}\label{abstract-1}}
+\hypertarget{abstract-1}{\section{Abstract}\label{abstract-1}}
 
@@
 models of behavioral adaption to public health recommendations and patterns of
-complex contagion (the need for repeated exposures to a something novel for it
+complex contagion (the need for repeated exposures to something novel for it
 to diffuse) using linear mixed effects models. These models show that complex
@@
 the information received by an ego, contagion is less likely to occur. This
-paper shows that the contagion process cannot be not fully understood without
+paper shows that the contagion process cannot be fully understood without
 looking at the context of each exposure to a contagion within the range of
@@
 religious and political conservatism, attention to television media sources, and
-online norms as measured by information-search behaviors. Before outlining my
+online norms as measured by information-search behaviors.
+
+Before outlining my
 central hypotheses, I offer an overview of the current state of the social
@@
 
-Individuals engage with each other and their distributive ties to create
+Individuals engage with each other and their distributed ties to create
 community contexts where norms, beliefs, and values circulate. These clusters of
@@
 behavior is tied to network autocorrelation, or ``the tendency for people to
-resemble their network neighbors.'' They show that the distance between to
+resemble their network neighbors.'' They show that the distance between two
 agents in sociocultural space can determine the likelihood of the adoption of a
@@
 
-\citep{centolaComplexContagionsWeakness2007} theorize that simple contagions are
+\citet{centolaComplexContagionsWeakness2007} theorize that simple contagions are
 not enough to spread behavioral change. Simple contagions are those in which
@@
 \end{hyp2}
+% TODO I think I ``get'' this, but could you define ``ego county''?
+Also, why not just look at the effect of alter's behavior on ego's behavior (why does the county come into the framework)?
+Do you mean {the subset of ego's alters who live in the same county as ego}?
 
@@
 For this paper, I theorize that a new concept of `discordance' must be
-considered as impacting complex contagion. discordance is the variance of
+considered as impacting complex contagion. Discordance is the variance of
 signals received by an alter; high discordance prevents reinforcement while low
@@
 ego, the less likely the alters will have any effect on the ego. I theorize that
-the behavior of a county-alter will be positively correlated with the behavior
+the behavior of a county-alter will be correlated with the behavior
 of another county-ego if the county-ego receives highly discordant signals, as
@@
 
-\hypertarget{associative-diffusion}{%
-\subsection{Associative Diffusion}\label{associative-diffusion}}
+\hypertarget{associative-diffusion}{\subsection{Associative Diffusion}\label{associative-diffusion}}
 
@@
 \input{tables/paper3/google-desc-table}
+%TODO define normalization, make sure its mentioned in the methods section
 
@@
 calculates the relative change in mobility in comparison to the median value of
-movement in the area for the same the corresponding day of the week, during the
+movement in the area for the same corresponding day of the week, during the
 5-week period Jan 3--Feb 6, 2020. As Google did not provide data on certain US
@@
 
-\hypertarget{covid-vaccination-uptake}{%
-\subsection{COVID vaccination uptake}\label{covid-vaccination-uptake}}
+\hypertarget{covid-vaccination-uptake}{\subsection{COVID vaccination uptake}\label{covid-vaccination-uptake}}
 
@@
 \end{figure}
+% TODO add which counties rose to 100% vaccination
 
@@
 
-\hypertarget{independent-variables-1}{%
-\subsection{Independent Variables}\label{independent-variables-1}}
+\hypertarget{independent-variables-1}{\subsection{Independent Variables}\label{independent-variables-1}}
 
-\hypertarget{network-signal}{%
-\subsubsection{Network Signal}\label{network-signal}}
+\hypertarget{network-signal}{\subsubsection{Network Signal}\label{network-signal}}
 
@@
 
-\hypertarget{signal-discordance}{%
-\subsubsection{Signal Discordance}\label{signal-discordance}}
+\hypertarget{signal-discordance}{\subsubsection{Signal Discordance}\label{signal-discordance}}
 
@@
 the weights and signals are calculated for an ego with only 5 alters.
+% TODO Navajo County, AZ, is probably a good one to talk about.
+Suppose it's composed of Native and non-Native communities, which are not in much communication with each other.
+Each (Native and non-Native) might have connections to different sets of alter counties.
+In brief: There could be a lot of homogeneity among non-Natives and a lot of homogeneity among Natives, but both might be masked by taking county as the unit.
+Thoughts?
+the assumption of homogeneity within county  (my comment on p.
+120) should be stated clearly.
 
@@
     x = \begin{bmatrix}29.9\\20.4\\27.7\\24.6\\24.3\end{bmatrix} \longrightarrow
-    \begin{matrix} \bar{x}*, signal = 25.083\\ s*, discordance = 1.41 \end{matrix} 
+    \begin{matrix} \bar{x}*, signal = 25.083\\ s*, discordance = 1.423 \end{matrix} 
   \end{equation}
@@
 
-\hypertarget{COVID-19-case-rates}{%
-\subsubsection{COVID-19 Case Rates}\label{COVID-19-case-rates}}
+\hypertarget{COVID-19-case-rates}{\subsubsection{COVID-19 Case Rates}\label{COVID-19-case-rates}}
 
@@
 
-\hypertarget{pillars-of-convervatism}{%
-\subsubsection{Pillars of Convervatism}\label{pillars-of-convervatism}}
+\hypertarget{pillars-of-convervatism}{\subsubsection{Pillars of Convervatism}\label{pillars-of-convervatism}}
 
@@
 across individual designated media markets areas (DMAs). I use this measure to
-indicate active interest in and attention toward Fox News. Google Search Trends
+indicate active interest in and attention toward Fox News. While Google Search Trends
 have been validated for use in a range of research contexts and for use with
@@
 scheitleGoogleInsightsSearch2011, stephensdavidowitzCostRacialAnimus2014,
-swearingenGoogleInsightsSenate2014}.
+swearingenGoogleInsightsSenate2014}, I provide a caution for these uses in 
+\hyperlink{paper-1}{Appendix A} and suggest these measures should only be used to measure attention.
 
-\hypertarget{demographics}{%
-\subsubsection{Demographics}\label{demographics}}
+\hypertarget{demographics}{\subsubsection{Demographics}\label{demographics}}
 
@@
 
-\hypertarget{analysis-and-results}{%
-\section{Analysis and Results}\label{analysis-and-results}}
+\hypertarget{analysis-and-results}{\section{Analysis and Results}\label{analysis-and-results}}
 
@@
 \ref{hyp:infection} through \ref{hyp:discordance} respectively. Each model
-utilizes normalized independent variables, i.e. variables that have been
+utilizes normalized independent variables, i.e.\ variables that have been
 centered and scaled to have a mean of 0 and standard deviation 1. The first
@@
 (\texttt{correlation\ =\ corAR1()}) to control for temporally autocorrelated
-error structures; models are also optimized using Nelder--Mead, quasi-Newton and
-conjugate-gradient algorithms for box-constrained optimization and simulated
-annealing (\texttt{control\ =\ lmeControl(opt\ =\ "optim")}). This first model
+error structures; models are also optimized using Nelder--Mead, quasi--Newton and
+conjugate--gradient algorithms for box-constrained optimization and simulated
+annealing (\texttt{control\ =\ lmeControl(opt\ =\ ``optim'')}). This first model
 will address Hypothesis \ref{hyp:infection}. To test Hypothesis
@@
 
-\hypertarget{stay-at-home-rate-results}{%
+\hypertarget{stay-at-home-rate-results}{
 \subsection{Stay-at-Home Rate results}\label{stay-at-home-rate-results}}
@@
 receiving a wide array of low and high signals, their stay-at-home rates won't
-be affected by social contagion. When a signal is concentrated or in agreement,
+be affected on average by social contagion. When a signal is concentrated or in agreement,
 the theoretical effect of movement signaling on the ego are the strongest. With
@@
 
-\hypertarget{vaccination-rate-results}{%
-\subsection{Vaccination Rate results}\label{vaccination-rate-results}}
+\hypertarget{vaccination-rate-results}{\subsection{Vaccination Rate results}\label{vaccination-rate-results}}
 
@@
 Google searches for information about the vaccine are likely to have lower rates
-of vaccination. The test of Hypothesis \ref{hyp:infection} also returns
+of vaccination. 
+% TODO On the Fox News result--Interesting.
+In hindsight, this too may have to do with inhomogeneities within counties, e.g., maybe it's the conservatives in liberal counties that tune in avidly to Fox News.
+The test of Hypothesis \ref{hyp:infection} also returns
 surprising results: every 1 standard deviation increase in county COVID-19 case
@@
 inconclusive.
+% TODO Those who perform Google searches for vaccine info are likely to have lower vaccination rates --> Maybe they are searching for info about why the vaccine is bad !!
+
+% TODO An increase in covid cases yields a decrease in vaccination rates. -- Well, the association would be like this if low vaccination rates lead to more covid cases.
 
@@
 
-\hypertarget{discussion-and-conclusion}{%
-\section{Discussion and Conclusion}\label{discussion-and-conclusion}}
+\hypertarget{discussion-and-conclusion}{\section{Discussion and Conclusion}\label{discussion-and-conclusion}}
 
@@
 distribution of behaviors that lead to the aggregate measures.
+% TODO As perhaps illustrated hypothetically in my comment on p. 120
 
-Regardless of limitations, this article is a unique and compelling contribution
+Despite limitations, this article is a unique and compelling contribution
 to the academic study of social contagion and social norms. First, this article

### 2022-04-15 paper1.tex
Most post-defense edits

@@
 Rwanda, a country where national surveys and censuses are rare and costly.
-However, \citet{blumenstockPredictingPovertyWealth2015} go to great lengths to
-demonstrate that their use of the cell phone data creates a reliable and valid
-construct; few social science papers utilizing big data dig into the construct
-validity of their metrics to this extent and even fewer publications focus on
+In this paper,  \citet{blumenstockPredictingPovertyWealth2015} put in an effort to 
+investigate the criterion validity of their measure; that is, they investigate 
+how well an \textit{operationalization} of a specific construct is able to 
+predict a \textit{theoretical representation} of the construct — the criterion. 
+Investigating the criterion validity in their paper demonstrate that their use
+of the cell phone data creates a reliable and valid construct. 
+Few other social science papers utilizing big data dig into the criterion
+validity of their metrics to this extent;even fewer publications focus on
 methodological guidelines of how to use sources of big data \citep[For
@@
 of big data \citep{boydCriticalQuestionsBig2012,lazerIssuesConstructValidity2015}, this
-paper evaluates the construct validity of Google Search Trends as an indicator
+paper evaluates the criterion validity of Google Search Trends as an indicator
 of three different cases, namely attitudes, disease prevalence and political
@@
 and identify potential pitfalls that can compromise the analysis including the
-focus of this paper, which shows that Google Trends has a lack of ecological
-validity.
+focus of this paper, which shows that Google Trends has a lack of criterion validity
+for multiple ways which researchers may want to use it.
 
@@
 this procedure, see \citet[p. 5]{park_etal}}. I interpolate missing data points
-in the longitudinal datasets using The Zoo package for R \citep{zoo}.
+in the longitudinal datasets using The Zoo package for R \citep{zoo} which estimates
+the values of missing data points based on the immediately preceding and succeeding
+time points for each separate time-series group. This differs from multiple imputation, 
+which would take other features into account when estimating the missing data point.
 

### 2022-04-15 paper2.tex
Most post-defense edits

@@
 
+Adapting these facets of UGT and social support to my own case, I theorize that
+online search allows for increased anonymity, a lowered social cost, and the
+potential avoidance of embarrassment and other negative social interactions,
+especially in the case on search engines.
+
 \begin{hyp}[H\ref{hyp:online-vs-network}] \label{hyp:online-vs-network}
@@
 
-Adapting these facets of UGT and social support to my own case, I theorize that
-online search allows for increased anonymity, a lowered social cost, and the
-potential avoidance of embarrassment and other negative social interactions,
-especially in the case on search engines.
-\citet{rainsCopingIllnessDigitally2018} finds that patients tend to search for
-technical information about an illness online but they then turn to their social
+\citet{rainsCopingIllnessDigitally2018} finds that while patients tend to search for
+technical information about an illness online, they then turn to their social
 network for experiential information from others facing similar circumstances in
@@
 specific expertise on a specific topic is desired by a searcher, they may reach
-out to personal connections that they see as expert such as a doctor, or if an
+out to personal connections that they see as expert such as a doctor. Or, if an
 individual distrusts the medical establishment, they may be more likely to
@@
 \citeyearpar{brashersInformationSeekingAvoiding2002} help us to theorize that
-the psychosocial needs like identity management or relational maintenance of an
-individual may influence the chosen information search modality: when the
+psychosocial needs like identity management or relational maintenance of each
+individual may influence their chosen information search modality: when the
 informational need is related to forming and deepening social ties search is
@@
 this model has the lowest McFadden's R\^{2}, indicating possible omitted
-variables.
+variables. Possible omissions may include personality type, psychosocial
+resources, and personal network composition.
 

### 2022-04-25 ch1.tex
final committee revisions

@@
 I examine the criterion validity of one of these new sources, Google Search
-Trends. I validate how Google Trends can be used to demonstrate three different
+Trends. Criterion validity looks at how well an operationalization of a specific
+construct is able to predict a theoretical representation of the construct — the criterion.
+I validate how Google Trends can be used as an operationalization of three different
 cases, namely attitudes, disease prevalence and political preferences using five
@@
 model interpretability remained low, even when controlling for demographic
-variables. This article shows that there is no external or criterion validity of
+variables. This article shows that there is no criterion validity of
 Google Trends for these uses and social scientists will find no replacement for

### 2022-04-25 paper1.tex
final committee revisions

@@
 \citet{bailPrestigeProximityPrejudice2019} even used Google trends to measure
-how they saw 'culture' spreads around the globe through the proliferation of
+how they saw `culture' spreads around the globe through the proliferation of
 search terms.
@@
 into a cohesive topic done by Google through it's Knowledge Graph product. For
-example, while 'Beyoncé', 'Beyonce' and 'beyonce knowles' are all separate
-search terms, 'Beyoncé Knowles' encompasses all of these into a single search
+example, while `Beyoncé', `Beyonce' and `beyonce knowles' are all separate
+search terms, `Beyoncé Knowles' encompasses all of these into a single search
 topic. Google Search Trends are only available cross-sectionally (a single
@@
 unscaled cross-sectional values, selecting a DMA to use to establish the
-rescaling ratio (I use 'Los Angeles CA'), and then finding the time-series
+rescaling ratio (I use `Los Angeles CA'), and then finding the time-series
 values for the one DMA. To find the rescaling ratio for each week in the
@@
 and median income to adjust for potentially confounded relationships between
-Google search Trends and credible indicators. 'County level fips mean' is included
+Google search Trends and credible indicators. `County level fips mean' is included
 in each model to control for within-group variation of the outcome, a standard practice
@@
 correlations, reveals similarly weak results with a maximum correlation of 0.32
-between 'smell loss' and rates of COVID-19. To further investigate the
+between `smell loss' and rates of COVID-19. To further investigate the
 relationship, I include the three trends in fixed effect hierarchical linear
@@
 E.g., translate it back into metric coefficients?
-For example, ''for every 100 additional calls to a suicide hotline, the suicide rate increases by x per 1,000 residents, according to the model,'' or something like that?
+For example, `'for every 100 additional calls to a suicide hotline, the suicide rate increases by x per 1,000 residents, according to the model,'' or something like that?
 The main thing is to have an intuitive description of what the effect size is, not just to look at a standardized coefficient of .002.
@@
 (Obsessive?) Is that right?
-Also, I may be not seeing this correctly, but again I think I'd be interested in an interpretation in the original metrics of variables: ''According to Model 1, for every 1,000 searches for Clinton, she received X% less of the total actual vote,'' or something like that.
+Also, I may be not seeing this correctly, but again I think I'd be interested in an interpretation in the original metrics of variables: `'According to Model 1, for every 1,000 searches for Clinton, she received X% less of the total actual vote,'' or something like that.
 In Table \ref{tab:pres_2016_analysis}, I outline the results for the model
@@
 are too costly \citep{blumenstockPredictingPovertyWealth2015}. Google Trends, in
-theory, sounds like a promising data source to 'nowcast' attitudinal, health,
+theory, sounds like a promising data source to `nowcast' attitudinal, health,
 and political indicators. Not only would the data be easily and freely

### 2022-04-25 paper2.tex
final committee revisions

@@
 Information is all around us and permeates every facet of human society, from
-the hordes of data gathered during the internet age or passing gossip between
+the hordes of data gathered during the internet age to passing gossip between
 friends. Human communication and human society are based on the circulation of
@@
 
+Information push and pull are inherently tied to arguments of structure and agency.
+That is, to what extent does the structure and institutions of society shape 
+individual human behavior and to what extent do individuals actors control 
+the decisions they make in the environment in which they find themselves. 
+Attempts to reconcile the false dichotomy between structure and agency
+are found among the majority of modern sociological theorists, particularly  
+\citet{coleman1994foundations} and \citet{bourdieu1987distinction}.
+Both renowned sociologists theorize how the external structures
+are internalized by actors and inspire individual agency, which in turn 
+can lead to an evolution of the external structures themselves.  
+This article joins Coleman and Bourdieu in rejecting the false dichotomy
+between structure and agency by investigating the complementary push (structure)  
+and pull (agency) of information diffusion.
+
 Information is especially important given the prominent trends of
@@
 \citep{starbird19, kata10}. While no belief in false information can be thought
-of as harmless \citep{douglas21} some discredited theories such as 'vaccines
+of as harmless \citep{douglas21} some discredited theories such as `vaccines
 cause autism' have major ramifications for both the individual and public
 health. For example, a newfound public resistance to vaccination against Measles
-by so-called 'anti-vaxxers' caused a 17\% increase in rates worldwide in 2019.
+by so-called `anti-vaxxers' caused a 17\% increase in rates worldwide in 2019.
 This increase killed  142,000 people, most of whom were children under the age
@@
 of misinformation and infodemiology \citep{eysenbach02}, much of the research
-focuses on the 'push' or 'supply' side of information, like spaces where
+focuses on the `push' or `supply' side of information, like spaces where
 individuals first encounter conspiracy theories or other information
@@
 of specific needs on an individual basis. UGT is based on Maslow’s
-\citeyear{maslowTheoryHumanMotivation1943} hierarchy of needs and is compatible
-with Lazarsfeld and Katz’s theory of two-step flow
-\citep{katzPersonalInfluencePart1955} because people can choose their media and
-the opinion leaders they follow. Modern-day theorists have extended UGT theory
+\citeyear{maslowTheoryHumanMotivation1943} hierarchy of needs.
+Modern-day theorists have extended UGT theory
 and classified the uses and gratifications of the internet and of social media.
@@
 Seeking information from experts, search engines, and other people
-will be the most common modes of information search in comparison
-to online forums and social networking sites. 
+will each be significantly more utilized modes of information search than seeking via 
+online forums and social networking sites. 
 \end{hyp}
@@
 0.09). See Figure \ref{fig:plot-model-3} for a visual representation of how
-these different coefficients are related to vaccination outlook. 'Gender, Other'
+these different coefficients are related to vaccination outlook. `Gender, Other'
 is likely an outlier with an inflated effect here due to only 6 participants
-being coded as 'Other' for their gender.
+being coded as `Other' for their gender.
 

### 2022-04-27 paper1.tex
final submission to graduate college complete!

@@
 Few other social science papers utilizing big data dig into the criterion
-validity of their metrics to this extent;even fewer publications focus on
+validity of their metrics to this extent; even fewer publications focus on
 methodological guidelines of how to use sources of big data \citep[For
